### 2023-01-18 paper/elsarticle/main.tex
paper template and structure

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Energy}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{Self-tunable approximated explicit MPC: Heat exchanger implementation}
%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author{Lenka Galčíková}
\author{Juraj Oravec}
\author{Petronela Belková}

\affiliation{organization={Slovak University of Technology in Bratislava, Faculty of Chemical and Food Technology, Institute of Information Engineering, Automation, and Mathematics,},%Department and Organization
            addressline={Radlinského 9}, 
            city={Bratislava},
            postcode={81237}, 
%            state={Slovakia},
            country={Slovakia}
}

\begin{abstract}
max 250 words!

\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:intro}

\section{Preliminaries}
\label{}

\section{Methodology}
\label{}

\section{Results and discussion}
\label{}

\section{Conclusion}
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2023-01-18 data/control_performance.m

@@ -1,5 +1,5 @@
 clc, close all, clear 
-load('ref_tracking28.mat')
+load('ref_tracking23.mat')
 %% plots
 figure(11)
 hold on; grid minor; box on

### 2023-01-18 data/ploty.m

@@ -1,4 +1,4 @@
-load('ref_tracking28.mat')
+load('ref_tracking29.mat')
 %% plots
 % close all
 figure(1)

### 2023-01-19 paper/elsarticle/main.tex
paper: results part1

@@
 \usepackage{amssymb}
+\usepackage{multirow}
+\usepackage{lineno}
+\usepackage[colorlinks,citecolor=black,linkcolor=black,urlcolor=black,bookmarks,bookmarksnumbered]{hyperref}
 %% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
+\usepackage{amsthm}
+\usepackage{amsmath}
 
@@
 \section{Introduction}
-\label{sec:intro}
+\label{sec:introduction}
 
 \section{Preliminaries}
-\label{}
+\label{sec:preliminaries}
+
+\subsection{Explicit model predictive control}
+\label{sec:eMPC}
+TODO: remark, ze sme si vedomi aj delta-u formulacie, ale vedie na zlozitejsie eMPC
+
+\subsection{Tunable explicit model predictive control}
+\label{sec:tunable}
+
+\subsection{Self-tunable explicit model predictive control}
+\label{sec:self_tunable}
 
 \section{Methodology}
-\label{}
+\label{sec:methodology}
+
+\subsection{Self-tunable technique for systems with asymmetric behavior}
+\label{sec:self_tunable_new}
+
+TODO: spomenut, ze to je vhodne celkovo aj pre klasicke online MPC
 
 \section{Results and discussion}
-\label{}
+\label{sec:results}
+
+In this section, the results of the proposed tuning method are presented.
+The plant on which the control was implemented is a laboratory liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Fig.~\ref{fig:HE}.
+The cold feed as well as heating medium are transported to the heat exchanger by two peristaltic pumps.
+The flow rate of the feed is constant, while the aim is to track the reference value of its temperature.
+Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger and the manipulated variable is the voltage $U$ corresponding to the power of the heating medium pump.
+The voltage is set in percentage, while it is constrained from 20\% to 100\%.
+As the heat exchange is a nonlinear and non-symmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
+
+The matrices of the linear state-space model of the plant, discretized with sampling time $T_\mathrm{s}$ = 1\,s, are
+
+\begin{subequations}
+	\label{eq:model_A_B} 
+	\begin{eqnarray}
+		A&=&\begin{bmatrix}
+			0.839
+		\end{bmatrix}, \\
+		B&=&\begin{bmatrix}
+			0.039
+		\end{bmatrix}, \\
+		C&=&\begin{bmatrix}
+			1
+		\end{bmatrix}, \\
+		D&=&\begin{bmatrix}
+			0
+		\end{bmatrix}.
+		\end{eqnarray}
+\end{subequations}
+
+The constraints are considered in the terms of manipulated variable, i.e.
+
+\begin{eqnarray}
+\label{eq:u_const}
+	-15\% \le u \le 65\%.
+\end{eqnarray}
+
+Note, the variable $u$ represents the manipulated variable in the deviation form.
+The values of feed temperature and voltage of the heating medium pump corresponding to zero steady state are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
+
+The penalty matrices of the problem TODO:ref were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for every MPC setup.
+The aim was to determine, which penalty matrix will be the tuned one.
+Based on observations, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the setpoint.
+The boundary values of matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
+The built-in integrator was penalized with $Q_\mathrm{x2}$ = 1 and the manipulated variable with $R$ = 10.
+The prediction horizon $N$ was 20 steps long.
+The control results for both control setups are compared in Fig.~\ref{fig:CV_boundaries} for the controlled variable, and in Fig.~\ref{fig:MV_boundaries} for the manipulated variable.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/HE}
+		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: feed pump\,(1), heating medium pump\,(2), feed tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
+		\label{fig:HE}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
+		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+		\label{fig:CV_boundaries}
+	\end{center}
+\end{figure}
+
+The trajectories in Fig.~\ref{fig:CV_boundaries} show the non-symmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
+When applying the control associated with the lower bound $Q_\mathrm{y, L}$, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
+
+These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$. The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
+		\caption{Manipulated variable trajectory for two boundary controllers. The solid lines represent the voltage and the dashed lines represent the constraints.}
+		\label{fig:MV_boundaries}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/CV}
+		\caption{Controlled variable trajectory for two boundary controllers and the tuned one. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+		\label{fig:CV}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/MV}
+		\caption{Manipulated variable trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage and the dashed lines represent the constraints.}
+		\label{fig:MV}
+	\end{center}
+\end{figure}
+
+\begin{table}[h!]
+	\begin{center}
+		\caption{Control performance criteria.}
+		\label{tab:control_performance}
+		\begin{tabular}{c|c|c|c|c|c} 
+			Reference step change & $Q_\mathrm{y}$ & ISE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
+			\hline
+			\multirow{2}{*}{1} & 1000 & 714 & 33.50 & 16.5 & \textbf{2.12} \\
+			    & 100 & 867 & 16.65 & 12.5 & 2.36 \\ 
+			    & tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
+			\hline
+			\multirow{2}{*}{2} & 1000 & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
+			    & 100 & 606 & 23.25 & 26.5 & 3.19 \\ 
+			    & tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
+			\hline
+		    \multirow{2}{*}{3} & 1000 & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
+				& 100 & 398 & 79.64 & 31 & \textbf{2.00} \\ 
+				& tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
+			\hline
+			\multirow{2}{*}{4} & 1000 & 1024 & 18.43 & 22.5 & 0.94 \\
+				& 100 & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
+				& tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10  
+		\end{tabular}
+	\end{center}
+\end{table}
 
 \section{Conclusion}
-\label{}
+\label{sec:conclusion}
 
@@
 %%
-%%  \bibliographystyle{elsarticle-num} 
-%%  \bibliography{<your bibdatabase>}
+
+\bibliographystyle{elsarticle-num} 
+\bibliography{references}
 
@@
 
-\begin{thebibliography}{00}
+%\begin{thebibliography}{00}
+%
+%%% \bibitem{label}
+%%% Text of bibliographic item
+%
+%\bibitem{}
+%
+%\end{thebibliography}
 
-%% \bibitem{label}
-%% Text of bibliographic item
-
-\bibitem{}
-
-\end{thebibliography}
 \end{document}

### 2023-01-19 data/ploty.m

@@ -1,5 +1,5 @@
-load('ref_tracking29.mat')
-%% plots
+load('ref_tracking24.mat')
+%% Ordinary plots
 % close all
 figure(1)
 hold on; grid minor; box on
@@ -13,3 +13,53 @@ plot(out.ScopeData(:,1),out.ScopeData(:,4),'LineWidth',1.5)
 % title('R = 200, Q_x = 0.1, Q_{integrator} = 8')
 legend('output','reference')
 xlim([0 3000])
+
+%% Paper
+close all, clear
+load('ref_tracking23.mat') %1 -> Q_y = 1000
+from = 801;
+to = 6000;
+time = out.ScopeData(1:to-from+1,1);
+ref = out.ScopeData(from:to,4);
+input1 = out.ScopeData(from:to,3);
+output1 = out.ScopeData(from:to,2);
+
+load('ref_tracking24.mat') %2 -> Q_y = 100
+input2 = out.ScopeData(from:to,3);
+output2 = out.ScopeData(from:to,2);
+
+load('ref_tracking27.mat') %2 -> Q_y = tuned
+input3 = out.ScopeData(from:to,3);
+output3 = out.ScopeData(from:to,2);
+
+set(0,'defaulttextinterpreter','latex')
+lw = 1.5;
+fs = 13;
+green   = [0.2, 0.7, 0.1];
+
+figure(3), hold on
+plot(time,output1,time,output2,'LineWidth',lw) %only boundaries
+% plot(time,output3,'LineWidth',lw,'Color',green) 
+plot(time,ref,'--','LineWidth',lw,'Color','k') 
+xlim([0 2600])
+xlabel('time [s]')
+set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
+xlabel('$t$ [s]')
+ylabel('$T$ [$^{\circ}$C]','FontSize', fs)
+legend('$Q_\mathrm{y} = 1000$', '$Q_\mathrm{y} = 100$', 'Interpreter','latex', 'FontSize', fs) %only boundaries
+% legend('$Q_\mathrm{y} = 1000$', '$Q_\mathrm{y} = 100$', '$Q_\mathrm{y}$ tuned', 'Interpreter','latex', 'FontSize', fs) %all
+grid minor
+
+figure(4), hold on
+plot(time,input1,time,input2,'LineWidth',lw) %only boundaries 
[…]

### 2023-01-19 ploty.m

@@ -1,0 +1,15 @@
+load('ref_tracking23.mat')
+%% plots
+% close all
+figure(1)
+hold on; grid minor; box on
+plot(out.ScopeData(:,1),out.ScopeData(:,3),'LineWidth',1.5)
+xlim([0 3000])
+
+figure(2)
+hold on; grid minor; box on
+plot(out.ScopeData(:,1),out.ScopeData(:,2),'LineWidth',1.5)
+plot(out.ScopeData(:,1),out.ScopeData(:,4),'LineWidth',1.5)
+% title('R = 200, Q_x = 0.1, Q_{integrator} = 8')
+legend('output','reference')
+xlim([0 3000])

### 2023-01-20 paper/elsarticle/main.tex
paper:results part2

@@
 The prediction horizon $N$ was 20 steps long.
+The explicit model predictive controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
+The controllers were implemented to track a time-varying reference.
+For the first 200 seconds, the system was in the steady state.
+After that the reference changed its value twice upwards and twice downwards.
+The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
 The control results for both control setups are compared in Fig.~\ref{fig:CV_boundaries} for the controlled variable, and in Fig.~\ref{fig:MV_boundaries} for the manipulated variable.
@@
 
-The trajectories in Fig.~\ref{fig:CV_boundaries} show the non-symmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
-When applying the control associated with the lower bound $Q_\mathrm{y, L}$, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
-On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
-
-These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$. The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
-
 \begin{figure}
@@
 \end{figure}
+
+The trajectories in Fig.~\ref{fig:CV_boundaries} show the non-symmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
+When applying the control associated with the lower bound $Q_\mathrm{y, L}$, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
+
+These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$. The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
+
+TODO: dopisat strucne princip ladenia podla toho, ako bude spisana teoria v ~\ref{sec:self_tunable_new}. odkazat sa na rovnice atd...
+
+The control results of the selt-tunable technique compared to the boundary controllers can be seen in Fig.~\ref{fig:CV} for the controlled variable, and in Fig.~\ref{fig:MV} for the manipulated variable.
+It can be seen that the tuned controller combined the benefits of the two boundary controllers.
+The overshoots and undershoots were reduced, as in the first half of control the penalty matrix $Q_\mathrm{y}$ acquired value from the first half of the penalty interval.
+When tracking the reference with negative change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
+The similarity with the boundary controllers can be seen also on the manipulated variable trajectory.
+Note, the constraints on the input variable were satisfied as they were scaled based on the boundary controllers which are constructed considering the contraints.
+
+TODO: what about state constraints?
 
@@
 
+The control performance was also investigated quantitatively.
+The Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria for the tuned and two boundary controllers.
+The control performance is evaluated for every reference step change respectively.
+The criteria are integral square error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$, settling time $t_{\epsilon}$ for 5\%-neighbourhood of the reference value, and the volume of the heating medium utilized for the corresponding control.
+To provide better readability of the results, the best (i.e.
+minimal) values are written in bold.
+
 \begin{table}[h!]
@@
 		\begin{tabular}{c|c|c|c|c|c} 
-			Reference step change & $Q_\mathrm{y}$ & ISE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
+			Reference step change & $Q_\mathrm{y}$ & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
 			\hline
@@
 \end{table}
+
+It can be seen in Table~\ref{tab:control_performance}, that real-time tuning of the controller helped to improve two to three criteria when tracking each reference value.
+The cost for this is the energy associated with control.
+Although the integral square error, maximal overshoot/undershoot and settling time decreased, the volume of consumed heating medium did not.
+Nevertheless, the average deterioration in the terms of consumed heating medium is approximately 17\%.
+
+The improvement or deterioration in percentage of using the tunable controller relative to the second best setup is summarized in Table~\ref{tab:improvement} for every reference step change separately.
+The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
+
+\begin{table}[h!]
+	\begin{center}
+		\caption{Improvement or deterioration of the control performance in percentage.}
+		\label{tab:improvement}
+		\begin{tabular}{c|c|c|c|c} 
+			Reference step change & $ISE$ & $\sigma_{\mathrm{max}}$ & $t_{\epsilon}$ & $V$ \\
+			\hline
+			1 & 5.04 & 8.77 & 24.00 & -12.26 \\ 
+			\hline
+			2 & 32.05 & 17.72 & -90.00 & -34.54 \\ 
+			\hline
+			3 & 24.08 & -29.97 & 0 & -4.48 \\ 
+			\hline
+			4 & 5.57 & 10.53 & 17.78 & -18.28  
+		\end{tabular}
+	\end{center}
+\end{table}
+
+It can be seen that implementing a tunable controller leads to improved control performance in many criteria.
+Utilizing a controller with a scalable aggressivity according to the operating conditions leads in general to higher accuracy, lower overshoot and faster achieving the reference value.
+%It should be also noted that the deterioration of every criterium is calculated subject to the best out of \textit{two} other controllers.
+It follows that the evaluation is strict as in practice only one controller would be available.
+Although the volume of the heating medium is not saved in this control scenario, the improved control performance may lead to other benefits. 
+TODO: krajsie skomentovat vyhody zlepsenia kvality riadenia
 

### 2023-01-21 paper/elsarticle/main.tex
paper:eMPC

@@
 
+(skor intro?)The benefit in form of lower computational complexity in the control phase comes hand in hand with a drawback.
+The size of the parametric solution may be so large, that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
+Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
+
 \section{Preliminaries}
 \label{sec:preliminaries}
+In this section, the theoretical background necessary for this work is summarized.
+First, the explicit model predictive control is recalled.
+Next, the tunable technique of the approximated explicit model predictive control is introduced.
+Last but not least, the self-tunable technique of the approximated explicit MPC is presented.
 
@@
 TODO: remark, ze sme si vedomi aj delta-u formulacie, ale vedie na zlozitejsie eMPC
+
+Explicit model predictive control~\cite{Bemporad_automatica} represents a parametric solution of the model predictive control which makes it suitable for online implementation.
+As the explicit solution is available, it is not necessary to solve the optimization problem in every control step.
+As this work deals with practical implementation, let us consider the optimization problem in the following form:
+
+\begin{subequations}
+	\label{eq:mpc_problem}
+	\begin{eqnarray}
+		\label{eq:mpc_problem_cost}
+		\min_{u_0,u_{1},\ldots,u_{N-1}} &~& \!
+\sum_{k=0}^{N-1} \!
+\left( (y_k-y_\mathrm{ref})^{\intercal} Q_\mathrm{y} (y_k-y_\mathrm{ref}) + u_{k}^{\intercal} R u_{k} + x_{\mathrm{I},k}^{\intercal} Q_\mathrm{x} x_{\mathrm{I},k} \right)  \\
+		\label{eq:mpc_problem_prediction_model_x}
+		\mathrm{s.t.\!:} &~& \widetilde{x}_{k+1} = \widetilde{A}\,\widetilde{x}_{k} + \widetilde{B}\,u_{k}, \\
+		\label{eq:mpc_problem_prediction_model_y}
+		&~& y_{k} = \widetilde{C}\,\widetilde{x}_{k}, \\
+		\label{eq:mpc_problem_input_constraints}
+		&~& u_{k} \in \mathcal{U}, \\
+		\label{eq:mpc_problem_state_constraints}
+		&~& y_{k} \in \mathcal{Y}, \\
+		\label{eq:mpc_problem_initial_coindition}
+		&~& \widetilde{x}_{0} = \theta, \\
+		\label{eq:mpc_problem_k_range}
+		&~& k = 0,1,\ldots, N-1,
+	\end{eqnarray}
+\end{subequations}
+
+where $k$ denotes the step of the prediction horizon $N$.
+The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically precomputed.
+The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of extended linear time-invariant (LTI) system for given extended state matrix $\widetilde{A} \in \mathbb{R}^{n_{\mathrm{x}} \times n_{\mathrm{x}}}$, extended input matrix $\widetilde{B} \in \mathbb{R}^{n_{\mathrm{x}} \times n_{\mathrm{u}}}$ and extended output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{x}}}$.
+Variables $\widetilde{x} \in \mathbb{R}^{n_{\mathrm{x}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding extended system states, control inputs and system outputs, respectively.
+The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{x}}}$ are sets of physical constraints on inputs and outputs, respectively.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squarred control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
+To obtain the offset-free control results, the built-in integrator was included in the state-space model, see e.q.~\cite{Ruscio_MPC_integral}.
+The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{x} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
+
+The model extended with the built-in integrator in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} can be rewritten as:
+
+\begin{subequations}
+	\begin{eqnarray} 
+		\label{eq:mpc_extended_model_x} 
+		\widetilde{x}_{k+1} &=& \begin{bmatrix} x_{k+1} \\ 	x_{\mathrm{I},k+1}\end{bmatrix} = \begin{bmatrix} A & \textit{0} \\ -T_\mathrm{s} C & I \end{bmatrix} \begin{bmatrix} x_{k} \\ x_{\mathrm{I},k} \end{bmatrix} + \begin{bmatrix} B \\ I \end{bmatrix} u_{k}, \\
+		\label{eq:mpc_extended_model_y}
+		y_k &=& \begin{bmatrix} C & \textit{0} \end{bmatrix} \begin{bmatrix} x_{k} \\ x_{\mathrm{I},k} \end{bmatrix},
+	\end{eqnarray}
+\end{subequations}
+
+where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time and matrices $A$, $B$, $C$ are well-known linear time-invariant state-space matrices that form the extended model.
+Thanks to this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error are penalized, but also its integral, which leads to similar results as incorporating integral part in PID controller.
+
+Solving the MPC quadratic optimization problem in Eq.~\eqref{eq:mpc_problem} parametrically leads to explicit solution in the form of piece-wise affine control law consisting of $r$ critical regions:
+
+\begin{eqnarray}
+\label{eq:PWA_control_law}
+u(\theta) = \left\{ 
+\begin{matrix}
+	F_{1} \, \theta + g_{1} & \mathrm{if} & \quad \theta \in \mathcal{R}_1, \\
+	F_{2} \, \theta + g_{2} & \mathrm{else}\,\,\mathrm{if} &\quad \theta \in \mathcal{R}_2, \\
+	\vdots & \\
+	F_{r} \, \theta + g_{r} & \mathrm{else}\,\,\mathrm{if} & \quad \theta \in \mathcal{R}_{r}, \\
+\end{matrix}
+\right.
+\end{eqnarray}
+where $F_{i}$ and $g_{i}$ respectively are the slope and affine section of the corresponding control law.
+The piece-wise affine function from Eq.~\eqref{eq:PWA_control_law} is stored and used in the online, i.e., control phase.
+Based on identifying the critical region where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law.
+
+Note, many other formulations of the optimization problems are elaborated, mainly in the terms of cost functions.
+Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extendsion of the vector of parameters $\theta$ and therefore the explicit MPC complexity increases.
+Another option for offset-free tracking is also disturbance observer.
+For such an overview see e.g.
+...TODO.
+Klauco reference governors? minimovka zdroje
 
@@
 
-The penalty matrices of the problem TODO:ref were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for every MPC setup.
+The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for every MPC setup.
 The aim was to determine, which penalty matrix will be the tuned one.

### 2023-01-23 paper/elsarticle/main.tex
paper:tunable start

@@
 Next, the tunable technique of the approximated explicit model predictive control is introduced.
-Last but not least, the self-tunable technique of the approximated explicit MPC is presented.
+Last but not least, the ideas of self-tunable technique of the approximated explicit MPC are presented.
 
@@
 \label{sec:eMPC}
-TODO: remark, ze sme si vedomi aj delta-u formulacie, ale vedie na zlozitejsie eMPC
-
 Explicit model predictive control~\cite{Bemporad_automatica} represents a parametric solution of the model predictive control which makes it suitable for online implementation.
@@
 The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically precomputed.
-The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of extended linear time-invariant (LTI) system for given extended state matrix $\widetilde{A} \in \mathbb{R}^{n_{\mathrm{x}} \times n_{\mathrm{x}}}$, extended input matrix $\widetilde{B} \in \mathbb{R}^{n_{\mathrm{x}} \times n_{\mathrm{u}}}$ and extended output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{x}}}$.
-Variables $\widetilde{x} \in \mathbb{R}^{n_{\mathrm{x}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding extended system states, control inputs and system outputs, respectively.
-The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{x}}}$ are sets of physical constraints on inputs and outputs, respectively.
+Variables $\widetilde{x} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding extended system states, control inputs and system outputs, respectively.
+The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of extended linear time-invariant (LTI) system for given extended state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, extended input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and extended output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
+The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are sets of physical constraints on inputs and outputs, respectively.
 The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squarred control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
@@
 ...TODO.
-Klauco reference governors? minimovka zdroje
+Klauco reference governors? minimovka zdroje + dizertacka str.33
 
@@
 \label{sec:tunable}
+
+\begin{subequations}
+	\begin{eqnarray}
+	\label{eq:tunable_matrices}
+		&~& R = (1-\rho)R_\mathrm{L} + \rho R_\mathrm{H}, \\
+		&~& Q_\mathrm{x} = (1-\rho)Q_\mathrm{x,L} + \rho Q_\mathrm{x,H}, \\
+		&~& Q_\mathrm{y} = (1-\rho)Q_\mathrm{y,L} + \rho Q_\mathrm{y,H},
+	\end{eqnarray}
+\end{subequations}
+
+\begin{subequations}
+	\begin{eqnarray}
+		\label{eq:tunable_u}
+		u = (1-\rho)u_\mathrm{L} + \rho u_\mathrm{H},
+	\end{eqnarray}
+\end{subequations}
 

### 2023-01-24 paper/elsarticle/main.tex
paper: tunable and self-tunable

@@
 \usepackage{amsmath}
+
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{remark}[theorem]{Remark}
 
@@
 As this work deals with practical implementation, let us consider the optimization problem in the following form:
-
 \begin{subequations}
@@
 The model extended with the built-in integrator in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} can be rewritten as:
-
 \begin{subequations}
@@
 Solving the MPC quadratic optimization problem in Eq.~\eqref{eq:mpc_problem} parametrically leads to explicit solution in the form of piece-wise affine control law consisting of $r$ critical regions:
-
 \begin{eqnarray}
@@
 \label{sec:tunable}
+The aggressivity of the controller and whole nature of the control can be influenced by tuning the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
+When the optimization problem is precomputed offline to obtain the parametric solution, it is not possible to tune the controller afterwards.
+As the operation conditions and demands on controller setup may differ throughout control, the ability to adjust the controller aggressivity can be very beneficial.
 
+The idea of approximated tunable explicit MPC comes from the work ~\cite{Klauco_tunable}, where the control action is calculated based on linear interpolation between two boundary control actions.
+These control actions result from evaluating two boundary explicit MPCs.
+The boundary explicit controllers have the same structure and setup, except one of the penalty matrices -- the tuned one.
+The boundary matrices are diagonal square matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of penalty matrix eigenvalues, $L$ and $U$ denote the lower and upper boundary setup respectively, and $s$ is the rank of the tuned penalty matrix.
+
+When considering the penalty matrices from cost function~\eqref{eq:mpc_problem_cost}, the penalty matrices are scaled in the following way:
 \begin{subequations}
+	\label{eq:tunable_matrices}
 	\begin{eqnarray}
-	\label{eq:tunable_matrices}
-		&~& R = (1-\rho)R_\mathrm{L} + \rho R_\mathrm{H}, \\
-		&~& Q_\mathrm{x} = (1-\rho)Q_\mathrm{x,L} + \rho Q_\mathrm{x,H}, \\
-		&~& Q_\mathrm{y} = (1-\rho)Q_\mathrm{y,L} + \rho Q_\mathrm{y,H},
+		\label{eq:tunable_R}
+		&~& R = (1-\rho)R_\mathrm{L} + \rho R_\mathrm{U}, \\
+		\label{eq:tunable_Qx}
+		&~& Q_\mathrm{x} = (1-\rho)Q_\mathrm{x,L} + \rho Q_\mathrm{x,U}, \\
+		\label{eq:tunable_Qy}
+		&~& Q_\mathrm{y} = (1-\rho)Q_\mathrm{y,L} + \rho Q_\mathrm{y,U},
 	\end{eqnarray}
@@
 
+where $\rho$ represents the scaling parameter and $0 \le \rho \le 1$ holds.
+Based on~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
+Note, it is practical to tune only one matrix, i.e., to store only two controllers corresponding to the boundary matrices.
+To determine which penalty matrix should be tuned, it is suggested to examine the control results subject to the specific system and to try systematic tuning of all the penalty matrices.
+
+When the scaling parameter $\rho$ is determined based on the current control conditions, the optimal control action is evaluated using the two optimal controllers.
+Based on the boundary control actions, the interpolated, i.e., tuned control action is calculated:
 \begin{subequations}
@@
 		\label{eq:tunable_u}
-		u = (1-\rho)u_\mathrm{L} + \rho u_\mathrm{H},
+		u = (1-\rho)u_\mathrm{L} + \rho u_\mathrm{U},
 	\end{eqnarray}
@@
 
+where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller respectively.
+The tuning of the controller online comes with a cost of storing and evaluating two explicit controllers.
+Nevertheless, the ability to tune the controller may be more important in many practical applications.
+
+Note, the concept of explicit MPC tuning can be applied also to other MPC formulations, based on the current specific needs.
+In this paper, the penalty matrices of cost function~\eqref{eq:mpc_problem_cost} are considered, as it is necessary to satisfy offset-free reference tracking.
+
+\begin{remark}
+	If stability guarantee and recursive feasibility is required, it is suggested to follow the instructions from \cite{Oravec_tunable}.
+In order to satisfy the requirements, the study introduces a procedure of choosing the terminal penalty and terminal set in the two boundary controllers.
+\end{remark}
+
 \subsection{Self-tunable explicit model predictive control}
 \label{sec:self_tunable}
+The advantage of tunable controller brings a question of how to design the logic of tuning the scaling parameter $\rho$.
+In this section, the idea of online self-tuning is summarized~\cite{self_tunable}.
+The concept of self-tuning provides the possibility to adjust the aggressiveness of the controller without the necessity to intervene and tune the penalty matrices during control.
+
+The need for real-time controller tuning often arises from tracking a time-varying reference.
+The work~\cite{self_tunable} focuses on adjusting the penalty matrix when the reference value is changed.
+The further the reference value is from the steady state, the more aggressive controller is tuned.
+The idea behind the suggested scaling liest in compensation of the nonlinear behavior of the system.
+
+The procedure of tuning the controller is based on evaluating the difference between the reference and the steady state, and using this deviation to scale the value of control action.
+First, the maximal absolute value of reference which can be set during control is defined.
+This value can be determined based on the general knowledge of future reference values.
+Another suggestion is to set the maximal deviation $d_{\max}$ simply based on the constraints on system outputs:
+\begin{eqnarray}
+	\label{eq:d_max}
+	d_{\max} = \max(\vert y_{\min} \vert, y_{\max}),
+\end{eqnarray}
+
+where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable.
+Using the information about the maximal possible deviation $d_{\max}$, the scaling parameter $\rho$ can be calculated as the ration between the current reference value and the maximal deviation:
+
+\begin{eqnarray}
+	\label{eq:rho_self_tunable}
+	\rho = \frac{\vert y_{\mathrm{ref}} \vert}{d_{\max}}.
+\end{eqnarray}
+
+Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
+As a result, the parameter $\rho$ represents a way how to normalize the deviation from steady state and is exploited to scale the penalty matrix or at the end of the day, the control action.
+
+When considering tuning the control action based on Eq.~\eqref{eq:tunable_u}, a higher value of scaling parameter $\rho$ leads to approaching the upper boundary controller and vice versa.
+When tuning e.g.
+the matrix $Q_\mathrm{y}$ penalizing the control error, a higher ratio $\rho$ would lead to more aggressive control actions.
+When controlling to the reference values closer to the steady state, the parameter $rho$ decreases and the control becomes sluggish.
+
+\begin{remark}
+	The parameter $d_{\max}$ is vector in general, as it depends on the size of system outputs.
+If $d_{\max}$ is scalar, the paramter $\rho$ is scalar as well and can be directly utilized to scale the control action.
+If multiple outputs are controlled, it is suggested to calculate the scaling parameter based on the maximal ratio:
+	\begin{eqnarray}
+		\label{eq:rho_max}
+		\rho = \max \left( \frac{\vert y_{\mathrm{ref}} \vert}{d_{\max}} \right).
+	\end{eqnarray}	
+\end{remark}
+
+Note, the relations \eqref{eq:rho_self_tunable} and \eqref{eq:rho_max} operate with the absolute value of the reference.
+It is not taken into account, whether the reference change was positive or negative, i.e., whether it changed upwards or downwards.
+As many plants have non-symmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to increase the control performance.
 
@@
 \label{sec:self_tunable_new}
+TODO: rozdelit dva spominane pristpy? dat dva navody?
 

### 2023-01-25 paper/elsarticle/main.tex
paper: novel theory

@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{definition}{Definition}[section]
 
@@
 
-where $\rho$ represents the scaling parameter and $0 \le \rho \le 1$ holds.
+where $\rho$ represents the tuning parameter and $0 \le \rho \le 1$ holds.
 Based on~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
@@
 
-When the scaling parameter $\rho$ is determined based on the current control conditions, the optimal control action is evaluated using the two optimal controllers.
+When the tuning parameter $\rho$ is determined based on the current control conditions, the optimal control action is evaluated using the two optimal controllers.
 Based on the boundary control actions, the interpolated, i.e., tuned control action is calculated:
@@
 \label{sec:self_tunable}
-The advantage of tunable controller brings a question of how to design the logic of tuning the scaling parameter $\rho$.
+The advantage of tunable controller brings a question of how to design the logic of setting the tuning parameter $\rho$.
 In this section, the idea of online self-tuning is summarized~\cite{self_tunable}.
@@
 where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable.
-Using the information about the maximal possible deviation $d_{\max}$, the scaling parameter $\rho$ can be calculated as the ration between the current reference value and the maximal deviation:
+Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
 
@@
 
-When considering tuning the control action based on Eq.~\eqref{eq:tunable_u}, a higher value of scaling parameter $\rho$ leads to approaching the upper boundary controller and vice versa.
+When considering tuning the control action based on Eq.~\eqref{eq:tunable_u}, a higher value of tuning parameter $\rho$ leads to approaching the upper boundary controller and vice versa.
 When tuning e.g.
 the matrix $Q_\mathrm{y}$ penalizing the control error, a higher ratio $\rho$ would lead to more aggressive control actions.
-When controlling to the reference values closer to the steady state, the parameter $rho$ decreases and the control becomes sluggish.
+When controlling to the reference values closer to the steady state, the parameter $\rho$ decreases and the control becomes sluggish.
 
@@
 	The parameter $d_{\max}$ is vector in general, as it depends on the size of system outputs.
-If $d_{\max}$ is scalar, the paramter $\rho$ is scalar as well and can be directly utilized to scale the control action.
-If multiple outputs are controlled, it is suggested to calculate the scaling parameter based on the maximal ratio:
+If $d_{\max}$ is scalar, the parameter $\rho$ is scalar as well and can be directly utilized to scale the control action.
+If multiple outputs are controlled, it is suggested to calculate the tuning parameter based on the maximal ratio:
 	\begin{eqnarray}
@@
 It is not taken into account, whether the reference change was positive or negative, i.e., whether it changed upwards or downwards.
-As many plants have non-symmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to increase the control performance.
+As many plants have non-symmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
 
@@
 \label{sec:methodology}
+This section extends the ideas of self-tunable explicit MPC in order to improve the control performance.
+First, a different way of tuning parameter calculation is introduced.
+Furthermore, an extended self-tunable technique is presented to scale the tuning parameter for applications, when it is beneficial to exploit a specific range of the tuning parameter in different operating conditions.
+
+\subsection{Tuning parameter based on the size of reference change}
+\label{sec:self_tunable_delta_ref}
+The approach of self-tunable explicit MPC in~\cite{self_tunable} suggested tuning based on the reference value distance from the steady state.
+The aim is to compensate the nonlinear behavior of system, when using a simple linear prediction model.
+This work provides another way of the tuning parameter calculation based on the size of reference change.
+When different sizes of reference step changes are made and the behavior of the closed-loop system is varying, it can be beneficial to inclue the size of the reference step change into the tuning procedure.
+
+In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be set during control operation:
+\begin{eqnarray}
+	\label{eq:rho_delta_ref}
+	\rho = \frac{\vert \Delta_{\mathrm{ref}} \vert}{d_{\max}},
+\end{eqnarray}
+
+where $\Delta_{\mathrm{ref}} = y_{\mathrm{ref},k}-y_{\mathrm{ref},k-1}$ is the size of the reference change.
+The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well.
+In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $d_{\max}$ as the maximal possible reference step.
+Analogously to the original approach, the maximal reference step can be set based on the general knowledge of future reference values.
+Another option is to exploit the information about the system constraints and set the parameter $d_{\max}$ according to Eq.~\eqref{eq:d_max}.
+
+Note, the tuning parameter $\rho$ should be updated only when the reference changes.
+Updating the tuning parameter in the control steps when $\Delta_{\mathrm{ref}} = 0$ would lead to using tuning parameter with zero value.
+
+TODO: je to znamienkovo symetricke
 
 \subsection{Self-tunable technique for systems with asymmetric behavior}
-\label{sec:self_tunable_new}
-TODO: rozdelit dva spominane pristpy? dat dva navody?
+\label{sec:self_tunable_rho_scaling}
+TODO: co ak nepriama umera? \\
+TODO: remark na nelinearnu interpolaciu \\
+TODO: zovseobecnit na viac usekov intervalu? \\
+TODO: intro veta sem\\
 
-TODO: spomenut, ze to je vhodne celkovo aj pre klasicke online MPC
+The suggested technique of tuning is suitable e.g.
+for systems with non-symmetric behavior, but can be used in any application, where ,,simple" tuning in the whole range of tuning parameter $\rho$ is not sufficient.
+
+The tuning method is based on splitting the interval of the tuning parameter $\rho$ in order to utilize different parts of the interval in different operating conditions.
+The adjusted tuning parameter $\widetilde{\rho}$ is then utilized to scale the control input according to Eq.~\eqref{eq:tunable_u} instead of the original value of tuning parameter $\rho$.
+
+\begin{definition}
+	If the tuning parameter is scaled in the first part of the interval, i.e., $\langle 0, \rho_{\mathrm{s}} \rangle$, where $\rho_{\mathrm{s}}$ is the splitting value of the tuning parameter, the following relation is used to adjust the tuning parameter:
+	\begin{eqnarray}
+		\label{eq:rho_up}
+		\widetilde{\rho} = \rho_{\mathrm{s}} \rho.
+	\end{eqnarray}
+\end{definition}
+
+\begin{corollary}
+	The following outcomes result from Eq.~\eqref{eq:rho_up}.
+If $\rho=0$, then $\widetilde{\rho} = 0$.
+When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$.
+In such way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value.
+Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
+\end{corollary}
+
+\begin{definition}
+	If the tuning parameter is scaled in the second part of the interval, i.e., $\langle \rho_{\mathrm{s}}, 1 \rangle$, the following relation is used to adjust the tuning parameter:	
+	\begin{eqnarray}
+		\label{eq:rho_down}
+		\widetilde{\rho} = (1-\rho_{\mathrm{s}}) \rho + \rho_{\mathrm{s}}.
+	\end{eqnarray}
+\end{definition}
+
+\begin{corollary}
+	The following outcomes result from Eq.~\eqref{eq:rho_down}.
+When $\rho=0$, $\widetilde{\rho} = \rho_{\mathrm{s}}$.
+When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$.
+In such way, the parameter $\rho$ can be scaled in the second part of the interval from to the splitting value up to 1.
+Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
+\end{corollary}
+
+The advantage of the proposed method remains in the self-tuning of the controller as in the approach from Section~\ref{sec:self_tunable}.
+Nevertheless, it is required to determine the splitting value of the tuning parameter $\rho_{\mathrm{s}}$ and assign the parts of the interval to the associated operating conditions.
+
+\begin{remark}
+	Note, the suggested scaling method is suitable also for online MPC, as the optimization problem is solved in every control step.
+Therefore, it is possible to include the controller tuning in the procedure of computing the optimal control input.
+It should be also noted that with updating penalty matrices, the optimization problem has to be rebuilt into a form suitable for a solver, so sufficient computational time is required.
+\end{remark}
 
@@
 The matrices of the linear state-space model of the plant, discretized with sampling time $T_\mathrm{s}$ = 1\,s, are
-
 \begin{subequations}
@@
 The constraints are considered in the terms of manipulated variable, i.e.
-
 \begin{eqnarray}
@@
 The boundary values of matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
-The built-in integrator was penalized with $Q_\mathrm{x2}$ = 1 and the manipulated variable with $R$ = 10.
+The built-in integrator was penalized with $Q_\mathrm{x}$ = 1 and the manipulated variable with $R$ = 10.
 The prediction horizon $N$ was 20 steps long.

### 2023-01-26 paper/elsarticle/main.tex
paper: abstract, conclusion, highlights

@@
 \begin{abstract}
-max 250 words!
-
+%max 250 words!
+The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
+This paper provides a self-tunable technique that does not require any further tuning or interventions of the control engineer during operation.
+Based on the current operating conditions, the tuning parameter adjusts itself and scales the control input using linear interpolation.
+The adjustment of the tuning parameter depends on the reference value, which makes this strategy suitable for reference tracking problems.
+Furthermore, a novel technique for scaling the tuning parameter is proposed.
+It provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and non-symmetric behavior.
+To ensure offset-free control, the built-in integrator was included in the explicit MPC.
+The asymmetric behavior of the plant was compensated by tuning the controller's aggressivity, as the negativity or positivity of reference change was considered in the tuning process.
+The control performance decreased maximal overshoots/undershoots, integral square error, and settling time compared to control with only one controller.
 \end{abstract}
@@
 \begin{highlights}
-\item Research highlight 1
-\item Research highlight 2
+% 3-5 highlights, every one should not exceed 85 characters including spaces
+\item Self-tunable control technique does not need any intervention during control
+\item Tuning based on the operating conditions compensates the nonlinear plant behavior
+\item Implementation of the proposed tuning method on a laboratory heat exchanger 
+\item Control performance improved compared to utilizing only one explicit MPC
 \end{highlights}
@@
 \begin{keyword}
+tunable explicit MPC \sep self-tunable technique \sep tuning parameter \sep heat exchanger \sep control performance
 %% keywords here, in the form: keyword \sep keyword
@@
 
-(skor intro?)The benefit in form of lower computational complexity in the control phase comes hand in hand with a drawback.
+(len skopirovany text z jadra - hodil sa mi viac do Introduction, neskor mozno pouzijem) The benefit in form of lower computational complexity in the control phase comes hand in hand with a drawback.
 The size of the parametric solution may be so large, that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
@@
 
-Note, the tuning parameter $\rho$ should be updated only when the reference changes.
-Updating the tuning parameter in the control steps when $\Delta_{\mathrm{ref}} = 0$ would lead to using tuning parameter with zero value.
+Note, only absolute value of $\Delta_{\mathrm{ref}}$ and $d_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
 
-TODO: je to znamienkovo symetricke
+\begin{remark}
+	The tuning parameter $\rho$ should be updated only when the reference changes.
+Updating the tuning parameter in the control steps when $\Delta_{\mathrm{ref}} = 0$ would lead to using tuning parameter $\rho$ with zero value, i.e., the control input would correspond to one boundary controller and would not be scaled.
+\end{remark}
 
@@
 \label{sec:self_tunable_rho_scaling}
-TODO: co ak nepriama umera? \\
+\noindent TODO: co ak nepriama umera? \\
 TODO: remark na nelinearnu interpolaciu \\
 TODO: zovseobecnit na viac usekov intervalu? \\
-TODO: intro veta sem\\
 
+This paper provides further extension of the self-tuning method proposed in~\cite{self_tunable}.
 The suggested technique of tuning is suitable e.g.
@@
 
-In this section, the results of the proposed tuning method are presented.
+In this section, the results of the proposed tuning method are presented on an experimental implementation.
+The tuning strategy utilizes tuning parameter based n the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
+
 The plant on which the control was implemented is a laboratory liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Fig.~\ref{fig:HE}.
@@
 The flow rate of the feed is constant, while the aim is to track the reference value of its temperature.
-Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger and the manipulated variable is the voltage $U$ corresponding to the power of the heating medium pump.
+Therefore, the controlled output is the feed temperature $T$ at the outlet of the heat exchanger and the control input is the voltage $U$ corresponding to the power of the heating medium pump.
 The voltage is set in percentage, while it is constrained from 20\% to 100\%.
@@
 
-The constraints are considered in the terms of manipulated variable, i.e.
+The constraints are considered in the terms of control inputs, i.e.
 \begin{eqnarray}
@@
 
-Note, the variable $u$ represents the manipulated variable in the deviation form.
+Note, the variable $u$ represents the control inputs in the deviation form.
 The values of feed temperature and voltage of the heating medium pump corresponding to zero steady state are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
@@
 The boundary values of matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
-The built-in integrator was penalized with $Q_\mathrm{x}$ = 1 and the manipulated variable with $R$ = 10.
+The built-in integrator was penalized with $Q_\mathrm{x}$ = 1 and the control input with $R$ = 10.
 The prediction horizon $N$ was 20 steps long.
@@
 For the first 200 seconds, the system was in the steady state.
-After that the reference changed its value twice upwards and twice downwards.
+After that, the reference changed its value twice upwards and twice downwards.
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
-The control results for both control setups are compared in Fig.~\ref{fig:CV_boundaries} for the controlled variable, and in Fig.~\ref{fig:MV_boundaries} for the manipulated variable.
+The control results for both control setups are compared in Fig.~\ref{fig:CV_boundaries} for the controlled outputs, and in Fig.~\ref{fig:MV_boundaries} for the control inputs.
 
@@
 		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+		\caption{Controlled output trajectory for two boundary controllers. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
 		\label{fig:CV_boundaries}
@@
 		\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
-		\caption{Manipulated variable trajectory for two boundary controllers. The solid lines represent the voltage and the dashed lines represent the constraints.}
+		\caption{Control input trajectory for two boundary controllers. The solid lines represent the voltage and the dashed lines represent the constraints.}
 		\label{fig:MV_boundaries}
@@
 
-These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$. The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
+These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$.
+The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
+Utilizing the boundary controller with the penalty matrix $Q_\mathrm{y,L}$ is preferred when the reference changes upwards.
+On the contrary, the controller associated with $Q_\mathrm{y,U}$ is preferred in control with negative reference changes.
+The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
+The last parameter that needed to be set was the maximal possible size of the reference step change $d_{\max}$, which was set to $15^{\circ}\mathrm{C}$.
 
-TODO: dopisat strucne princip ladenia podla toho, ako bude spisana teoria v ~\ref{sec:self_tunable_new}. odkazat sa na rovnice atd...
-
-The control results of the selt-tunable technique compared to the boundary controllers can be seen in Fig.~\ref{fig:CV} for the controlled variable, and in Fig.~\ref{fig:MV} for the manipulated variable.
+The control results of the selt-tunable technique compared to the boundary controllers can be seen in Fig.~\ref{fig:CV} for the controlled outputs, and in Fig.~\ref{fig:MV} for the control inputs.
 It can be seen that the tuned controller combined the benefits of the two boundary controllers.
@@
 When tracking the reference with negative change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
-The similarity with the boundary controllers can be seen also on the manipulated variable trajectory.
-Note, the constraints on the input variable were satisfied as they were scaled based on the boundary controllers which are constructed considering the contraints.
+The similarity with the boundary controllers can be seen also on the control inputs trajectory.
+Note, the constraints on the input variable were satisfied as they were scaled using linear interpolation based on the boundary controllers which are constructed considering the contraints.
 
@@
 		\includegraphics[width=0.8\textwidth]{images/CV}
-		\caption{Controlled variable trajectory for two boundary controllers and the tuned one. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+		\caption{Controlled output trajectory for two boundary controllers and the tuned one. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
 		\label{fig:CV}
@@
 		\includegraphics[width=0.8\textwidth]{images/MV}
-		\caption{Manipulated variable trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage and the dashed lines represent the constraints.}
+		\caption{Control input trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage and the dashed lines represent the constraints.}
 		\label{fig:MV}
@@
 Although the integral square error, maximal overshoot/undershoot and settling time decreased, the volume of consumed heating medium did not.
-Nevertheless, the average deterioration in the terms of consumed heating medium is approximately 17\%.
+Nevertheless, the average deterioration in the terms of consumed heating medium is approximately~17\%.
 
@@
 Although the volume of the heating medium is not saved in this control scenario, the improved control performance may lead to other benefits.
+
 TODO: krajsie skomentovat vyhody zlepsenia kvality riadenia
@@
 \label{sec:conclusion}
+This paper deals with the experimental implementation of tunable approximated explicit model predictive control and provides a technique for self-tuning controller design.
+Based on the current reference value, the tuning parameter is scaled using linear interpolation.
+The previously published paper related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the steady state.
+This paper presents a novel idea of tuning based on the size of reference step change.
+The tuning procedures aim to compensate for the nonlinear behavior of the controlled system.
+The tuning parameter is updated when the reference changes.
+It is calculated as the ratio between the size of the reference change and the maximal possible size of the reference change, which is specified before operation.
+Another novel contribution comes with splitting the interval of tuning parameter into two ranges, while both ranges are assigned to different operating conditions.
+The proposed method is implemented on a laboratory heat exchanger with nonlinear and non-symmetric behavior.
+The non-symmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
+The decision criterium is negativity or positivity of reference change.
+When the reference changed upwards, the control input was tuned in the first part of the interval and approached the boundary controller associated with the lower bound on the penalty matrix.
+On the contrary, when the reference changed downwards, the control input was tuned to approach the control input from the boundary controller with the upper bound on the penalty matrix.
+To investigate the control results properly, the control performance was evaluated quantitatively.
+Compared to control with only one controller, the self-tunable technique helped to decrease the maximal overshoots/undershoots, integral square error, and settling time.
 

### 2023-01-27 paper/elsarticle/main.tex
paper:acknowledgements, nomenclature added and title changed

@@
 
-\title{Self-tunable approximated explicit MPC: Heat exchanger implementation}
+\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys}
 %\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}
@@
 
+\section*{Acknowledgements}
+This research is funded by the European Union’s Horizon Europe under grant no.
+101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, the Slovak Research and Development Agency under the project APVV-20-0261.
+
+\section*{Nomenclature}
+
+\subsection{Abbreviations}
+\noindent  \textit{MPC}: model predictive control \\
+\textit{ISE}: integral square error \\
+\textit{LTI}: linear time-invariant \\
+
+\subsection{Symbols}
+\noindent $A$: system state matrix \\
+$\widetilde{A}$: extended system state matrix \\
+$B$: system input matrix \\
+$\widetilde{B}$: extended system input matrix \\
+$C$: system output matrix \\
+$\widetilde{C}$: extended system output matrix \\
+$d_{\max}$: maximal deviation from the steady state \\
+TODO: odlisit max size of reference step change \\
+$F$: slope of the affine control law \\
+$g$: section of the affine control law \\
+$I$: identity matrix \\	
+$k$: step of the prediction horizon \\
+$N$: prediction horizon \\
+$n_{\mathrm{u}}$: size of system inputs \\
+$n_{\mathrm{y}}$: size of system outputs \\
+$n_{\widetilde{\mathrm{x}}}$: size of extended system states \\
+$Q_{\mathrm{x}}$: penalty matrix of the built-in integrator \\
+$Q_{\mathrm{x,L}}$: lower bound on the penalty matrix of the built-in integrator \\
+$Q_{\mathrm{x,U}}$: upper bound on the penalty matrix of the built-in integrator \\
+$Q_{\mathrm{y}}$: penalty matrix of the control error \\
+$Q_{\mathrm{y,L}}$: lower bound on the penalty matrix of the control error \\
+$Q_{\mathrm{y,U}}$: upper bound on the penalty matrix of the control error \\
+$R$: penalty matrix of system inputs \\
+$R_{\mathrm{L}}$: lower bound on the penalty matrix of system inputs \\
+$R_{\mathrm{U}}$: upper bound on the penalty matrix of system inputs \\
+$\mathcal{R}$: critical region \\
+$\mathbb{R}$: Euclidean space of real numbers \\
+$t$: time, s \\
+$t_{\epsilon}$: settling time, s \\
+$T$: temperature, $^{\circ}\mathrm{C}$ \\
+$T_{\mathrm{s}}$: sampling time, s \\
+$T^{\mathrm{s}}$: steady state of temperature, $^{\circ}\mathrm{C}$ \\
+$u$: control inputs \\
+$u_{\mathrm{L}}$: control inputs asscociated with the lower boundary controller\\
+$u_{\mathrm{U}}$: control inputs asscociated with the upper boundary controller\\
+$U$: voltage, \% \\
+$U^{\mathrm{s}}$: steady state of voltage, \% \\
+$\mathcal{U}$: set of control inputs \\
+$V$: volume of heating medium, l \\
+$x$: system states \\
+$\widetilde{x}$: extended system states \\
+$x_{\mathrm{I}}$: system states corresponding to the built-in integrator \\
+$y$: system outputs \\
+$y_\mathrm{\max}$: maximal value of system outputs \\
+$y_\mathrm{\min}$: minimal value of system outputs \\
+$y_\mathrm{ref}$: reference value of system outputs \\	
+$\mathcal{Y}$: set of system outputs \\
+\textit{0}: zero matrix
+
+\subsection{Greek letters}
+\noindent $\Delta_\mathrm{ref}$: size of the reference change, $^{\circ}\mathrm{C}$ \\
+$\rho$:	tuning factor \\
+$\widetilde{\rho}$: scaled tuning factor \\
+$\rho_{\mathrm{s}}$: splitting value of the tuning factor \\
+$\sigma_{\max}$: maximal overshoot, \% \\
+$\theta$: parameter of optimization problem \\
+$\Theta$: set of parameter values
+
 %% The Appendices part is started with the command \appendix;

### 2023-01-27 paper/elsarticle/main.tex
Review: Nomenclature

--- 2023-01-26 paper/elsarticle/main.tex
@@
 
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \affiliation{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-%% \fntext[label3]{}
-
-\title{Self-tunable approximated explicit MPC: Heat exchanger implementation}
-%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \affiliation[label1]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-%%
-%% \affiliation[label2]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-
-\author{Lenka Galčíková}
-\author{Juraj Oravec}
-\author{Petronela Belková}
-
-\affiliation{organization={Slovak University of Technology in Bratislava, Faculty of Chemical and Food Technology, Institute of Information Engineering, Automation, and Mathematics,},%Department and Organization
-            addressline={Radlinského 9}, 
-            city={Bratislava},
-            postcode={81237}, 
-%            state={Slovakia},
-            country={Slovakia}
-}
-
-\begin{abstract}
-%max 250 words!
+%% TODO: UNCOMMENT THIS SECTION TO COMPILE ALSO INITIAL PART OF THE PAPAER
+%
+%\begin{frontmatter}
+%
+%%% Title, authors and addresses
+%
+%%% use the tnoteref command within \title for footnotes;
+%%% use the tnotetext command for theassociated footnote;
+%%% use the fnref command within \author or \address for footnotes;
+%%% use the fntext command for theassociated footnote;
+%%% use the corref command within \author for corresponding author footnotes;
+%%% use the cortext command for theassociated footnote;
+%%% use the ead command for the email address,
+%%% and the form \ead[url] for the home page:
+%%% \title{Title\tnoteref{label1}}
+%%% \tnotetext[label1]{}
+%%% \author{Name\corref{cor1}\fnref{label2}}
+%%% \ead{email address}
+%%% \ead[url]{home page}
+%%% \fntext[label2]{}
+%%% \cortext[cor1]{}
+%%% \affiliation{organization={},
+%%%             addressline={},
+%%%             city={},
+%%%             postcode={},
+%%%             state={},
+%%%             country={}}
+%%% \fntext[label3]{}
+%
+%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys}
+%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}
+%
+%%% use optional labels to link authors explicitly to addresses:
+%%% \author[label1,label2]{}
+%%% \affiliation[label1]{organization={},
+%%%             addressline={},
+%%%             city={},
+%%%             postcode={},
+%%%             state={},
+%%%             country={}}
+%%%
+%%% \affiliation[label2]{organization={},
+%%%             addressline={},
+%%%             city={},
+%%%             postcode={},
+%%%             state={},
+%%%             country={}}
+%
+%\author{Lenka Galčíková}
+%\author{Juraj Oravec}
+%\author{Petronela Belková}
+%
+%\affiliation{organization={Slovak University of Technology in Bratislava, Faculty of Chemical and Food Technology, Institute of Information Engineering, Automation, and Mathematics,},%Department and Organization
+%            addressline={Radlinského 9}, 
+%            city={Bratislava},
+%            postcode={81237}, 
+%%            state={Slovakia},
+%            country={Slovakia}
+%}
+%
+%\begin{abstract}
+%%max 250 words!
 The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
@@
 The control performance decreased maximal overshoots/undershoots, integral square error, and settling time compared to control with only one controller.
-\end{abstract}
-
-%%Graphical abstract
-\begin{graphicalabstract}
-%\includegraphics{grabs}
-\end{graphicalabstract}
-
-%%Research highlights
-\begin{highlights}
-% 3-5 highlights, every one should not exceed 85 characters including spaces
-\item Self-tunable control technique does not need any intervention during control
-\item Tuning based on the operating conditions compensates the nonlinear plant behavior
-\item Implementation of the proposed tuning method on a laboratory heat exchanger 
-\item Control performance improved compared to utilizing only one explicit MPC
-\end{highlights}
-
-\begin{keyword}
-tunable explicit MPC \sep self-tunable technique \sep tuning parameter \sep heat exchanger \sep control performance
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
+%\end{abstract}
+%
+%%%Graphical abstract
+%\begin{graphicalabstract}
+%%\includegraphics{grabs}
+%\end{graphicalabstract}
+%
+%%%Research highlights
+%\begin{highlights}
+%% 3-5 highlights, every one should not exceed 85 characters including spaces
+%\item Self-tunable control technique does not need any intervention during control
+%\item Tuning based on the operating conditions compensates the nonlinear plant behavior
+%\item Implementation of the proposed tuning method on a laboratory heat exchanger 
+%\item Control performance improved compared to utilizing only one explicit MPC
+%\end{highlights}
+%
+%\begin{keyword}
+%tunable explicit MPC \sep self-tunable technique \sep tuning parameter \sep heat exchanger \sep control performance
+%%% keywords here, in the form: keyword \sep keyword
+%
+%%% PACS codes here, in the form: \PACS code \sep code
+%
+%%% MSC codes here, in the form: \MSC code \sep code
+%%% or \MSC[2008] code \sep code (2000 is the default)
+%
+%\end{keyword}
+%
+%\end{frontmatter}
 
@@
 
+\section*{Acknowledgements}
+This research is funded by the European Union’s Horizon Europe under grant no.
+101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, the Slovak Research and Development Agency under the project APVV-20-0261.
+
+\section*{Nomenclature}
+
+\subsection*{Symbols}
+\begin{center}
+	\begin{tabular}{ l l }
+$A$ & system state matrix \\
+$\widetilde{A}$ & extended system state matrix \\
+$B$ & system input matrix \\
+$\widetilde{B}$ & extended system input matrix \\
+$C$ & system output matrix \\
+$\widetilde{C}$ & extended system output matrix \\
+$d_{\max}$ & maximal deviation from the steady state \\
+TODO & odlisit max size of reference step change \\
+$F$ & slope of the affine control law \\
+$g$ & section of the affine control law \\
+$I$ & identity matrix \\	
+$k$ & step of the prediction horizon \\
+$N$ & prediction horizon \\
+$n_{\mathrm{u}}$ & size of system inputs \\
+$n_{\mathrm{y}}$ & size of system outputs \\
+$n_{\widetilde{\mathrm{x}}}$ & size of extended system states \\
+$Q_{\mathrm{x}}$ & penalty matrix of the built-in integrator \\
+$Q_{\mathrm{x,L}}$ & lower bound on the penalty matrix of the built-in integrator \\
+$Q_{\mathrm{x,U}}$ & upper bound on the penalty matrix of the built-in integrator \\
+$Q_{\mathrm{y}}$ & penalty matrix of the control error \\
+$Q_{\mathrm{y,L}}$ & lower bound on the penalty matrix of the control error \\
+$Q_{\mathrm{y,U}}$ & upper bound on the penalty matrix of the control error \\
+$R$ & penalty matrix of system inputs \\
+$R_{\mathrm{L}}$ & lower bound on the penalty matrix of system inputs \\
+$R_{\mathrm{U}}$ & upper bound on the penalty matrix of system inputs \\
+$\mathcal{R}$ & critical region \\
+$\mathbb{R}$ & Euclidean space of real numbers \\
+$t$ & time, s \\
+$t_{\epsilon}$ & settling time, s \\
+$T$ & temperature, $^{\circ}\mathrm{C}$ \\
+$T_{\mathrm{s}}$ & sampling time, s \\
+$T^{\mathrm{s}}$ & steady state of temperature, $^{\circ}\mathrm{C}$ \\
+$u$ & control inputs \\
+$u_{\mathrm{L}}$ & control inputs asscociated with the lower boundary controller\\
+$u_{\mathrm{U}}$ & control inputs asscociated with the upper boundary controller\\
+\end{tabular}
+\end{center}
+
+%% Page - break
+
+\begin{center}
+	\begin{tabular}{ l l }
+$U$ & voltage, \% \\
+$U^{\mathrm{s}}$ & steady state of voltage, \% \\
+$\mathcal{U}$ & set of control inputs \\
+$V$ & volume of heating medium, l \\
+$x$ & system states \\
+$\widetilde{x}$ & extended system states \\
+$x_{\mathrm{I}}$ & system states corresponding to the built-in integrator \\
+$y$ & system outputs \\
+$y_\mathrm{\max}$ & maximal value of system outputs \\
+$y_\mathrm{\min}$ & minimal value of system outputs \\
+$y_\mathrm{ref}$ & reference value of system outputs \\	
+$\mathcal{Y}$ & set of system outputs \\
+\textit{0} & zero matrix
+\end{tabular}
+\end{center}
+
+\subsection{Greek letters}
+\begin{center}
+	\begin{tabular}{ l l }
+		$\Delta_\mathrm{ref}$ & size of the reference change, $^{\circ}\mathrm{C}$ \\
+		$\rho$:	tuning factor \\
+		$\widetilde{\rho}$ & scaled tuning factor \\
+		$\rho_{\mathrm{s}}$ & splitting value of the tuning factor \\
+		$\sigma_{\max}$ & maximal overshoot, \% \\
+		$\theta$ & parameter of optimization problem \\
+		$\Theta$ & set of parameter values
+	\end{tabular}
+\end{center}
+
+\subsection*{Abbreviations}
+\begin{center}
+	\begin{tabular}{ l l }
+		MPC & model predictive control \\
+		ISE & integral square error \\
+		LTI & linear time-invariant \\
+	\end{tabular}
+\end{center}
+
 %% The Appendices part is started with the command \appendix;

### 2023-01-27 paper/elsarticle/main.tex
Review: Introduction

@@
 %\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys}
-%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a non-symmetric behavior}
+%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a asymmetric behavior}
 %
@@
 %%max 250 words!
+\textcolor{red}{TODO: Please, checkthe  word limit.}
+
 The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
-This paper provides a self-tunable technique that does not require any further tuning or interventions of the control engineer during operation.
-Based on the current operating conditions, the tuning parameter adjusts itself and scales the control input using linear interpolation.
-The adjustment of the tuning parameter depends on the reference value, which makes this strategy suitable for reference tracking problems.
+This paper provides a novel self-tunable control policy that does not require any further tuning or interventions of the control engineer during operation.
+Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
+The adjustment of the tuning parameter depends on the current reference value, which makes this strategy suitable for reference tracking problems.
 Furthermore, a novel technique for scaling the tuning parameter is proposed.
 It provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and non-symmetric behavior.
-To ensure offset-free control, the built-in integrator was included in the explicit MPC.
-The asymmetric behavior of the plant was compensated by tuning the controller's aggressivity, as the negativity or positivity of reference change was considered in the tuning process.
-The control performance decreased maximal overshoots/undershoots, integral square error, and settling time compared to control with only one controller.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+To ensure offset-free reference tracking control, the built-in integrator was included in the explicit MPC design.
+The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
+The designed self-tunable controller improved control performance by decreasing integral square error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-self-tunable) controller.
 %\end{abstract}
@@
 
-(len skopirovany text z jadra - hodil sa mi viac do Introduction, neskor mozno pouzijem) The benefit in form of lower computational complexity in the control phase comes hand in hand with a drawback.
-The size of the parametric solution may be so large, that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
+(len skopirovany text z jadra - hodil sa mi viac do Introduction, neskor mozno pouzijem)
+
+The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
+The size of the parametric solution may increase to the value that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
@@
 It is not taken into account, whether the reference change was positive or negative, i.e., whether it changed upwards or downwards.
-As many plants have non-symmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
+As many plants have asymmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
 
@@
 The suggested technique of tuning is suitable e.g.
-for systems with non-symmetric behavior, but can be used in any application, where ,,simple" tuning in the whole range of tuning parameter $\rho$ is not sufficient.
+for systems with asymmetric behavior, but can be used in any application, where ,,simple" tuning in the whole range of tuning parameter $\rho$ is not sufficient.
 
@@
 The voltage is set in percentage, while it is constrained from 20\% to 100\%.
-As the heat exchange is a nonlinear and non-symmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
+As the heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
 
@@
 
-The trajectories in Fig.~\ref{fig:CV_boundaries} show the non-symmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
+The trajectories in Fig.~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
 When applying the control associated with the lower bound $Q_\mathrm{y, L}$, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
@@
 Another novel contribution comes with splitting the interval of tuning parameter into two ranges, while both ranges are assigned to different operating conditions.
-The proposed method is implemented on a laboratory heat exchanger with nonlinear and non-symmetric behavior.
+The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The non-symmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
@@
 		MPC & model predictive control \\
-		ISE & integral square error \\
+		ISE & integral squared error \\
 		LTI & linear time-invariant \\

### 2023-01-27 paper/elsarticle/main.tex
GITIGNORE and clean-up

@@
 The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
-The size of the parametric solution may increase to the value that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
+The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
 
-\section{Preliminaries}
+[TODO: Please, write a paper structure]
+
+The paper is organized as follows...
+
+\section{Theoretical backgrounds}
+% \section{Preliminaries}
 \label{sec:preliminaries}
-In this section, the theoretical background necessary for this work is summarized.
+
+In this section, the theoretical backgrounds necessary for the proposed method  work is summarized.
 First, the explicit model predictive control is recalled.

### 2023-01-27 paper/elsarticle/main.tex
Review: Sec.2.1

@@
 
-In this section, the theoretical backgrounds necessary for the proposed method  work is summarized.
-First, the explicit model predictive control is recalled.
+In this section, the theoretical backgrounds necessary for the proposed method is summarized.
+First, the explicit model predictive control is briefly recalled.
 Next, the tunable technique of the approximated explicit model predictive control is introduced.
-Last but not least, the ideas of self-tunable technique of the approximated explicit MPC are presented.
+Finally, the ideas of self-tunable technique of the approximated explicit MPC are presented.
 
@@
 \label{sec:eMPC}
-Explicit model predictive control~\cite{Bemporad_automatica} represents a parametric solution of the model predictive control which makes it suitable for online implementation.
-As the explicit solution is available, it is not necessary to solve the optimization problem in every control step.
-As this work deals with practical implementation, let us consider the optimization problem in the following form:
+
+Explicit model predictive control~\cite{Bemporad_automatica} utilizes a parametric solution of the model predictive control introducing its application range towards the systems with the fast dynamics.
+Moreover, the explicit solution enables providing a rigorous analysis and certification of the closed-loop system stability, constraints satisfaction, etc.
+As the explicit solution is available, real-time solving of the optimization problem in every control step is omitted.
+As this work deals with the industrial-oriented implementation, consider the optimization problem in the following form:
 \begin{subequations}
@@
 \end{subequations}
-
 where $k$ denotes the step of the prediction horizon $N$. 
-The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically precomputed.
-Variables $\widetilde{x} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding extended system states, control inputs and system outputs, respectively.
-The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of extended linear time-invariant (LTI) system for given extended state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, extended input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and extended output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
-The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are sets of physical constraints on inputs and outputs, respectively.
+%
+To obtain the offset-free control results, the built-in integrator was included in the state-space model, e.g., see~\cite{Ruscio_MPC_integral}. 
+The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of augmented linear time-invariant (LTI) system for given augmented state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, augmented input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and augmented output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
+%
+Variables $\widetilde{x} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding augmented system states, control inputs and system outputs, respectively.
+%
+The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are convex polytopic sets of physical constraints on inputs and outputs, respectively.
 The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squarred control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
 The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
-To obtain the offset-free control results, the built-in integrator was included in the state-space model, see e.q.~\cite{Ruscio_MPC_integral}.
+%
 The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{x} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$. 
+%
+The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically pre-computed.
 
-The model extended with the built-in integrator in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} can be rewritten as:
+The augmented model of the controlled system with the built-in integrator in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} us rewritten as follows:
 \begin{subequations}
 	\begin{eqnarray} 
-		\label{eq:mpc_extended_model_x} 
+		\label{eq:mpc_augmented_model_x} 
 		\widetilde{x}_{k+1} &=& \begin{bmatrix} x_{k+1} \\ 	x_{\mathrm{I},k+1}\end{bmatrix} = \begin{bmatrix} A & \textit{0} \\ -T_\mathrm{s} C & I \end{bmatrix} \begin{bmatrix} x_{k} \\ x_{\mathrm{I},k} \end{bmatrix} + \begin{bmatrix} B \\ I \end{bmatrix} u_{k}, \\
-		\label{eq:mpc_extended_model_y}
+		\label{eq:mpc_augmented_model_y}
 		y_k &=& \begin{bmatrix} C & \textit{0} \end{bmatrix} \begin{bmatrix} x_{k} \\ x_{\mathrm{I},k} \end{bmatrix},
@@
 \end{subequations}
+where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time and matrices $A$, $B$, $C$ are well-known the state-space matrices that form the augmented LTI model.
+As the consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error are penalized, but also its integral, which leads to analogous offset-free reference tracking results as incorporating integral part in PID controller.
 
-where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time and matrices $A$, $B$, $C$ are well-known linear time-invariant state-space matrices that form the extended model.
-Thanks to this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error are penalized, but also its integral, which leads to similar results as incorporating integral part in PID controller.
-
-Solving the MPC quadratic optimization problem in Eq.~\eqref{eq:mpc_problem} parametrically leads to explicit solution in the form of piece-wise affine control law consisting of $r$ critical regions:
+Parametric solution of the optimization problem of the quadratic programming (QP) in~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piece-wise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $F_{i}$ and $g_{i}$ respectively are the slope and affine section of the corresponding control law.
-The piece-wise affine function from Eq.~\eqref{eq:PWA_control_law} is stored and used in the online, i.e., control phase.
-Based on identifying the critical region where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law.
+where $F_{i} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{x}}}$ and $g_{i}  \in \mathbb{R}^{n_{\mathrm{u}}}$ respectively are the slope and affine section of the corresponding control law.
+The PWA function defined in Eq.~\eqref{eq:PWA_control_law} is stored and recalled in the online phase, i.e., during the real-time control.
+Based on identifying the specific critical region $\mathcal{R}_{i}$, where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law in~\eqref{eq:PWA_control_law}.
 
-Note, many other formulations of the optimization problems are elaborated, mainly in the terms of cost functions.
-Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extendsion of the vector of parameters $\theta$ and therefore the explicit MPC complexity increases.
-Another option for offset-free tracking is also disturbance observer.
+Note, many other formulations of the optimization problems for the explicit MPC design, were mainly in the terms of the definition of the cost functions in~\eqref{eq:mpc_problem_cost}.
+Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$ and therefore also the complexity of the explicit MPC controller increases.
+Another option for offset-free tracking is introducing the disturbance estimation.
 For such an overview see e.g.
+
+\textcolor{red}{TODO: Please, fix}
+
 ...TODO. 
@@
 \label{sec:tunable}
+
 The aggressivity of the controller and whole nature of the control can be influenced by tuning the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
@@
 $A$ & system state matrix \\
-$\widetilde{A}$ & extended system state matrix \\
+$\widetilde{A}$ & augmented system state matrix \\
 $B$ & system input matrix \\
-$\widetilde{B}$ & extended system input matrix \\
+$\widetilde{B}$ & augmented system input matrix \\
 $C$ & system output matrix \\
-$\widetilde{C}$ & extended system output matrix \\
+$\widetilde{C}$ & augmented system output matrix \\
 $d_{\max}$ & maximal deviation from the steady state \\
@@
 $n_{\mathrm{y}}$ & size of system outputs \\
-$n_{\widetilde{\mathrm{x}}}$ & size of extended system states \\
+$n_{\widetilde{\mathrm{x}}}$ & size of augmented system states \\
 $Q_{\mathrm{x}}$ & penalty matrix of the built-in integrator \\
@@
 $x$ & system states \\
-$\widetilde{x}$ & extended system states \\
+$\widetilde{x}$ & augmented system states \\
 $x_{\mathrm{I}}$ & system states corresponding to the built-in integrator \\

### 2023-01-27 paper/elsarticle/main.tex
Review: Sec.2.2

@@
 
-[TODO: Please, write a paper structure]
+\textcolor{red}{[TODO: Please, clearly point out the main contributions]}
+
+This work directly extends our results presented in~\cite{self_tunable}, where the basic principles of the self-tunable approximated explicit MPC were introduced.
+Compared to~\cite{self_tunable}, we...
+
+\textcolor{red}{[TODO: Please, write a paper structure]}
 
@@
 
-\textcolor{red}{TODO: Please, fix}
+\textcolor{red}{[TODO: Please, fix.]}
 
@@
 
-The aggressivity of the controller and whole nature of the control can be influenced by tuning the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
-When the optimization problem is precomputed offline to obtain the parametric solution, it is not possible to tune the controller afterwards.
-As the operation conditions and demands on controller setup may differ throughout control, the ability to adjust the controller aggressivity can be very beneficial.
+The aggressivity of the controller and whole nature of the control is influenced by appropriate fine tuning of the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
+When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterwards without trading off a significant increase of the controller complexity or the performance loss.
+As the operation conditions and requirementson controller setup may differ throughout control, the ability to adjust the controller aggressivity can be very beneficial.
 
@@
 The boundary explicit controllers have the same structure and setup, except one of the penalty matrices -- the tuned one.
-The boundary matrices are diagonal square matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of penalty matrix eigenvalues, $L$ and $U$ denote the lower and upper boundary setup respectively, and $s$ is the rank of the tuned penalty matrix.
+The boundary penalty matrices are diagonal square matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
 
-When considering the penalty matrices from cost function~\eqref{eq:mpc_problem_cost}, the penalty matrices are scaled in the following way:
+When considering the penalty matrices in cost function~\eqref{eq:mpc_problem_cost}, these penalty matrices are scaled in the following way:
 \begin{subequations}
@@
 		\label{eq:tunable_R}
-		&~& R = (1-\rho)R_\mathrm{L} + \rho R_\mathrm{U}, \\
+		&~& R(t) = (1-\rho(t)) \, R_\mathrm{L} + \rho(t) \, R_\mathrm{U}, \\
 		\label{eq:tunable_Qx}
-		&~& Q_\mathrm{x} = (1-\rho)Q_\mathrm{x,L} + \rho Q_\mathrm{x,U}, \\
+		&~& Q_\mathrm{x}(t) = (1-\rho(t)) \, Q_\mathrm{x,L} + \rho(t) \, Q_\mathrm{x,U}, \\
 		\label{eq:tunable_Qy}
-		&~& Q_\mathrm{y} = (1-\rho)Q_\mathrm{y,L} + \rho Q_\mathrm{y,U},
+		&~& Q_\mathrm{y}(t) = (1-\rho(t)) \, Q_\mathrm{y,L} + \rho(t) \, Q_\mathrm{y,U},
 	\end{eqnarray}
 \end{subequations}
+where $\rho$ represents the tuning parameter such that $0 \le \rho \le 1$ holds.
+Based on the rules in~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
+From the implementation point of view, it is preferred to tune just a single penalty matrix, i.e., to store only two controllers corresponding to the boundary values of the selected penalty matrix.
+To determine which penalty matrix in~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance subject to the specific system and systematically tune all of the penalty matrices.
 
-where $\rho$ represents the tuning parameter and $0 \le \rho \le 1$ holds.
-Based on~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
-Note, it is practical to tune only one matrix, i.e., to store only two controllers corresponding to the boundary matrices.
-To determine which penalty matrix should be tuned, it is suggested to examine the control results subject to the specific system and to try systematic tuning of all the penalty matrices.
-
-When the tuning parameter $\rho$ is determined based on the current control conditions, the optimal control action is evaluated using the two optimal controllers.
-Based on the boundary control actions, the interpolated, i.e., tuned control action is calculated:
-\begin{subequations}
+When the tuning parameter $\rho$ is determined based on the current control conditions, the approximated optimal control action is evaluated using the two optimal controllers.
+Based on the boundary control actions, the interpolated, i.e., tuned control action is calculated using the convex combination:
+%\begin{subequations}
 	\begin{eqnarray}
 		\label{eq:tunable_u}
-		u = (1-\rho)u_\mathrm{L} + \rho u_\mathrm{U},
+		u(t) = (1-\rho(t)) \, u_\mathrm{L} + \rho(t) \, u_\mathrm{U},
 	\end{eqnarray}
-\end{subequations}
-
+%\end{subequations}
 where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller respectively.
-The tuning of the controller online comes with a cost of storing and evaluating two explicit controllers.
+The online tuning of the controller online comes with a cost of storing and evaluating two explicit controllers.
 Nevertheless, the ability to tune the controller may be more important in many practical applications.
 
-Note, the concept of explicit MPC tuning can be applied also to other MPC formulations, based on the current specific needs.
-In this paper, the penalty matrices of cost function~\eqref{eq:mpc_problem_cost} are considered, as it is necessary to satisfy offset-free reference tracking.
+We point out, the concept of explicit MPC tuning is applicable for a wide class of MPC design formulations, based on the current specific needs.
+Without loss of generality, hereafter, we consider the penalty matrices of cost function~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
 
 \begin{remark}
-	If stability guarantee and recursive feasibility is required, it is suggested to follow the instructions from \cite{Oravec_tunable}.
-In order to satisfy the requirements, the study introduces a procedure of choosing the terminal penalty and terminal set in the two boundary controllers.
+	If the asymptotic stability and recursive feasibility guarantees are required, we refer the reader to follow the instructions from \cite{Oravec_tunable}.
+In order to satisfy these requirements, the study introduces a procedure of computing the common terminal penalty and terminal set for the two boundary controllers.
 \end{remark}
@@
 \section*{Acknowledgements}
-This research is funded by the European Union’s Horizon Europe under grant no.
-101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+
 The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, the Slovak Research and Development Agency under the project APVV-20-0261.
+This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
 

### 2023-01-27 paper/elsarticle/main.tex
Review: Sec.2.3

@@
 %%max 250 words!
-\textcolor{red}{TODO: Please, checkthe  word limit.}
+
+\textcolor{red}{[ TODO: Please, prevent using ``When...''-formulation to often. ]}
+
+\textcolor{red}{[ TODO: Please, checkthe  word limit. ]}
 
@@
 
-\textcolor{red}{[TODO: Please, clearly point out the main contributions]}
+\textcolor{red}{[ TODO: Please, clearly point out the main contributions. ]}
 
@@
 
-\textcolor{red}{[TODO: Please, write a paper structure]}
+\textcolor{red}{[ TODO: Please, write a paper structure. ]}
 
@@
 
-\textcolor{red}{[TODO: Please, fix.]}
+\textcolor{red}{[ TODO: Please, fix. ]}
 
@@
 \label{sec:self_tunable}
+
+\textcolor{red}{[ TODO: How about ``upgrading'' this subsection into the Section? ]}
+
 The advantage of tunable controller brings a question of how to design the logic of setting the tuning parameter $\rho$.
@@
 
-The need for real-time controller tuning often arises from tracking a time-varying reference.
+The need for real-time controller tuning often arises from tracking a time-varying piece-wise constant (PWC) reference.
 The work~\cite{self_tunable} focuses on adjusting the penalty matrix when the reference value is changed.
@@
 
-The procedure of tuning the controller is based on evaluating the difference between the reference and the steady state, and using this deviation to scale the value of control action.
-First, the maximal absolute value of reference which can be set during control is defined.
-This value can be determined based on the general knowledge of future reference values.
-Another suggestion is to set the maximal deviation $d_{\max}$ simply based on the constraints on system outputs:
+Consider a single-input and single-output (SISO) system or a multiple-inputs and multiple-outputs (MIMO) system with a completely decoupled pairs of the control inputs and the system outputs. 
+Then, the procedure of tuning the controller is based on evaluating the different operating points between the current value of the reference and the system steady-state value.
+This deviation is considered to scale the value of control action.
+First, the maximal admissible absolute value of reference is defined.
+Analogous to the reference trajectory preview concept of MPC design, this value can be determined based on the general knowledge of the expected future reference values.
+Another suggestion is to fit the maximal deviation $d_{\max}$ based on the constraints on system outputs:
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable.
+where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, ie., zero corresponds to the system steady-state value.
 Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
-
 \begin{eqnarray}
@@
 Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
-As a result, the parameter $\rho$ represents a way how to normalize the deviation from steady state and is exploited to scale the penalty matrix or at the end of the day, the control action.
+As a consequence, the parameter $\rho$ represents a way how to normalize the deviation from the steady-state value and is exploited to scale the penalty matrix or, implicitly, to scale the aggressiveness of the control action.
 
 When considering tuning the control action based on Eq.~\eqref{eq:tunable_u}, a higher value of tuning parameter $\rho$ leads to approaching the upper boundary controller and vice versa.
-When tuning e.g.
-the matrix $Q_\mathrm{y}$ penalizing the control error, a higher ratio $\rho$ would lead to more aggressive control actions.
-When controlling to the reference values closer to the steady state, the parameter $\rho$ decreases and the control becomes sluggish.
+When tuning, e.g., the matrix $Q_\mathrm{y}$ penalizing the control error, a higher ratio $\rho$ would lead to more aggressive control actions.
+When operating with the reference value close to the system steady-state value, the parameter $\rho$ decreases and the control profiles becomes sluggish.
 
@@
 Note, the relations \eqref{eq:rho_self_tunable} and \eqref{eq:rho_max} operate with the absolute value of the reference.
-It is not taken into account, whether the reference change was positive or negative, i.e., whether it changed upwards or downwards.
+It is not taken into account, whether the reference change was positive or negative with respect to the system steady-state value placed in the origin, i.e., whether it changed upwards or downwards.
 As many plants have asymmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
@@
 	\begin{tabular}{ l l }
+		MIMO & multiple-inputs and multiple-outputs (system) \\
 		MPC  & model predictive control \\
 		ISE  & integral squared error \\
-		LTI & linear time-invariant \\
+		LTI  & linear time-invariant (system) \\
+		mp-QP& multi-parametric quadratic programming (problem) \\
+		PWA  & piece-wise affine (function) \\
+		PWC  & piece-wise constant (function) \\
+		QP   & quadratic programming (problem) \\
+		SISO & single-input and single-output (system) \\
 	\end{tabular}

### 2023-01-27 paper/elsarticle/main.tex
Review: Sec.3

@@
 		\label{eq:tunable_R}
-		&~& R(t) = (1-\rho(t)) \, R_\mathrm{L} + \rho(t) \, R_\mathrm{U}, \\
+		&~& R(k) = (1-\rho(k)) \, R_\mathrm{L} + \rho(k) \, R_\mathrm{U}, \\
 		\label{eq:tunable_Qx}
-		&~& Q_\mathrm{x}(t) = (1-\rho(t)) \, Q_\mathrm{x,L} + \rho(t) \, Q_\mathrm{x,U}, \\
+		&~& Q_\mathrm{x}(k) = (1-\rho(k)) \, Q_\mathrm{x,L} + \rho(k) \, Q_\mathrm{x,U}, \\
 		\label{eq:tunable_Qy}
-		&~& Q_\mathrm{y}(t) = (1-\rho(t)) \, Q_\mathrm{y,L} + \rho(t) \, Q_\mathrm{y,U},
+		&~& Q_\mathrm{y}(k) = (1-\rho(k)) \, Q_\mathrm{y,L} + \rho(k) \, Q_\mathrm{y,U},
 	\end{eqnarray}
@@
 		\label{eq:tunable_u}
-		u(t) = (1-\rho(t)) \, u_\mathrm{L} + \rho(t) \, u_\mathrm{U},
+		u(k) = (1-\rho(k)) \, u_\mathrm{L} + \rho(k) \, u_\mathrm{U},
 	\end{eqnarray}
@@
 		\label{eq:rho_max}
-		\rho = \max \left( \frac{\vert y_{\mathrm{ref}} \vert}{d_{\max}} \right).
+		\rho(k) = \max \left( \frac{\vert y_{\mathrm{ref}}(k) \vert}{d_{\max}} \right).
 	\end{eqnarray}	
@@
 First, a different way of tuning parameter calculation is introduced.
-Furthermore, an extended self-tunable technique is presented to scale the tuning parameter for applications, when it is beneficial to exploit a specific range of the tuning parameter in different operating conditions.
+Furthermore, an extended self-tunable technique is presented to scale the tuning parameter for industrial-oriented applications, when it is beneficial to exploit a specific range of the tuning parameter in different operating conditions.
 
@@
 \label{sec:self_tunable_delta_ref}
-The approach of self-tunable explicit MPC in~\cite{self_tunable} suggested tuning based on the reference value distance from the steady state.
+The approach of self-tunable explicit MPC in~\cite{self_tunable} suggested tuning based on the current reference value distance from the steady state.
 The aim is to compensate the nonlinear behavior of system, when using a simple linear prediction model.
-This work provides another way of the tuning parameter calculation based on the size of reference change.
+This work provides also another useful way of the real-time evaluation of the tuning parameter $\rho$ based on the size of reference change.
 When different sizes of reference step changes are made and the behavior of the closed-loop system is varying, it can be beneficial to inclue the size of the reference step change into the tuning procedure.
 
-In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be set during control operation:
+In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be realized during control operation:
 \begin{eqnarray}
 	\label{eq:rho_delta_ref}
-	\rho = \frac{\vert \Delta_{\mathrm{ref}} \vert}{d_{\max}},
+	\rho(k) = \frac{\vert \Delta_{\mathrm{ref}}(k) \vert}{d_{\max}},
 \end{eqnarray} 
-
-where $\Delta_{\mathrm{ref}} = y_{\mathrm{ref},k}-y_{\mathrm{ref},k-1}$ is the size of the reference change.
+where $\Delta_{\mathrm{ref}}(k) = y_{\mathrm{ref}}(k) - y_{\mathrm{ref}}(k-1)$ is the size of the reference step change.
 The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well.
-In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $d_{\max}$ as the maximal possible reference step.
-Analogously to the original approach, the maximal reference step can be set based on the general knowledge of future reference values.
+In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $d_{\max}$ as the maximal possible reference step change given by: $  d_{\max}(k) = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty} $.
+Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values.
 Another option is to exploit the information about the system constraints and set the parameter $d_{\max}$ according to Eq.~\eqref{eq:d_max}.
@@
 This paper provides further extension of the self-tuning method proposed in~\cite{self_tunable}.
-The suggested technique of tuning is suitable e.g.
-for systems with asymmetric behavior, but can be used in any application, where ,,simple" tuning in the whole range of tuning parameter $\rho$ is not sufficient.
+The suggested technique of tuning is suitable, e.g., for systems with asymmetric behavior, but can be used in any application, where ``simple'' tuning in the whole range of tuning parameter $\rho$ is not sufficient.
 
-The tuning method is based on splitting the interval of the tuning parameter $\rho$ in order to utilize different parts of the interval in different operating conditions.
-The adjusted tuning parameter $\widetilde{\rho}$ is then utilized to scale the control input according to Eq.~\eqref{eq:tunable_u} instead of the original value of tuning parameter $\rho$.
+The proposed self-tuning method is based on splitting the interval of the tuning parameter $\rho$ in order to utilize different parts of the interval in different operating conditions.
+Instead of the original value of tuning parameter $\rho$, the adjusted tuning parameter $\widetilde{\rho}$ is then utilized to scale the control input according to Eq.~\eqref{eq:tunable_u}.
+
+\textcolor{red}{[ TODO: Please, consider rearranging the following objects. Missing some formal requirements, such as: ``Given...'' ]}
 
@@
 \end{definition}
+
+\textcolor{red}{[ TODO: Please, consider spliting the Corollaries into the Lemma and Proof. ]}
 
@@
 The advantage of the proposed method remains in the self-tuning of the controller as in the approach from Section~\ref{sec:self_tunable}.
-Nevertheless, it is required to determine the splitting value of the tuning parameter $\rho_{\mathrm{s}}$ and assign the parts of the interval to the associated operating conditions.
+Nevertheless, it is required to appropriately determine the splitting value of the tuning parameter $\rho_{\mathrm{s}}$ and assign the parts of the interval to the associated operating conditions.
+
+\textcolor{red}{[ TODO: Please, consider rearranging the confusing Remark, as the task of the tuning is transformed into the Hessian updates. ]}
 
@@
 Therefore, it is possible to include the controller tuning in the procedure of computing the optimal control input.
-It should be also noted that with updating penalty matrices, the optimization problem has to be rebuilt into a form suitable for a solver, so sufficient computational time is required.
+It should be also noted that with real-time updating penalty matrices, the optimization problem has to be rebuilt into a form suitable for a solver, so sufficient computational time is required.
 \end{remark}

### 2023-01-27 paper/elsarticle/main.tex
Review: Sec.4

@@
 
-In this section, the results of the proposed tuning method are presented on an experimental implementation.
-The tuning strategy utilizes tuning parameter based n the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
+In this section, the results of the proposed self-tuning method are analyzed using an experimental implementation.
+The self-tuning strategy utilizes tuning parameter based on the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
 
-The plant on which the control was implemented is a laboratory liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Fig.~\ref{fig:HE}.
+The plant on which the control was implemented and analyzed is a laboratory counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
 The cold feed as well as heating medium are transported to the heat exchanger by two peristaltic pumps.
-The flow rate of the feed is constant, while the aim is to track the reference value of its temperature.
-Therefore, the controlled output is the feed temperature $T$ at the outlet of the heat exchanger and the control input is the voltage $U$ corresponding to the power of the heating medium pump.
-The voltage is set in percentage, while it is constrained from 20\% to 100\%.
+The flow rate of the feed of the cold medium (water) is constant, while the aim of control is to track the reference value of the cold medium temperature.
+Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger.
+The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium (water).
+The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
+The manipulated variable is constrained from 20\,\% to 100\,\% to respect the physical limitations of the operating conditions.
 As the heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
 
-The matrices of the linear state-space model of the plant, discretized with sampling time $T_\mathrm{s}$ = 1\,s, are
+The matrices of the linear state-space model of the plant are
 \begin{subequations}
@@
 	\begin{eqnarray}
-		A&=&\begin{bmatrix}
+		A = \begin{bmatrix}
 			0.839
-		\end{bmatrix}, \\
-		B&=&\begin{bmatrix}
+		\end{bmatrix}, \quad
+		B = \begin{bmatrix}
 			0.039
-		\end{bmatrix}, \\
-		C&=&\begin{bmatrix}
+		\end{bmatrix}, \quad
+		C = \begin{bmatrix}
 			1
-		\end{bmatrix}, \\
-		D&=&\begin{bmatrix}
-			0
-		\end{bmatrix}.
+		\end{bmatrix}, 
+%		\quad
+%		D = \begin{bmatrix}
+%			0
+%		\end{bmatrix}.
 		\end{eqnarray}
 \end{subequations}
-
-The constraints are considered in the terms of control inputs, i.e.
+considering the sampling time $T_\mathrm{s}$ = 1\,s. 
+The constraints are considered in the terms of control inputs
 \begin{eqnarray}
 \label{eq:u_const}
-	-15\% \le u \le 65\%.
+	-15\% \le u \le 65\%
 \end{eqnarray}
+where the variable $u$ represents the control inputs in the deviation form.
+The values of feed temperature and voltage of the heating medium pump corresponding to zero steady state are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
+To fully investigate the control performance of the pure self-tuning method, the constraints on the system states~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.
 
-Note, the variable $u$ represents the control inputs in the deviation form.
-The values of feed temperature and voltage of the heating medium pump corresponding to zero steady state are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
+The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setup.
+First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
+Based on the set of experimentally collected data, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the reference value.
+Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
+The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{x}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
+The prediction horizon $N$ was set to 20 control steps.
+The explicit MPC controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
+The controllers were implemented to track a time-varying PWC reference.
 
-The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for every MPC setup.
-The aim was to determine, which penalty matrix will be the tuned one.
-Based on observations, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the setpoint.
-The boundary values of matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
-The built-in integrator was penalized with $Q_\mathrm{x}$ = 1 and the control input with $R$ = 10.
-The prediction horizon $N$ was 20 steps long.
-The explicit model predictive controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
-The controllers were implemented to track a time-varying reference.
-For the first 200 seconds, the system was in the steady state.
+\textcolor{red}{[ TODO: Please, consider introducing the sequence of the reference values/control scenarios here. ]}
+
+For the initial 200 seconds, the system was in its steady-state value.
 After that, the reference changed its value twice upwards and twice downwards.
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
-The control results for both control setups are compared in Fig.~\ref{fig:CV_boundaries} for the controlled outputs, and in Fig.~\ref{fig:MV_boundaries} for the control inputs.
+The control profiles generated for the both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled outputs, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
+Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not to be saturated/truncated afterwards.
 
@@
 		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-		\caption{Controlled output trajectory for two boundary controllers. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+		\caption{Controlled variable: output cold medium temperature for two boundary controllers.
+The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
 		\label{fig:CV_boundaries}
@@
 		\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
-		\caption{Control input trajectory for two boundary controllers. The solid lines represent the voltage and the dashed lines represent the constraints.}
+		\caption{Manipulated variables: input hot medium flow-rate for two boundary controllers.
+The solid lines represent the voltage $U$ and the dashed lines represent the constraints $U_{\mathrm{bound}}$.}
 		\label{fig:MV_boundaries}
@@
 
-The trajectories in Fig.~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the process of heat exchange mainly when observing the overshoots and undershoots.
-When applying the control associated with the lower bound $Q_\mathrm{y, L}$, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
-On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
+The trajectories in Figure~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the plant of plate heat exchange mainly when observing the overshoots and undershoots.
+When applying the control inputs associated with the lower bound $Q_\mathrm{y, L}$ in~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
 
-These observations form the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$.
-The strategy follows the ideas summarized in Section~\ref{sec:self_tunable_new}.
-Utilizing the boundary controller with the penalty matrix $Q_\mathrm{y,L}$ is preferred when the reference changes upwards.
-On the contrary, the controller associated with $Q_\mathrm{y,U}$ is preferred in control with negative reference changes.
+These main experimental observations established the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$.
+The strategy follows the ideas summarized in Section~\ref{sec:self_tunable}.
+Therefore, utilizing the boundary controller with the penalty matrix $Q_\mathrm{y,L}$ is preferred when the reference changes upwards.
+On the contrary, the controller associated with $Q_\mathrm{y,U}$ is preferred for negative reference step changes.
 The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
-The last parameter that needed to be set was the maximal possible size of the reference step change $d_{\max}$, which was set to $15^{\circ}\mathrm{C}$.
+The remaining parameter that needed to be set was the maximal admissible size of the reference step change $d_{\max}$, which was experimentally determined to $15\,^{\circ}\mathrm{C}$.
 
-The control results of the selt-tunable technique compared to the boundary controllers can be seen in Fig.~\ref{fig:CV} for the controlled outputs, and in Fig.~\ref{fig:MV} for the control inputs.
+The control results of the self-tunable technique compared to the boundary controllers can be seen in Figure~\ref{fig:CV} for the controlled outputs, and in Figure~\ref{fig:MV} for the control inputs.
 It can be seen that the tuned controller combined the benefits of the two boundary controllers.
 The overshoots and undershoots were reduced, as in the first half of control the penalty matrix $Q_\mathrm{y}$ acquired value from the first half of the penalty interval.
-When tracking the reference with negative change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
-The similarity with the boundary controllers can be seen also on the control inputs trajectory.
-Note, the constraints on the input variable were satisfied as they were scaled using linear interpolation based on the boundary controllers which are constructed considering the contraints.
-
-TODO: what about state constraints?
+When tracking the reference with negative step change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
+The similarity with the boundary controllers can be seen also on the control inputs profiles.
+Note, the constraints on the input variable were satisfied as they were scaled using linear interpolation based on the boundary controllers which are constructed considering the input constraints.
 
@@
 The control performance was also investigated quantitatively.
-The Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria for the tuned and two boundary controllers.
-The control performance is evaluated for every reference step change respectively.
-The criteria are integral square error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$, settling time $t_{\epsilon}$ for 5\%-neighbourhood of the reference value, and the volume of the heating medium utilized for the corresponding control.
-To provide better readability of the results, the best (i.e.
-minimal) values are written in bold.
+The Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria computed for the two boundary controllers and for the self-tuned controller.
+The control performance is evaluated for each reference step change separately.
+The considered quality criteria are: sum-of-squared based criterion -- integral squared error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$, settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$, and the volume of the hot medium $V$ consumed for the corresponding control.
+To provide a better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
 
@@
 			\hline
-			\multirow{2}{*}{1} & 1000 & 714 & 33.50 & 16.5 & \textbf{2.12} \\
+			\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 714 & 33.50 & 16.5 & \textbf{2.12} \\
 			    & 100 & 867 & 16.65 & 12.5 & 2.36 \\ 
-			    & tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
+			    & self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
 			\hline
-			\multirow{2}{*}{2} & 1000 & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
 			    & 100 & 606 & 23.25 & 26.5 & 3.19 \\ 
-			    & tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
+			    & self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
 			\hline
-		    \multirow{2}{*}{3} & 1000 & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
+		    \multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
 				& 100 & 398 & 79.64 & 31 & \textbf{2.00} \\ 
-				& tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
+				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
 			\hline
-			\multirow{2}{*}{4} & 1000 & 1024 & 18.43 & 22.5 & 0.94 \\
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1000 & 1024 & 18.43 & 22.5 & 0.94 \\
 				& 100 & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
-				& tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10  
+				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10  
 		\end{tabular}
@@
 
-It can be seen in Table~\ref{tab:control_performance}, that real-time tuning of the controller helped to improve two to three criteria when tracking each reference value.
+As can be seen in Table~\ref{tab:control_performance}, that real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value.
 The cost for this is the energy associated with control.
 Although the integral square error, maximal overshoot/undershoot and settling time decreased, the volume of consumed heating medium did not.
-Nevertheless, the average deterioration in the terms of consumed heating medium is approximately~17\%.
+Nevertheless, the average deterioration in the terms of consumed heating medium is approximately by~17\,\%.
 
-The improvement or deterioration in percentage of using the tunable controller relative to the second best setup is summarized in Table~\ref{tab:improvement} for every reference step change separately.
+The relative improvement in percentage of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
 The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
@@
 	\begin{center}
-		\caption{Improvement or deterioration of the control performance in percentage.}
+		\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
 		\label{tab:improvement}
 		\begin{tabular}{c|c|c|c|c} 
-			Reference step change & $ISE$ & $\sigma_{\mathrm{max}}$ & $t_{\epsilon}$ & $V$ \\
+			Reference step change & $\Delta ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
 			\hline
-			1 & 5.04 & 8.77 & 24.00 & -12.26 \\ 
-			\hline
-			2 & 32.05 & 17.72 & -90.00 & -34.54 \\ 
-			\hline
-			3 & 24.08 & -29.97 & 0 & -4.48 \\ 
-			\hline
-			4 & 5.57 & 10.53 & 17.78 & -18.28  
+			35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C &  5 &  9 & 24 &$-12$ \\ 
+			% \hline
+			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32 & 18 &$-90$ & $-35$ \\ 
+			% \hline
+			50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 24 &$-30$& 0 &$-4$\\ 
+			% \hline
+			45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C &  6 & 11 & 18 &$-18$  
 		\end{tabular}
@@
 \end{table}
+%\begin{table}[h!]
+%	\begin{center}
+%		\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
+%		\label{tab:improvement}
+%		\begin{tabular}{c|c|c|c|c} 
+%			Reference step change & $\Delta ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
+%			\hline
+%			35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 5.04 & 8.77 & 24.00 & -12.26 \\ 
+%			\hline
+%			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32.05 & 17.72 & -90.00 & -34.54 \\ 
+%			\hline
+%			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 24.08 & -29.97 & 0 & -4.48 \\ 
+%			\hline
+%			45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C & 5.57 & 10.53 & 17.78 & -18.28  
+%		\end{tabular}
+%	\end{center}
+%\end{table}
 
-It can be seen that implementing a tunable controller leads to improved control performance in many criteria.
-Utilizing a controller with a scalable aggressivity according to the operating conditions leads in general to higher accuracy, lower overshoot and faster achieving the reference value.
+Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:control_performance}.
+In general, utilizing a proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy ($ISE$), lower value of the overshoots ($\sigma_{\mathrm{max}}$), and faster achieving the reference value ($t_{\epsilon}$).
 %It should be also noted that the deterioration of every criterium is calculated subject to the best out of \textit{two} other controllers.
 It follows that the evaluation is strict as in practice only one controller would be available.
-Although the volume of the heating medium is not saved in this control scenario, the improved control performance may lead to other benefits.
+Although the volume of the hot medium $V$ is not reduced in the considered control scenario, the improved control performance may lead to other benefits.
 
@@
 
+\textcolor{red}{[ TODO: How about to simply omit the evaluation of the volume $V$ and write something around these lines: ]}
+
+Compared to the considered non-self-tunable controllers, the generated control trajectories and the computed quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behaviour.
+For various operating conditions, the proposed self-tunable controller outperformed the conventional controllers in the means of the squared-error-based criterion ($ISE$) of the output temperature $T$ within a range $[5-30]$\,\%.
+Together with the reduced overshoots and settling times, the achieved improvements of the control performance enables non-negligible energy savings when the precision and the operating time to ensure the product with the required properties.
+Although the analyzed extensive case study was realized considering the laboratory scaled heat exhcnager plant, the introduced self-tunable control policy enables significant reduction of the corresponding carbon footprint emissions in the industrial applications.
+
 \section{Conclusion}
 \label{sec:conclusion}
+
 This paper deals with the experimental implementation of tunable approximated explicit model predictive control and provides a technique for self-tuning controller design.
@@
 $T$ & temperature, $^{\circ}\mathrm{C}$ \\
+$T_{\mathrm{ref}}$ & sampling time, s \\
 $T_{\mathrm{s}}$ & sampling time, s \\
@@
 $u$ & control inputs \\
-$u_{\mathrm{L}}$ & control inputs asscociated with the lower boundary controller\\
-$u_{\mathrm{U}}$ & control inputs asscociated with the upper boundary controller\\
 \end{tabular}
@@
 	\begin{tabular}{ l l }
+$u_{\mathrm{L}}$ & control inputs asscociated with the lower boundary controller\\
+$u_{\mathrm{U}}$ & control inputs asscociated with the upper boundary controller\\
 $U$ & voltage, \% \\
+$U_{\mathrm{bound}}$ & steady state of voltage, \% \\
 $U^{\mathrm{s}}$ & steady state of voltage, \% \\

### 2023-01-27 paper/elsarticle/main.tex
Review: Conclusions

@@
 
+\textcolor{red}{[ TODO: Please, make consistent notation of equations: Eq-based vs. non-Eq notation. ]}
+
 \textcolor{red}{[ TODO: Please, checkthe  word limit. ]}
@@
 (len skopirovany text z jadra - hodil sa mi viac do Introduction, neskor mozno pouzijem)
+
+\textcolor{red}{[ TODO: We need a well-elaborated introduction/review to strongly motivate our control approach.
+Please, take into account the industrial-oriented reviewers, mostly experts in the field of the chemical engineering (heat exchangers and energy balances).
+]}
 
@@
 \label{sec:self_tunable_rho_scaling}
+
+\textcolor{red}{[ TODO: Please, fix. ]}
+
 \noindent TODO: co ak nepriama umera? \\
@@
 
-The plant on which the control was implemented and analyzed is a laboratory counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
+The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
 The cold feed as well as heating medium are transported to the heat exchanger by two peristaltic pumps.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:conclusion}
 
-This paper deals with the experimental implementation of tunable approximated explicit model predictive control and provides a technique for self-tuning controller design.
+This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provides a strategy for an effective self-tuning controller design.
 Based on the current reference value, the tuning parameter is scaled using linear interpolation.
-The previously published paper related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the steady state.
+The previously published work related to the self-tunable explicit MPC suggested tuning just based on the distance of the reference value from the system steady-state value.
 This paper presents a novel idea of tuning based on the size of reference step change.
-The tuning procedures aim to compensate for the nonlinear behavior of the controlled system.
-The tuning parameter is updated when the reference changes.
+The self-tuning algorithm aims to compensate for the nonlinear behavior of the controlled system.
+The self-tuning parameter is updated when the reference changes.
 It is calculated as the ratio between the size of the reference change and the maximal possible size of the reference change, which is specified before operation.
-Another novel contribution comes with splitting the interval of tuning parameter into two ranges, while both ranges are assigned to different operating conditions.
+Another novel contribution addresses the challenging control problem of the asymmetric system behaviour by splitting the interval of tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
 The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
@@
 On the contrary, when the reference changed downwards, the control input was tuned to approach the control input from the boundary controller with the upper bound on the penalty matrix.
-To investigate the control results properly, the control performance was evaluated quantitatively.
-Compared to control with only one controller, the self-tunable technique helped to decrease the maximal overshoots/undershoots, integral square error, and settling time.
+To investigate the control results properly, the control performance was evaluated also quantitatively.
+Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the sum-of-squared control error, maximal overshoots/undershoots, and settling time.
+As the consqquence, the self-tunable controllers enables significant energy savings and the corresponding reduction of the carbon footprint emissions in the industrial applications.
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 

### 2023-01-27 paper/elsarticle/main.tex
Review: Grammarly

@@
 
-%% TODO: UNCOMMENT THIS SECTION TO COMPILE ALSO INITIAL PART OF THE PAPAER
+	%% TODO: UNCOMMENT THIS SECTION TO COMPILE ALSO INITIAL PART OF THE PAPER
 	%
@@
 		%
-%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys}
-%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with a asymmetric behavior}
+		%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analyses}
+		%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behaviour}
 		%
@@
 It provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behaviour.
 To ensure offset-free reference tracking control, the built-in integrator was included in the explicit MPC design.
-The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
+The asymmetric behaviour of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
 The designed self-tunable controller improved control performance by decreasing integral square error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-self-tunable) controller.
@@
 			%\item Self-tunable control technique does not need any intervention during control
-%\item Tuning based on the operating conditions compensates the nonlinear plant behavior
+			%\item Tuning based on the operating conditions compensates the nonlinear plant behaviour
 			%\item Implementation of the proposed tuning method on a laboratory heat exchanger 
@@
 	\textcolor{red}{[ TODO: We need a well-elaborated introduction/review to strongly motivate our control approach.
-Please, take into account the industrial-oriented reviewers, mostly experts in the field of the chemical engineering (heat exchangers and energy balances).
+Please, take into account the industrial-oriented reviewers - mostly the experts in the field of chemical engineering (heat exchangers and energy balances).
 ]}
@@
 	The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
-The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
+The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) the memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
@@
 
-In this section, the theoretical backgrounds necessary for the proposed method is summarized.
+	In this section, the theoretical backgrounds necessary for the proposed method are summarized.
 First, the explicit model predictive control is briefly recalled.
 Next, the tunable technique of the approximated explicit model predictive control is introduced.
-Finally, the ideas of self-tunable technique of the approximated explicit MPC are presented.
+Finally, the ideas of a self-tunable technique of the approximated explicit MPC are presented.
 
@@
 
-Explicit model predictive control~\cite{Bemporad_automatica} utilizes a parametric solution of the model predictive control introducing its application range towards the systems with the fast dynamics.
-Moreover, the explicit solution enables providing a rigorous analysis and certification of the closed-loop system stability, constraints satisfaction, etc.
+	Explicit model predictive control~\cite{Bemporad_automatica} utilizes a parametric solution of the model predictive control introducing its application range towards the systems with fast dynamics.
+Moreover, the explicit solution enables providing rigorous analysis and certification of the closed-loop system stability, constraints satisfaction, etc.
 As the explicit solution is available, real-time solving of the optimization problem in every control step is omitted.
-As this work deals with the industrial-oriented implementation, consider the optimization problem in the following form:
+As this work deals with industrial-oriented implementation, consider the optimization problem in the following form:
 	\begin{subequations}
@@
 	To obtain the offset-free control results, the built-in integrator was included in the state-space model, e.g., see~\cite{Ruscio_MPC_integral}. 
-The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of augmented linear time-invariant (LTI) system for given augmented state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, augmented input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and augmented output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
+	The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of augmented linear time-invariant (LTI) system for a given augmented state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, augmented input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and augmented output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
 	%
@@
 	The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are convex polytopic sets of physical constraints on inputs and outputs, respectively.
-The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squarred control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
 The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
@@
 	where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time and matrices $A$, $B$, $C$ are well-known the state-space matrices that form the augmented LTI model.
-As the consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error are penalized, but also its integral, which leads to analogous offset-free reference tracking results as incorporating integral part in PID controller.
+As the consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error is penalized, but also an integrated value, which leads to analogous offset-free reference tracking results as incorporating an integral part in PID controller.
 
-Parametric solution of the optimization problem of the quadratic programming (QP) in~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piece-wise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
+	The parametric solution of the optimization problem of the quadratic programming (QP) in~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
 	\begin{eqnarray}
@@
 Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$ and therefore also the complexity of the explicit MPC controller increases.
-Another option for offset-free tracking is introducing the disturbance estimation.
+Another option for offset-free tracking is introducing disturbance estimation.
 For such an overview see e.g.
@@
 
-The aggressivity of the controller and whole nature of the control is influenced by appropriate fine tuning of the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
-When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterwards without trading off a significant increase of the controller complexity or the performance loss.
-As the operation conditions and requirementson controller setup may differ throughout control, the ability to adjust the controller aggressivity can be very beneficial.
+	The aggressivity of the controller and the whole nature of the control is influenced by appropriate fine-tuning of the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
+When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterwards without trading off a significant increase in the controller complexity or the performance loss.
+As the operation conditions and requirements of controller setup may differ throughout the control, the ability to adjust the controller's aggressivity can be very beneficial.
 
@@
 These control actions result from evaluating two boundary explicit MPCs.
-The boundary explicit controllers have the same structure and setup, except one of the penalty matrices -- the tuned one.
+The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices -- the tuned one.
 The boundary penalty matrices are diagonal square matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
@@
 	where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller respectively.
-The online tuning of the controller online comes with a cost of storing and evaluating two explicit controllers.
+The online tuning of the controller online comes with the cost of storing and evaluating two explicit controllers.
 Nevertheless, the ability to tune the controller may be more important in many practical applications.
 
-We point out, the concept of explicit MPC tuning is applicable for a wide class of MPC design formulations, based on the current specific needs.
+	We point out, the concept of explicit MPC tuning is applicable to a wide class of MPC design formulations, based on the current specific needs.
 Without loss of generality, hereafter, we consider the penalty matrices of cost function~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
@@
 		If the asymptotic stability and recursive feasibility guarantees are required, we refer the reader to follow the instructions from \cite{Oravec_tunable}.
-In order to satisfy these requirements, the study introduces a procedure of computing the common terminal penalty and terminal set for the two boundary controllers.
+In order to satisfy these requirements, the study introduces a procedure for computing the common terminal penalty and terminal set for the two boundary controllers.
 	\end{remark}
@@
 
-The advantage of tunable controller brings a question of how to design the logic of setting the tuning parameter $\rho$.
+	The advantage of a tunable controller brings a question of how to design the logic of setting the tuning parameter $\rho$.
 In this section, the idea of online self-tuning is summarized~\cite{self_tunable}.
@@
 The work~\cite{self_tunable} focuses on adjusting the penalty matrix when the reference value is changed.
-The further the reference value is from the steady state, the more aggressive controller is tuned.
-The idea behind the suggested scaling liest in compensation of the nonlinear behavior of the system.
+The further the reference value is from the steady state, the more aggressively the controller is tuned.
+The idea behind the suggested scaling lies in compensation for the nonlinear behaviour of the system.
 
-Consider a single-input and single-output (SISO) system or a multiple-inputs and multiple-outputs (MIMO) system with a completely decoupled pairs of the control inputs and the system outputs. 
+	Consider a single-input and single-output (SISO) system or a multiple-inputs and multiple-outputs (MIMO) system with completely decoupled pairs of the control inputs and the system outputs. 
 	Then, the procedure of tuning the controller is based on evaluating the different operating points between the current value of the reference and the system steady-state value.
 This deviation is considered to scale the value of control action.
-First, the maximal admissible absolute value of reference is defined.
+First, the maximal admissible absolute value of the reference is defined.
 Analogous to the reference trajectory preview concept of MPC design, this value can be determined based on the general knowledge of the expected future reference values.
@@
 When tuning, e.g., the matrix $Q_\mathrm{y}$ penalizing the control error, a higher ratio $\rho$ would lead to more aggressive control actions.
-When operating with the reference value close to the system steady-state value, the parameter $\rho$ decreases and the control profiles becomes sluggish.
+When operating with the reference value close to the system steady-state value, the parameter $\rho$ decreases and the control profiles become sluggish.
 
 	\begin{remark}
-	The parameter $d_{\max}$ is vector in general, as it depends on the size of system outputs.
+		In general, the parameter $d_{\max}$ is a vector, as it depends on the size of the system outputs.
 If $d_{\max}$ is scalar, the parameter $\rho$ is scalar as well and can be directly utilized to scale the control action.
@@
 It is not taken into account, whether the reference change was positive or negative with respect to the system steady-state value placed in the origin, i.e., whether it changed upwards or downwards.
-As many plants have asymmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
+As many plants have asymmetric behaviour, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
 
@@
 	\label{sec:methodology}
-This section extends the ideas of self-tunable explicit MPC in order to improve the control performance.
+	This section extends the ideas of self-tunable explicit MPC in order to improve control performance.
 First, a different way of tuning parameter calculation is introduced.
@@
 	The approach of self-tunable explicit MPC in~\cite{self_tunable} suggested tuning based on the current reference value distance from the steady state.
-The aim is to compensate the nonlinear behavior of system, when using a simple linear prediction model.
+The aim is to compensate for the nonlinear behaviour of a system when using a simple linear prediction model.
 This work provides also another useful way of the real-time evaluation of the tuning parameter $\rho$ based on the size of reference change.
-When different sizes of reference step changes are made and the behavior of the closed-loop system is varying, it can be beneficial to inclue the size of the reference step change into the tuning procedure.
+When different sizes of reference step changes are made and the behaviour of the closed-loop system is varying, it can be beneficial to include the size of the reference step change in the tuning procedure.
 
-In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be realized during control operation:
+	In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be realized during the control operation:
 	\begin{eqnarray}
@@
 
-Note, only absolute value of $\Delta_{\mathrm{ref}}$ and $d_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
+	Note, only the absolute value of $\Delta_{\mathrm{ref}}$ and $d_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
 
@@
 
-\subsection{Self-tunable technique for systems with asymmetric behavior}
+	\subsection{Self-tunable technique for systems with asymmetric behaviour}
 	\label{sec:self_tunable_rho_scaling}
@@
 
-This paper provides further extension of the self-tuning method proposed in~\cite{self_tunable}.
-The suggested technique of tuning is suitable, e.g., for systems with asymmetric behavior, but can be used in any application, where ``simple'' tuning in the whole range of tuning parameter $\rho$ is not sufficient.
+	This paper provides a further extension of the self-tuning method proposed in~\cite{self_tunable}.
+The suggested technique of tuning is suitable, e.g., for systems with asymmetric behaviour, but can be used in any application, where ``simple'' tuning in the whole range of tuning parameter $\rho$ is not sufficient.
 
@@
 When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$.
-In such way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value.
+In such a way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value.
 Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
@@
 When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$.
-In such way, the parameter $\rho$ can be scaled in the second part of the interval from to the splitting value up to 1.
+In such a way, the parameter $\rho$ can be scaled in the second part of the interval from the splitting value up to 1.
 Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
@@
 	The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
-The cold feed as well as heating medium are transported to the heat exchanger by two peristaltic pumps.
+The cold feed as well as a heating medium are transported to the heat exchanger by two peristaltic pumps.
 The flow rate of the feed of the cold medium (water) is constant, while the aim of control is to track the reference value of the cold medium temperature.
@@
 The manipulated variable is constrained from 20\,\% to 100\,\% to respect the physical limitations of the operating conditions.
-As the heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
+As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
 
@@
 			\end{bmatrix}, 
-%		\quad
-%		D = \begin{bmatrix}
-%			0
-%		\end{bmatrix}.
+			%\quad
+			%D = \begin{bmatrix}
+				%0
+				%\end{bmatrix}.
 		\end{eqnarray}
@@
 	where the variable $u$ represents the control inputs in the deviation form.
-The values of feed temperature and voltage of the heating medium pump corresponding to zero steady state are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
+The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
 	To fully investigate the control performance of the pure self-tuning method, the constraints on the system states~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.
 
-The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setup.
+	The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
 	First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
@@
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
-The control profiles generated for the both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled outputs, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
-Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not to be saturated/truncated afterwards.
+The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled outputs, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
+	Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterwards.
 
@@
 	The control performance was also investigated quantitatively.
-The Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria computed for the two boundary controllers and for the self-tuned controller.
+Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria computed for the two boundary controllers and for the self-tuned controller.
 The control performance is evaluated for each reference step change separately.
 The considered quality criteria are: sum-of-squared based criterion -- integral squared error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$, settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$, and the volume of the hot medium $V$ consumed for the corresponding control.
-To provide a better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
+To provide better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
 
@@
 
-The relative improvement in percentage of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
+	The relative improvement in the percentage of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
 The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
@@
 	%\begin{table}[h!]
-%	\begin{center}
-%		\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
-%		\label{tab:improvement}
-%		\begin{tabular}{c|c|c|c|c} 
-%			Reference step change & $\Delta ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
-%			\hline
-%			35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 5.04 & 8.77 & 24.00 & -12.26 \\ 
-%			\hline
-%			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32.05 & 17.72 & -90.00 & -34.54 \\ 
-%			\hline
-%			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 24.08 & -29.97 & 0 & -4.48 \\ 
-%			\hline
-%			45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C & 5.57 & 10.53 & 17.78 & -18.28  
-%		\end{tabular}
-%	\end{center}
+		%\begin{center}
+			%\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
+			%\label{tab:improvement}
+			%\begin{tabular}{c|c|c|c|c} 
+				%Reference step change & $\Delta ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
+				%\hline
+				%35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 5.04 & 8.77 & 24.00 & -12.26 \\ 
+				%\hline
+				%45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32.05 & 17.72 & -90.00 & -34.54 \\ 
+				%\hline
+				%45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 24.08 & -29.97 & 0 & -4.48 \\ 
+				%\hline
+				%45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C & 5.57 & 10.53 & 17.78 & -18.28  
+				%\end{tabular}
+			%\end{center}
 		%\end{table}
@@
 	For various operating conditions, the proposed self-tunable controller outperformed the conventional controllers in the means of the squared-error-based criterion ($ISE$) of the output temperature $T$ within a range $[5-30]$\,\%.
-Together with the reduced overshoots and settling times, the achieved improvements of the control performance enables non-negligible energy savings when the precision and the operating time to ensure the product with the required properties.
-Although the analyzed extensive case study was realized considering the laboratory scaled heat exhcnager plant, the introduced self-tunable control policy enables significant reduction of the corresponding carbon footprint emissions in the industrial applications.
+	Together with the reduced overshoots and settling times, the achieved improvements in the control performance enable non-negligible energy savings when the precision and the operating time ensure the product with the required properties.
+Although the analyzed extensive case study was realized considering the laboratory-scaled heat exchanger plant, the introduced self-tunable control policy enables a significant reduction of the corresponding carbon footprint emissions in industrial applications.
 
@@
 
-This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provides a strategy for an effective self-tuning controller design.
+	This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provide a strategy for an effective self-tuning controller design.
 Based on the current reference value, the tuning parameter is scaled using linear interpolation.
@@
 This paper presents a novel idea of tuning based on the size of reference step change.
-The self-tuning algorithm aims to compensate for the nonlinear behavior of the controlled system.
+The self-tuning algorithm aims to compensate for the nonlinear behaviour of the controlled system.
 The self-tuning parameter is updated when the reference changes.
@@
 Another novel contribution addresses the challenging control problem of the asymmetric system behaviour by splitting the interval of tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
-The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behaviour.
 The non-symmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
@@
 Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the sum-of-squared control error, maximal overshoots/undershoots, and settling time.
-As the consqquence, the self-tunable controllers enables significant energy savings and the corresponding reduction of the carbon footprint emissions in the industrial applications.
+As a consequence, the self-tunable controllers enable significant energy savings and the corresponding reduction of carbon footprint emissions in industrial applications.
 
@@
 
-The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, the Slovak Research and Development Agency under the project APVV-20-0261.
+	The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, and the Slovak Research and Development Agency under the project APVV-20-0261.
 	This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
@@
 			$\widetilde{C}$ & augmented system output matrix \\
-$d_{\max}$ & maximal deviation from the steady state \\
+			$d_{\max}$ & maximal deviation from the steady-state value \\
 			TODO & odlisit max size of reference step change \\
@@
 		\begin{tabular}{ l l }
-$u_{\mathrm{L}}$ & control inputs asscociated with the lower boundary controller\\
-$u_{\mathrm{U}}$ & control inputs asscociated with the upper boundary controller\\
+			$u_{\mathrm{L}}$ & control inputs associated with the lower boundary controller\\
+			$u_{\mathrm{U}}$ & control inputs associated with the upper boundary controller\\
 			$U$ & voltage, \% \\
@@
 			$\Delta_\mathrm{ref}$ & size of the reference change, $^{\circ}\mathrm{C}$ \\
-		$\rho$:	tuning factor \\
+			$\rho$:tuning factor \\
 			$\widetilde{\rho}$ & scaled tuning factor \\

### 2023-01-29 paper/elsarticle/main.tex
Review: Some further TODOs

@@
 
+			\textcolor{red}{[ TODO: Please, emphasize the chemical engineering viewpoint, especially in Sec.4. ]}
+
+			\textcolor{red}{[ TODO: Please, extend the Control setup, as there is missing e.g., the initial laboratory temperature, the identification procedure of the system model, etc. ]}
+
 			\textcolor{red}{[ TODO: Please, prevent using ``When...''-formulation to often. ]}
@@
 
-			\textcolor{red}{[ TODO: Please, checkthe  word limit. ]}
+			\textcolor{red}{[ TODO: Please, check the word limit of Abstract. ]}
 
@@
 
+	\textcolor{red}{[ TODO: How about the following table notation? ]}
+
+	\begin{table}[h!]
+		\begin{center}
+			\caption{Control performance criteria.}
+			\label{tab:control_performance}
+			\begin{tabular}{c|c|c|c|c|c} 
+				Reference step change & Explicit MPC controller & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
+				\hline
+				\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 714 & 33.50 & 16.5 & \textbf{2.12} \\
+				& damped & 867 & 16.65 & 12.5 & 2.36 \\ 
+				& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
+				\hline
+				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & aggressive & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
+				& damped & 606 & 23.25 & 26.5 & 3.19 \\ 
+				& self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
+				\hline
+				\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
+				& damped & 398 & 79.64 & 31 & \textbf{2.00} \\ 
+				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
+				\hline
+				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & aggressive & 1024 & 18.43 & 22.5 & 0.94 \\
+				& damped & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
+				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10 
+			\end{tabular}
+		\end{center}
+	\end{table}
+
 	\begin{table}[h!]

### 2023-01-30 paper/elsarticle/main.tex
paper:minor updates

@@
 
-			\textcolor{red}{[ TODO: Please, prevent using ``When...''-formulation to often. ]}
-
-			\textcolor{red}{[ TODO: Please, make consistent notation of equations: Eq-based vs. non-Eq notation. ]}
-
-			\textcolor{red}{[ TODO: Please, check the word limit of Abstract. ]}
-
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
@@
 	To obtain the offset-free control results, the built-in integrator was included in the state-space model, e.g., see~\cite{Ruscio_MPC_integral}. 
-	The prediction model in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of augmented linear time-invariant (LTI) system for a given augmented state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, augmented input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and augmented output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
+	The prediction model in Eq.~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} has the form of augmented linear time-invariant (LTI) system for a given augmented state matrix $\widetilde{A} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\widetilde{\mathrm{x}}}}$, augmented input matrix $\widetilde{B} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}} \times n_{\mathrm{u}}}$ and augmented output matrix $\widetilde{C} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\widetilde{\mathrm{x}}}}$.
 	%
@@
 
-	The augmented model of the controlled system with the built-in integrator in~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} us rewritten as follows:
+	The augmented model of the controlled system with the built-in integrator in Eq.~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} us rewritten as follows:
 	\begin{subequations}
@@
 
-	The parametric solution of the optimization problem of the quadratic programming (QP) in~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
+	The parametric solution of the optimization problem of the quadratic programming (QP) in Eq.~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
 	\begin{eqnarray}
@@
 The PWA function defined in Eq.~\eqref{eq:PWA_control_law} is stored and recalled in the online phase, i.e., during the real-time control.
-Based on identifying the specific critical region $\mathcal{R}_{i}$, where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law in~\eqref{eq:PWA_control_law}.
+Based on identifying the specific critical region $\mathcal{R}_{i}$, where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law in Eq.~\eqref{eq:PWA_control_law}.
 
-	Note, many other formulations of the optimization problems for the explicit MPC design, were mainly in the terms of the definition of the cost functions in~\eqref{eq:mpc_problem_cost}.
+	Note, many other formulations of the optimization problems for the explicit MPC design, were mainly in the terms of the definition of the cost functions in Eq.~\eqref{eq:mpc_problem_cost}.
 Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$ and therefore also the complexity of the explicit MPC controller increases.
@@
 
-	The aggressivity of the controller and the whole nature of the control is influenced by appropriate fine-tuning of the penalty matrices in the optimization problem~\eqref{eq:mpc_problem}.
+	The aggressivity of the controller and the whole nature of the control is influenced by appropriate fine-tuning of the penalty matrices in the optimization problem in Eq.~\eqref{eq:mpc_problem}.
 When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterwards without trading off a significant increase in the controller complexity or the performance loss.
@@
 
-	When considering the penalty matrices in cost function~\eqref{eq:mpc_problem_cost}, these penalty matrices are scaled in the following way:
+	Let us consider the penalty matrices in cost function in Eq.~\eqref{eq:mpc_problem_cost}. The penalty matrices are scaled in the following way:
 	\begin{subequations}
@@
 	where $\rho$ represents the tuning parameter such that $0 \le \rho \le 1$ holds.
-Based on the rules in~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
+Based on the rules in Eq.~\eqref{eq:tunable_matrices}, it is possible to choose online any controller setup from the lower to the upper boundary of the tuned matrix.
 From the implementation point of view, it is preferred to tune just a single penalty matrix, i.e., to store only two controllers corresponding to the boundary values of the selected penalty matrix.
-To determine which penalty matrix in~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance subject to the specific system and systematically tune all of the penalty matrices.
+To determine which penalty matrix in Eq.~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance subject to the specific system and systematically tune all of the penalty matrices.
 
@@
 	We point out, the concept of explicit MPC tuning is applicable to a wide class of MPC design formulations, based on the current specific needs.
-Without loss of generality, hereafter, we consider the penalty matrices of cost function~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
+Without loss of generality, hereafter, we consider the penalty matrices of cost function in Eq.~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
 
@@
 		\label{eq:rho_self_tunable}
-		\rho = \frac{\vert y_{\mathrm{ref}} \vert}{d_{\max}}.
+		\rho = \frac{\vert y_{\mathrm{ref}(k)} \vert}{d_{\max}}.
 	\end{eqnarray}
@@
 
-	Note, the relations \eqref{eq:rho_self_tunable} and \eqref{eq:rho_max} operate with the absolute value of the reference.
+	Note, the relations in Eq.~\eqref{eq:rho_self_tunable} and Eq.~\eqref{eq:rho_max} operate with the absolute value of the reference.
 It is not taken into account, whether the reference change was positive or negative with respect to the system steady-state value placed in the origin, i.e., whether it changed upwards or downwards.
@@
 	\begin{definition}
-		If the tuning parameter is scaled in the first part of the interval, i.e., $\langle 0, \rho_{\mathrm{s}} \rangle$, where $\rho_{\mathrm{s}}$ is the splitting value of the tuning parameter, the following relation is used to adjust the tuning parameter:
+		Given the current parameter value $\rho$.
+If the tuning parameter is scaled in the first part of the interval, i.e., $\langle 0, \rho_{\mathrm{s}} \rangle$, where $\rho_{\mathrm{s}}$ is the splitting value of the tuning parameter interval, the following relation is used to adjust the tuning parameter:
 		\begin{eqnarray}
@@
 	\begin{definition}
+		Given the current parameter value $\rho$.
 If the tuning parameter is scaled in the second part of the interval, i.e., $\langle \rho_{\mathrm{s}}, 1 \rangle$, the following relation is used to adjust the tuning parameter:
@@
 
-	The matrices of the linear state-space model of the plant are
+	\textcolor{red}{The system was identified by experimental identification. More specifically, several step responses were made.} The matrices of the linear state-space model of the plant are
 	\begin{subequations}
@@
 The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
-	To fully investigate the control performance of the pure self-tuning method, the constraints on the system states~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.
+	To fully investigate the control performance of the pure self-tuning method, the constraints on the system states in Eq.~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.
 
@@
 	The controllers were implemented to track a time-varying PWC reference. 
-
-	\textcolor{red}{[ TODO: Please, consider introducing the sequence of the reference values/control scenarios here. ]}
-
-	For the initial 200 seconds, the system was in its steady-state value.
+	For the initial 200 seconds, the reference temperature was the steady-state value.
 After that, the reference changed its value twice upwards and twice downwards.
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
+Specifically, the reference temperature values were 35$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 50$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$ and 35$^{\circ}\mathrm{C}$.
 The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled outputs, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
@@
 			\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-			\caption{Controlled variable: output cold medium temperature for two boundary controllers.
+			\caption{\textcolor{red} {Controlled variable}: output cold medium temperature for two boundary controllers.
 The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
@@
 			\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
-			\caption{Manipulated variables: input hot medium flow-rate for two boundary controllers.
-The solid lines represent the voltage $U$ and the dashed lines represent the constraints $U_{\mathrm{bound}}$.}
+			\caption{\textcolor{red} {Manipulated variables}: input hot medium flow-rate for two boundary controllers.
+The solid lines represent the voltage $U$ and the dashed lines represent the constraints \textcolor{red} {$U_{\mathrm{bound}}$}.}
 			\label{fig:MV_boundaries}
@@
 	The trajectories in Figure~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the plant of plate heat exchange mainly when observing the overshoots and undershoots.
-When applying the control inputs associated with the lower bound $Q_\mathrm{y, L}$ in~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
-On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
+When applying the control inputs associated with the lower bound $Q_\mathrm{y, L}$ in Eq.~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
 
@@
 			\begin{tabular}{c|c|c|c|c} 
-				Reference step change & $\Delta ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
+				Reference step change & $\textcolor{red} {\Delta} ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
 				\hline
@@
 	Compared to the considered non-self-tunable controllers, the generated control trajectories and the computed quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behaviour.
-	For various operating conditions, the proposed self-tunable controller outperformed the conventional controllers in the means of the squared-error-based criterion ($ISE$) of the output temperature $T$ within a range $[5-30]$\,\%.
+	For various operating conditions, the proposed self-tunable controller outperformed the conventional controllers in the means of the squared-error-based criterion ($ISE$) of the output temperature $T$ within a range $[5-32]$\,\%.
 	Together with the reduced overshoots and settling times, the achieved improvements in the control performance enable non-negligible energy savings when the precision and the operating time ensure the product with the required properties.
@@
 			$d_{\max}$ & maximal deviation from the steady-state value \\
-			TODO & odlisit max size of reference step change \\
+			\textcolor{red} {TODO} & odlisit max size of reference step change \\
 			$F$ & slope of the affine control law \\
@@
 			$U$ & voltage, \% \\
-			$U_{\mathrm{bound}}$ & steady state of voltage, \% \\
+			$U_{\mathrm{bound}}$ & \textcolor{red} {steady state of voltage}, \% \\
 			$U^{\mathrm{s}}$ & steady state of voltage, \% \\
@@
 			$\Delta_\mathrm{ref}$ & size of the reference change, $^{\circ}\mathrm{C}$ \\
-			$\rho$:tuning factor \\
+			$\rho$ & tuning factor \\
 			$\widetilde{\rho}$ & scaled tuning factor \\
@@
 		\begin{tabular}{ l l }
+			ISE  & integral squared error \\
+			LTI  & linear time-invariant (system) \\
 			MIMO & multiple-inputs and multiple-outputs (system) \\
 			MPC  & model predictive control \\
-			ISE  & integral squared error \\
-			LTI  & linear time-invariant (system) \\
 			mp-QP& multi-parametric quadratic programming (problem) \\

### 2023-01-31 paper/elsarticle/main.tex
paper: review and minor updates

@@
 
-			\textcolor{red}{[ TODO: Please, emphasize the chemical engineering viewpoint, especially in Sec.4. ]}
-
-			\textcolor{red}{[ TODO: Please, extend the Control setup, as there is missing e.g., the initial laboratory temperature, the identification procedure of the system model, etc. ]}
-
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
@@
 The asymmetric behaviour of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
-The designed self-tunable controller improved control performance by decreasing integral square error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-self-tunable) controller.
+The designed self-tunable controller improved control performance by decreasing integral square error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (not tuned) controller.
 		%\end{abstract}
@@
 
-	\textcolor{red}{[ TODO: Please, write a paper structure. ]}
-
-	The paper is organized as follows...
+	The paper is organized as follows.
+First, the theoretical backgorunds are presented.
+The topics of explicit MPC, tunable explicit MPC and an existing self-tunable technique are elaborated.
+Then, the novel proposed method of self-tunable procedure is explained.
+Finally, the results of the tuning implementation on a heat exchanger are discussed.
 
@@
 
-	We point out, the concept of explicit MPC tuning is applicable to a wide class of MPC design formulations, based on the current specific needs.
-Without loss of generality, hereafter, we consider the penalty matrices of cost function in Eq.~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
+	The concept of explicit MPC tuning is applicable to a wide class of MPC design formulations, based on the current specific needs.
+Without loss of generality, hereafter, let us consider the penalty matrices of cost function in Eq.~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
 
 	\begin{remark}
-		If the asymptotic stability and recursive feasibility guarantees are required, we refer the reader to follow the instructions from \cite{Oravec_tunable}.
+		If the asymptotic stability and recursive feasibility guarantees are required, the reader is referred to follow the instructions from \cite{Oravec_tunable}.
 In order to satisfy these requirements, the study introduces a procedure for computing the common terminal penalty and terminal set for the two boundary controllers.
+	\end{remark}
+
+	\begin{remark}
+		Not only Eq.~\eqref{eq:tunable_u} needs to be chosen for interpolation of the control input. Another way of tuning the control input can be using some nonlinear relation for the interpolation. 
 	\end{remark}
@@
 	\label{sec:self_tunable}	
-
-	\textcolor{red}{[ TODO: How about ``upgrading'' this subsection into the Section? ]}
-
 	The advantage of a tunable controller brings a question of how to design the logic of setting the tuning parameter $\rho$.
@@
 		\label{eq:rho_delta_ref}
-		\rho(k) = \frac{\vert \Delta_{\mathrm{ref}}(k) \vert}{d_{\max}},
+		\rho(k) = \frac{\vert \Delta_{\mathrm{ref}}(k) \vert}{\Delta_{\max}},
 	\end{eqnarray} 
@@
 The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well.
-In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $d_{\max}$ as the maximal possible reference step change given by: $  d_{\max}(k) = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty} $.
+In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change given by: \textcolor{red}{$\Delta_{\max}(k) = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty} $}.
 	Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values.
-Another option is to exploit the information about the system constraints and set the parameter $d_{\max}$ according to Eq.~\eqref{eq:d_max}.
+Another option is to exploit the information about the system constraints and set the parameter $\Delta_{\max}$ according to Eq.~\eqref{eq:d_max}.
 
-	Note, only the absolute value of $\Delta_{\mathrm{ref}}$ and $d_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
+	Note, only the absolute value of $\Delta_{\mathrm{ref}}$ and $\Delta_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
 
@@
 	\label{sec:self_tunable_rho_scaling}
-
-	\textcolor{red}{[ TODO: Please, fix. ]}
-
-	\noindent TODO: co ak nepriama umera? \\
-	TODO: remark na nelinearnu interpolaciu \\
-	TODO: zovseobecnit na viac usekov intervalu? \\
 
@@
 
-	\textcolor{red}{[ TODO: Please, consider rearranging the confusing Remark, as the task of the tuning is transformed into the Hessian updates. ]}
-
 	\begin{remark}
@@
 Therefore, it is possible to include the controller tuning in the procedure of computing the optimal control input.
-It should be also noted that with real-time updating penalty matrices, the optimization problem has to be rebuilt into a form suitable for a solver, so sufficient computational time is required.
 	\end{remark}
@@
 	The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
-The cold feed as well as a heating medium are transported to the heat exchanger by two peristaltic pumps.
-The flow rate of the feed of the cold medium (water) is constant, while the aim of control is to track the reference value of the cold medium temperature.
+The heat exchanger is 90 mm wide, 103 mm long, and 160 mm high.
+The cold feed as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
+The flow rate of the feed (water) is constant, while the aim of control is to track the reference value of the feed temperature.
 Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger.
+The temperature of the heated feed in the outlet stream was measured by the type K thermocouple.
 The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium (water).
 The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
-The manipulated variable is constrained from 20\,\% to 100\,\% to respect the physical limitations of the operating conditions.
+For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
 
-	\textcolor{red}{The system was identified by experimental identification. More specifically, several step responses were made.} The matrices of the linear state-space model of the plant are
+	The system was identified by experimental identification.
+More specifically, several step responses were obtained in the whole range of the input variable steps.
+Every step response was identified as a first-order system and nominal transfer function was calculated.
+Finally, the transfer function was converted to the state-space model.
+The matrices of the discrete-time state-space model of the plant are
 	\begin{subequations}
@@
 	considering the sampling time $T_\mathrm{s}$ = 1\,s. 
-	The constraints are considered in the terms of control inputs
+	To respect the physical limitations of the operating conditions, the constraints are considered in the terms of control inputs
 	\begin{eqnarray}
 		\label{eq:u_const}
-		-15\% \le u \le 65\%
+		-15\% \le u \le 65\%,
 	\end{eqnarray}
@@
 The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
-	To fully investigate the control performance of the pure self-tuning method, the constraints on the system states in Eq.~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.
+Therefore, the physical constraints on the manipualted variable are actually
+	\begin{eqnarray}
+		\label{eq:U_const}
+		20\% \le U \le 100\%.
+	\end{eqnarray}	
+	\textcolor{red}{To fully investigate the control performance of the pure self-tuning method, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.}
 
@@
 The explicit MPC controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
-	The controllers were implemented to track a time-varying PWC reference. 
+
+	%The initial temperature of the feed was laboratory temperature, i.e., 23$^{\circ}\mathrm{C}$. The temperature of the heating medium was 70$^{\circ}\mathrm{C}$.
+
+	The designed controllers were implemented to track a time-varying PWC reference. 
 	For the initial 200 seconds, the reference temperature was the steady-state value.
@@
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
-Specifically, the reference temperature values were 35$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 50$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$ and 35$^{\circ}\mathrm{C}$.
-The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled outputs, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
+Specifically, the reference temperature values were $T_{\mathrm{ref}}$ = 35$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 50$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 35$^{\circ}\mathrm{C}$.
+The temperature of the heating medium was 70$^{\circ}\mathrm{C}$.
+The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled variable, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
 	Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterwards.
@@
 			\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-			\caption{\textcolor{red} {Controlled variable}: output cold medium temperature for two boundary controllers.
+			\caption{Controlled variable trajectory for two boundary controllers.
 The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
@@
 			\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
-			\caption{\textcolor{red} {Manipulated variables}: input hot medium flow-rate for two boundary controllers.
-The solid lines represent the voltage $U$ and the dashed lines represent the constraints \textcolor{red} {$U_{\mathrm{bound}}$}.}
+			\caption{Manipulated variable trajectory for two boundary controllers. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
 			\label{fig:MV_boundaries}
@@
 
-	The control results of the self-tunable technique compared to the boundary controllers can be seen in Figure~\ref{fig:CV} for the controlled outputs, and in Figure~\ref{fig:MV} for the control inputs.
+	The control results of the self-tunable technique compared to the boundary controllers can be seen in Figure~\ref{fig:CV} for the controlled variable, and in Figure~\ref{fig:MV} for the manipulated variable.
 It can be seen that the tuned controller combined the benefits of the two boundary controllers.
@@
 When tracking the reference with negative step change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
-	The similarity with the boundary controllers can be seen also on the control inputs profiles.
+	The similarity with the boundary controllers can be seen also on the manipulated variable profiles.
 Note, the constraints on the input variable were satisfied as they were scaled using linear interpolation based on the boundary controllers which are constructed considering the input constraints.
@@
 			\includegraphics[width=0.8\textwidth]{images/CV}
-			\caption{Controlled output trajectory for two boundary controllers and the tuned one. The solid lines represent the controlled temperature and the dashed line represents the reference value.}
+			\caption{Controlled variable trajectory for two boundary controllers and the tuned one.
+The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $^{\circ}\mathrm{C}$.}
 			\label{fig:CV}
@@
 			\includegraphics[width=0.8\textwidth]{images/MV}
-			\caption{Control input trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage and the dashed lines represent the constraints.}
+			\caption{Manipulated variable trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
 			\label{fig:MV}
@@
 To provide better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
-
-	\textcolor{red}{[ TODO: How about the following table notation? ]}
-
-	\begin{table}[h!]
-		\begin{center}
-			\caption{Control performance criteria.}
-			\label{tab:control_performance}
-			\begin{tabular}{c|c|c|c|c|c} 
-				Reference step change & Explicit MPC controller & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
-				\hline
-				\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 714 & 33.50 & 16.5 & \textbf{2.12} \\
-				& damped & 867 & 16.65 & 12.5 & 2.36 \\ 
-				& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
-				\hline
-				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & aggressive & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
-				& damped & 606 & 23.25 & 26.5 & 3.19 \\ 
-				& self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
-				\hline
-				\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & aggressive & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
-				& damped & 398 & 79.64 & 31 & \textbf{2.00} \\ 
-				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
-				\hline
-				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & aggressive & 1024 & 18.43 & 22.5 & 0.94 \\
-				& damped & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
-				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10 
-			\end{tabular}
-		\end{center}
-	\end{table}
 
@@
 
-	The relative improvement in the percentage of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
+	The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
 The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
@@
 			\begin{tabular}{c|c|c|c|c} 
-				Reference step change & $\textcolor{red} {\Delta} ISE$\,[\%] & $\Delta \sigma_{\mathrm{max}}$\,[\%] & $\Delta t_{\epsilon}$\,[\%] & $\Delta V$\,[\%] \\
+				Reference step change & $\delta ISE$\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%] & $\delta V$\,[\%] \\
 				\hline
@@
 	Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:control_performance}.
-In general, utilizing a proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy ($ISE$), lower value of the overshoots ($\sigma_{\mathrm{max}}$), and faster achieving the reference value ($t_{\epsilon}$).
+In general, utilizing a proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (lower $\sigma_{\mathrm{max}}$), and faster achieving the reference value (lower $t_{\epsilon}$).
 %It should be also noted that the deterioration of every criterium is calculated subject to the best out of \textit{two} other controllers.
@@
 	Although the volume of the hot medium $V$ is not reduced in the considered control scenario, the improved control performance may lead to other benefits.
-
-	TODO: krajsie skomentovat vyhody zlepsenia kvality riadenia
 
@@
 Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the sum-of-squared control error, maximal overshoots/undershoots, and settling time.
-As a consequence, the self-tunable controllers enable significant energy savings and the corresponding reduction of carbon footprint emissions in industrial applications.
+\textcolor{red}{As a consequence, the self-tunable controllers enable significant energy savings and the corresponding reduction of carbon footprint emissions in industrial applications.
+}
 
@@
 	\subsection*{Symbols}
-	\begin{center}
+%	\begin{center}
 		\begin{tabular}{ l l }
@@
 			$d_{\max}$ & maximal deviation from the steady-state value \\
-			\textcolor{red} {TODO} & odlisit max size of reference step change \\
 			$F$ & slope of the affine control law \\
@@
 			$T$ & temperature, $^{\circ}\mathrm{C}$ \\
-			$T_{\mathrm{ref}}$ & sampling time, s \\
+			$T_{\mathrm{ref}}$ & reference temperature, $^{\circ}\mathrm{C}$ \\
 			$T_{\mathrm{s}}$ & sampling time, s \\
@@
 		\end{tabular}
-	\end{center}
+%	\end{center}
 
@@
 
-	\begin{center}
+%	\begin{center}
 		\begin{tabular}{ l l }
@@
 			$U$ & voltage, \% \\
-			$U_{\mathrm{bound}}$ & \textcolor{red} {steady state of voltage}, \% \\
 			$U^{\mathrm{s}}$ & steady state of voltage, \% \\
@@
 		\end{tabular}
-	\end{center}
+%	\end{center}
 
 	\subsection{Greek letters}
-	\begin{center}
+%	\begin{center}
 		\begin{tabular}{ l l }
+			$\delta$ & relative improvement, \% \\
+			$\Delta_\mathrm{max}$ & maximal size of the reference change, $^{\circ}\mathrm{C}$  \\
 			$\Delta_\mathrm{ref}$ & size of the reference change, $^{\circ}\mathrm{C}$ \\
@@
 		\end{tabular}
-	\end{center}
+%	\end{center}
 
 	\subsection*{Abbreviations}
-	\begin{center}
+%	\begin{center}
 		\begin{tabular}{ l l }

### 2023-02-01 paper/elsarticle/main.tex
minor updates - images/CL and small paper updates

@@
 		%
-		%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analyses}
+		%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis}
 		%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behaviour}
@@
 
-	(len skopirovany text z jadra - hodil sa mi viac do Introduction, neskor mozno pouzijem)
-
-	\textcolor{red}{[ TODO: We need a well-elaborated introduction/review to strongly motivate our control approach.
-Please, take into account the industrial-oriented reviewers - mostly the experts in the field of chemical engineering (heat exchangers and energy balances).
-]}
-
 	The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
-The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) the memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation.
+The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) the memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available sample time for control action implementation.
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
 
-	\textcolor{red}{[ TODO: Please, clearly point out the main contributions. ]}
-
 	This work directly extends our results presented in~\cite{self_tunable}, where the basic principles of the self-tunable approximated explicit MPC were introduced.
-Compared to~\cite{self_tunable}, we...
+In this paper, a novel method of tuning parameter setup is introduced.
+Compared to~\cite{self_tunable}, the tuning method is based on the size of reference step change.
+Next, the idea of further scaling of the tuning parameter is elaborated.
+The interval of the tuning parameter is splitted at some value and every part of the interval corresponds to specific operating conditions specified by control engineer.
+In such way, e.g.
+the system's asymmetry can be compensated.
+Last but not least, the proposed tuning technique was implemented in a control of a laboratory plate heat exchanger.
+This work also provides the control performance evaluation and comparison with using only one non-tunable controller.
 
@@
 Then, the novel proposed method of self-tunable procedure is explained.
-Finally, the results of the tuning implementation on a heat exchanger are discussed.
+Finally, the results of the controller tuning implementation on a heat exchanger are discussed.
 
@@
 The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
-The remaining parameter that needed to be set was the maximal admissible size of the reference step change $d_{\max}$, which was experimentally determined to $15\,^{\circ}\mathrm{C}$.
+The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was experimentally determined to $15\,^{\circ}\mathrm{C}$.
 

### 2023-02-01 paper/elsarticle/main.tex
Paper: Theory: update

@@
 \newtheorem{remark}[theorem]{Remark}
+\newtheorem{lemma}{Lemma}[theorem]
 \newtheorem{corollary}{Corollary}[theorem]
@@
 			\label{eq:tunable_u}
-			u(k) = (1-\rho(k)) \, u_\mathrm{L} + \rho(k) \, u_\mathrm{U},
+			u(k) = (1-\rho(k)) \, u_\mathrm{L}(k) + \rho(k) \, u_\mathrm{U}(k) ,
 		\end{eqnarray}
@@
 
-	\textcolor{red}{[ TODO: Please, consider rearranging the following objects. Missing some formal requirements, such as: ``Given...'' ]}
+	%% TODO: DEF RULE/CONDITION GAMMA
 
 	\begin{definition}
-		Given the current parameter value $\rho$.
-If the tuning parameter is scaled in the first part of the interval, i.e., $\langle 0, \rho_{\mathrm{s}} \rangle$, where $\rho_{\mathrm{s}}$ is the splitting value of the tuning parameter interval, the following relation is used to adjust the tuning parameter:
+		\label{def:rho_tilde}
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the decision parameter $\gamma$, $0 \leq \gamma \leq 1$.
+Then the scaling tuning parameter $\widetilde{\rho}$ is given by:
 		\begin{eqnarray}
-			\label{eq:rho_up}
-			\widetilde{\rho} = \rho_{\mathrm{s}} \rho.
+			\label{eq:rho_tilde_def}
+			\widetilde{\rho} = \left\{ 
+			\begin{matrix}
+				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} ), \\
+				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle,
+			\end{matrix}
+			\right.
 		\end{eqnarray}
+		where $0 \leq \rho_{\mathrm{s}} \leq 1$ holds.
 		\end{definition}
 
-	\textcolor{red}{[ TODO: Please, consider spliting the Corollaries into the Lemma and Proof. ]}
+%\begin{definition}
+%		If the tuning parameter is scaled in the first part of the interval, i.e., $\langle 0, \rho_{\mathrm{s}} \rangle$, where $\rho_{\mathrm{s}}$ is the splitting value of the tuning parameter interval, the following relation is used to adjust the tuning parameter:
+%		\begin{eqnarray}
+%			\label{eq:rho_up}
+%			\widetilde{\rho} = \rho_{\mathrm{s}} \rho.
+%		\end{eqnarray}
+%		$\widetilde{\rho}$ such that $0 \leq \widetilde{\rho} \leq 1$ 
+%\end{definition}
 
-	\begin{corollary}
+%	\begin{definition}
+%	Given the current parameter value $\rho$.
+If the tuning parameter is scaled in the second part of the interval, i.e., $\langle \rho_{\mathrm{s}}, 1 \rangle$, the following relation is used to adjust the tuning parameter:
+%	\begin{eqnarray}
+%		\label{eq:rho_down}
+%		\widetilde{\rho} = (1-\rho_{\mathrm{s}}) \rho + \rho_{\mathrm{s}}.
+%	\end{eqnarray}
+%	\end{definition}
+
+	\begin{remark}
+		\label{rem:rho_tilde}
+		Note, the introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals.
+If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each interval.
+Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in the analogous way.
+	\end{remark}
+
 	The following outcomes result from Eq.~\eqref{eq:rho_up}.
+
+	\begin{lemma}
+		\label{lem:PWA_control_law_interval}
+		% TODO: Convert to Lemma
+		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaling tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}.
+Then the control law  approximated into the form:
+		\begin{eqnarray}
+			\label{eq:PWA_control_law_interval}
+			u(k) = (1-\widetilde{\rho}(k)) \, u_\mathrm{L}(k) + \widetilde{\rho}(k) \, u_\mathrm{U}(k),
+		\end{eqnarray}
+		preserves the closed-loop system stability and recursive feasibility of the original control law in~\eqref{eq:PWA_control_law}.
+		% 
+		% The following outcomes result from Eq.~\eqref{eq:rho_up}.
 If $\rho=0$, then $\widetilde{\rho} = 0$.
@@
 Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
-	\end{corollary}
+	\end{lemma}
 
-	\begin{definition}
-		Given the current parameter value $\rho$.
-If the tuning parameter is scaled in the second part of the interval, i.e., $\langle \rho_{\mathrm{s}}, 1 \rangle$, the following relation is used to adjust the tuning parameter:
-		\begin{eqnarray}
-			\label{eq:rho_down}
-			\widetilde{\rho} = (1-\rho_{\mathrm{s}}) \rho + \rho_{\mathrm{s}}.
-		\end{eqnarray}
-	\end{definition}
+	\begin{proof}
+		\label{proof:rho_tilde}
+		. 
+	\end{proof}
 

### 2023-02-01 paper/elsarticle/main.tex
Paper: Theory: update

@@
 	%% TODO: DEF RULE/CONDITION GAMMA
+	\begin{definition}[Decision function]
+		\label{def:gamma}
+		For given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho < 1$ be a boundary value splitting an interval into the two parts.
+Let $\gamma: \mathbb{R} \rightarrow \mathbb{R}$ be an arbitrary function such that $0 \leq \gamma \leq 1$ holds.
+Then the decision function $\gamma$ is constructed to assign its value either $\gamma \leq \rho_{\mathrm{s}}$ or $\gamma > \rho_{\mathrm{s}}$.
+	\end{definition}
 
-	\begin{definition}
+	\begin{definition}[Scaling tuning parameter]
 		\label{def:rho_tilde}
-		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the decision parameter $\gamma$, $0 \leq \gamma \leq 1$.
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the value of the decision function $\gamma$, $0 \leq \gamma \leq 1$.
 Then the scaling tuning parameter $\widetilde{\rho}$ is given by:
@@
 			\begin{matrix}
-				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} ), \\
+				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} \rangle , \\
 				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle,
@@
 		\label{rem:rho_tilde}
-		Note, the introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals.
-If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each interval.
+		The introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals.
+If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each part of the interval.
 Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in the analogous way.
@@
 
-	The following outcomes result from Eq.~\eqref{eq:rho_up}.
-
+	The following outcomes result from Eq.~\eqref{eq:rho_tilde_def}. 
+	%	\begin{corollary}
+	% The following outcomes result from Eq.~\eqref{eq:rho_up}.
+If $\rho=0$, then $\widetilde{\rho} = 0$.
+When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$.
+In such a way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value.
+Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
+	%	\end{corollary}
+	%
+	%	\begin{corollary}
+	%		The following outcomes result from Eq.~\eqref{eq:rho_down}.
+When $\rho=0$, $\widetilde{\rho} = \rho_{\mathrm{s}}$.
+When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$.
+In such a way, the parameter $\rho$ can be scaled in the second part of the interval from the splitting value up to 1.
+Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
+	%	\end{corollary}
 	\begin{lemma}
 		\label{lem:PWA_control_law_interval}
-		% TODO: Convert to Lemma
 		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaling tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}.
@@
 		preserves the closed-loop system stability and recursive feasibility of the original control law in~\eqref{eq:PWA_control_law}.
-		% 
-		% The following outcomes result from Eq.~\eqref{eq:rho_up}.
-If $\rho=0$, then $\widetilde{\rho} = 0$.
-When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = \rho_{\mathrm{s}}$.
-In such a way, the parameter $\rho$ can be scaled in the first part of the interval up to the splitting value.
-Note, as the relation in Eq.~\eqref{eq:rho_up} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
 	\end{lemma}
@@
 		\label{proof:rho_tilde}
-		. 
+		It has been proven~\cite{Oravec_tunable} that for the asymptotic stable and recursive feasible pair of control inputs $(u_{\mathrm{L}}, u_{\mathrm{U}})$, the approximated control law in~\eqref{eq:PWA_control_law} preserves these properties for any $\rho$ satisfying $0 \leq \rho \leq 1$, see Theorem~3.6 in~\cite{Oravec_tunable}.
+		% 
+		It remains to prove that for any value of the scaling tuning parameter $\widetilde{\rho}$ according to the Definition~\ref{def:rho_tilde} the same results hold. 
+		The rest of the proof of Lemma~\ref{lem:PWA_control_law_interval} consists of two parts. 
+		\\
+		First, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
+		$\widetilde{\rho} = 0$. 
+		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = \rho_{\mathrm{s}} < 1$.
+Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $0 < \widetilde{\rho} < \rho_{\mathrm{s}} $ holds.
+		Therefore, any value of $\widetilde{\rho}$ satisfy $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$.
+As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
+		\\
+		Secondly, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$.
+Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
+		$\widetilde{\rho} = \rho_{\mathrm{s}}$. 
+		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = 1$.
+Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $\rho_{\mathrm{s}} < \widetilde{\rho} < 1 $ holds.
+		Therefore, any value of $\widetilde{\rho}$ satisfy $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$.
+As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
+		% The rest of the proof follows the proof of the Theorem~3.6 in~\cite{Oravec_tunable}. 
 	\end{proof}
 
-	\begin{corollary}
-		The following outcomes result from Eq.~\eqref{eq:rho_down}.
-When $\rho=0$, $\widetilde{\rho} = \rho_{\mathrm{s}}$.
-When considering the other extreme, i.e., $\rho=1$, then $\widetilde{\rho} = 1$.
-In such a way, the parameter $\rho$ can be scaled in the second part of the interval from the splitting value up to 1.
-Note, as the relation in Eq.~\eqref{eq:rho_down} is linear and $0 \le \rho \le 1$ holds, for $\widetilde{\rho}$ it is impossible to acquire other values than in the given interval of parameter $\rho$.
-	\end{corollary}
+	\begin{remark}
+		The Lemma~\ref{lem:PWA_control_law_interval} can be extended subject to the multiple intervals in an analogous way following the Remark~\ref{rem:rho_tilde}.
+	\end{remark}
 

### 2023-02-02 paper/elsarticle/main.tex
Paper: Theory: update
Paper: Theory: further update

@@
 	\end{definition}
+	Various decision functions $\gamma$ can be considered. In this work, we implemented and analyzed a decision function $\gamma$ according to~\eqref{eq:rho_max}, \eqref{eq:rho_delta_ref}.
 
@@
 		It remains to prove that for any value of the scaling tuning parameter $\widetilde{\rho}$ according to the Definition~\ref{def:rho_tilde} the same results hold. 
-		The rest of the proof of Lemma~\ref{lem:PWA_control_law_interval} consists of two parts. 
+		The rest of the proof of Lemma~\ref{lem:PWA_control_law_interval} consists of two parts corresponding to each particular rule in~\eqref{eq:rho_tilde_def}. 
 		\\
-		First, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
+		First, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
 		$\widetilde{\rho} = 0$. 
-		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = \rho_{\mathrm{s}} < 1$.
-Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $0 < \widetilde{\rho} < \rho_{\mathrm{s}} $ holds.
+		For the upper bound value of $\rho=1$, from~\eqref{eq:rho_tilde_def} holds $\widetilde{\rho} = \rho_{\mathrm{s}} < 1$.
+Next, for any value $0 < \rho < 1$ evaluation of the linear rule in~\eqref{eq:rho_tilde_def} leads to the convex combination, i.e., $0 < \widetilde{\rho} < \rho_{\mathrm{s}} $ holds.
 		Therefore, any value of $\widetilde{\rho}$ satisfy $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$.
@@
 		\\
-		Secondly, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$.
-Substituting a lower bound $\rho=0$ into~\eqref{eq:PWA_control_law_interval} leads to
+		Secondly, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
 		$\widetilde{\rho} = \rho_{\mathrm{s}}$. 
-		For the upper bound value of $\rho=1$, from~\eqref{eq:PWA_control_law_interval} holds $\widetilde{\rho} = 1$.
-Next, for any value $0 < \rho < 1$ evaluation of~\eqref{eq:PWA_control_law} leads to the convex combination, i.e., $\rho_{\mathrm{s}} < \widetilde{\rho} < 1 $ holds.
+		For the upper bound value of $\rho=1$, from~\eqref{eq:rho_tilde_def} holds $\widetilde{\rho} = 1$.
+Next, for any value $0 < \rho < 1$ evaluation of the linear rule in~\eqref{eq:rho_tilde_def} leads to the convex combination, i.e., $\rho_{\mathrm{s}} < \widetilde{\rho} < 1 $ holds.
 		Therefore, any value of $\widetilde{\rho}$ satisfy $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$.

### 2023-02-02 paper/elsarticle/main.tex
introduction 1st part

@@
 
-	The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
+	TODO: Vyhnut sa pouzivaniu "we", "our" atd.
+
+	%The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
 The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) the memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available sample time for control action implementation.
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
+
+	One of the promising control techniques came with the formation of model predictive control~\cite{Morari_MPC}.
+MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system.
+Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, so further saturation is not necessary.
+Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection.
+
+	The applicability of model predictive control expanded with the parametric solution of MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online (control) phase.
+Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action.
+The lower computational complexity makes the explicit MPC more suitable for practical implementation.
+Nevertheless, the explicit MPC is not tunable in default as the conventional approach from~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+
+	The possibility to tune the explicit MPC online came with publishing of~\cite{Baric_tunable}.
+The tuning parameter penalizing the control inputs became a parameter, for which the optimal controller was precomputed.
+Nevertheless, the application was limited only for linear cost functions.
+To satisfy the demands for often-used quadratic cost functions, the approximated tunable explicit MPC was presented in~\cite{Klauco_tunable}.
+The technique is based on two explicit model predictive controllers which differ in the setup of one penalty matrix.
+The two explicit MPCs provide upper and lower boundary optimal controllers.
+Based on the evaluation of the two boundary control inputs, the tuned control input is calculated by linear interpolation.
+The follow-up work~\cite{Oravec_tunable} provided stability and recursive feasibility guarantees by proper choosing of the terminal penalty matrix and terminal set constraint~\cite{Mayne_stability}.
+Moreover, the strategy in~\cite{Oravec_tunable} extends the tuning ability based on \textit{any} penalty matrix and not just the input penalty.
+
+	The idea of approximated tunable MPC with neural networks is presented in~\cite{Kis_NN_MPC}.
+To ensure the tuning property, the penalty matrices were included in the training process.
+As a result, it was possible to tune the neural network-based controller online, while mimicking the nearly optimal MPC.
+In~\cite{Kis_NN_MPC_corrector}, the neural network-based tunable controller MPC was extended with a corrector which steered the controller such that the contraints on the manipulated and process variables were satisfied.
+
+	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical implementation.
+The procedure of self-tunable controller technique is presented.
+The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+Tuning based on the distance from the steady state represented a way how to compensate the system's nonlinearity.
 
@@
 
-	The parametric solution of the optimization problem of the quadratic programming (QP) in Eq.~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine (PWA) control law defined above the domain consisting of $r$ critical regions:
+	The parametric solution of the optimization problem of the quadratic programming (QP) in Eq.~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine PWA control law defined above the domain consisting of $r$ critical regions:
 	\begin{eqnarray}
@@
 Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$ and therefore also the complexity of the explicit MPC controller increases.
-Another option for offset-free tracking is introducing disturbance estimation.
-For such an overview see e.g.
-
-	\textcolor{red}{[ TODO: Please, fix. ]}
-
-	...TODO. 
-	Klauco reference governors? minimovka zdroje + dizertacka str.33
+Another option for offset-free tracking is introducing disturbance modelling and estimation.
+For such an overview see e.g.~\cite{Klauco_mpc}
 
@@
 The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well.
-In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change given by: \textcolor{red}{$\Delta_{\max}(k) = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty} $}.
+In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change given by: $\Delta_{\max} = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty}, \forall k \ge 0 $.
 	Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values.

### 2023-02-02 paper/elsarticle/main.tex
minor updates

@@
 Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection.
+The model predictive control was intensively investigated in connection with heat exchangers.
+In~\cite{Vinaya_HE_MPC}, the authors developed a model predictive control for a shell and tube heat exchanger.
+In~\cite{Oravec_energy}, the robust MPC of a plate heat exchanger with soft constraints was analyzed.
+Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}.
+A two-level control structure was applied on a heat exchanger network in ~\cite{Gonzales_HE_MPC}.
+In this study, the low level of control was ensured by MPC and the high level by a supervisory online optimiser.
 
@@
 The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well.
-In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change given by: $\Delta_{\max} = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty}, \forall k \ge 0 $.
-	Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values.
+In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change.
+Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values, i.e., $\Delta_{\max} = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty}, \forall k \ge 0 $.
 	Another option is to exploit the information about the system constraints and set the parameter $\Delta_{\max}$ according to Eq.~\eqref{eq:d_max}.

### 2023-02-02 paper/elsarticle/main.tex
minor updates

@@
 
-	TODO: Vyhnut sa pouzivaniu "we", "our" atd.
+	TODO: Vyhnut sa pouzivaniu "we", "our",...
+
+	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)
 
@@
 			\label{eq:tunable_u}
-			u(k) = (1-\rho(k)) \, u_\mathrm{L}(k) + \rho(k) \, u_\mathrm{U}(k) ,
+			u(k) = (1-\rho(k)) \, u_\mathrm{L}(k) + \rho(k) \, u_\mathrm{U}(k),
 		\end{eqnarray}
@@
 		\label{def:gamma}
-		For given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho < 1$ be a boundary value splitting an interval into the two parts.
+		For given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$ be a boundary value splitting the interval into two parts.
 Let $\gamma: \mathbb{R} \rightarrow \mathbb{R}$ be an arbitrary function such that $0 \leq \gamma \leq 1$ holds.
@@
 	\end{definition}
-	Various decision functions $\gamma$ can be considered. In this work, we implemented and analyzed a decision function $\gamma$ according to~\eqref{eq:rho_max}, \eqref{eq:rho_delta_ref}.
+	\textcolor{red}{TODO: replace in the line above: $\gamma \ge \rho_{\mathrm{s}}$?}\\
+	Various decision functions $\gamma$ can be considered.
+In this work, the decision functions according to Eq.~\eqref{eq:rho_max} and Eq.~\eqref{eq:rho_delta_ref} are considered, while Eq.~\eqref{eq:rho_delta_ref} was implemented in the experimental case study.
 
@@
 		\label{def:rho_tilde}
-		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 \leq \rho_{\mathrm{s}} \leq 1$, and the value of the value of the decision function $\gamma$, $0 \leq \gamma \leq 1$.
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, $0 < \gamma < 1$.
 Then the scaling tuning parameter $\widetilde{\rho}$ is given by:
@@
 				\rho \, \rho_{\mathrm{s}} & \mathrm{if} & \quad \gamma \in \langle 0, \rho_{\mathrm{s}} \rangle , \\
-				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle,
+				\rho \, (1-\rho_{\mathrm{s}}) + \rho_{\mathrm{s}}, & \mathrm{else}\,\,\mathrm{if} &\quad \gamma \in \langle \rho_{\mathrm{s}}, 1 \rangle.
 			\end{matrix}
@@
 		\end{eqnarray}
-		where $0 \leq \rho_{\mathrm{s}} \leq 1$ holds.
 		\end{definition}
@@
 		\\
-		First, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
+		First, it is proved that the Lemma~\ref{lem:PWA_control_law_interval} holds for any $\gamma \leq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
 		$\widetilde{\rho} = 0$. 
@@
 Next, for any value $0 < \rho < 1$ evaluation of the linear rule in~\eqref{eq:rho_tilde_def} leads to the convex combination, i.e., $0 < \widetilde{\rho} < \rho_{\mathrm{s}} $ holds.
-		Therefore, any value of $\widetilde{\rho}$ satisfy $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$.
+		Therefore, any value of $\widetilde{\rho}$ satisfies $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$.
 As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
 		\\
-		Secondly, we prove the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$. Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
+		Secondly, it is proved that the Lemma~\ref{lem:PWA_control_law_interval} holds also for any $\gamma \geq \rho_{\mathrm{s}}$.
+Substituting a lower bound $\rho=0$ into~\eqref{eq:rho_tilde_def} leads to
 		$\widetilde{\rho} = \rho_{\mathrm{s}}$. 
@@
 Next, for any value $0 < \rho < 1$ evaluation of the linear rule in~\eqref{eq:rho_tilde_def} leads to the convex combination, i.e., $\rho_{\mathrm{s}} < \widetilde{\rho} < 1 $ holds.
-		Therefore, any value of $\widetilde{\rho}$ satisfy $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$.
+		Therefore, any value of $\widetilde{\rho}$ satisfies $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$.
 As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
@@
 	\end{eqnarray}	
-	\textcolor{red}{To fully investigate the control performance of the pure self-tuning method, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} were omitted to prevent shaping the computed control inputs by taking into account the bounds on the controlled variable.}
+	As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} can be omitted.
+Another motivation to include the output/state constraints would be the necesity to retain the controlled variable in some comfort range, specified by operation requirements.
+As it was not the aim of the case study, this reason also lead to omitting the constraints in Eq.~\eqref{eq:mpc_problem_state_constraints} to fully investigate the control performance of the pure self-tuning method.
 

### 2023-02-02 data/energy_evaluation.m

@@ -1,0 +1,20 @@
+clc, clear all
+from = 801;
+to = 6000;
+
+load('ref_tracking23.mat') %1000
+P_per = out.ScopeData2(1:to-from+1,3);
+P = P_per/100*2; %kJ/s
+E_1000 = sum(P*Ts) %kJ
+
+load('ref_tracking24.mat') %100
+P_per = out.ScopeData2(1:to-from+1,3);
+P = P_per/100*2; %kJ/s
+E_100 = sum(P*Ts) %kJ
+
+load('ref_tracking27.mat') %tuned
+P_per = out.ScopeData2(1:to-from+1,3);
+P = P_per/100*2; %kJ/s
+E = sum(P*Ts) %kJ
+
+

### 2023-02-02 paper/elsarticle/main.tex
results:energy consumption results

@@
 The control performance is evaluated for each reference step change separately.
-The considered quality criteria are: sum-of-squared based criterion -- integral squared error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$, settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$, and the volume of the hot medium $V$ consumed for the corresponding control.
+The considered quality criteria are: sum-of-squared based criterion -- integral squared error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ and the settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$.
 To provide better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
+
+%	\begin{table}[h!]
+%		\begin{center}
+%			\caption{Control performance criteria.}
+%			\label{tab:control_performance}
+%			\begin{tabular}{c|c|c|c|c|c} 
+%				Reference step change & $Q_\mathrm{y}$ & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
+%				\hline
+%				\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 714 & 33.50 & 16.5 & \textbf{2.12} \\
+%				& 100 & 867 & 16.65 & 12.5 & 2.36 \\ 
+%				& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
+%				\hline
+%				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
+%				& 100 & 606 & 23.25 & 26.5 & 3.19 \\ 
+%				& self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
+%				\hline
+%				\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
+%				& 100 & 398 & 79.64 & 31 & \textbf{2.00} \\ 
+%				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
+%				\hline
+%				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1000 & 1024 & 18.43 & 22.5 & 0.94 \\
+%				& 100 & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
+%				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10  
+%			\end{tabular}
+%		\end{center}
+%	\end{table}
 
@@
 		\label{tab:control_performance}
-			\begin{tabular}{c|c|c|c|c|c} 
-				Reference step change & $Q_\mathrm{y}$ & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s] & $V$\,[l] \\
+		\begin{tabular}{c|c|c|c|c} 
+			Reference step change & $Q_\mathrm{y}$ & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
 			\hline
-				\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 714 & 33.50 & 16.5 & \textbf{2.12} \\
-				& 100 & 867 & 16.65 & 12.5 & 2.36 \\ 
-				& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5} & 2.38 \\ 
+			\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 714 & 33.50 & 16.5 \\
+			& 100 & 867 & 16.65 & 12.5 \\ 
+			& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5}  \\ 
 			\hline
-				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 365 & 47.20 & \textbf{5} & \textbf{2.49} \\
-				& 100 & 606 & 23.25 & 26.5 & 3.19 \\ 
-				& self-tuned & \textbf{248} & \textbf{19.13} & 9.5 & 3.35 \\ 
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 365 & 47.20 & \textbf{5} \\
+			& 100 & 606 & 23.25 & 26.5  \\ 
+			& self-tuned & \textbf{248} & \textbf{19.13} & 9.5  \\ 
 			\hline
-				\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 245 & \textbf{18.92} & \textbf{6.5} & \textbf{2.00} \\
-				& 100 & 398 & 79.64 & 31 & \textbf{2.00} \\ 
-				& self-tuned & \textbf{186} & 24.59 & \textbf{6.5} & 2.10 \\ 
+			\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 245 & \textbf{18.92} & \textbf{6.5}  \\
+			& 100 & 398 & 79.64 & 31  \\ 
+			& self-tuned & \textbf{186} & 24.59 & \textbf{6.5}  \\ 
 			\hline
-				\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1000 & 1024 & 18.43 & 22.5 & 0.94 \\
-				& 100 & 1402 & 41.87 & 90 & \textbf{0.93} \\ 
-				& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5} & 1.10  
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1000 & 1024 & 18.43 & 22.5  \\
+			& 100 & 1402 & 41.87 & 90  \\ 
+			& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5}   
 		\end{tabular}
@@
 The cost for this is the energy associated with control.
-Although the integral square error, maximal overshoot/undershoot and settling time decreased, the volume of consumed heating medium did not.
-Nevertheless, the average deterioration in the terms of consumed heating medium is approximately by~17\,\%.
 
@@
 			\label{tab:improvement}
-			\begin{tabular}{c|c|c|c|c} 
-				Reference step change & $\delta ISE$\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%] & $\delta V$\,[\%] \\
+			\begin{tabular}{c|c|c|c} 
+				Reference step change & $\delta ISE$\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 				\hline
-				35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C &  5 &  9 & 24 &$-12$ \\ 
+				35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C &  5 &  9 & 24 \\ 
 				% \hline
-				45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32 & 18 &$-90$ & $-35$ \\ 
+				45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32 & 18 &$-90$  \\ 
 				% \hline
-				50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 24 &$-30$& 0 &$-4$\\ 
+				50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 24 &$-30$& 0 \\ 
 				% \hline
-				45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C &  6 & 11 & 18 &$-18$  
+				45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C &  6 & 11 & 18   
 			\end{tabular}
@@
 
-	Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:control_performance}.
+		\begin{table}[h!]
+			\begin{center}
+				\caption{Energy consumption evaluation.}
+				\label{tab:energy}
+				\begin{tabular}{c|c} 
+					$Q_\mathrm{y}$ & E\,[kJ]   \\
+					\hline
+					1000 &  883  \\ 
+					% \hline
+					100 & 938   \\ 
+					% \hline
+					self-tuned & 921   
+				\end{tabular}
+			\end{center}
+		\end{table}
+
+	Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:control_performance} and Table~\ref{tab:improvement}.
 In general, utilizing a proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (lower $\sigma_{\mathrm{max}}$), and faster achieving the reference value (lower $t_{\epsilon}$).
@@
 It follows that the evaluation is strict as in practice only one controller would be available.
-	Although the volume of the hot medium $V$ is not reduced in the considered control scenario, the improved control performance may lead to other benefits.
-
-	\textcolor{red}{[ TODO: How about to simply omit the evaluation of the volume $V$ and write something around these lines: ]}
 
@@
 			$\mathcal{U}$ & set of control inputs \\			
-			$V$ & volume of heating medium, l \\
 			$x$ & system states \\

### 2023-02-02 paper/elsarticle/main.tex
schemes
Review: Introduction

@@
 
-	One of the promising control techniques came with the formation of model predictive control~\cite{Morari_MPC}.
+	One of the promising control strategies addressing all these issues in an optimal way came with the formation and tuning of the model predictive control (MPC), e.g., see~\cite{Morari_MPC}.
 MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system.
-Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, so further saturation is not necessary.
-Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection.
+Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, and additional saturation is not necessary.
+Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control policy~\cite{receding_horizon} having a significant benefit mainly in the terms of disturbance rejection.
 The model predictive control was intensively investigated in connection with heat exchangers.
 In~\cite{Vinaya_HE_MPC}, the authors developed a model predictive control for a shell and tube heat exchanger.
-In~\cite{Oravec_energy}, the robust MPC of a plate heat exchanger with soft constraints was analyzed.
+In~\cite{Oravec_energy}, the control performance of the robust MPC implemented for a plate heat exchanger with soft constraints was analyzed.
 Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}.
-A two-level control structure was applied on a heat exchanger network in ~\cite{Gonzales_HE_MPC}.
+A two-level control structure was applied on a heat exchanger network in~\cite{Gonzales_HE_MPC}.
 In this study, the low level of control was ensured by MPC and the high level by a supervisory online optimiser.
@@
 	The applicability of model predictive control expanded with the parametric solution of MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
-As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online (control) phase.
-Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action.
-The lower computational complexity makes the explicit MPC more suitable for practical implementation.
-Nevertheless, the explicit MPC is not tunable in default as the conventional approach from~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in the real-time control.
+Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
+The lower computational complexity makes the explicit MPC more suitable for practical industrial implementation.
+Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
 
@@
 
-	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical implementation.
+	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
 The procedure of self-tunable controller technique is presented.
 The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-Tuning based on the distance from the steady state represented a way how to compensate the system's nonlinearity.
+Tuning based on the distance from the steady-state operating point represented a way on how to compensate the system's nonlinear behaviour.
 
 	This work directly extends our results presented in~\cite{self_tunable}, where the basic principles of the self-tunable approximated explicit MPC were introduced.
-In this paper, a novel method of tuning parameter setup is introduced.
-Compared to~\cite{self_tunable}, the tuning method is based on the size of reference step change.
-Next, the idea of further scaling of the tuning parameter is elaborated.
-The interval of the tuning parameter is splitted at some value and every part of the interval corresponds to specific operating conditions specified by control engineer.
-In such way, e.g.
-the system's asymmetry can be compensated.
-Last but not least, the proposed tuning technique was implemented in a control of a laboratory plate heat exchanger.
-This work also provides the control performance evaluation and comparison with using only one non-tunable controller.
+In this paper, a novel method of a self-tuning parameter setup is introduced.
+Compared to~\cite{self_tunable}, the self-tuning method is based on the size of reference step change.
+Moreover, the idea of further scaling of the tuning parameter is elaborated.
+The interval of the values of the self-tuning parameter is splitted at some certain value, where each part of the interval corresponds to the specific operating conditions defined by control engineer.
+In such way, e.g., the system's asymmetric behaviour is compensated.
+Finally, to investigate the benefits of the proposed approach, the proposed self-tuning control policy was implemented to control of a laboratory-scaled counter-current plate heat exchanger.
+This work provides the control performance evaluation and analysis with using one non-tunable controller.
 
-	The paper is organized as follows.
-First, the theoretical backgorunds are presented.
-The topics of explicit MPC, tunable explicit MPC and an existing self-tunable technique are elaborated.
-Then, the novel proposed method of self-tunable procedure is explained.
-Finally, the results of the controller tuning implementation on a heat exchanger are discussed.
+	The rest of the paper is organized as follows.
+First, the theoretical backgrounds are presented in Section~\ref{sec:preliminaries}, where the explicit MPC, the approximated tunable explicit MPC, and an existing self-tunable methods are briefly elaborated.
+Then, the novel proposed method of self-tunable procedure is explained in detail in Section~\ref{sec:methodology}.
+Finally, the experimental results of the self-tuning controller implementation on a heat exchanger are discussed in Section~\ref{sec:results}, followed by the main conclusions in Section~\ref{sec:conclusion}.
 

### 2023-02-02 paper/elsarticle/main.tex
Review: References and Grammarly

@@
 	One of the promising control strategies addressing all these issues in an optimal way came with the formation and tuning of the model predictive control (MPC), e.g., see~\cite{Morari_MPC}.
-MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system.
+MPC provides optimal control input based on the minimization of a specified cost function while considering a model of the system.
 Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, and additional saturation is not necessary.
@@
 
-	The applicability of model predictive control expanded with the parametric solution of MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
-As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in the real-time control.
+	The applicability of model predictive control expanded with the parametric solution of the MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in real-time control.
 Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
@@
 
-	The possibility to tune the explicit MPC online came with publishing of~\cite{Baric_tunable}.
+	The possibility to tune the explicit MPC online came with the publishing of~\cite{Baric_tunable}.
 The tuning parameter penalizing the control inputs became a parameter, for which the optimal controller was precomputed.
-Nevertheless, the application was limited only for linear cost functions.
+Nevertheless, the application was limited only to linear cost functions.
 To satisfy the demands for often-used quadratic cost functions, the approximated tunable explicit MPC was presented in~\cite{Klauco_tunable}.
@@
 Based on the evaluation of the two boundary control inputs, the tuned control input is calculated by linear interpolation.
-The follow-up work~\cite{Oravec_tunable} provided stability and recursive feasibility guarantees by proper choosing of the terminal penalty matrix and terminal set constraint~\cite{Mayne_stability}.
+The follow-up work~\cite{Oravec_tunable} provided stability and recursive feasibility guarantees by proper choice of the terminal penalty matrix and terminal set constraint~\cite{Mayne_stability}.
 Moreover, the strategy in~\cite{Oravec_tunable} extends the tuning ability based on \textit{any} penalty matrix and not just the input penalty.
@@
 As a result, it was possible to tune the neural network-based controller online, while mimicking the nearly optimal MPC.
-In~\cite{Kis_NN_MPC_corrector}, the neural network-based tunable controller MPC was extended with a corrector which steered the controller such that the contraints on the manipulated and process variables were satisfied.
+In~\cite{Kis_NN_MPC_corrector}, the neural network-based tunable controller MPC was extended with a corrector which steered the controller such that the constraints on the manipulated and process variables were satisfied.
 
 	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-The procedure of self-tunable controller technique is presented.
+The procedure of the self-tunable controller technique is presented.
 The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-Tuning based on the distance from the steady-state operating point represented a way on how to compensate the system's nonlinear behaviour.
+Tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behaviour.
 
 	This work directly extends our results presented in~\cite{self_tunable}, where the basic principles of the self-tunable approximated explicit MPC were introduced.
-In this paper, a novel method of a self-tuning parameter setup is introduced.
-Compared to~\cite{self_tunable}, the self-tuning method is based on the size of reference step change.
-Moreover, the idea of further scaling of the tuning parameter is elaborated.
-The interval of the values of the self-tuning parameter is splitted at some certain value, where each part of the interval corresponds to the specific operating conditions defined by control engineer.
-In such way, e.g., the system's asymmetric behaviour is compensated.
-Finally, to investigate the benefits of the proposed approach, the proposed self-tuning control policy was implemented to control of a laboratory-scaled counter-current plate heat exchanger.
-This work provides the control performance evaluation and analysis with using one non-tunable controller.
+In this paper, a novel method of self-tuning parameter setup is introduced.
+Compared to~\cite{self_tunable}, the self-tuning method is based on the size of the reference step change.
+Moreover, the idea of further scaling the tuning parameter is elaborated.
+The interval of the values of the self-tuning parameter is split at some certain value, where each part of the interval corresponds to the specific operating conditions defined by the control engineer.
+In such a way, e.g., the system's asymmetric behaviour is compensated.
+Finally, to investigate the benefits of the proposed approach, the proposed self-tuning control policy was implemented to control a laboratory-scaled counter-current plate heat exchanger.
+This work provides the control performance evaluation and analysis using one non-tunable controller.
 
 	The rest of the paper is organized as follows.
-First, the theoretical backgrounds are presented in Section~\ref{sec:preliminaries}, where the explicit MPC, the approximated tunable explicit MPC, and an existing self-tunable methods are briefly elaborated.
+First, the theoretical backgrounds are presented in Section~\ref{sec:preliminaries}, where the explicit MPC, the approximated tunable explicit MPC, and existing self-tunable methods are briefly elaborated.
 Then, the novel proposed method of self-tunable procedure is explained in detail in Section~\ref{sec:methodology}.

### 2023-02-02 paper/elsarticle/main.tex
results and conclusion updated - energy consumption

--- 2023-02-02 paper/elsarticle/main.tex
@@
 
+	For better insight of the proposed technique, the procedure of self-tuning is depicted in Fig.~\ref{fig:tuning}.
+
+	\begin{figure}
+	\begin{center}
+		\includegraphics[width=\textwidth]{images/CL/tuning}
+		\caption[Self-tuning scheme]{Self-tuning scheme.}
+		\label{fig:tuning}
+	\end{center}
+	\end{figure}
+
 	\section{Results and discussion}
@@
 
-	In this section, the results of the proposed self-tuning method are analyzed using an experimental implementation.
-The self-tuning strategy utilizes tuning parameter based on the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
+In this section, the results of the proposed self-tuning method are analyzed by experimental implementation.
+The self-tuning strategy utilizes tuning parameter calculation based on the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
 
@@
 The heat exchanger is 90 mm wide, 103 mm long, and 160 mm high.
+The heat exchange is performed between the cold feed (water) and hot medium (water).
 The cold feed as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
-The flow rate of the feed (water) is constant, while the aim of control is to track the reference value of the feed temperature.
+The flow rate of the feed is constant, while the aim of control is to track the reference value of the feed temperature.
 Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger.
 The temperature of the heated feed in the outlet stream was measured by the type K thermocouple.
-The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium (water).
+The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium.
 The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
@@
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
+The corresponding simplified closed-loop scheme can be seen in Figure~\ref{fig:CL}.
+Note, the ,,Self-tuning" block correponds to more detailed scheme in Figure~\ref{fig:tuning}.
 
@@
 The prediction horizon $N$ was set to 20 control steps.
-The explicit MPC controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
+The explicit model predictive controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
 
@@
 
-	The designed controllers were implemented to track a time-varying PWC reference. 
+The designed explicit model predictive controllers were implemented to track a time-varying PWC reference. 
 For the initial 200 seconds, the reference temperature was the steady-state value.
@@
 Specifically, the reference temperature values were $T_{\mathrm{ref}}$ = 35$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 50$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 35$^{\circ}\mathrm{C}$.
-The temperature of the heating medium was 70$^{\circ}\mathrm{C}$.
+
+Beside the control design of two boundary explicit MPCs, it was necessary to keep the temperature of the heating medium constant.
+The heating medium was transported back to the heater after leaving the heat exchanger, i.e., the volume of the heating medium was recycled during whole operation.
+The temperature of the heating medium was maintained on the value 70$^{\circ}\mathrm{C}$ with a simple proportional controller with proportional gain $P = 20$.
+The control input from the proportional controller was the electric power which could acquire the values in range [$0-2$]\,kW and was also normalized to percentage.
+
 The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled variable, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
@@
 	\begin{center}
+		\includegraphics[width=\textwidth]{images/CL/CL}
+		\caption[Closed-loop scheme]{Closed-loop scheme.}
+		\label{fig:CL}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
 		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-			\caption{Controlled variable trajectory for two boundary controllers.
-The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
+		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
 		\label{fig:CV_boundaries}
@@
 These main experimental observations established the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$.
-The strategy follows the ideas summarized in Section~\ref{sec:self_tunable}.
+The strategy follows the ideas summarized in Section~\ref{sec:methodology}.
 Therefore, utilizing the boundary controller with the penalty matrix $Q_\mathrm{y,L}$ is preferred when the reference changes upwards.
@@
 The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
-The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was experimentally determined to $15\,^{\circ}\mathrm{C}$.
+The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was determined to $15\,^{\circ}\mathrm{C}$ as the investigated range of controlled temperature was [$35-50$]$^{\circ}\mathrm{C}$.
 
@@
 
-	As can be seen in Table~\ref{tab:control_performance}, that real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value.
-The cost for this is the energy associated with control.
-
+As can be seen in Table~\ref{tab:control_performance}, the real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value. 	
 The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
@@
 
+Compared to the considered non-self-tunable controllers, the control trajectories and the evaluated quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behaviour.
+Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
+The squared-error-based criterion ($ISE$) improved in every control scenario within a range $[5-32]$\,\%, the maximal overshoots/undershoots $\sigma_{\mathrm{max}}$ reduced up to 18\,\%, and the settling time $t_{\epsilon}$ decreased up to 24\,\%.
+
+To analyze the control more objectively, the energy consumption was also investigated.
+More specifically, the power used to heat the heating medium was measured and summarized for the whole control, but for every controller setup respectively.
+The energy consumption $E$ necessary for every control can be seen in Table~\ref{tab:energy}.
+
 \begin{table}[h!]
@@
 
-	Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:control_performance} and Table~\ref{tab:improvement}.
-In general, utilizing a proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (lower $\sigma_{\mathrm{max}}$), and faster achieving the reference value (lower $t_{\epsilon}$).
-%It should be also noted that the deterioration of every criterium is calculated subject to the best out of \textit{two} other controllers.
-It follows that the evaluation is strict as in practice only one controller would be available.
-
-	Compared to the considered non-self-tunable controllers, the generated control trajectories and the computed quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behaviour.
-	For various operating conditions, the proposed self-tunable controller outperformed the conventional controllers in the means of the squared-error-based criterion ($ISE$) of the output temperature $T$ within a range $[5-32]$\,\%.
-	Together with the reduced overshoots and settling times, the achieved improvements in the control performance enable non-negligible energy savings when the precision and the operating time ensure the product with the required properties.
-Although the analyzed extensive case study was realized considering the laboratory-scaled heat exchanger plant, the introduced self-tunable control policy enables a significant reduction of the corresponding carbon footprint emissions in industrial applications.
+It can be seen in Table~\ref{tab:energy}, that utilizing the self-tuned controller leads to energy consumption which acquires value between the energy consumptions associated with the boundary controllers.
+Although it is not the minimum one, the energy is still saved compared to the boundary controller with $Q_\mathrm{y} = 100$.
+Note, though the controller with $Q_\mathrm{y} = 1000$ leads to minimum energy consumption, using this single non-tuned controller does not lead to such control performance improvement.
+
+In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (lower $\sigma_{\mathrm{max}}$), and faster achieving the reference value (lower $t_{\epsilon}$), while the control does not suffer in the terms of energy consumption.
+
+%	Together with the reduced overshoots and settling times, the achieved improvements in the control performance enable non-negligible energy savings when the precision and the operating time ensure the product with the required properties.
 
@@
 
-	This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provide a strategy for an effective self-tuning controller design.
+This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provides a strategy for an effective self-tuning controller design.
 Based on the current reference value, the tuning parameter is scaled using linear interpolation.
-The previously published work related to the self-tunable explicit MPC suggested tuning just based on the distance of the reference value from the system steady-state value.
+The previously published work related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the system steady-state value.
 This paper presents a novel idea of tuning based on the size of reference step change.
@@
 The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behaviour.
-The non-symmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
+The asymmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
 The decision criterium is negativity or positivity of reference change.
@@
 Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the sum-of-squared control error, maximal overshoots/undershoots, and settling time.
-\textcolor{red}{As a consequence, the self-tunable controllers enable significant energy savings and the corresponding reduction of carbon footprint emissions in industrial applications.
-}
+In addition, the energy consumption corresponding to every controller was evaluated as well.
+The value of consumed energy was between the two boundary controllers, i.e., the energy consumption did not deteriorate in general.
+With saving the energy compared to one of the boundary controllers, the control performance was significantly improved.
 

### 2023-02-02 paper/elsarticle/main.tex
one update in nomenclature

@@
 			$n_{\widetilde{\mathrm{x}}}$ & size of augmented system states \\
+			$P$ & proportional gain of proportional controller\\
 			$Q_{\mathrm{x}}$ & penalty matrix of the built-in integrator \\

### 2023-02-02 paper/elsarticle/main.tex
Paper: Introduction: initial part

--- 2023-02-02 paper/elsarticle/main.tex
@@
 
-	TODO: Vyhnut sa pouzivaniu "we", "our",...
-
-	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)
+%	TODO: Vyhnut sa pouzivaniu "we", "our",...
+%	
+%	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)
 
@@
 Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
+
+	The current crisis of energy resources emphasizes the long-term goal of achieving sustainable industrial production and optimal energy utilization.
+Moreover, minimizing the energy utilization directly reduces the corresponding CO$_{2}$ emissions.
+Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.
+
+	The heat exchangers in their numerous variants integrated into the many industrial plants represent energy-demanding plants.
+From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}.
+Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when comes to energy savings.
+Various extensions built above the well-tuned PID controller were developed to compensate for the non-linear and asymmetric behaviour, often affected by the additional impact of the uncertain parameters originated e.g., in the fouling~\cite{MT19}.
+Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08,Liptak}, and references therein.
 

### 2023-02-02 paper/elsarticle/main.tex

--- 2023-02-02 paper/elsarticle/main.tex
@@
 
-	One of the promising control techniques came with the formation of model predictive control~\cite{Morari_MPC}.
-MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system.
-Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, so further saturation is not necessary.
-Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection.
+	The current crisis of energy resources emphasizes the long-term goal of achieving sustainable industrial production and optimal energy utilization.
+Moreover, minimizing the energy utilization directly reduces the corresponding CO$_{2}$ emissions.
+Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.
+
+	The heat exchangers in their numerous variants integrated into the many industrial plants represent energy-demanding plants.
+From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}.
+Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when comes to energy savings.
+Various extensions built above the well-tuned PID controller were developed to compensate for the non-linear and asymmetric behaviour, often affected by the additional impact of the uncertain parameters originated e.g., in the fouling~\cite{MT19}.
+Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08,Liptak}, and references therein.
+
+	One of the promising control strategies addressing all these issues in an optimal way came with the formation and tuning of the model predictive control (MPC), e.g., see~\cite{Morari_MPC}.
+MPC provides optimal control input based on the minimization of a specified cost function while considering a model of the system.
+Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, and additional saturation is not necessary.
+Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control policy~\cite{receding_horizon} having a significant benefit mainly in the terms of disturbance rejection.
 The model predictive control was intensively investigated in connection with heat exchangers.
 In~\cite{Vinaya_HE_MPC}, the authors developed a model predictive control for a shell and tube heat exchanger.
-In~\cite{Oravec_energy}, the robust MPC of a plate heat exchanger with soft constraints was analyzed.
+In~\cite{Oravec_energy}, the control performance of the robust MPC implemented for a plate heat exchanger with soft constraints was analyzed.
 Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}.
-A two-level control structure was applied on a heat exchanger network in ~\cite{Gonzales_HE_MPC}.
+A two-level control structure was applied on a heat exchanger network in~\cite{Gonzales_HE_MPC}.
 In this study, the low level of control was ensured by MPC and the high level by a supervisory online optimiser.
 
-	The applicability of model predictive control expanded with the parametric solution of MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
-As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online (control) phase.
-Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action.
-The lower computational complexity makes the explicit MPC more suitable for practical implementation.
-Nevertheless, the explicit MPC is not tunable in default as the conventional approach from~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
-
-	The possibility to tune the explicit MPC online came with publishing of~\cite{Baric_tunable}.
+	The applicability of model predictive control expanded with the parametric solution of the MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in real-time control.
+Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
+The lower computational complexity makes the explicit MPC more suitable for practical industrial implementation.
+Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+
+	The possibility to tune the explicit MPC online came with the publishing of~\cite{Baric_tunable}.
 The tuning parameter penalizing the control inputs became a parameter, for which the optimal controller was precomputed.
-Nevertheless, the application was limited only for linear cost functions.
+Nevertheless, the application was limited only to linear cost functions.
 To satisfy the demands for often-used quadratic cost functions, the approximated tunable explicit MPC was presented in~\cite{Klauco_tunable}.
@@
 As a result, it was possible to tune the neural network-based controller online, while mimicking the nearly optimal MPC.
-In~\cite{Kis_NN_MPC_corrector}, the neural network-based tunable controller MPC was extended with a corrector which steered the controller such that the contraints on the manipulated and process variables were satisfied.
-
-	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical implementation.
-The procedure of self-tunable controller technique is presented.
+In~\cite{Kis_NN_MPC_corrector}, the neural network-based tunable controller MPC was extended with a corrector which steered the controller such that the constraints on the manipulated and process variables were satisfied.
+
+	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+The procedure of the self-tunable controller technique is presented.
 The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-Tuning based on the distance from the steady state represented a way how to compensate the system's nonlinearity.
+Tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behaviour.
 
 	This work directly extends our results presented in~\cite{self_tunable}, where the basic principles of the self-tunable approximated explicit MPC were introduced.
-In this paper, a novel method of tuning parameter setup is introduced.
-Compared to~\cite{self_tunable}, the tuning method is based on the size of reference step change.
-Next, the idea of further scaling of the tuning parameter is elaborated.
-The interval of the tuning parameter is splitted at some value and every part of the interval corresponds to specific operating conditions specified by control engineer.
-In such way, e.g.
-the system's asymmetry can be compensated.
-Last but not least, the proposed tuning technique was implemented in a control of a laboratory plate heat exchanger.
-This work also provides the control performance evaluation and comparison with using only one non-tunable controller.
-
-	The paper is organized as follows.
-First, the theoretical backgorunds are presented.
-The topics of explicit MPC, tunable explicit MPC and an existing self-tunable technique are elaborated.
-Then, the novel proposed method of self-tunable procedure is explained.
-Finally, the results of the controller tuning implementation on a heat exchanger are discussed.
+In this paper, a novel method of self-tuning parameter setup is introduced.
+Compared to~\cite{self_tunable}, the self-tuning method is based on the size of the reference step change.
+Moreover, the idea of further scaling the tuning parameter is elaborated.
+The interval of the values of the self-tuning parameter is split at some certain value, where each part of the interval corresponds to the specific operating conditions defined by the control engineer.
+In such a way, e.g., the system's asymmetric behaviour is compensated.
+Finally, to investigate the benefits of the proposed approach, the proposed self-tuning control policy was implemented to control a laboratory-scaled counter-current plate heat exchanger.
+This work provides the control performance evaluation and analysis using one non-tunable controller.
+
+	The rest of the paper is organized as follows.
+First, the theoretical backgrounds are presented in Section~\ref{sec:preliminaries}, where the explicit MPC, the approximated tunable explicit MPC, and existing self-tunable methods are briefly elaborated.
+Then, the novel proposed method of self-tunable procedure is explained in detail in Section~\ref{sec:methodology}.
+Finally, the experimental results of the self-tuning controller implementation on a heat exchanger are discussed in Section~\ref{sec:results}, followed by the main conclusions in Section~\ref{sec:conclusion}.
 

### 2023-02-03 paper/elsarticle/main.tex
grammarly

@@
 It provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behaviour.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 To ensure offset-free reference tracking control, the built-in integrator was included in the explicit MPC design.
-The asymmetric behaviour of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
-The designed self-tunable controller improved control performance by decreasing integral square error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (not tuned) controller.
+The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
+The designed self-tunable controller improved control performance by decreasing integral squared error, maximal overshoots/undershoots and settling time compared to the conventional control strategy based on a single (not tuned) controller.
 		%\end{abstract}
@@
 
-%	TODO: Vyhnut sa pouzivaniu "we", "our",...
-%	
-%	TODO: dopisat zaciatok uvodu o vymennikoch tepla, ladeni regulatorov vseobecne, gain-scheduling atd (neskor je pokryte MPC, MPC riadenie vymennikov tepla, eMPC, tunable eMPC a self-tunable)
-
 	%The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
@@
 
-	The heat exchangers in their numerous variants integrated into the many industrial plants represent energy-demanding plants.
-From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}.
-Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when comes to energy savings.
-Various extensions built above the well-tuned PID controller were developed to compensate for the non-linear and asymmetric behaviour, often affected by the additional impact of the uncertain parameters originated e.g., in the fouling~\cite{MT19}.
-Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08,Liptak}, and references therein.
+	The heat exchangers, in their numerous variants integrated into many industrial plants, represent energy-demanding plants.
+From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task, see~\cite{RL20}.
+Although the conventional and widely-used proportional–integral–derivative (PID) controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
+Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the fouling~\cite{MT19}.
+Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08}, and references therein.
+
+	TODO: nepouzivat nasobne referencie ako [4,5] vyssie
 
@@
 Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, and additional saturation is not necessary.
-Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control policy~\cite{receding_horizon} having a significant benefit mainly in the terms of disturbance rejection.
+Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control policy~\cite{receding_horizon}, having a significant benefit mainly in the terms of disturbance rejection.
 The model predictive control was intensively investigated in connection with heat exchangers.
@@
 Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}.
-A two-level control structure was applied on a heat exchanger network in~\cite{Gonzales_HE_MPC}.
-In this study, the low level of control was ensured by MPC and the high level by a supervisory online optimiser.
+A two-level control structure was applied on a heat exchanger network in~\cite{Gonzales_HE_MPC}, where the low level of control was ensured by MPC and the high level by a supervisory online optimizer.
 
@@
 The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-Tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behaviour.
+Tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
 
@@
 Moreover, the idea of further scaling the tuning parameter is elaborated.
-The interval of the values of the self-tuning parameter is split at some certain value, where each part of the interval corresponds to the specific operating conditions defined by the control engineer.
-In such a way, e.g., the system's asymmetric behaviour is compensated.
+The interval of the values of the self-tuning parameter is split at some certain value and each part of the interval corresponds to the specific operating conditions defined by the control engineer.
+In such a way, e.g., the system's asymmetric behavior is compensated.
 Finally, to investigate the benefits of the proposed approach, the proposed self-tuning control policy was implemented to control a laboratory-scaled counter-current plate heat exchanger.
-This work provides the control performance evaluation and analysis using one non-tunable controller.
-
-	The rest of the paper is organized as follows.
+This work provides the control performance evaluation and analysis using the self-tunable controller compared to the boundary explicit MPCs.
+
+	The paper is organized as follows.
 First, the theoretical backgrounds are presented in Section~\ref{sec:preliminaries}, where the explicit MPC, the approximated tunable explicit MPC, and existing self-tunable methods are briefly elaborated.
@@
 As the explicit solution is available, real-time solving of the optimization problem in every control step is omitted.
-As this work deals with industrial-oriented implementation, consider the optimization problem in the following form:
+As this work deals with industrial-oriented implementation, let us consider the optimization problem in the following form:
 	\begin{subequations}
@@
 	%
-	Variables $\widetilde{x} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding augmented system states, control inputs and system outputs, respectively.
+	Variables $\widetilde{x} \in \mathbb{R}^{n_{\widetilde{\mathrm{x}}}}$, $u \in \mathbb{R}^{n_{\mathrm{u}}}$, $y \in \mathbb{R}^{n_{\mathrm{y}}}$ are vectors of corresponding augmented system states, control inputs, and system outputs, respectively.
 	%
@@
 	\end{subequations}
-	where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time and matrices $A$, $B$, $C$ are well-known the state-space matrices that form the augmented LTI model.
+	where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time, and matrices $A$, $B$, $C$ are well-known the state-space matrices that form the augmented LTI model.
 As the consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error is penalized, but also an integrated value, which leads to analogous offset-free reference tracking results as incorporating an integral part in PID controller.
@@
 	Note, many other formulations of the optimization problems for the explicit MPC design, were mainly in the terms of the definition of the cost functions in Eq.~\eqref{eq:mpc_problem_cost}.
-Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$ and therefore also the complexity of the explicit MPC controller increases.
-Another option for offset-free tracking is introducing disturbance modelling and estimation.
+Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$, and therefore also the complexity of the explicit MPC controller increases.
+Another option for offset-free tracking is introducing disturbance modeling and estimation.
 For such an overview see e.g.~\cite{Klauco_mpc}
@@
 	The aggressivity of the controller and the whole nature of the control is influenced by appropriate fine-tuning of the penalty matrices in the optimization problem in Eq.~\eqref{eq:mpc_problem}.
-When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterwards without trading off a significant increase in the controller complexity or the performance loss.
-As the operation conditions and requirements of controller setup may differ throughout the control, the ability to adjust the controller's aggressivity can be very beneficial.
+When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterward without trading off a significant increase in the controller complexity or the performance loss.
+As the operating conditions and requirements of controller setup may differ throughout the control, the ability to adjust the controller's aggressivity can be very beneficial.
 
@@
 
-	Let us consider the penalty matrices in cost function in Eq.~\eqref{eq:mpc_problem_cost}. The penalty matrices are scaled in the following way:
+	Let us consider the penalty matrices in the cost function in Eq.~\eqref{eq:mpc_problem_cost}. The penalty matrices are scaled in the following way:
 	\begin{subequations}
@@
 	The concept of explicit MPC tuning is applicable to a wide class of MPC design formulations, based on the current specific needs.
-Without loss of generality, hereafter, let us consider the penalty matrices of cost function in Eq.~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
+Without loss of generality, hereafter, let us consider the penalty matrices of the cost function in Eq.~\eqref{eq:mpc_problem_cost}, as it is necessary to satisfy offset-free reference tracking.
 
@@
 The further the reference value is from the steady state, the more aggressively the controller is tuned.
-The idea behind the suggested scaling lies in compensation for the nonlinear behaviour of the system.
+The idea behind the suggested scaling lies in compensation for the nonlinear behavior of the system.
 
@@
 	\end{eqnarray}
-	where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, ie., zero corresponds to the system steady-state value.
+	where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero corresponds to the system steady-state value.
 Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
@@
 It is not taken into account, whether the reference change was positive or negative with respect to the system steady-state value placed in the origin, i.e., whether it changed upwards or downwards.
-As many plants have asymmetric behaviour, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
+As many plants have asymmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
 
@@
 	The approach of self-tunable explicit MPC in~\cite{self_tunable} suggested tuning based on the current reference value distance from the steady state.
-The aim is to compensate for the nonlinear behaviour of a system when using a simple linear prediction model.
+The aim is to compensate for the nonlinear behavior of a system when using a simple linear prediction model.
 This work provides also another useful way of the real-time evaluation of the tuning parameter $\rho$ based on the size of reference change.
-When different sizes of reference step changes are made and the behaviour of the closed-loop system is varying, it can be beneficial to include the size of the reference step change in the tuning procedure.
+When different sizes of reference step changes are made and the behavior of the closed-loop system is varying, it can be beneficial to include the size of the reference step change in the tuning procedure.
 
@@
 
-	\subsection{Self-tunable technique for systems with asymmetric behaviour}
+	\subsection{Self-tunable technique for systems with asymmetric behavior}
 	\label{sec:self_tunable_rho_scaling}
@@
 	This paper provides a further extension of the self-tuning method proposed in~\cite{self_tunable}.
-The suggested technique of tuning is suitable, e.g., for systems with asymmetric behaviour, but can be used in any application, where ``simple'' tuning in the whole range of tuning parameter $\rho$ is not sufficient.
+The suggested technique of tuning is suitable, e.g., for systems with asymmetric behavior, but can be used in any application, where ``simple'' tuning in the whole range of tuning parameter $\rho$ is not sufficient.
 
@@
 		\label{def:gamma}
-		For given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$ be a boundary value splitting the interval into two parts.
+		For a given interval of tuning parameter $\rho$, $0 \leq \rho \leq 1$, let $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$ be a boundary value splitting the interval into two parts.
 Let $\gamma: \mathbb{R} \rightarrow \mathbb{R}$ be an arbitrary function such that $0 \leq \gamma \leq 1$ holds.
@@
 	\label{rem:rho_tilde}		
-		The introduction of the splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only for 2 intervals.
-If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s},i}$ for each part of the interval.
-Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in the analogous way.
+		The introduction of splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only to two intervals.
+If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s}, i}$ for each part of the interval.
+Next, the tuning rules in~\eqref{eq:rho_tilde_def} are adopted in an analogous way.
 	\end{remark}
@@
 
-	For better insight of the proposed technique, the procedure of self-tuning is depicted in Fig.~\ref{fig:tuning}.
+	For a better insight into the proposed technique, the procedure of self-tuning is depicted in Fig.~\ref{fig:tuning}.
 
@@
 
-In this section, the results of the proposed self-tuning method are analyzed by experimental implementation.
+In this section, the results of the proposed self-tuning method are analyzed by an experimental implementation.
 The self-tuning strategy utilizes tuning parameter calculation based on the size of reference change (Section~\ref{sec:self_tunable_delta_ref}) and the scaling of tuning parameter based on splitting the interval of the parameter and assigning the interval parts to specific operating conditions (Section~\ref{sec:self_tunable_rho_scaling}).
@@
 The heat exchanger is 90 mm wide, 103 mm long, and 160 mm high.
-The heat exchange is performed between the cold feed (water) and hot medium (water).
+The heat exchange is performed between the cold feed (water) and the hot medium (water).
 The cold feed as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
@@
 The corresponding simplified closed-loop scheme can be seen in Figure~\ref{fig:CL}.
-Note, the ,,Self-tuning" block correponds to more detailed scheme in Figure~\ref{fig:tuning}.
+Note, the ,,Self-tuning" block corresponds to the more detailed scheme in Figure~\ref{fig:tuning}.
 
@@
 More specifically, several step responses were obtained in the whole range of the input variable steps.
-Every step response was identified as a first-order system and nominal transfer function was calculated.
+Every step response was identified as a first-order system and the nominal transfer function was calculated.
 Finally, the transfer function was converted to the state-space model.
@@
 The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
-Therefore, the physical constraints on the manipualted variable are actually
+Therefore, the physical constraints on the manipulated variable are actually
 \begin{eqnarray}
@@
 As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} can be omitted.
-Another motivation to include the output/state constraints would be the necesity to retain the controlled variable in some comfort range, specified by operation requirements.
-As it was not the aim of the case study, this reason also lead to omitting the constraints in Eq.~\eqref{eq:mpc_problem_state_constraints} to fully investigate the control performance of the pure self-tuning method.
+Another motivation to include the output/state constraints would be the necessity to retain the controlled variable in some comfort range, specified by operation requirements.
+As it was not the aim of the case study, this reason also leads to omitting the constraints in Eq.~\eqref{eq:mpc_problem_state_constraints} to fully investigate the control performance of the pure self-tuning method.
 
@@
 
-Beside the control design of two boundary explicit MPCs, it was necessary to keep the temperature of the heating medium constant.
-The heating medium was transported back to the heater after leaving the heat exchanger, i.e., the volume of the heating medium was recycled during whole operation.
+Besides the control design of two boundary explicit MPCs, it was necessary to keep the temperature of the heating medium constant.
+The heating medium was transported back to the heater after leaving the heat exchanger, i.e., the volume of the heating medium was recycled during the whole operation.
 The temperature of the heating medium was maintained on the value 70$^{\circ}\mathrm{C}$ with a simple proportional controller with proportional gain $P = 20$.
-The control input from the proportional controller was the electric power which could acquire the values in range [$0-2$]\,kW and was also normalized to percentage.
+The control input from the proportional controller was the electric power which could acquire the values in the range [$0-2$]\,kW and was also normalized to percentage.
 
 The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled variable, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
-Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterwards.
+Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterward.
 
@@
 The strategy follows the ideas summarized in Section~\ref{sec:methodology}.
-Therefore, utilizing the boundary controller with the penalty matrix $Q_\mathrm{y,L}$ is preferred when the reference changes upwards.
-On the contrary, the controller associated with $Q_\mathrm{y,U}$ is preferred for negative reference step changes.
+Therefore, utilizing the boundary controller with the penalty matrix $Q_\mathrm{y, L}$ is preferred when the reference changes upwards.
+On the contrary, the controller associated with $Q_\mathrm{y, U}$ is preferred for negative reference step changes.
 The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
@@
 The overshoots and undershoots were reduced, as in the first half of control the penalty matrix $Q_\mathrm{y}$ acquired value from the first half of the penalty interval.
-When tracking the reference with negative step change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y,U}$.
+When tracking the reference with negative step change, the penalty matrix acquired the values from the second half of the interval, i.e., closer to the upper bound $Q_\mathrm{y, U}$.
 The similarity with the boundary controllers can be seen also on the manipulated variable profiles.
@@
 The control performance was also investigated quantitatively.
-Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria computed for the two boundary controllers and for the self-tuned controller.
+Table~\ref{tab:control_performance} summarizes the evaluated control performance criteria computed for the two boundary controllers and the self-tuned controller.
 The control performance is evaluated for each reference step change separately.
@@
 
-Compared to the considered non-self-tunable controllers, the control trajectories and the evaluated quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behaviour.
+Compared to the considered non-self-tunable controllers, the control trajectories and the evaluated quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behavior.
 Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
@@
 
-To analyze the control more objectively, the energy consumption was also investigated.
-More specifically, the power used to heat the heating medium was measured and summarized for the whole control, but for every controller setup respectively.
+To analyze the control more objectively, energy consumption was also investigated.
+More specifically, the power used to heat the heating medium was measured and summarized for the whole control but for every controller setup, respectively.
 The energy consumption $E$ necessary for every control can be seen in Table~\ref{tab:energy}.
@@
 This paper presents a novel idea of tuning based on the size of reference step change.
-The self-tuning algorithm aims to compensate for the nonlinear behaviour of the controlled system.
+The self-tuning algorithm aims to compensate for the nonlinear behavior of the controlled system.
 The self-tuning parameter is updated when the reference changes.
 It is calculated as the ratio between the size of the reference change and the maximal possible size of the reference change, which is specified before operation.
-Another novel contribution addresses the challenging control problem of the asymmetric system behaviour by splitting the interval of tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
-The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behaviour.
+	Another novel contribution addresses the challenging control problem of asymmetric system behavior by splitting the interval of tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
+The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
@@
 To investigate the control results properly, the control performance was evaluated also quantitatively.
-Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the sum-of-squared control error, maximal overshoots/undershoots, and settling time.
+Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the integral squared control error, maximal overshoots/undershoots, and settling time.
 In addition, the energy consumption corresponding to every controller was evaluated as well.
 The value of consumed energy was between the two boundary controllers, i.e., the energy consumption did not deteriorate in general.
-With saving the energy compared to one of the boundary controllers, the control performance was significantly improved.
+With saving energy compared to one of the boundary controllers, the control performance was significantly improved.
 
@@
 			mp-QP& multi-parametric quadratic programming (problem) \\
+			PID  & proportional–integral–derivative (controller) \\
 			PWA  & piece-wise affine (function) \\

### 2023-02-03 paper/elsarticle/main.tex
schemes fixed + cover letter

@@
 		%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis}
-		%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behaviour}
+		%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behavior}
 		%
@@
 		%\author{Lenka Galčíková}
+		%\author{Petronela Belková}
 		%\author{Juraj Oravec}
-		%\author{Petronela Belková}
 		%
@@
 			%\item Self-tunable control technique does not need any intervention during control
-			%\item Tuning based on the operating conditions compensates the nonlinear plant behaviour
+			%\item Tuning based on the operating conditions compensates for the nonlinear plant behavior
 			%\item Implementation of the proposed tuning method on a laboratory heat exchanger 
@@
 Let $\gamma: \mathbb{R} \rightarrow \mathbb{R}$ be an arbitrary function such that $0 \leq \gamma \leq 1$ holds.
-Then the decision function $\gamma$ is constructed to assign its value either $\gamma \leq \rho_{\mathrm{s}}$ or $\gamma > \rho_{\mathrm{s}}$.
+Then the decision function $\gamma$ is constructed to assign its value either $\gamma \leq \rho_{\mathrm{s}}$ or $\gamma \ge \rho_{\mathrm{s}}$.
 	\end{definition}
-	\textcolor{red}{TODO: replace in the line above: $\gamma \ge \rho_{\mathrm{s}}$?}\\
 	Various decision functions $\gamma$ can be considered.
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{images/CL/tuning}
+		\includegraphics[width=\textwidth]{images/tuning}
 		\caption[Self-tuning scheme]{Self-tuning scheme.}
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{images/CL/CL}
+		\includegraphics[width=\textwidth]{images/cl}
 		\caption[Closed-loop scheme]{Closed-loop scheme.}

### 2023-02-03 paper/elsarticle/main.tex
Review: Introduction: references: extended

@@
 Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.
-
-	The heat exchangers, in their numerous variants integrated into many industrial plants, represent energy-demanding plants.
-From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task, see~\cite{RL20}.
+Recent survey on the applied thermal engineering focused on the energy saving and pollution reduction from the industrial perspective is provided in~\cite{YV16}.
+
+	The heat exchangers in their numerous variants are integrated into the many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
+Simultaneously, the heat exchangers are energy-demanding and resources-intensive plants.
+Moreover, from the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}.
 Although the conventional and widely-used proportional–integral–derivative (PID) controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
 Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the fouling~\cite{MT19}.
-Such widely-used control strategies include, e.g., the robust control~\cite{DO15,WY18}, the gain-scheduling, multi-zone control, see~\cite{MF08}, and references therein.
-
-	TODO: nepouzivat nasobne referencie ako [4,5] vyssie
+Such widely-used control strategies including, e.g., the robust control~\cite{WY18}, the gain-scheduling, self-tuning, adaptive and optimal control, see~\cite{MF08} for the rigorous mathematical modeling and controller design methods in general, and~\cite{Liptak} for the controller design tailored for the process control engineers.
 
@@
 A two-level control structure was applied on a heat exchanger network in~\cite{Gonzales_HE_MPC}, where the low level of control was ensured by MPC and the high level by a supervisory online optimizer.
+The fast nonlinear MPC was designed to optimize the waste heat recovery~\cite{WC19}.
+The multi-layer control designed in~\cite{DZ18} designed the MPC in the leader loop to optimize the thermal response to the improved control performance.
 
@@
 	\section{Theoretical backgrounds}
-	% \section{Preliminaries}
 	\label{sec:preliminaries}

### 2023-02-03 paper/elsarticle/main_LOCAL_471.tex
relative energy

--- 2023-02-03 paper/elsarticle/main.tex
@@
 More specifically, the power used to heat the heating medium was measured and summarized for the whole control but for every controller setup, respectively.
-The energy consumption $E$ necessary for every control can be seen in Table~\ref{tab:energy}.
+The energy consumption $E$ necessary for every control as well as the relative improvement subject to every boundary controller can be seen in Table~\ref{tab:energy}.
 
@@
 		\label{tab:energy}
-		\begin{tabular}{c|c} 
-			$Q_\mathrm{y}$ & E\,[kJ]   \\
+		\begin{tabular}{c|c|c} 
+			$Q_\mathrm{y}$ & E\,[kJ] & $\delta E\,[\%]$   \\
 			\hline
-			1000 &  883  \\ 
+			1000 &  883 & -4\\ 
 			% \hline
-			100 & 938   \\ 
+			100 & 938 & 2 \\ 
 			% \hline
-			self-tuned & 921   
+			self-tuned & 921 & -   
 		\end{tabular}
@@
 To investigate the control results properly, the control performance was evaluated also quantitatively.
-Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the integral squared control error, maximal overshoots/undershoots, and settling time.
+Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the integral squared control error up to 32\%, maximal overshoots/undershoots up to 18\%, and settling time up to 24\%.
 In addition, the energy consumption corresponding to every controller was evaluated as well.
 The value of consumed energy was between the two boundary controllers, i.e., the energy consumption did not deteriorate in general.
-With saving energy compared to one of the boundary controllers, the control performance was significantly improved.
+With saving the energy compared to one of the boundary controllers, the control performance was significantly improved.
 

### 2023-02-03 paper/elsarticle/main.tex
intro:grammar

@@
 Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.
-Recent survey on the applied thermal engineering focused on the energy saving and pollution reduction from the industrial perspective is provided in~\cite{YV16}.
+A recent survey on applied thermal engineering focused on energy saving and pollution reduction from the industrial perspective is provided in~\cite{YV16}.
 
 	The heat exchangers in their numerous variants are integrated into the many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
-Simultaneously, the heat exchangers are energy-demanding and resources-intensive plants.
-Moreover, from the control viewpoint, the controller design taking into account the nonlinear and asymmetric behaviour of the heat exchangers is a challenging task, see~\cite{RL20}.
+Simultaneously, the heat exchangers are energy-demanding and resource-intensive plants.
+Moreover, from the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task, see~\cite{RL20}.
 Although the conventional and widely-used proportional–integral–derivative (PID) controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
@@
 The fast nonlinear MPC was designed to optimize the waste heat recovery~\cite{WC19}.
-The multi-layer control designed in~\cite{DZ18} designed the MPC in the leader loop to optimize the thermal response to the improved control performance.
+The multi-layer control designed in~\cite{DZ18} designed the MPC in the leader loop to optimize the thermal response to improved control performance.
 
@@
 			\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
+			\caption{Controlled variable trajectory for two boundary controllers.
+The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
 			\label{fig:CV_boundaries}
@@
 			\label{tab:energy}
-		\begin{tabular}{c|c} 
-			$Q_\mathrm{y}$ & E\,[kJ]   \\
+			\begin{tabular}{c|c|c} 
+				$Q_\mathrm{y}$ & E\,[kJ] & $\delta E\,[\%]$   \\
 				\hline
-			1000 &  883  \\ 
+				1000 &  883 & -4\\ 
 				% \hline
-			100 & 938   \\ 
+				100 & 938 & 2 \\ 
 				% \hline
-			self-tuned & 921   
+				self-tuned & 921 & -   
 			\end{tabular}

### 2023-02-03 paper/elsarticle/main.tex
Review: Conclusions

--- 2023-02-03 paper/elsarticle/main.tex
@@
 
-	This paper deals with the experimental implementation of the self-tunable approximated explicit model predictive control and provides a strategy for an effective self-tuning controller design.
-Based on the current reference value, the tuning parameter is scaled using linear interpolation.
-The previously published work related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the system steady-state value.
-This paper presents a novel idea of tuning based on the size of reference step change.
+	This paper deals with the experimental implementation and analysis of the novel self-tunable approximated explicit model predictive control method and provides a strategy for an effective self-tuning controller design.
+Based on the current value of the piece-wise constant reference, the tuning parameter is scaled using linear interpolation.
+	In contrast to the previously published work related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the system steady-state value.
+This paper presents a novel perspective idea of the self-tuning based on the size of reference step change.
 The self-tuning algorithm aims to compensate for the nonlinear behavior of the controlled system.
-The self-tuning parameter is updated when the reference changes.
-It is calculated as the ratio between the size of the reference change and the maximal possible size of the reference change, which is specified before operation.
-	Another novel contribution addresses the challenging control problem of asymmetric system behavior by splitting the interval of tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
-The proposed method is implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
-The asymmetry makes the plant a suitable candidate for splitting the interval of the tuning parameter.
+The self-tuning parameter is updated whenever the reference changes.
+the tuning value is calculated as the ratio between the size of the reference change and the maximal admissible size of the reference change, which is specified before operation.
+	Another novel contribution addresses the challenging control problem of asymmetric system behavior by splitting the interval of the self-tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
+The proposed method is implemented on a laboratory-scaled heat exchanger with nonlinear and asymmetric behavior.
+The asymmetry makes the plant a suitable candidate to analyze the benefits of splitting the interval of the tuning parameter.
 The decision criterium is negativity or positivity of reference change.
-When the reference changed upwards, the control input was tuned in the first part of the interval and approached the boundary controller associated with the lower bound on the penalty matrix.
+When the reference changed upwards, the control input was tuned in the first part of the interval and approached the boundary controller associated with the lower bound on the selected penalty matrix.
 On the contrary, when the reference changed downwards, the control input was tuned to approach the control input from the boundary controller with the upper bound on the penalty matrix.
-To investigate the control results properly, the control performance was evaluated also quantitatively.
-Compared to the conventional control strategy handling just a single controller, the self-tunable control approach decreased the integral squared control error, maximal overshoots/undershoots, and settling time.
-In addition, the energy consumption corresponding to every controller was evaluated as well.
-The value of consumed energy was between the two boundary controllers, i.e., the energy consumption did not deteriorate in general.
-With saving energy compared to one of the boundary controllers, the control performance was significantly improved.
+To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
+Compared to the self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the integral squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
+The energy consumption of the self-tunable explicit MPC controller was in between the values of the two boundary non-tunable explicit MPC controllers, i.e., the total energy consumption trades off the performance of the boundary controllers.
+% did not deteriorate in general.
+	With saving the energy compared to one of the boundary controllers, the control performance was significantly improved.
 

### 2023-02-03 paper/elsarticle/main.tex
Review: Sec.4

@@
 	The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
-The heat exchanger is 90 mm wide, 103 mm long, and 160 mm high.
+The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
 The heat exchange is performed between the cold feed (water) and the hot medium (water).
@@
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
-The corresponding simplified closed-loop scheme can be seen in Figure~\ref{fig:CL}.
-Note, the ,,Self-tuning" block corresponds to the more detailed scheme in Figure~\ref{fig:tuning}.
+The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``self-tuning'' block substitutes the more detailed scheme in Figure~\ref{fig:tuning}.
 
@@
 Based on the set of experimentally collected data, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the reference value.
-Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1000.
+Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
 The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{x}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
@@
 			\includegraphics[width=\textwidth]{images/cl}
-			\caption[Closed-loop scheme]{Closed-loop scheme.}
+			\caption[Scheme of the implemented closed-loop control setup.]{Closed-loop scheme.}
 			\label{fig:CL}
@@
 
-	To analyze the control more objectively, energy consumption was also investigated.
-More specifically, the power used to heat the heating medium was measured and summarized for the whole control but for every controller setup, respectively.
-The energy consumption $E$ necessary for every control as well as the relative improvement subject to every boundary controller can be seen in Table~\ref{tab:energy}.
+	To analyze the control from the environmental viewpoint, the energy consumption was also investigated.
+Technically, the total power supply utilized to heat the heating medium was measured and summarized for the whole control but for each controller setup, respectively.
+The total energy consumption $E$ consumed by each controller as well as the relative improvement subject to each boundary controller is summarized in Table~\ref{tab:energy}.
 
@@
 		\begin{center}
-			\caption{Energy consumption evaluation.}
+			\caption{Evaluation of the total energy consumption.}
 			\label{tab:energy}
@@
 				\hline
-				1000 &  883 & -4\\ 
+				1000 &  883 & $-4$\\ 
 				% \hline
-				100 & 938 & 2 \\ 
+				100 & 938 & $2$ \\ 
 				% \hline
-				self-tuned & 921 & -   
+				self-tuned & 921 & $-$
 			\end{tabular}
@@
 
-	It can be seen in Table~\ref{tab:energy}, that utilizing the self-tuned controller leads to energy consumption which acquires value between the energy consumptions associated with the boundary controllers.
+	It can be seen in Table~\ref{tab:energy}, that utilizing the self-tuned controller leads to energy consumption which acquires value between the energy consumption corresponding to the boundary controllers.
 Although it is not the minimum one, the energy is still saved compared to the boundary controller with $Q_\mathrm{y} = 100$.
-Note, though the controller with $Q_\mathrm{y} = 1000$ leads to minimum energy consumption, using this single non-tuned controller does not lead to such control performance improvement.
-
-	In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (lower $\sigma_{\mathrm{max}}$), and faster achieving the reference value (lower $t_{\epsilon}$), while the control does not suffer in the terms of energy consumption.
+Note, though the controller with $Q_\mathrm{y} = 1\,000$ leads to minimum energy consumption, using this single non-tunable controller does not ensured the required control performance.
+As for the test bed served the laboratory-scaled heat exchanger plant, the greater energy savings are expected for the industrial-scaled plants.
+
+	In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$), while the control performance does not suffer in the terms of energy consumption.
 

### 2023-02-03 paper/elsarticle/main.tex
Review: Sec.3

@@
 
-	For a better insight into the proposed technique, the procedure of self-tuning is depicted in Fig.~\ref{fig:tuning}.
+	For a detailed insight into the proposed control technique, the procedure of self-tuning evaluation is depicted in Figure~\ref{fig:tuning}.
 
@@
 			\includegraphics[width=\textwidth]{images/tuning}
-			\caption[Self-tuning scheme]{Self-tuning scheme.}
+			\caption[Self-tuning scheme]{Scheme of the self-tuning control evaluation.}
 			\label{fig:tuning}

### 2023-02-03 paper/elsarticle/main.tex
FINALLY

@@
 	%
-	%\begin{frontmatter}
-		%
-		%%% Title, authors and addresses
-		%
-		%%% use the tnoteref command within \title for footnotes;
-		%%% use the tnotetext command for theassociated footnote;
-		%%% use the fnref command within \author or \address for footnotes;
-		%%% use the fntext command for theassociated footnote;
-		%%% use the corref command within \author for corresponding author footnotes;
-		%%% use the cortext command for theassociated footnote;
-		%%% use the ead command for the email address,
-		%%% and the form \ead[url] for the home page:
-		%%% \title{Title\tnoteref{label1}}
-		%%% \tnotetext[label1]{}
-		%%% \author{Name\corref{cor1}\fnref{label2}}
-		%%% \ead{email address}
-		%%% \ead[url]{home page}
-		%%% \fntext[label2]{}
-		%%% \cortext[cor1]{}
-		%%% \affiliation{organization={},
-			%%%             addressline={},
-			%%%             city={},
-			%%%             postcode={},
-			%%%             state={},
-			%%%             country={}}
-		%%% \fntext[label3]{}
-		%
-		%\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis}
-		%%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behavior}
-		%
-		%%% use optional labels to link authors explicitly to addresses:
-		%%% \author[label1,label2]{}
-		%%% \affiliation[label1]{organization={},
-			%%%             addressline={},
-			%%%             city={},
-			%%%             postcode={},
-			%%%             state={},
-			%%%             country={}}
-		%%%
-		%%% \affiliation[label2]{organization={},
-			%%%             addressline={},
-			%%%             city={},
-			%%%             postcode={},
-			%%%             state={},
-			%%%             country={}}
-		%
-		%\author{Lenka Galčíková}
-		%\author{Petronela Belková}
-		%\author{Juraj Oravec}
-		%
-		%\affiliation{organization={Slovak University of Technology in Bratislava, Faculty of Chemical and Food Technology, Institute of Information Engineering, Automation, and Mathematics,},%Department and Organization
-			%            addressline={Radlinského 9}, 
-			%            city={Bratislava},
-			%            postcode={81237}, 
-			%%            state={Slovakia},
-			%            country={Slovakia}
-			%}
-		%
-		%\begin{abstract}
+	\begin{frontmatter}
+
+		%% Title, authors and addresses
+
+		%% use the tnoteref command within \title for footnotes;
+		%% use the tnotetext command for theassociated footnote;
+		%% use the fnref command within \author or \address for footnotes;
+		%% use the fntext command for theassociated footnote;
+		%% use the corref command within \author for corresponding author footnotes;
+		%% use the cortext command for theassociated footnote;
+		%% use the ead command for the email address,
+		%% and the form \ead[url] for the home page:
+		%% \title{Title\tnoteref{label1}}
+		%% \tnotetext[label1]{}
+		%% \author{Name\corref{cor1}\fnref{label2}}
+		%% \ead{email address}
+		%% \ead[url]{home page}
+		%% \fntext[label2]{}
+		%% \cortext[cor1]{}
+		%% \affiliation{organization={},
+			%%             addressline={},
+			%%             city={},
+			%%             postcode={},
+			%%             state={},
+			%%             country={}}
+		%% \fntext[label3]{}
+
+		\title{Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis}
+		%\title{Self-tunable approximated explicit MPC: Implementation on a heat exchanger with an asymmetric behavior}
+
+		%% use optional labels to link authors explicitly to addresses:
+		%% \author[label1,label2]{}
+		%% \affiliation[label1]{organization={},
+			%%             addressline={},
+			%%             city={},
+			%%             postcode={},
+			%%             state={},
+			%%             country={}}
+		%%
+		%% \affiliation[label2]{organization={},
+			%%             addressline={},
+			%%             city={},
+			%%             postcode={},
+			%%             state={},
+			%%             country={}}
+
+		\author{Lenka Galčíková}
+		\author{Petronela Belková}
+		\author{Juraj Oravec}
+
+		\affiliation{organization={Slovak University of Technology in Bratislava, Faculty of Chemical and Food Technology, Institute of Information Engineering, Automation, and Mathematics,},%Department and Organization
+			            addressline={Radlinského 9}, 
+			            city={Bratislava},
+			            postcode={81237}, 
+			%            state={Slovakia},
+			            country={Slovakia}
+			}
+
+		\begin{abstract}
 			%%max 250 words!
@@
 The designed self-tunable controller improved control performance by decreasing integral squared error, maximal overshoots/undershoots and settling time compared to the conventional control strategy based on a single (not tuned) controller.
-			%\end{abstract}
+			\end{abstract}
 		%
@@
 		%
-		%%%Research highlights
-		%\begin{highlights}
-			%% 3-5 highlights, every one should not exceed 85 characters including spaces
-			%\item Self-tunable control technique does not need any intervention during control
-			%\item Tuning based on the operating conditions compensates for the nonlinear plant behavior
-			%\item Implementation of the proposed tuning method on a laboratory heat exchanger 
-			%\item Control performance improved compared to utilizing only one explicit MPC
-			%\end{highlights}
-		%
-		%\begin{keyword}
-			%tunable explicit MPC \sep self-tunable technique \sep tuning parameter \sep heat exchanger \sep control performance
-			%%% keywords here, in the form: keyword \sep keyword
-			%
-			%%% PACS codes here, in the form: \PACS code \sep code
-			%
-			%%% MSC codes here, in the form: \MSC code \sep code
-			%%% or \MSC[2008] code \sep code (2000 is the default)
-			%
-			%\end{keyword}
-		%
-		%\end{frontmatter}
+		%%Research highlights
+		\begin{highlights}
+			% 3-5 highlights, every one should not exceed 85 characters including spaces
+			\item Self-tunable control technique does not need any intervention during control
+			\item Tuning based on operating conditions compensates for the nonlinear plant behavior
+			\item Implementation of the proposed tuning method on a laboratory heat exchanger 
+			\item Control performance improved compared to utilizing only one explicit MPC
+			\end{highlights}
+
+		\begin{keyword}
+			tunable explicit MPC \sep self-tunable technique \sep tuning parameter \sep heat exchanger \sep control performance
+			%% keywords here, in the form: keyword \sep keyword
+
+			%% PACS codes here, in the form: \PACS code \sep code
+
+			%% MSC codes here, in the form: \MSC code \sep code
+			%% or \MSC[2008] code \sep code (2000 is the default)
+
+			\end{keyword}
+
+		\end{frontmatter}
 
@@
 Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the fouling~\cite{MT19}.
-Such widely-used control strategies including, e.g., the robust control~\cite{WY18}, the gain-scheduling, self-tuning, adaptive and optimal control, see~\cite{MF08} for the rigorous mathematical modeling and controller design methods in general, and~\cite{Liptak} for the controller design tailored for the process control engineers.
-
-	One of the promising control strategies addressing all these issues in an optimal way came with the formation and tuning of the model predictive control (MPC), e.g., see~\cite{Morari_MPC}.
+Such widely-used
+	control strategies include, e.g., the robust control~\cite{WY18}, the gain-scheduling, adaptive and optimal control.
+For the rigorous mathematical modeling and controller design methods in general, see~\cite{MF08} and for the controller design tailored for the process control engineers see~\cite{Liptak}.
+
+	One of the promising control strategies addressing all these issues in an optimal way came with the formation of the model predictive control (MPC), e.g., see~\cite{Morari_MPC}.
 MPC provides optimal control input based on the minimization of a specified cost function while considering a model of the system.
@@
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
-The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``self-tuning'' block substitutes the more detailed scheme in Figure~\ref{fig:tuning}.
+The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``Self-tuning'' block substitutes the more detailed scheme in Figure~\ref{fig:tuning}.
 
@@
 		\includegraphics[width=\textwidth]{images/cl}
-			\caption[Scheme of the implemented closed-loop control setup.]{Closed-loop scheme.}
+		\caption[Scheme of the implemented closed-loop control setup.]{Scheme of the implemented closed-loop control setup.}
 		\label{fig:CL}
@@
 		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-			\caption{Controlled variable trajectory for two boundary controllers.
-The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
+		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
 		\label{fig:CV_boundaries}
@@
 
-	To analyze the control from the environmental viewpoint, the energy consumption was also investigated.
-Technically, the total power supply utilized to heat the heating medium was measured and summarized for the whole control but for each controller setup, respectively.
+To analyze the control from the environmental viewpoint, energy consumption was also investigated.
+Technically, the total power supply utilized to heat the heating medium was measured and summarized for the whole control but for each controller setup respectively.
 The total energy consumption $E$ consumed by each controller as well as the relative improvement subject to each boundary controller is summarized in Table~\ref{tab:energy}.
@@
 Although it is not the minimum one, the energy is still saved compared to the boundary controller with $Q_\mathrm{y} = 100$.
-Note, though the controller with $Q_\mathrm{y} = 1\,000$ leads to minimum energy consumption, using this single non-tunable controller does not ensured the required control performance.
-As for the test bed served the laboratory-scaled heat exchanger plant, the greater energy savings are expected for the industrial-scaled plants.
+Note, though the controller with $Q_\mathrm{y} = 1\,000$ leads to minimum energy consumption, using this single non-tunable controller does not ensure the required control performance.
+As the laboratory-scaled heat exchanger plant served as the testbed, greater energy savings are expected for the industrial-scaled plants.
 
@@
 Based on the current value of the piece-wise constant reference, the tuning parameter is scaled using linear interpolation.
-	In contrast to the previously published work related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the system steady-state value.
-This paper presents a novel perspective idea of the self-tuning based on the size of reference step change.
+	The previously published work related to the self-tunable explicit MPC suggested tuning based on the distance of the reference value from the system steady-state value.
+This paper presents a novel perspective idea of self-tuning based on the size of reference step change.
 The self-tuning algorithm aims to compensate for the nonlinear behavior of the controlled system.
 The self-tuning parameter is updated whenever the reference changes.
-the tuning value is calculated as the ratio between the size of the reference change and the maximal admissible size of the reference change, which is specified before operation.
+The tuning value is calculated as the ratio between the size of the reference change and the maximal admissible size of the reference change, which is specified before operation.
 	Another novel contribution addresses the challenging control problem of asymmetric system behavior by splitting the interval of the self-tuning parameter into two ranges, while both intervals are assigned to different operating conditions.
@@
 To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
-Compared to the self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the integral squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the integral squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
 In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
-The energy consumption of the self-tunable explicit MPC controller was in between the values of the two boundary non-tunable explicit MPC controllers, i.e., the total energy consumption trades off the performance of the boundary controllers.
+The energy consumption of the self-tunable explicit MPC controller was in between the values of the two boundary non-tunable explicit MPC controllers.
+% the total energy consumption trades off the performance of the boundary controllers.
 % did not deteriorate in general.
-	With saving the energy compared to one of the boundary controllers, the control performance was significantly improved.
+	To conclude, with saving energy compared to one of the boundary controllers, the control performance was significantly improved.
 

### 2023-02-03 paper/elsarticle/main.tex
submission files

@@
 The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
-To ensure offset-free reference tracking control, the built-in integrator was included in the explicit MPC design.
 The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
-The designed self-tunable controller improved control performance by decreasing integral squared error, maximal overshoots/undershoots and settling time compared to the conventional control strategy based on a single (not tuned) controller.
+The designed self-tunable controller improved control performance by decreasing integral squared error, maximal overshoots/undershoots and settling time compared to the conventional control strategy based on a single controller.
 			\end{abstract}

### 2023-06-19 paper/ATE/cover_letter.tex
ATE update1

\documentclass[a4paper,10pt]{letter}
\usepackage{amsmath}
\usepackage{xcolor}
\linespread{1.2}
\begin{document}
\pagestyle{headings}
\begin{letter}{Dr. Xue-Chao Wang, Managing Guest Editor for Virtual Special Issue, ENERGY}

\opening{Dear Dr. Xue-Chao Wang,}

Enclosed you will find an electronic submission of a manuscript entitled ``Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis''. 
This is an original paper which has neither previously nor simultaneously been submitted to any other journal. This paper is an invited submission to the Virtual Special Issue of ENERGY with title ``Sustainable Use of Energy Contributes to Carbon Emissions Neutrality and Environmental Footprints Reduction''.

We would like to highlight the following contributions of the paper:
\begin{itemize}
	\item Self-tunable control technique does not need any intervention during control
	\item Tuning based on operating conditions compensates for the nonlinear plant behavior
	\item Implementation of the proposed tuning method on a laboratory heat exchanger 
	\item Control performance improved compared to utilizing only one explicit MPC
\end{itemize}

We believe that the presented study is, due to its character, of both industrial and academic interest and within the scope of the journal. We would very much appreciate if you would consider the manuscript for publication in the journal ENERGY.

Sincerely yours, \\
Lenka Gal\v{c}\'{i}kov\'{a}, Petronela Belkov\'{a}, and Juraj~Oravec
% \closing{Sincerely yours,\\Juraj~Oravec, Michaela Horv\'{a}thov\'{a}, and Monika Bako\v{s}ov\'{a}}

\end{letter}
\end{document}

### 2023-06-19 paper/ATE/main.tex
ATE update1

--- 2023-02-03 paper/elsarticle/main.tex
@@
 
-\journal{Energy}
+\journal{Applied Thermal Engineering}
 
@@
 			\item Implementation of the proposed tuning method on a laboratory heat exchanger 
-			\item Control performance improved compared to utilizing only one explicit MPC
+			\item Control performance improved compared to utilizing explicit MPC with constant setup
 			\end{highlights}
@@
 		\begin{center}
-			\includegraphics[width=\textwidth]{images/tuning}
+			\includegraphics[width=\textwidth]{images/tuning2}
 			\caption[Self-tuning scheme]{Scheme of the self-tuning control evaluation.}
@@
 The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
+The maximal voltage 5\,V or 100\% corresponds to flow rate 11.5\,$\mathrm{ml}\,\mathrm{s}^{-1}$.
 For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{images/cl}
-		\caption[Scheme of the implemented closed-loop control setup.]{Scheme of the implemented closed-loop control setup.}
+		\includegraphics[width=\textwidth]{images/cl2}
+		\caption[Scheme of the implemented closed-loop control setup.]{Scheme of the implemented closed-loop control setup, where ``eMPC'' denotes explicit MPC.}
 		\label{fig:CL}
@@
 On the contrary, the controller associated with $Q_\mathrm{y, U}$ is preferred for negative reference step changes.
-The splitting value of the tuning parameter was chosen in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
+The splitting value of the tuning parameter was chosen simply in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
 The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was determined to $15\,^{\circ}\mathrm{C}$ as the investigated range of controlled temperature was [$35-50$]$^{\circ}\mathrm{C}$.
@@
 		\begin{tabular}{ l l }
+			eMPC & explicit model predictive control \\
 			ISE  & integral squared error \\

### 2023-06-19 data/ploty.m

@@ -1,4 +1,4 @@
-load('ref_tracking38.mat')
+load('ref_tracking23.mat')
 %% Ordinary plots
 % close all
 figure(5)
@@ -16,8 +16,8 @@ xlim([0 3000])
 
 %% Paper
 close all, clear
-tuned = 0; %default - for boundary controllers
-load('ref_tracking35.mat') %1 -> Q_y = 1000
+tuned = 0; %default 0 - for boundary controllers
+load('ref_tracking31.mat') %1 -> Q_y = 1000
 from = 801;
 to = 6000;
 time = out.ScopeData(1:to-from+1,1);
@@ -25,7 +25,7 @@ ref = out.ScopeData(from:to,4);
 input1 = out.ScopeData(from:to,3);
 output1 = out.ScopeData(from:to,2);
 
-load('ref_tracking34.mat') %2 -> Q_y = 100
+load('ref_tracking32.mat') %2 -> Q_y = 100
 input2 = out.ScopeData(from:to,3);
 output2 = out.ScopeData(from:to,2);
 
@@ -76,3 +76,280 @@ else
     legend('$Q_\mathrm{y} = 1000$', '$Q_\mathrm{y} = 100$', 'Interpreter','latex', 'FontSize', fs) %only boundaries
 end
 grid minor
+%% Q
+Q = [100, 400, 250, 700, 850];
+t = out.ScopeData(1:5000,1);
+Qt = [];
+for i = 1:length(Q)
+    if i == 1
+        Qt = [Qt; Q(i)*ones(200,1)];
+    else
+        Qt = [Qt; Q(i)*ones(1200,1)];
+    end
+    
+end
+close all
+
+
+set(0,'defaulttextinterpreter','latex')
+lw = 1.5;
+fs = 13;
+green   = [0.2, 0.7, 0.1];
+
+figure, hold on, grid minor
+plot(t,Qt,'LineWidth',lw,'Color',green)
+plot(t,ones(5000,1)*100,'--','LineWidth',lw,'Color','k')
+plot(t,ones(5000,1)*1000,'--','LineWidth',lw,'Color','k')
+ylim([0 1100])
+set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
+xlabel('$t$ [s]')
+ylabel('$Q_{\mathrm{y}}$','FontSize', fs)
[…]

### 2023-06-20 paper/ATE/main.tex
ATE update2

@@
 	where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller respectively.
-The online tuning of the controller online comes with the cost of storing and evaluating two explicit controllers.
+The online tuning of the controller comes with the cost of storing and evaluating two explicit controllers.
 Nevertheless, the ability to tune the controller may be more important in many practical applications.
@@
 	\begin{remark}
-		Not only Eq.~\eqref{eq:tunable_u} needs to be chosen for interpolation of the control input. Another way of tuning the control input can be using some nonlinear relation for the interpolation. 
+		Not only Eq.~\eqref{eq:tunable_u} needs to be chosen for interpolation of the control input. Another way of tuning of the control input can be using some nonlinear relation for the interpolation. 
 	\end{remark}
@@
 	Various decision functions $\gamma$ can be considered.
-In this work, the decision functions according to Eq.~\eqref{eq:rho_max} and Eq.~\eqref{eq:rho_delta_ref} are considered, while Eq.~\eqref{eq:rho_delta_ref} was implemented in the experimental case study.
-
-	\begin{definition}[Scaling tuning parameter]
+In this work, the decision functions according to Eq.~\eqref{eq:rho_max} and Eq.~\eqref{eq:rho_delta_ref} are \textcolor{red}{suggested}, while Eq.~\eqref{eq:rho_delta_ref} was implemented in the experimental case study.
+
+	\begin{definition}[Scaling of the tuning parameter]
 		\label{def:rho_tilde}
-		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, in control law~\eqref{eq:PWA_control_law}, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, $0 < \gamma < 1$.
-Then the scaling tuning parameter $\widetilde{\rho}$ is given by:
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, $0 < \gamma < 1$.
+Then the scaling of the tuning parameter $\widetilde{\rho}$ is given by:
 		\begin{eqnarray}
@@
 		\label{rem:rho_tilde}		
-		The introduction of splitting the scaling tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only to two intervals.
+		The introduction of splitting the tuning parameter $\widetilde{\rho}$ into the tuning intervals in~\eqref{eq:rho_tilde_def} is not limited only to two intervals.
 If the nature of the controlled plant would benefit from splitting the operating range into more intervals, e.g., when the plant operates in the multiple steady-states values, then these intervals are simply determined by the corresponding values of $\rho_{\mathrm{s}, i}$ for each part of the interval.
@@
 		\label{lem:PWA_control_law_interval}
-		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaling tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}.
+		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaled tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}.
 Then the control law  approximated into the form:
@@
 		% 
-		It remains to prove that for any value of the scaling tuning parameter $\widetilde{\rho}$ according to the Definition~\ref{def:rho_tilde} the same results hold. 
+		It remains to prove that for any value of the scaled tuning parameter $\widetilde{\rho}$ according to the Definition~\ref{def:rho_tilde} the same results hold. 
 		The rest of the proof of Lemma~\ref{lem:PWA_control_law_interval} consists of two parts corresponding to each particular rule in~\eqref{eq:rho_tilde_def}. 
@@
 
+	\textcolor{red}{From the point of computational complexity, the proposed tuning procedure does not lead to any significantly demanding mathematical operations.
+Simple relations in Eq.~\eqref{eq:rho_delta_ref} and Eq.~\eqref{eq:rho_tilde_def} are evaluated.}
+
 	\begin{figure}
@@
 The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
-The maximal voltage 5\,V or 100\% corresponds to flow rate 11.5\,$\mathrm{ml}\,\mathrm{s}^{-1}$.
-For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
+\textcolor{red}{The maximal voltage 5\,V or 100\% corresponds to flow rate 11.5\,$\mathrm{ml}\,\mathrm{s}^{-1}$.} For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
@@
 
-These main experimental observations established the base for the strategy of self-tuning the penalty matrix $Q_\mathrm{y}$.
+\textcolor{red}{These main experimental observations established the base for the strategy of controller self-tuning.
 The strategy follows the ideas summarized in Section~\ref{sec:methodology}.
-Therefore, utilizing the boundary controller with the penalty matrix $Q_\mathrm{y, L}$ is preferred when the reference changes upwards.
-On the contrary, the controller associated with $Q_\mathrm{y, U}$ is preferred for negative reference step changes.
+Utilizing the nature of the boundary controller with the penalty matrix $Q_\mathrm{y, L}$ is preferred when the reference changes upwards.
+Therefore, in these operating conditions, the tuning factor is scaled in the first part of the whole interval, i.e., closer to the lower bound.
+On the contrary, tuning the controller closer to the upper boundary controller associated with $Q_\mathrm{y, U}$ is preferred for negative reference step changes.
+Therefore, in these operating conditions, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$, i.e., closer to the upper bound.
 The splitting value of the tuning parameter was chosen simply in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
 The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was determined to $15\,^{\circ}\mathrm{C}$ as the investigated range of controlled temperature was [$35-50$]$^{\circ}\mathrm{C}$.
+Based on the aforementioned parameters and real-time information about the current reference change, the tuning factor was updated during control.
+The evolution of the scaled tuning factor can be seen in Fig.~\ref{fig:rho}.
+When the positive reference changes are tracked, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$.
+On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$.}
+
+\textcolor{red}{The setup of the tuning factor can be associated with tuning of the penalty matrix $Q_{\mathrm{y}}$ according to Eq.~\eqref{eq:tunable_Qy}.
+The evolution of the penalty matrix during control is depicted in Fig.~\ref{fig:Q}.
+Note, the penalty matrix evolution in Fig.~\ref{fig:Q} does not correspond to tuning of the optimal MPC, but serves for a better vision of association of the interpolated control inputs with the optimal explicit MPC setup.}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/rho}
+		\caption{Evolution of the scaled tuning factor $\widetilde{\rho}$ during control.
+When tracking positive reference changes, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$.
+On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$.}
+		\label{fig:rho}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/Q}
+		\caption{Evolution of the penalty matrix $Q_{\mathrm{y}}$ during control.
+When tracking positive reference changes, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, L}$.
+On the contrary, when the reference changes are negative, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, U}$.}
+		\label{fig:Q}
+	\end{center}
+\end{figure}
 
@@
 
-To analyze the control from the environmental viewpoint, energy consumption was also investigated.
+%To analyze the control from the environmental viewpoint, energy consumption was also investigated.
 Technically, the total power supply utilized to heat the heating medium was measured and summarized for the whole control but for each controller setup respectively.
@@
 
-\begin{table}[h!]
-	\begin{center}
-		\caption{Evaluation of the total energy consumption.}
-		\label{tab:energy}
-		\begin{tabular}{c|c|c} 
-			$Q_\mathrm{y}$ & E\,[kJ] & $\delta E\,[\%]$   \\
-			\hline
-			1000 &  883 & $-4$\\ 
+%\begin{table}[h!]
+%	\begin{center}
+%		\caption{Evaluation of the total energy consumption.}
+%		\label{tab:energy}
+%		\begin{tabular}{c|c} 
+%			$Q_\mathrm{y}$ & $E$\,[kJ] \\
 %			\hline
-			100 & 938 & $2$ \\ 
-			% \hline
-			self-tuned & 921 & $-$
-		\end{tabular}
-	\end{center}
-\end{table}
-
-It can be seen in Table~\ref{tab:energy}, that utilizing the self-tuned controller leads to energy consumption which acquires value between the energy consumption corresponding to the boundary controllers.
+%			1000 &  885 \\ 
+%			% \hline
+%			100 & 904 \\ 
+%			% \hline
+%			self-tuned & 943
+%		\end{tabular}
+%	\end{center}
+%\end{table}
+
+%It can be seen in Table~\ref{tab:energy}, that utilizing the self-tuned controller leads to energy consumption which acquires value between the energy consumption corresponding to the boundary controllers.
 Although it is not the minimum one, the energy is still saved compared to the boundary controller with $Q_\mathrm{y} = 100$.
@@
 
-In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$), while the control performance does not suffer in the terms of energy consumption.
+In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$).
+%, while the control performance does not suffer in the terms of energy consumption.
 
@@
 The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the integral squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
-In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
+%In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
 The energy consumption of the self-tunable explicit MPC controller was in between the values of the two boundary non-tunable explicit MPC controllers.
@@
 % did not deteriorate in general.
-	To conclude, with saving energy compared to one of the boundary controllers, the control performance was significantly improved.
+	%To conclude, with saving energy compared to one of the boundary controllers, the control performance was significantly improved.
 

### 2023-06-21 paper/ATE/main.tex
ATE update3

@@
 	\textcolor{red}{From the point of computational complexity, the proposed tuning procedure does not lead to any significantly demanding mathematical operations.
-Simple relations in Eq.~\eqref{eq:rho_delta_ref} and Eq.~\eqref{eq:rho_tilde_def} are evaluated.}
+Simple relations in Eq.~\eqref{eq:rho_delta_ref} and Eq.~\eqref{eq:rho_tilde_def} are evaluated.
+Q: Mergnut s tym, co som pridala ako dosledky tunable eMPC ako takeho?
+Ze sa zvysi pamat a cas, lebo sa vyuzivaju dva eMPC?}
 
@@
 The system was identified by experimental identification.
-More specifically, several step responses were obtained in the whole range of the input variable steps.
+\textcolor{red}{The aim was to work with linear nominal model in MPC optimization problem to decrease the numerical complexity.
+To avoid plant-model mismatch in order to ensure offset-free tracking, either disturbance observer or built-in integrator (Eq.~\eqref{eq:mpc_problem}) can be employed.
+Note, in this work, the built-in integrator was considered.
+The system was identified based on several step responses.
+The step changes were performed in the whole range of admissible values of manipulated variable and every step response was identified by transfer function.
+It was possible to identify every step response as a first-order system, while the nominal gain and time constant are respectively $K = 0.2418\,^{\circ}\mathrm{C}$ and $\tau = 5.7$\,s.
+(TODO: checknut units pre gain a pridat symboly do nomenklatury, ak sa zhodneme na oznaceni)}
+%More specifically, several step responses were obtained in the whole range of the input variable steps.
 Every step response was identified as a first-order system and the nominal transfer function was calculated.
-Finally, the transfer function was converted to the state-space model.
-The matrices of the discrete-time state-space model of the plant are
+Finally, the nominal transfer function was converted to the state-space model. The matrices of the discrete-time state-space model of the plant are
 \begin{subequations}
@@
 Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterward.
+
+\textcolor{red}{An interesting phenomenon can be observed during tracking the third reference value, i.e.
+$T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
+Although the steady-state values of temperature have the same value, the values of the manipulated variable are different.
+To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
+The reason could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s.
+After approximately 100\,s the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller.
+This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which can be explained by the nonlinear behavior of the heat transfer process.
+When working in higher temperatures, the heat transfer process gain decreases and the sensitivity to changes in the heating medium flow is lower.
+Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
+}
 
@@
 
+	\textcolor{red}{Note, this strategy relies on a proper design of the two boundary controllers.
+In case a disturbance occurs, both boundary controllers should be able to solve a disturbance rejection problem, as the final value of the manipulated variables is interpolated between them.
+The future work will focus on incorporating also the measurable disturbances into the tuning strategy.}
 	\section*{Acknowledgments}

### 2023-06-22 paper/ATE/main.tex
ATE update4

@@
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
-This paper provides a novel self-tunable control policy that does not require any further tuning or interventions of the control engineer during operation.
+This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation \textcolor{red}{in order to properly tune the controller}.
 Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
@@
 
-	The heat exchangers in their numerous variants are integrated into the many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
+	The heat exchangers in their numerous variants are integrated into many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
 Simultaneously, the heat exchangers are energy-demanding and resource-intensive plants.
 Moreover, from the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task, see~\cite{RL20}.
-Although the conventional and widely-used proportional–integral–derivative (PID) controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
-Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the fouling~\cite{MT19}.
-Such widely-used
-	control strategies include, e.g., the robust control~\cite{WY18}, the gain-scheduling, adaptive and optimal control.
+What should be also considered, is a choice of the controlled variable, as the outlet stream temperature does not have to be always the efficient one.
+In~\cite{JIN_CV}, the idea is to optimize the controlled variable of counter flow heat exchanger.
+A new controlled variable named as heat exchanger comprehensive effectiveness is introduced, based on maximizing the amount of heat exchange and minimizing the irreversible loss.
+
+	Very common challenge in terms of heat exchangers is fouling.
+In~\cite{TRAFCZYNSKI_fouling}, the authors address this effect while using proportional–integral–derivative (PID) control.
+If the thermal resistance of fouling is increased and the parameters of controller remain unchanged, it could lead to oscillations of the controlled temperature, too slow response to setpoint changes or significant temperature overshoot.
+To prevent these effects, the PID controller parameters are adjusted.
+
+	Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
+Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the already mentioned fouling~\cite{MT19}.
+Such widely-used control strategies include, e.g., the robust control~\cite{WY18}, the gain-scheduling, adaptive and optimal control.
+In~\cite{VASICKANINOVA_HE}, a neural network predictive controller together with the fuzzy controller in the complex control structure with an auxiliary control variable was investigated.
 For the rigorous mathematical modeling and controller design methods in general, see~\cite{MF08} and for the controller design tailored for the process control engineers see~\cite{Liptak}.
@@
 In~\cite{Vinaya_HE_MPC}, the authors developed a model predictive control for a shell and tube heat exchanger.
-In~\cite{Oravec_energy}, the control performance of the robust MPC implemented for a plate heat exchanger with soft constraints was analyzed.
+%In~\cite{Oravec_energy}, the control performance of the robust MPC implemented on a plate heat exchanger with soft constraints was analyzed.
 	Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}.
@@
 The multi-layer control designed in~\cite{DZ18} designed the MPC in the leader loop to optimize the thermal response to improved control performance.
+In~\cite{DYRSKA_HE}, the authors focus on reduction of computational complexity associated with the evaluation of control action of MPC.
+By implementing the constraint removal technique, the energy consumption of the microcontroller is reduced.
 
@@
 \sum_{k=0}^{N-1} \!
-\left( (y_k-y_\mathrm{ref})^{\intercal} Q_\mathrm{y} (y_k-y_\mathrm{ref}) + u_{k}^{\intercal} R u_{k} + x_{\mathrm{I},k}^{\intercal} Q_\mathrm{x} x_{\mathrm{I},k} \right)  \\
+\left( (y_k-y_\mathrm{ref})^{\intercal} Q_\mathrm{y} (y_k-y_\mathrm{ref}) + u_{k}^{\intercal} R u_{k} + x_{\mathrm{I},k}^{\intercal} Q_\mathrm{I} x_{\mathrm{I},k} \right)  \\
 			\label{eq:mpc_problem_prediction_model_x}
@@
 	%
-	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{x} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$. 
+	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$. 
 	%
@@
 
-	The augmented model of the controlled system with the built-in integrator in Eq.~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} us rewritten as follows:
+	The augmented model of the controlled system with the built-in integrator in Eq.~\eqref{eq:mpc_problem_prediction_model_x}--\eqref{eq:mpc_problem_prediction_model_y} is rewritten as follows:
 	\begin{subequations}
@@
 	\end{subequations}
-	where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time, and matrices $A$, $B$, $C$ are well-known the state-space matrices that form the augmented LTI model.
-As the consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error is penalized, but also an integrated value, which leads to analogous offset-free reference tracking results as incorporating an integral part in PID controller.
-
-	The parametric solution of the optimization problem of the quadratic programming (QP) in Eq.~\eqref{eq:mpc_problem}, leads to the explicit solution in the form of piecewise affine PWA control law defined above the domain consisting of $r$ critical regions:
+	where $x_{\mathrm{I}} \in \mathbb{R}^{n_{\mathrm{y}}}$ is the integral of the control error, $T_\mathrm{s}$ denotes the sampling time, and matrices $A$, $B$, $C$ are the well-known state-space matrices that form the augmented LTI model.
+As a consequence of this extension and penalization in the cost function in Eq.~\eqref{eq:mpc_problem_cost}, not only the control error is penalized, but also the integrated value, which leads to analogous offset-free reference tracking results as incorporating an integral part in the PID controller.
+
+	The parametric solution of the optimization problem of the quadratic programming (QP) in Eq.~\eqref{eq:mpc_problem} leads to the explicit solution in the form of piecewise affine PWA control law defined above the domain consisting of $r$ critical regions:
 	\begin{eqnarray}
@@
 The PWA function defined in Eq.~\eqref{eq:PWA_control_law} is stored and recalled in the online phase, i.e., during the real-time control.
-Based on identifying the specific critical region $\mathcal{R}_{i}$, where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law in Eq.~\eqref{eq:PWA_control_law}.
-
-	Note, many other formulations of the optimization problems for the explicit MPC design, were mainly in the terms of the definition of the cost functions in Eq.~\eqref{eq:mpc_problem_cost}.
+Based on identifying the specific polytopic critical region $\mathcal{R}_{i}$, where the parameter $\theta$ belongs, the optimal control input is calculated based on the associated control law in Eq.~\eqref{eq:PWA_control_law}.
+
+	Note, many other formulations of the optimization problems for the explicit MPC design were formulated mainly in terms of the definition of the cost functions in Eq.~\eqref{eq:mpc_problem_cost}.
 Also, the incremental (velocity) formulation of the state-space model is common, but leads to further extension of the vector of parameters $\theta$, and therefore also the complexity of the explicit MPC controller increases.
@@
 When the multi-parametric QP (mp-QP) problem is precomputed offline to obtain the corresponding parametric solution, it is not possible to tune the controller afterward without trading off a significant increase in the controller complexity or the performance loss.
-As the operating conditions and requirements of controller setup may differ throughout the control, the ability to adjust the controller's aggressivity can be very beneficial.
+As the operating conditions and requirements on controller setup may differ throughout the control, the ability to adjust the controller's aggressivity can be very beneficial.
 
@@
 			\label{eq:tunable_Qx}
-			&~& Q_\mathrm{x}(k) = (1-\rho(k)) \, Q_\mathrm{x,L} + \rho(k) \, Q_\mathrm{x,U}, \\
+			&~& Q_\mathrm{I}(k) = (1-\rho(k)) \, Q_\mathrm{I,L} + \rho(k) \, Q_\mathrm{I,U}, \\
 			\label{eq:tunable_Qy}
@@
 	Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
-As a consequence, the parameter $\rho$ represents a way how to normalize the deviation from the steady-state value and is exploited to scale the penalty matrix or, implicitly, to scale the aggressiveness of the control action.
+As a consequence, the parameter $\rho$ represents a way how to normalize the deviation from the steady-state value and is exploited to scale the control action or, implicitly, to tune the aggressiveness of the controller.
 
@@
 		\label{def:rho_tilde}
-		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, $0 < \gamma < 1$.
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, \textcolor{red}{$0 < \gamma < 1$}.
 Then the scaling of the tuning parameter $\widetilde{\rho}$ is given by:
@@
 		\label{lem:PWA_control_law_interval}
-		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaled tuning parameter $\widetilde{\rho}$ according Definition~\ref{def:rho_tilde}.
-Then the control law  approximated into the form:
+		Given control law in~\eqref{eq:PWA_control_law}, its approximation given by the convex combination in~\eqref{eq:tunable_u}, and given scaled tuning parameter $\widetilde{\rho}$ according to Definition~\ref{def:rho_tilde}.
+Then the control action approximated into the form:
 		\begin{eqnarray}
@@
 		Therefore, any value of $\widetilde{\rho}$ satisfies $0 \leq \widetilde{\rho} \leq \rho_{\mathrm{s}} < 1$.
-As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
+As a consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
 		\\
@@
 		Therefore, any value of $\widetilde{\rho}$ satisfies $\rho_{\mathrm{s}} \leq \widetilde{\rho} \leq 1$.
-As the consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
+As a consequence, according to the Theorem~3.6 in~\cite{Oravec_tunable}, the asymptotic stability and recursive feasibility of the control law in~\eqref{eq:PWA_control_law_interval} are preserved.
 		% The rest of the proof follows the proof of the Theorem~3.6 in~\cite{Oravec_tunable}. 
@@
 The step changes were performed in the whole range of admissible values of manipulated variable and every step response was identified by transfer function.
-It was possible to identify every step response as a first-order system, while the nominal gain and time constant are respectively $K = 0.2418\,^{\circ}\mathrm{C}$ and $\tau = 5.7$\,s.
-(TODO: checknut units pre gain a pridat symboly do nomenklatury, ak sa zhodneme na oznaceni)}
+It was possible to identify every step response as a first-order system, while the nominal gain and time constant are respectively $K = 0.24\,^{\circ}\mathrm{C}$ and $\tau = 5.7$\,s.
+(TODO: pridat symboly do nomenklatury, ak sa zhodneme na oznaceni)}
 %More specifically, several step responses were obtained in the whole range of the input variable steps.
@@
 
-The penalty matrices of the problem Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
+The penalty matrices of the problem in Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
 First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
@@
 Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
-The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{x}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
+The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{I}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
 The prediction horizon $N$ was set to 20 control steps.
@@
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which can be explained by the nonlinear behavior of the heat transfer process.
-When working in higher temperatures, the heat transfer process gain decreases and the sensitivity to changes in the heating medium flow is lower.
+When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
 Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{images/cl2}
+		\includegraphics[width=\textwidth]{images/cl3}
 		\caption[Scheme of the implemented closed-loop control setup.]{Scheme of the implemented closed-loop control setup, where ``eMPC'' denotes explicit MPC.}
@@
 
-The trajectories in Figure~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the plant of plate heat exchange mainly when observing the overshoots and undershoots.
-When applying the control inputs associated with the lower bound $Q_\mathrm{y, L}$ in Eq.~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
+The trajectories in Figure~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the plant of plate heat exchanger mainly when observing the overshoots and undershoots.
+When applying the control inputs associated with the lower boundary penalty matrix $Q_\mathrm{y, L}$ in Eq.~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
 On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
@@
 Based on the aforementioned parameters and real-time information about the current reference change, the tuning factor was updated during control.
-The evolution of the scaled tuning factor can be seen in Fig.~\ref{fig:rho}.
+The evolution of the scaled tuning factor can be seen in Figure~\ref{fig:rho}.
 When the positive reference changes are tracked, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$.
@@
 \textcolor{red}{The setup of the tuning factor can be associated with tuning of the penalty matrix $Q_{\mathrm{y}}$ according to Eq.~\eqref{eq:tunable_Qy}.
-The evolution of the penalty matrix during control is depicted in Fig.~\ref{fig:Q}.
-Note, the penalty matrix evolution in Fig.~\ref{fig:Q} does not correspond to tuning of the optimal MPC, but serves for a better vision of association of the interpolated control inputs with the optimal explicit MPC setup.}
+The evolution of the penalty matrix during control is depicted in Figure~\ref{fig:Q}.
+Note, the penalty matrix evolution in Figure~\ref{fig:Q} does not correspond to tuning of the optimal MPC, but serves for a better vision of association of the interpolated control inputs with the optimal explicit MPC setup.}
 

### 2023-06-22 paper/ATE/cover_letter.tex
ATE cover letter

@@
 \pagestyle{headings}
-\begin{letter}{Dr. Xue-Chao Wang, Managing Guest Editor for Virtual Special Issue, ENERGY}
+\begin{letter}{Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}
 
-\opening{Dear Dr. Xue-Chao Wang,}
+\opening{Dear Dr. Christos N. Markides,}
 
 Enclosed you will find an electronic submission of a manuscript entitled ``Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis''.
-This is an original paper which has neither previously nor simultaneously been submitted to any other journal.
-This paper is an invited submission to the Virtual Special Issue of ENERGY with title ``Sustainable Use of Energy Contributes to Carbon Emissions Neutrality and Environmental Footprints Reduction''.
+It is an original paper that has already been submitted to the journal Energy and rejected due to insufficient communication of the proposed method in the results section.
+We updated the manuscript based on the reviewers' comments and suggestions, and hope that we managed to make the manuscript more readable and of higher quality.
 
@@
 	\item Implementation of the proposed tuning method on a laboratory heat exchanger 
-	\item Control performance improved compared to utilizing only one explicit MPC
+	\item Control performance improved compared to utilizing explicit MPC with constant setup
 \end{itemize}
@@
 We believe that the presented study is, due to its character, of both industrial and academic interest and within the scope of the journal.
-We would very much appreciate if you would consider the manuscript for publication in the journal ENERGY.
+We would very much appreciate if you would consider the manuscript for publication in the journal Applied Thermal Engineering.
 

### 2023-06-28 paper/ATE/cover_letter.tex
ATE update5

@@
 \pagestyle{headings}
-\begin{letter}{Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}
+\begin{letter}{Professor Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}
 
-\opening{Dear Dr. Christos N. Markides,}
+\opening{Dear Professor Christos N. Markides,}
 
@@
 It is an original paper that has already been submitted to the journal Energy and rejected due to insufficient communication of the proposed method in the results section.
-We updated the manuscript based on the reviewers' comments and suggestions, and hope that we managed to make the manuscript more readable and of higher quality.
+We carefully revisited and updated the manuscript based on the reviewers' comments and suggestions, and hope that we managed to make the manuscript more readable and of higher quality.
 
@@
 
-Sincerely yours, \\
+Sincerely Yours, \\
 Lenka Gal\v{c}\'{i}kov\'{a}, Petronela Belkov\'{a}, and Juraj~Oravec

### 2023-06-28 paper/ATE/main.tex
ATE update5

@@
 			%%max 250 words!			
-
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
-This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation \textcolor{red}{in order to properly tune the controller}.
+This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to properly tune the controller.
 Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
@@
 The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
-The designed self-tunable controller improved control performance by decreasing integral squared error, maximal overshoots/undershoots and settling time compared to the conventional control strategy based on a single controller.
+The designed self-tunable controller improved control performance by decreasing sum-of-squared control error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-tunable) controller.
 		\end{abstract}
@@
 	The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are convex polytopic sets of physical constraints on inputs and outputs, respectively.
+These sets include the origin in their strict interiors.
 The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
@@
 			F_{2} \, \theta + g_{2} & \mathrm{else}\,\,\mathrm{if} &\quad \theta \in \mathcal{R}_2, \\
-			\vdots & \\
+			& \vdots & \\
 			F_{r} \, \theta + g_{r} & \mathrm{else}\,\,\mathrm{if} & \quad \theta \in \mathcal{R}_{r}, \\
@@
 Another option for offset-free tracking is introducing disturbance modeling and estimation.
-For such an overview see e.g.~\cite{Klauco_mpc}
+For such an overview see, e.g,.~\cite{Klauco_mpc}
 
@@
 		%\end{subequations}
-	where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller respectively.
+	where $u_\mathrm{L}$ and $u_\mathrm{U}$ denote the optimal control actions from the lower and upper boundary controller, respectively.
 The online tuning of the controller comes with the cost of storing and evaluating two explicit controllers.
@@
 	\end{eqnarray}
-	where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero corresponds to the system steady-state value.
+	where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
 Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
@@
 If $d_{\max}$ is scalar, the parameter $\rho$ is scalar as well and can be directly utilized to scale the control action.
-If multiple outputs are controlled, it is suggested to calculate the tuning parameter based on the maximal ratio:
+If multiple outputs are controlled, it is suggested to calculate the tuning parameter based on the maximal ratio as follows:
 		\begin{eqnarray}
@@
 	Various decision functions $\gamma$ can be considered.
-In this work, the decision functions according to Eq.~\eqref{eq:rho_max} and Eq.~\eqref{eq:rho_delta_ref} are \textcolor{red}{suggested}, while Eq.~\eqref{eq:rho_delta_ref} was implemented in the experimental case study.
+In this work, the decision functions according to Eq.~\eqref{eq:rho_max} and Eq.~\eqref{eq:rho_delta_ref} are suggested, while Eq.~\eqref{eq:rho_delta_ref} was implemented in the experimental case study.
 
@@
 		\label{def:rho_tilde}
-		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, \textcolor{red}{$0 < \gamma < 1$}.
+		Given the value of tuning parameter $\rho$, $0 \leq \rho \leq 1$, the splitting value of the tuning parameter interval $\rho_{\mathrm{s}}$, $0 < \rho_{\mathrm{s}} < 1$, and the value of the decision function $\gamma$, $0 \leq \gamma \leq 1$.
 Then the scaling of the tuning parameter $\widetilde{\rho}$ is given by:
@@
 
-	\textcolor{red}{From the point of computational complexity, the proposed tuning procedure does not lead to any significantly demanding mathematical operations.
-Simple relations in Eq.~\eqref{eq:rho_delta_ref} and Eq.~\eqref{eq:rho_tilde_def} are evaluated.
-Q: Mergnut s tym, co som pridala ako dosledky tunable eMPC ako takeho?
-Ze sa zvysi pamat a cas, lebo sa vyuzivaju dva eMPC?}
+	From the point of computational complexity, the proposed tuning procedure does not lead to any significantly demanding mathematical operations.
+Simple algebraic operations in Eq.~\eqref{eq:rho_delta_ref} and Eq.~\eqref{eq:rho_tilde_def} are evaluated.
+Note, the overall control strategy still comes with the cost of storing and evaluating two explicit controllers.
 
@@
 The voltage is within the range of [$0-5$]\,V normalized into the relative values in percentage.
-\textcolor{red}{The maximal voltage 5\,V or 100\% corresponds to flow rate 11.5\,$\mathrm{ml}\,\mathrm{s}^{-1}$.} For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
+The maximal voltage 5\,V or 100\% corresponds to volumetric flow rate 11.5\,$\mathrm{ml}\,\mathrm{s}^{-1}$.
+For further technical specifications of the laboratory heat exchanger, the reader is referred to~\cite{pct23}.
 As heat exchange is a nonlinear and asymmetric process~\cite{Liptak}, this heat exchanger represents a suitable candidate for the presented controller tuning strategy.
-The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``Self-tuning'' block substitutes the more detailed scheme in Figure~\ref{fig:tuning}.
+The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``Self-tuning'' block substitutes the more detailed scheme of the tuning procedure in Figure~\ref{fig:tuning}.
 
 The system was identified by experimental identification.
-\textcolor{red}{The aim was to work with linear nominal model in MPC optimization problem to decrease the numerical complexity.
+The aim was to work with linear nominal model in MPC optimization problem to decrease the numerical complexity.
 To avoid plant-model mismatch in order to ensure offset-free tracking, either disturbance observer or built-in integrator (Eq.~\eqref{eq:mpc_problem}) can be employed.
-Note, in this work, the built-in integrator was considered.
-The system was identified based on several step responses.
+Due to the ease of implementation, in this work, the built-in integrator was considered.
+The system was identified based on several measured step responses.
 The step changes were performed in the whole range of admissible values of manipulated variable and every step response was identified by transfer function.
 It was possible to identify every step response as a first-order system, while the nominal gain and time constant are respectively $K = 0.24\,^{\circ}\mathrm{C}$ and $\tau = 5.7$\,s.
-(TODO: pridat symboly do nomenklatury, ak sa zhodneme na oznaceni)}
 %More specifically, several step responses were obtained in the whole range of the input variable steps.
@@
 	\label{eq:u_const}
-	-15\% \le u \le 65\%,
+	-15\,\% \le u \le 65\,\%,
 \end{eqnarray}
 where the variable $u$ represents the control inputs in the deviation form.
-The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35 $^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\%.
+The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35\,$^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\,\%.
 Therefore, the physical constraints on the manipulated variable are actually
@@
 	\label{eq:U_const}
-	20\% \le U \le 100\%.
+	20\,\% \le U \le 100\,\%.
 \end{eqnarray}	
@@
 The reference changes also acquired different sizes in order to examine the proposed tuning method as it is dependent on the size of the reference step change.
-Specifically, the reference temperature values were $T_{\mathrm{ref}}$ = 35$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 50$^{\circ}\mathrm{C}$, 45$^{\circ}\mathrm{C}$, 35$^{\circ}\mathrm{C}$.
+Specifically, the reference temperature values were $T_{\mathrm{ref}}$ = 35\,$^{\circ}\mathrm{C}$, 45\,$^{\circ}\mathrm{C}$, 50\,$^{\circ}\mathrm{C}$, 45\,$^{\circ}\mathrm{C}$, 35\,$^{\circ}\mathrm{C}$.
 
@@
 The heating medium was transported back to the heater after leaving the heat exchanger, i.e., the volume of the heating medium was recycled during the whole operation.
-The temperature of the heating medium was maintained on the value 70$^{\circ}\mathrm{C}$ with a simple proportional controller with proportional gain $P = 20$.
+The temperature of the heating medium was maintained on the value 70\,$^{\circ}\mathrm{C}$ with a simple proportional controller with proportional gain $P = 20$.
 The control input from the proportional controller was the electric power which could acquire the values in the range [$0-2$]\,kW and was also normalized to percentage.
@@
 
-\textcolor{red}{An interesting phenomenon can be observed during tracking the third reference value, i.e.
-$T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
+An interesting phenomenon can be observed during tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
 Although the steady-state values of temperature have the same value, the values of the manipulated variable are different.
 To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
-The reason could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s.
-After approximately 100\,s the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller.
+The reason could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~\ref{fig:MV_boundaries}, blue.
+After approximately 100\,s, the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller, see Figure~\ref{fig:MV_boundaries}, red.
 This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
-This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which can be explained by the nonlinear behavior of the heat transfer process.
+This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
 When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
 Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
-}
 
@@
 When applying the control inputs associated with the lower boundary penalty matrix $Q_\mathrm{y, L}$ in Eq.~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
-On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards.
-
-\textcolor{red}{These main experimental observations established the base for the strategy of controller self-tuning.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards, see Figure~\ref{fig:CV_boundaries}, blue.
+
+These main experimental observations established the base for the strategy of controller self-tuning.
 The strategy follows the ideas summarized in Section~\ref{sec:methodology}.
@@
 The splitting value of the tuning parameter was chosen simply in the middle of the interval, i.e., $\rho_{\mathrm{s}} = 0.5$.
-The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was determined to $15\,^{\circ}\mathrm{C}$ as the investigated range of controlled temperature was [$35-50$]$^{\circ}\mathrm{C}$.
+The remaining parameter that needed to be set was the maximal admissible size of the reference step change $\Delta_{\max}$, which was determined to $15\,^{\circ}\mathrm{C}$ as the investigated range of controlled temperature was [$35-50$]\,$^{\circ}\mathrm{C}$.
 Based on the aforementioned parameters and real-time information about the current reference change, the tuning factor was updated during control.
-The evolution of the scaled tuning factor can be seen in Figure~\ref{fig:rho}.
+The evolution of the scaled tuning factor $\widetilde{\rho}$ can be seen in Figure~\ref{fig:rho}.
 When the positive reference changes are tracked, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$.
-On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$.}
-
-\textcolor{red}{The setup of the tuning factor can be associated with tuning of the penalty matrix $Q_{\mathrm{y}}$ according to Eq.~\eqref{eq:tunable_Qy}.
-The evolution of the penalty matrix during control is depicted in Figure~\ref{fig:Q}.
-Note, the penalty matrix evolution in Figure~\ref{fig:Q} does not correspond to tuning of the optimal MPC, but serves for a better vision of association of the interpolated control inputs with the optimal explicit MPC setup.}
+On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$.
+
+The setup of the tuning factor can be associated with tuning of the penalty matrix $Q_{\mathrm{y}}$ according to Eq.~\eqref{eq:tunable_Qy}.
+The evolution of the penalty matrix $Q_{\mathrm{y}}$ during control is depicted in Figure~\ref{fig:Q}.
+Note, the penalty matrix evolution in Figure~\ref{fig:Q} does not correspond to tuning of the optimal MPC, but serves for a deeper insight into the association of the interpolated control inputs with the optimal explicit MPC setup.
 
@@
 		\includegraphics[width=0.8\textwidth]{images/rho}
-		\caption{Evolution of the scaled tuning factor $\widetilde{\rho}$ during control.
-When tracking positive reference changes, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$.
-On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$.}
+		\caption{Evolution of the scaled tuning factor $\widetilde{\rho}$ during real-time control.
+When tracking positive reference changes, the tuning factor is scaled below the splitting value $\rho_{\mathrm{s}}$ (200 -- 1\,400\,s).
+On the contrary, when the reference changes are negative, the tuning factor is scaled above the splitting value $\rho_{\mathrm{s}}$ (1\,400 -- 2\,600\,s).}
 		\label{fig:rho}
@@
 		\includegraphics[width=0.8\textwidth]{images/Q}
-		\caption{Evolution of the penalty matrix $Q_{\mathrm{y}}$ during control.
-When tracking positive reference changes, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, L}$.
-On the contrary, when the reference changes are negative, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, U}$.}
+		\caption{Evolution of the penalty matrix $Q_{\mathrm{y}}$ during real-time control.
+When tracking positive reference changes, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, L}$ (200 -- 1\,400\,s).
+On the contrary, when the reference changes are negative, the controller is tuned to operate closer to the lower boundary matrix $Q_\mathrm{y, U}$ (1\,400 -- 2\,600\,s).}
 		\label{fig:Q}
@@
 The control performance is evaluated for each reference step change separately.
-The considered quality criteria are: sum-of-squared based criterion -- integral squared error $ISE$, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ and the settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$.
+The considered quality criteria are: sum-of-squared control error SSE, maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ and the settling time $t_{\epsilon}$ for 5\,\%-neighbourhood of the reference temperature $T_{\mathrm{ref}}$.
 To provide better readability of the computed results in Table~\ref{tab:control_performance}, the best values, i.e., the minimum values, are emphasized using a bold font style.
@@
 		\begin{tabular}{c|c|c|c|c} 
-			Reference step change & $Q_\mathrm{y}$ & $ISE$ [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
+			Reference step change & $Q_\mathrm{y}$ & SSE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
 			\hline
-			\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 714 & 33.50 & 16.5 \\
-			& 100 & 867 & 16.65 & 12.5 \\ 
-			& self-tuned & \textbf{678} & \textbf{15.19} & \textbf{9.5}  \\ 
+			\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 714 & 33.5 & 16.5 \\
+			& 100 & 867 & 16.7 & 12.5 \\ 
+			& self-tuned & \textbf{678} & \textbf{15.2} & \textbf{9.5}  \\ 
 			\hline
-			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 365 & 47.20 & \textbf{5} \\
-			& 100 & 606 & 23.25 & 26.5  \\ 
-			& self-tuned & \textbf{248} & \textbf{19.13} & 9.5  \\ 
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1\,000 & 365 & 47.2 & \textbf{5} \\
+			& 100 & 606 & 23.3 & 26.5  \\ 
+			& self-tuned & \textbf{248} & \textbf{19.1} & 9.5  \\ 
 			\hline
-			\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 245 & \textbf{18.92} & \textbf{6.5}  \\
-			& 100 & 398 & 79.64 & 31  \\ 
-			& self-tuned & \textbf{186} & 24.59 & \textbf{6.5}  \\ 
+			\multirow{2}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 245 & \textbf{18.9} & \textbf{6.5}  \\
+			& 100 & 398 & 79.6 & 31  \\ 
+			& self-tuned & \textbf{186} & 24.6 & \textbf{6.5}  \\ 
 			\hline
-			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1000 & 1024 & 18.43 & 22.5  \\
-			& 100 & 1402 & 41.87 & 90  \\ 
-			& self-tuned & \textbf{967} & \textbf{16.49} & \textbf{18.5}   
+			\multirow{2}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1\,000 & 1\,024 & 18.4 & 22.5  \\
+			& 100 & 1\,402 & 41.9 & 90  \\ 
+			& self-tuned & \textbf{967} & \textbf{16.5} & \textbf{18.5}   
 		\end{tabular}
@@
 		\begin{tabular}{c|c|c|c} 
-			Reference step change & $\delta ISE$\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+			Reference step change & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 			\hline
@@
 Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
-The squared-error-based criterion ($ISE$) improved in every control scenario within a range $[5-32]$\,\%, the maximal overshoots/undershoots $\sigma_{\mathrm{max}}$ reduced up to 18\,\%, and the settling time $t_{\epsilon}$ decreased up to 24\,\%.
+The squared-error-based criterion (SSE) improved in every control scenario within a range $[5-32]$\,\%, the maximal overshoots/undershoots $\sigma_{\mathrm{max}}$ reduced up to 18\,\%, and the settling time $t_{\epsilon}$ decreased up to 24\,\%.
 
@@
 
-In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower $ISE$), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$).
+In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower SSE), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$).
 %, while the control performance does not suffer in the terms of energy consumption.
@@
 To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
-The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the integral squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
 %In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
@@
 
-	\textcolor{red}{Note, this strategy relies on a proper design of the two boundary controllers.
-In case a disturbance occurs, both boundary controllers should be able to solve a disturbance rejection problem, as the final value of the manipulated variables is interpolated between them.
-The future work will focus on incorporating also the measurable disturbances into the tuning strategy.}
+	Note, this strategy relies on a proper design of the two boundary controllers.
+In case a non-negligible disturbance occurs, both boundary controllers should be able to solve a disturbance rejection problem, as the final value of the manipulated variables is interpolated between them.
+The future work will focus on incorporating also the measurable disturbances into the self-tuning strategy.
 	\section*{Acknowledgments}
@@
 			$k$ & step of the prediction horizon \\
+			$K$ & system gain, $^{\circ}\mathrm{C}$\\
 			$N$ & prediction horizon \\
@@
 			$\sigma_{\max}$ & maximal overshoot, \% \\
+			$\tau$ & system time constant, s\\
 			$\theta$ & parameter of optimization problem \\
@@
 			eMPC & explicit model predictive control \\			
-			ISE  & integral squared error \\
 			LTI  & linear time-invariant (system) \\
@@
 			SISO & single-input and single-output (system) \\
+			SSE  & sum-of-squared error 
 		\end{tabular}

### 2023-06-28 data/ploty.m

@@ -82,7 +82,7 @@ t = out.ScopeData(1:5000,1);
 Qt = [];
 for i = 1:length(Q)
     if i == 1
-        Qt = [Qt; Q(i)*ones(200,1)];
+        Qt = [Qt; Q(i)*ones(400,1)];
     else
         Qt = [Qt; Q(i)*ones(1200,1)];
     end
@@ -190,7 +190,7 @@ t = out.ScopeData(1:5000,1);
 Qt = [];
 for i = 1:length(Q)
     if i == 1
-        Qt = [Qt; Q(i)*ones(200,1)];
+        Qt = [Qt; Q(i)*ones(400,1)];
     else
         Qt = [Qt; Q(i)*ones(1200,1)];
     end
@@ -320,7 +320,7 @@ axis([0 2600 0 1100])
 set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
 xlabel('$t$ [s]')
 ylabel('$Q_{\mathrm{y}}$','FontSize', fs)
-% legend('$Q_\mathrm{y}$ tuned', '$Q_\mathrm{y,L}, Q_\mathrm{y,U}$ ', 'Interpreter','latex', 'FontSize', fs) 
+legend('$Q_\mathrm{y}$ tuned', '$Q_\mathrm{y,L}, Q_\mathrm{y,U}$ ', 'Interpreter','latex', 'FontSize', fs) 
 
 %% rho
 ro = [0, 0.333, 0.167, 0.667, 0.833];

### 2023-06-29 paper/ATE/main.tex
highlights added and main updated

@@
 		%%Research highlights
-		\begin{highlights}
+%		\begin{highlights}
 			% 3-5 highlights, every one should not exceed 85 characters including spaces
-			\item Self-tunable control technique does not need any intervention during control
-			\item Tuning based on operating conditions compensates for the nonlinear plant behavior
-			\item Implementation of the proposed tuning method on a laboratory heat exchanger 
-			\item Control performance improved compared to utilizing explicit MPC with constant setup
-			\end{highlights}
+%			\item Self-tunable control technique does not need any intervention during control
+%			\item Tuning based on operating conditions compensates for the nonlinear plant behavior
+%			\item Implementation of the proposed tuning method on a laboratory heat exchanger 
+%			\item Control performance improved compared to utilizing explicit MPC with constant setup
+%			\end{highlights}
 
@@
 			%% keywords here, in the form: keyword \sep keyword
-
 			%% PACS codes here, in the form: \PACS code \sep code
-
 			%% MSC codes here, in the form: \MSC code \sep code
@@
 	\label{sec:introduction}
-
-	%The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback.
-The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) the memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available sample time for control action implementation.
-Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.
 
@@
 	The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, and the Slovak Research and Development Agency under the project APVV-20-0261.
-	This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+	This research is funded by the European Union’s Horizon Europe under grant no.
+101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+L.~Galčíková acknowledges the STU Grant scheme for Support of Young Researchers.
 

### 2023-07-19 paper/JoPC/main.tex
preparation for JoPC

--- 2023-06-29 paper/ATE/main.tex
@@
 
-\journal{Applied Thermal Engineering}
+\journal{Journal of Process Control}
 
@@
 Simultaneously, the heat exchangers are energy-demanding and resource-intensive plants.
-Moreover, from the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task, see~\cite{RL20}.
-What should be also considered, is a choice of the controlled variable, as the outlet stream temperature does not have to be always the efficient one.
+From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task~\cite{RL20}.
+
+	%What should be also considered, is a choice of the controlled variable, as the outlet stream temperature does not have to be always the efficient one.
 In~\cite{JIN_CV}, the idea is to optimize the controlled variable of counter flow heat exchanger.
@@
 
-	Very common challenge in terms of heat exchangers is fouling.
-In~\cite{TRAFCZYNSKI_fouling}, the authors address this effect while using proportional–integral–derivative (PID) control.
-If the thermal resistance of fouling is increased and the parameters of controller remain unchanged, it could lead to oscillations of the controlled temperature, too slow response to setpoint changes or significant temperature overshoot.
-To prevent these effects, the PID controller parameters are adjusted.
-
-	Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient when it comes to energy savings.
-Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters originated, e.g., in the already mentioned fouling~\cite{MT19}.
-Such widely-used control strategies include, e.g., the robust control~\cite{WY18}, the gain-scheduling, adaptive and optimal control.
-In~\cite{VASICKANINOVA_HE}, a neural network predictive controller together with the fuzzy controller in the complex control structure with an auxiliary control variable was investigated.
+	A very common challenge in terms of the changing behavior of heat exchangers is fouling.
+The authors in~\cite{AGUEL_fouling} focus on modeling the thermal efficiency in a cross-flow heat exchanger using an artificial neural network, which leads to a highly accurate model.
+In~\cite{TRAFCZYNSKI_fouling}, the authors address the effect of fouling by adjusting the parameters of the proportional–integral–derivative (PID) controller.
+
+	Although the conventional and widely-used PID controllers are robust and easy to tune, their control performance may not be sufficient.
+Various extensions built above the well-tuned PID controller were developed to compensate for the nonlinear and asymmetric behavior, often affected by the additional impact of the uncertain parameters.
+Such widely-used control strategies include, e.g., the robust control~\cite{WY18}, the gain-scheduling, and adaptive control.
+In a recent study~\cite{VANNIEKERK_tuning}, the authors suggest to adjust the controller online, based on a minimization of an objective function designed to achieve the desired control performance.
+%In~\cite{VASICKANINOVA_HE}, a neural network predictive controller together with the fuzzy controller in the complex control structure was investigated.
 	For the rigorous mathematical modeling and controller design methods in general, see~\cite{MF08} and for the controller design tailored for the process control engineers see~\cite{Liptak}.
@@
 The multi-layer control designed in~\cite{DZ18} designed the MPC in the leader loop to optimize the thermal response to improved control performance.
-In~\cite{DYRSKA_HE}, the authors focus on reduction of computational complexity associated with the evaluation of control action of MPC.
+%In~\cite{DYRSKA_HE}, the authors focus on reduction of computational complexity associated with the evaluation of control action of MPC.
 By implementing the constraint removal technique, the energy consumption of the microcontroller is reduced.
@@
 	The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, and the Slovak Research and Development Agency under the project APVV-20-0261.
-	This research is funded by the European Union’s Horizon Europe under grant no.
-101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
-L.~Galčíková acknowledges the STU Grant scheme for Support of Young Researchers.
+	This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
 

### 2023-07-19 paper/JoPC/cover_letter.tex
cover letter

--- 2023-06-28 paper/ATE/cover_letter.tex
@@
 \pagestyle{headings}
-\begin{letter}{Professor Christos N. Markides, BA (Hons), MEng, MA, PhD, Editor-in-Chief, Applied Thermal Engineering}
+\begin{letter}{Professor Martin Guay, Editor-in-Chief, Journal of Process Control}
 
-\opening{Dear Professor Christos N. Markides,}
+\opening{Dear Professor Martin Guay,}
 
@@
 We believe that the presented study is, due to its character, of both industrial and academic interest and within the scope of the journal.
-We would very much appreciate if you would consider the manuscript for publication in the journal Applied Thermal Engineering.
+We would very much appreciate if you would consider the manuscript for publication in the Journal of Process Control.
 

### 2023-07-21 paper/JoPC/main.tex
edit JoPC

@@
 Furthermore, a novel technique for scaling the tuning parameter is proposed.
-It provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
+This extension provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
 The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
-The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning process.
+The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
 The designed self-tunable controller improved control performance by decreasing sum-of-squared control error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-tunable) controller.
@@
 Therefore, sustainable industrial production is focused on the wide implementation of advanced control methods~\cite{MN20}.
-A recent survey on applied thermal engineering focused on energy saving and pollution reduction from the industrial perspective is provided in~\cite{YV16}.
+A recent survey on applied thermal engineering focused on energy saving and pollution reduction from the industrial perspective is provided in~\cite{YV16}, and references therein.
 
 	The heat exchangers in their numerous variants are integrated into many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
-Simultaneously, the heat exchangers are energy-demanding and resource-intensive plants.
+Simultaneously, the heat exchangers are highly energy-demanding and resource-intensive plants.
 From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task~\cite{RL20}.
@@
 
-	A very common challenge in terms of the changing behavior of heat exchangers is fouling.
+	A very common challenge in terms of the time-varying behavior of heat exchangers is fouling.
 The authors in~\cite{AGUEL_fouling} focus on modeling the thermal efficiency in a cross-flow heat exchanger using an artificial neural network, which leads to a highly accurate model.
@@
 %In~\cite{VASICKANINOVA_HE}, a neural network predictive controller together with the fuzzy controller in the complex control structure was investigated.
-	For the rigorous mathematical modeling and controller design methods in general, see~\cite{MF08} and for the controller design tailored for the process control engineers see~\cite{Liptak}.
+	For the rigorous mathematical modeling and controller design methods in general, see~\cite{MF08}, and for the controller design tailored for the process control engineers see~\cite{Liptak}.
 
@@
 The tuning parameter penalizing the control inputs became a parameter, for which the optimal controller was precomputed.
-Nevertheless, the application was limited only to linear cost functions.
+Nevertheless, the application was limited only to linear cost functions of the optimization problem.
 To satisfy the demands for often-used quadratic cost functions, the approximated tunable explicit MPC was presented in~\cite{Klauco_tunable}.
@@
 Compared to~\cite{self_tunable}, the self-tuning method is based on the size of the reference step change.
-Moreover, the idea of further scaling the tuning parameter is elaborated.
+Moreover, the idea of further scaling of the tuning parameter is elaborated.
 The interval of the values of the self-tuning parameter is split at some certain value and each part of the interval corresponds to the specific operating conditions defined by the control engineer.

### 2023-07-24 paper/JoPC/main.tex
JoPC udpate - partitions added, authors updated

@@
 		\author{Lenka Galčíková}
-		\author{Petronela Belková}
 		\author{Juraj Oravec}
@@
 %		\begin{highlights}
-			% 3-5 highlights, every one should not exceed 85 characters including spaces
+%			 %3-5 highlights, every one should not exceed 85 characters including spaces
 %			\item Self-tunable control technique does not need any intervention during control
@@
 \end{eqnarray}
-As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} can be omitted.
-Another motivation to include the output/state constraints would be the necessity to retain the controlled variable in some comfort range, specified by operation requirements.
-As it was not the aim of the case study, this reason also leads to omitting the constraints in Eq.~\eqref{eq:mpc_problem_state_constraints} to fully investigate the control performance of the pure self-tuning method.
+
+As the controlled system is naturally stable even if the maximal or minimal value of the manipulated variable is constantly applied, the constraints on the controlled variable in Eq.~\eqref{eq:mpc_problem_state_constraints} could be omitted.
+On the other hand, unbounded states/outputs lead to higher memory consumption, because covering the whole possible range of parameters requires more critical regions.
+Therefore, the "artificial" constraints on the outputs were included in order to reduce the number of critical regions and the overall memory footprint of the explicit controllers.
+The output constraints were set as:
+\begin{eqnarray}
+	\label{eq:y_const}
+	-15\,^{\circ}\mathrm{C} \le y \le 20\,^{\circ}\mathrm{C}.
+\end{eqnarray}
+
+The constraints in Eq.~\eqref{eq:y_const} are equal to physical temperature as follows:
+\begin{eqnarray}
+	\label{eq:Y_const}
+	20\,^{\circ}\mathrm{C} \le y \le 55\,^{\circ}\mathrm{C},
+\end{eqnarray}
+which corresponds to the range of temperature values which are achievable in the considered laboratory conditions and setup.
 
@@
 The explicit model predictive controllers were constructed in MATLAB R2020b using the Multi-Parametric Toolbox 3~\cite{mpt_conf}.
+
+The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions.
+The corresponding polytopic partitions can be seen in Fig.~{ref} and Fig.~{ref}.
+To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required.
+Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.
 
@@
 	The authors gratefully acknowledge the contribution of the Scientific Grant Agency of the Slovak Republic under the grants 1/0545/20, 1/0297/22, and the Slovak Research and Development Agency under the project APVV-20-0261.
-	This research is funded by the European Union’s Horizon Europe under grant no. 101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+	This research is funded by the European Union’s Horizon Europe under grant no.
+101079342 (Fostering Opportunities Towards Slovak Excellence in Advanced Control for Smart Industries).
+The authors also acknowledge Petronela Belková for help with generating the experimental data.
 

### 2023-07-25 paper/JoPC/main.tex
polytopic partitions added

@@
 The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions.
-The corresponding polytopic partitions can be seen in Fig.~{ref} and Fig.~{ref}.
+The corresponding polytopic partitions can be seen in Fig.~\ref{fig:partition_U} for the upper boundary controller and Fig.~\ref{fig:partition_L} for the lower boundary controller.
 To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required.
 Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/partition_U}
+		\caption{Polytopic partition of the upper boundary explicit MPC.}
+		\label{fig:partition_U}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/partition_L}
+		\caption{Polytopic partition of the lower boundary explicit MPC.}
+	\label{fig:partition_L}
+\end{center}
+\end{figure}
 
@@
 \end{figure}
+
+The control input is applied to the system each second, so there is a possible concern regarding the speed at which two explicit MPCs are evaluated.
+By analyzing the computational speed, it was concluded that the approximate control input can be generated in an average time of 0.01 seconds, which is 100 times faster than the sampling time.
 

### 2023-07-25 data/ploty.m

@@ -353,3 +353,28 @@ set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
 xlabel('$t$ [s]')
 ylabel('$\widetilde{\rho}$','FontSize', fs)
 legend('$\widetilde{\rho}$', '$\rho_\mathrm{s}$ ', 'Interpreter','latex', 'FontSize', fs) 
+%% Partitions
+load('expmpc_L.mat')
+load('expmpc_U.mat')
+%%
+set(0,'defaulttextinterpreter','latex')
+fs = 13;
+
+figure(1)
+expmpc_L.partition.plot
+
+set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
+xlabel('$x$','FontSize', fs)
+ylabel('$x_{\mathrm{I}}$','FontSize', fs)
+zlabel('$y_{\mathrm{ref}}$','FontSize', fs)
+axis tight
+
+
+figure(2)
+expmpc_U.partition.plot
+
+set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
+xlabel('$x$','FontSize', fs)
+ylabel('$x_{\mathrm{I}}$','FontSize', fs)
+zlabel('$y_{\mathrm{ref}}$','FontSize', fs)
+axis tight

### 2023-07-25 paper/JoPC/main.tex
Paper: update

@@
 On the other hand, unbounded states/outputs lead to higher memory consumption, because covering the whole possible range of parameters requires more critical regions.
-Therefore, the "artificial" constraints on the outputs were included in order to reduce the number of critical regions and the overall memory footprint of the explicit controllers.
+Therefore, the ``redundant'' constraints on the system outputs were included in order to reduce the number of critical regions and the overall memory footprint of the explicit controllers.
 The output constraints were set as:
@@
 The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions.
-The corresponding polytopic partitions can be seen in Fig.~\ref{fig:partition_U} for the upper boundary controller and Fig.~\ref{fig:partition_L} for the lower boundary controller.
-To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required.
-Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.
+The corresponding polytopic partitions can be seen in Figure~\ref{fig:partition_U} for the upper boundary controller and Figure~\ref{fig:partition_L} for the lower boundary controller.
+To store the parametric solution associated with the upper boundary explicit MPC, 17.49\,MB of memory space is required.
+Storing the lower boundary explicit MPC, one needs 4.33\,MB of memory space.
 

### 2024-02-20 paper/JoPC/response_letter.tex
response letter added

\documentclass[a4paper,10pt]{article}

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{a4wide}
\usepackage{multicol}
\usepackage[ansinew]{inputenc}
\usepackage{color}
\usepackage{url}
%\usepackage{floatflt}
\usepackage{multirow}
\usepackage{rotating, graphicx}

\newcommand{\opt}{^{\star}} % \opt
\newcommand{\tr}{\intercal} % transpose

% RESPONSE LETTER SYNTAX:
% =====================================================
\newcommand{\change}[1]{\textcolor{red}{#1}}

\newcommand{\comment}[1]{
	\begin{itemize}
		\item \textbf{Comment:}\\ \sf{#1}
	\end{itemize}
}

\newcommand{\answer}[1]{
	\begin{itemize}
		\item[] \textbf{Answer:}\\ #1
	\end{itemize}
}

\newcommand{\pointout}[1]{\textcolor{blue}{#1}}
\definecolor{YJ}{rgb}{0.0,0.5,0.0}

% =====================================================

\newcommand{\diam}[1]{\mathrm{diam}\left(#1\right)}

% \newcommand {\mm}[1]{\textcolor{blue}{#1}}

%opening
\title{Response to the review comments}
\author{}
\date{}

\sloppy
\begin{document}

	\maketitle

	The authors would like to thank the reviewers for the constructive and thoughtful comments on our paper.
	We have revised the document based on these comments and we provide point-to-point answers below.
	All changes relative to our initial submission have been highlighted in \change{red}.

	\section*{Answer to Editor in Chief}
	The authors would like to thank the Editor in chief for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality. The authors revised the paper based on the reviewers' comments and incorporated the suggestions into our manuscript. The authors reformulated or added the corresponding statements to clarify the ideas.

	\section*{Answer to Reviewer 1}
	\comment{The paper develops a method to automatically tune explicit MPC controllers, and demonstrates application of the proposed approach on a laboratory scale heat exchanger system. Overall, the paper is well written and the presented ideas and experimental results are clear. However, the following points should be addressed before publication: \\

	The main motivation that a practitioner may want different controller tunings based on operating scenarios and different sizes of reference changes/disturbances does not clearly stand out in the introduction section. The initial few paragraphs can be revised to clearly emphasize the need of a "self-tunable" MPC controller in practice.
	}

	\comment{
		The introduction section showed an overview of various control methods, but few studies discussed the embedded/industrial hardware. It is difficult to understand what control method is more suitable for embedded/industrial hardware applications. Related discussion is needed to be covered more in this section.
	}

	\comment{
		The authors state, "The lower computational complexity makes the explicit MPC more suitable for a practical industrial implementation." in the introduction section. It should be noted, however, that the explicit MPC suffers from the curse of dimensionality, and the number of polytopic regions in the PWA control law can grow exponentially with the size of states, control inputs, and the MPC forecasting horizon. Thereby, making it not practically implementable for a large class of industrial systems.
	}

	\comment{
		The main idea behind the self-tunable approximate explicit MPC controller is that two extreme controllers are designed with aggressive and slow tunings called the "boundary controllers", and a linear interpolation of those two controllers is taken to produce the final control input. How can this approach be applied to multivariable interacting systems with multiple control inputs?
	}

	\comment{
		In the final simulation studies presented, the closed-loop performance of the self-tuned approximate MPC is compared only with the two extreme boundary controllers. However, a moderately tuned (E.g, Qy=500-600) "optimal" MPC controller may also provide a reasonable and potentially better performance than the two boundary controllers. I encourage the authors to comment on its performance and elaborate whether the control improvements reported in Table 2 still remain.
	}
	\comment{
		The performance of the two boundary controllers shown in Figures 6 and 7 are also depicted in Figures 10 and 11. So some of the figures can be removed for a concise presentation of the results.
	}

	\comment{
		Unmeasured disturbances are encountered in a large-class of industrial applications, and treating such disturbances is almost a required feature in the control algorithm to be considered for practical deployment. I recommend the authors to comment on how can the approach be applied to systems with unmeasured disturbances, or what complications may arise.
	}

	\section*{Answer to Reviewer 2}

	\comment{
		A self-tuning explicit MPC scheme is presented and applied to a heat exchange process. The main contribution above the authors other work appears to be the self-tuning aspect. Overall, the paper would greatly benefit from a thorough revision, clarifying ambiguous definitions, discussions, and descriptions. Also, the experimental setup should be clarified, as important dynamics that seem relevant (hot stream dynamics) appear to be ignored, raising doubts about the repeatability and therefore, conclusions drawn from the experiments. My specific comments are listed below.

		In the abstract, define what the term "properly tune the controller" means.
	}

	\comment{
		Optimize the phrasing of the second paragraph of the introduction. The phrasing makes it sounds like heat exchangers are energy demanding, but I assume the intended meaning is that the utility generation for heating/cooling is energy-demanding.
	}

	\comment{
		Define what is meant by asymmetric behavior.
	}

	\comment{
		What are the assumptions on the penalty matrices? Include an explicit statement of these assumptions Section 2.1 (e.g., must be diagonal matrices).
	}
	\comment{
		Similarly, for the two boundary controllers explain the assumptions on the penalty matrices. Clearly, if the "upper" boundary matrices are equivalent to the "lower" boundary matrices multiplied by a scalar, there will be no difference between the solutions obtained by solving either controller. Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
	}

	\comment{
		Please clarify the last sentence on page 7, extending into page 8, which describes the tuning process as systematic, but the description appears to be ad hoc and depend on the system.
	}

	\comment{
		Does the method only support SISO or MIMO system with decoupled pairs of inputs/outputs? This seems to be suggested by the statement made on page 9. If so, this should be stated explicitly in the problem setup.
	}

	\comment{
		How is the aggressiveness of the controller being defined?
	}

	\comment{
		What are the properties of the reference values selected? Are they reachable?
	}

	\comment{
		In Eq. 7, there is a missing time dependence on rho and the "(k)" in $y_\mathrm{ref}$ should not be a subscript.
	}

	\comment{
		Please clarify the role of rho and dmax. What is the symbol $\lvert.\rvert$ mean for a vector (element-wise absolute value)? It seems that dmax would need to be inherently conservative, in the sense that it is the maximum magnitude of all possible references values. If this is the case, it would seem that rho would mostly be less than 1. On the other hand, if dmax is not the maximum magnitude of all possible reference, there is a possibility of rho $>$ 1. What happens in this case? Why is it appropriate to make rho closer to 1 for references with large magnitudes.
	}

	\comment{
		At the end of Section 2, it is mentioned that the positivity or negativity of the reference change could be considered. What does this mean? A precise mathematical description would be helpful.
	}

	\comment{
	 	Given the lack of clear definition of asymmetric behavior, the need for a modified self tuning technique (Section 3.2) is a bit unclear. A clear description of its need in the beginning of Section 3.2 would be helpful.
	}

	\comment{
		In Definition 3.1, is the domain of gamma indeed R?
	}

	\comment{
		Figure 4 seems out of place (should be after figure 1).
	}

	\comment{
		A diagram or schematic of the heat exchange process would be helpful. Also, referring to the cold water stream as the feed when the outlet temperature is regulated is a bit confusing.
	}

	\comment{
		How was it determined that Qy has the most significant effect in the heat exchange process? What constitutes "significant effect"?
	}

	\comment{
		In the heat exchange process, the dynamics of the hot stream appears to be neglected. Why is this the case? I am not sure about the explanation given on why different steady-state inputs are observed. The flow rate of the hot stream is adjusted so the cold stream outlet temperature is maintained at the reference value is done. It seems, though not shown, that the hot stream inlet temperature is maintained to be constant. Based on the results, it would seem that the steady-state hot stream temperature is free to vary. What about the cold stream inlet temperature? Please given the trajectories of all these variables, or at least, the temperatures. What is the impact of the repeatability of the experiments given that the hot stream temperature is allowed to vary? In any case, the metrics presented in Table 1 are reported for one experiment per scenario. I would encourage computing these metrics for several experiments to ensure repeatability of the experiments and make the results more convincing.
	}

	\answer{
		This is a very important comment as it targets the main motivation of the paper---pointing out the benefits of the proposed control method from the implementation point of view. The implementation on the embedded platforms requires a memory-efficient and computationally tractable evaluation with minimum dependencies on the advanced software libraries. Therefore, we extended the corresponding part of the section Introduction which now reads as follows:

		\begin{quote}
			Embedded hardware is becoming increasingly popular in many applications due to its low-cost, open architecture, and wide range of relevant applications. \change{However, the computational power and memory storage of the embedded hardware is still low compared to other devices used in the industry. As the consequence, there is a significant requirement to implement such control strategies that provide inexpensive and low-power consuming controllers. 
			For instance, the well-known proportional-integral-derivative (PID) controllers.  In~\cite{HM14} a detailed case study analyzing the implementation of various PID controllers considering multiprocessor system-on-chip and multicore microcontrollers is conducted. The designed controllers are compared in terms of design time, design effort, and closed-loop control performance. The paper also summarizes the rules for handling the multiprocessor systems for embedded control design.}
		\end{quote}	 		
	}

	\bibliographystyle{plain}
	\bibliography{references}

\end{document}

### 2024-02-20 paper/JoPC/response_letter.tex
response letter part1

@@
 
-	The authors would like to thank the reviewers for the constructive and thoughtful comments on our paper.
-	We have revised the document based on these comments and we provide point-to-point answers below.
-	All changes relative to our initial submission have been highlighted in \change{red}.
+	We would like to thank the reviewers for the constructive and thoughtful comments on our manuscript.
+	We revised the document based on these comments and we provide point-to-point answers below.
+	All changes relative to our initial submission are highlighted in \change{red}.
 
-	\section*{Answer to Editor in Chief}
-	The authors would like to thank the Editor in chief for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality.
-The authors revised the paper based on the reviewers' comments and incorporated the suggestions into our manuscript.
-The authors reformulated or added the corresponding statements to clarify the ideas.
+	\section*{Answer to Editor}
+	We would like to thank the Editor for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality.
+We revised the paper based on the reviewers' comments and incorporated the suggestions into our manuscript.
+We reformulated or added the corresponding statements to clarify the ideas.
 
@@
 
-	\comment{
-		The introduction section showed an overview of various control methods, but few studies discussed the embedded/industrial hardware.
-It is difficult to understand what control method is more suitable for embedded/industrial hardware applications.
-Related discussion is needed to be covered more in this section.
+	\answer{
+		In order to clearly emphasize the need of a self-tunable technique, we revised the Introduction section in a following way:
+		\begin{quote}
+			The paper [27] pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+		\end{quote}
 	}
@@
 Thereby, making it not practically implementable for a large class of industrial systems.
+	}
+
+	\answer{
+		We thank the reviewer for an important comment. We reformulated the sentence as follows:
+		\begin{quote}
+			\change{If the MPC optimization problem can be pre-solved explicitly, the lower online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
+		\end{quote}
 	}
@@
 	}
+
+	\answer{
+		We thank the reviewer for the question and comment.
+If a moderately tuned optimal MPC also provided a reasonable or potentially better performance than the two boundary controllers, the self-tunable technique would be out of scope for such control application.
+Nevertheless, there are situations, when using only one controller with a constant setup leads to just ''satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance (e.g.
+high overshoots or settling time).
+When working on our case study results, different setups of penalty matrices were explored, also $Q_\mathrm{y} = 500$.
+In this scenario, the control performance was comparable with the tuned controller for the first two reference step changes (tracking the reference upwards).
+However, when the reference was tracked downwards, the undershoots similar to lower boundary controller, i.e., $Q_\mathrm{y} = 100$ were present.
+Therefore, it supports the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the control performance could be improved by including the benefits of two boundary controllers.
+	}
+
 	\comment{
 		The performance of the two boundary controllers shown in Figures 6 and 7 are also depicted in Figures 10 and 11. So some of the figures can be removed for a concise presentation of the results.
+	}
+
+	\answer{
+		We removed the Figure 6 and 7 in order to improve the concise presentation of the control results.
 	}
@@
 I recommend the authors to comment on how can the approach be applied to systems with unmeasured disturbances, or what complications may arise.
+	}
+
+	\answer{
+		We thank the reviewer for this important comment.
+We revisited the Conclusion section containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
+(Na zvazenie: As the thoughts and ideas remind discussion more than conclusion, this part was transferred to the section Results and discussion.)
+		\begin{quote}
+			Note, this strategy relies on a proper design of the two boundary controllers.
+			In case a non-negligible disturbance occurs, both boundary controllers
+			should be able to solve a disturbance rejection problem, as the final
+			value of the manipulated variables is interpolated between them.
+\change{It is also possible to include the disturbance into the design process of the MPC controller.
+In such case, e.g., a robust MPC strategy (REF?) would be beneficial, which would lead to more conservative control actions in order to create space for a disturbance.
+Nevertheless, if the problem is not large-scale and it is possible to obtain the explicit solution, it is still possible to interpolate between the control actions from the robust controllers.} The future work will focus on incorporating also the measurable disturbances into the self-tuning strategy.
+(Really?)
+		\end{quote}	
 	}
@@
 	\answer{
-		This is a very important comment as it targets the main motivation of the paper---pointing out the benefits of the proposed control method from the implementation point of view.
-The implementation on the embedded platforms requires a memory-efficient and computationally tractable evaluation with minimum dependencies on the advanced software libraries.
-Therefore, we extended the corresponding part of the section Introduction which now reads as follows:
 
-		\begin{quote}
-			Embedded hardware is becoming increasingly popular in many applications due to its low-cost, open architecture, and wide range of relevant applications.
-\change{However, the computational power and memory storage of the embedded hardware is still low compared to other devices used in the industry.
-As the consequence, there is a significant requirement to implement such control strategies that provide inexpensive and low-power consuming controllers.
-			For instance, the well-known proportional-integral-derivative (PID) controllers.
-In~\cite{HM14} a detailed case study analyzing the implementation of various PID controllers considering multiprocessor system-on-chip and multicore microcontrollers is conducted.
-The designed controllers are compared in terms of design time, design effort, and closed-loop control performance.
-The paper also summarizes the rules for handling the multiprocessor systems for embedded control design.}
-		\end{quote}	 		
 	}

### 2024-02-21 paper/JoPC/response_letter.tex
reviewer 2 - the first part

@@
 
+	\answer{
+		We understand that this formulation might sound vague, so we reformulated the corresponding sentence as follows:
+		\begin{quote}
+			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller}.
+		\end{quote}	
+	}
+
 	\comment{
@@
 The phrasing makes it sounds like heat exchangers are energy demanding, but I assume the intended meaning is that the utility generation for heating/cooling is energy-demanding.
+	}
+
+	\answer{
+		We thank the Reviewer for this important comment. We utilized the Reviewer's suggested formulation in a following way:
+		\begin{quote}
+			\change{Simultaneously, the utility generation for heating/cooling is energy-demanding.}
+		\end{quote}	
 	}
@@
 
+	\answer{
+		We revisited the Introduction section in order to define the asymmetric behavior at the place of its first occurrence.
+		\begin{quote}
+			From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior \change{(i.e.
+different dynamics (behavior?) when the temperature is rising or decreasing)} of the heat exchangers is a challenging task [4].
+		\end{quote}	
+	}
+
 	\comment{
@@
 	}
+
+	\answer{
+		We revisited the Section 2.1 in order to define the assumptions on the penalty matrices. The corresponding part reads as:
+		\begin{quote}
+			The sets $\mathcal{U} \subseteq \mathbb{R}^{n_{\mathrm{u}}}$, $\mathcal{Y} \subseteq \mathbb{R}^{n_{\mathrm{y}}}$ are convex polytopic sets of physical constraints on inputs and outputs, respectively.
+These sets include the origin in their strict interiors.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ \change{$\succeq 0$} penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ \change{$\succ 0$} penalizes the squarred value of control inputs.
+			%
+			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ \change{$\succeq 0$}.
+\change{All the penalty matrices are considered to be diagonal due to the applicability of the tunable explicit MPC approach.}
+			The parameter $\theta \in \Theta$ in Eq.~(1f) represents the initial condition of the optimization problem for which it is parametrically pre-computed. 
+		\end{quote}	
+	}
+
 	\comment{
@@
 Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
+	}
+
+	\answer{
+		To explain the assumptions on the penalty matrices and specify the tuned matrix in the corresponding paragraph of the Section 2.2 in the following way:
+		\begin{quote}
+			The idea of approximated tunable explicit MPC comes from the work ~\cite{Klauco_tunable}, where the control action is calculated based on linear interpolation between two boundary control actions.
+These control actions result from evaluating two boundary explicit MPCs.
+The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices -- the tuned one.
+\change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any tuning parameter.
+The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
+}
+		\end{quote}	
 	}
@@
 		In Eq. 7, there is a missing time dependence on rho and the "(k)" in $y_\mathrm{ref}$ should not be a subscript.
+	}
+
+	\answer{
+		We thank the Reviewer for a careful review. The equation was corrected as follows:
+		\begin{quote}
+			\change{
+			\begin{eqnarray*}				
+				\rho (k) = \frac{\vert y_{\mathrm{ref}}(k) \vert}{d_{\max}}.
+			\end{eqnarray*}
+		}
+		\end{quote}
+
 	}

### 2024-02-22 paper/JoPC/response_letter.tex
reviewer 2 - the second part

@@
 		\begin{quote}
-			\change{Simultaneously, the utility generation for heating/cooling is energy-demanding.}
+			\change{Simultaneously, the utility generation for heating or cooling is energy-demanding.}
 		\end{quote}	
@@
 
+	\answer{
+		We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the calculation process of $\rho$ in Eq.~(7) and Eq.~(9).
+Regarding the MPC optimization problem, the reference signal is a parameter which is usually constrained such that it covers the operating range of the corresponding control application.
+Therefore, during the control, the reference can be set only as a value from the feasible set.
+If the MPC problem is precomputed also for non-reachable references, e.g., because it is not clear a priori which reference values will be set during control, this would ''only'' lead to larger explicit solution of MPC because of larger range of reference signal.
+Regarding the calculation of parameter $\rho$, the setup of reference value is more strict, i.e., the value should be reachable and from the operating range to ensure that $0 \le \rho \le 1 $.
+		\begin{quote}
+			TODO
+		\end{quote}
+
+	}
+
 	\comment{
@@
 
+	\answer{
+		The parameter $\gamma$ depends on the value of $\rho$, which is scalar. From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
+	}
+
 	\comment{
 		Figure 4 seems out of place (should be after figure 1).
+	}
+
+	\answer{
+		We thank the reviewer for this attentive comment. We corrected the order of Figures.
 	}

### 2024-02-22 data/control_performance.m

@@ -1,4 +1,4 @@
-clc, close all, clear 
+% clc, close all, clear 
 load('ref_tracking25.mat')
 %% plots
 figure(11)

### 2024-02-22 paper/JoPC/response_letter.tex
reviewer 2 - minor update

@@
 
+	\answer{
+		\begin{quote}
+			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
+			First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
+\change{Based on the set of experimentally collected data, the penalty matrix $Q_\mathrm{y}$ was chosen as the tuned one.} Based on the set of experimentally collected data, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the reference value.
+Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
+		\end{quote}
+	}
+
 	\comment{

### 2024-02-23 paper/JoPC/response_letter.tex
reviewer 2 - third part

@@
 		\begin{quote}
-			The paper [27] pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+			TODO: Update the introduction
+			%The paper [27] pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
 		\end{quote}
@@
 We revisited the Conclusion section containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
-(Na zvazenie: As the thoughts and ideas remind discussion more than conclusion, this part was transferred to the section Results and discussion.)
+As the thoughts and ideas remind discussion more than conclusion, this part was transferred to the section Results and discussion.
 		\begin{quote}
@@
 \change{It is also possible to include the disturbance into the design process of the MPC controller.
-In such case, e.g., a robust MPC strategy (REF?) would be beneficial, which would lead to more conservative control actions in order to create space for a disturbance.
-Nevertheless, if the problem is not large-scale and it is possible to obtain the explicit solution, it is still possible to interpolate between the control actions from the robust controllers.} The future work will focus on incorporating also the measurable disturbances into the self-tuning strategy.
-(Really?)
+In such case, e.g., a robust MPC strategy (REF!) would be beneficial, which would lead to more conservative control actions in order to create space for disturbances.
+Nevertheless, if the problem is not large-scale and it is possible to obtain the explicit solution, it is still possible to interpolate between the control actions from the robust controllers.}
 		\end{quote}	
@@
 			From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior \change{(i.e.
-different dynamics (behavior?) when the temperature is rising or decreasing)} of the heat exchangers is a challenging task [4].
+different behavior when the temperature is rising or decreasing)} of the heat exchangers is a challenging task [4].
 		\end{quote}	
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ \change{$\succeq 0$} penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
-The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ \change{$\succ 0$} penalizes the squarred value of control inputs.
+The penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The matrix $R \change{\succ 0} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
 			%
-			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ \change{$\succeq 0$}.
+			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
 \change{All the penalty matrices are considered to be diagonal due to the applicability of the tunable explicit MPC approach.}
@@
 
+	\answer{
+		The aggressiveness of the MPC controller is associated with the setup of penalty matrices, namely $Q_\mathrm{y}$, $Q_\mathrm{I}$, $R$, as it determines the aggressiveness of the final control input.
+In general, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
+This process is similar to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, see e.g.~\cite{Maciejowski_MPC}.
+In order to make the notation of aggressive controller more clear for a reader, we added this description to the Section.
+
+		\begin{quote}
+			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+The procedure of the self-tunable controller technique is presented.
+The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+\change{In the context of MPC, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
+In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
+This process is similar to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable leads to more sluggish control, see e.g.~\cite{Maciejowski_MPC}.
+The MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
+		\end{quote} 
+	}
+
 	\comment{
@@
 		\begin{quote}
-			TODO
+			TODO: Somehow update text in manusctipt?
 		\end{quote}
@@
 
+	\answer{
+		To improve the readability of the manuscript, we added the mathematical description to the corresponding sentence.
+Moreover, based on the following comment, we added the description of asymmetric behavior in this paragraph as follows:
+		\begin{quote}
+			Note, the relations in Eq.~(7) and Eq.~(8) operate with the absolute value of the reference.
+\change{It is not taken into account, whether the reference changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.}
+		\end{quote}
+	}
+
 	\comment{
@@
 A clear description of its need in the beginning of Section 3.2 would be helpful.
+	}
+
+	\answer{
+		 The incorporation of this comment into the manuscript was merged with the previous comment, as it corresponds to the thoughts in the same paragraph.
 	}
@@
 
-	\answer{
-
-	}
-
 	\bibliographystyle{plain}

### 2024-02-24 paper/JoPC/response_letter.tex
Paper: review: Reviewer 1: update

@@
 	\answer{
+
+		\textcolor{blue}{ [ TODO: Odporú?am prida? po?akovanie na úvod prvej odpovede každému recenzentovi---nastaví sa tým úvodná (pozitívna) ``nálada'' komunikácie. ] }
+
+		\textcolor{blue}{ We thank the Reviewer for pointing out unclear motivation for self-tunable control approach in section Introduciton.} 
 		In order to clearly emphasize the need of a self-tunable technique, we revised the Introduction section in a following way:
@@
 	\answer{
+
+		\textcolor{blue}{ [ TODO: Odporú?am po?akova? za konkrétnu vec, aby to nevyznelo len ako ``prázdne'' / všeobecné po?akovanie. ] }
+
 		We thank the reviewer for an important comment. We reformulated the sentence as follows:
@@
 			\change{If the MPC optimization problem can be pre-solved explicitly, the lower online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
+		\end{quote}
+
+		\textcolor{blue}{We thank the reviewer for an important comment on application range of the proposed control method.
+We reformulated the corresponding sentence to make the implementation limits clear}:
+		\begin{quote}
+			\change{If the MPC design problem can be addressed in a tractable form and pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
 		\end{quote}
@@
 Therefore, it supports the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the control performance could be improved by including the benefits of two boundary controllers.
+
+		\textcolor{blue}{
+		We thank the reviewer for the comment on the performance of the proposed method.
+Obviously, if there exists a well-tuned (``universal'') controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, than implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, there are numerous practical situations, when using only one controller with a constant setup leads to poor or just to ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices were investigated, among them also the requested value of $Q_\mathrm{y} = 500$.
+In this control scenario, the control performance was comparable with the self-tuned controller for the first two step changes of the reference value (tracking the reference upwards).
+However, when the reference was tracked downwards, the significant undershoots were present---similar to the closed-loop performance of the lower boundary controller, i.e., $Q_\mathrm{y} = 100$.
+Therefore, these observations support the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the closed-loop control performance is improved by introducing the benefits of the self-tuning based on the two boundary MPC controllers.
+		} 
 	}
@@
 Nevertheless, if the problem is not large-scale and it is possible to obtain the explicit solution, it is still possible to interpolate between the control actions from the robust controllers.}
+		\end{quote}
+
+		\textcolor{blue}{We thank the reviewer for this important comment on the reliable implementation in the industrial applications.
+We revisited the corresponding text in section Conclusion containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
+As the revised extended text includes ideas and comments reminding discussion more than conclusion, this part was transferred to the section Results and discussion, and now reads as follows:}
+		\begin{quote}
+			Note, this strategy relies on a proper design of the two boundary controllers.
+			In case a non-negligible disturbance occurs, both boundary controllers
+			should be able to solve a disturbance rejection problem, as the final
+			value of the manipulated variables is interpolated between them.
+\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy \cite{PR11} should be considered.
+Obviously, any robust MPC design method leads to conservative control actions as some portion of performance is scarified to compensate the impact of the disturbances.
+Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of robust explicit MPC offline, then exactly the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
 		\end{quote}	

### 2024-02-24 paper/JoPC/response_letter.tex
Paper: review: Reviewer 2: update

@@
 	\answer{
+
+		\textcolor{blue}{ [ TODO: Odporú?am po?akova? za konkrétnu vec, aby to nevyznelo len ako ``prázdne'' / všeobecné po?akovanie. ] }
+
 		We understand that this formulation might sound vague, so we reformulated the corresponding sentence as follows:
@@
 		\end{quote}
+
+		\textcolor{blue}{We agree that the used formulation sounds vague, therefore, we reformulated the corresponding sentence in Abstract as follows:
+		\begin{quote}
+			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller whenever the operating conditions are changed/updated.}.
+		\end{quote}	
+		}
 	}
@@
 	\answer{
-		We revisited the Introduction section in order to define the asymmetric behavior at the place of its first occurrence.
+		We revisited the Introduction section in order to \textcolor{blue}{clearly} define the asymmetric behavior \textcolor{blue}{of heat exchanger device, placed} at the place of its first occurrence.
 		\begin{quote}
@@
 		\end{quote}	
+		\begin{quote}
+			\change{From the control viewpoint, the controller design of the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
+different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see [4].}
+		\end{quote}
+
 	}
@@
 	\answer{
-		We revisited the Section 2.1 in order to define the assumptions on the penalty matrices. The corresponding part reads as:
+		We revisited the Section 2.1 in order to \textcolor{blue}{explicitly} define the assumptions on the penalty matrices \textcolor{blue}{of the optimization problem}. The corresponding part reads as:
 		\begin{quote}
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
-The matrix $R \change{\succ 0} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
+\textcolor{blue}{The penalty matrices are expected to ensure strictly convex optimization problem of MPC design.
+Therefore,} the penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The matrix $R \change{\succ 0} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squared value of control inputs.
 			%
 			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
-\change{All the penalty matrices are considered to be diagonal due to the applicability of the tunable explicit MPC approach.}
+\change{\textcolor{blue}{Without loss of generality, } all the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
 			The parameter $\theta \in \Theta$ in Eq.~(1f) represents the initial condition of the optimization problem for which it is parametrically pre-computed. 
@@
 	\answer{
-		To explain the assumptions on the penalty matrices and specify the tuned matrix in the corresponding paragraph of the Section 2.2 in the following way:
+		To explain \textcolor{blue}{in detail} the assumptions on the penalty matrices and specify the tuned matrix, \textcolor{blue}{we revisited the text} in the corresponding paragraph of the Section 2.2 in the following way:
 		\begin{quote}
@@
 \change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any tuning parameter.
+The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
+}
+		\end{quote}
+
+		\begin{quote}
+			The idea of approximated tunable explicit MPC comes from the work ~\cite{Klauco_tunable}, where the control action is calculated based on linear interpolation between two boundary control actions.
+These control actions result from evaluating two boundary explicit MPCs.
+The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
+\change{The tuned matrix is either the state penalty or the control input penalty matrix.
+Based on the specific control application, and following the well-known LQR-based tuning rules, any penalty matrix can be determined/selected as the tuned parameter.
+Therefore, this approach is applicable for any tuning parameter.
 The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
@@
 
+	\answer{
+		\textcolor{blue}{
+		The ``aggressiveness'' of the MPC controller is associated with the setup of penalty matrices, namely $Q_\mathrm{y}$, $Q_\mathrm{I}$, $R$, as it determines the aggressiveness of the final control input.
+In general, following the LQR design riles, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
+This tuning procedure is also similar to increasing the proportional gain of PID controller.
+On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
+In order to make the notation of aggressive controller more clear, we added the following description:
+		}
+
+		\begin{quote}
+			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+The procedure of the self-tunable controller technique is presented.
+\change{The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the considered linearization point of the model linearization point.
+In the context of MPC design, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
+In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
+This tuning procedure is similar to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
+The MPC tuning based on the distance from the steady-state operating point represented an efficient way how to compensate for the nonlinear behavior of the controlled system.}
+		\end{quote}
+
+		\begin{quote}
+			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+The procedure of the self-tunable controller technique is presented.
+\change{The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the considered linearization point of the model linearization point.
+In the context of MPC design, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
+In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
+This tuning procedure is similar to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
+The MPC tuning based on the distance from the steady-state operating point represented an efficient way how to compensate for the nonlinear behavior of the controlled system.}
+		\end{quote} 
+	}
+
 	\comment{
@@
 Regarding the calculation of parameter $\rho$, the setup of reference value is more strict, i.e., the value should be reachable and from the operating range to ensure that $0 \le \rho \le 1 $.
+		}
+
+		\answer{
+			\textcolor{blue}{
+			We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the procedure to determine the tuning parameter $\rho$ in Eq.~(7), (9).
+			}
+
+			\textcolor{blue}{
+			First, regarding the MPC optimization problem, the reference signal is a parameter which is usually constrained such that it covers the operating range of the corresponding control application.
+Therefore, during the real-time control, the reference value can be selected only as a value from the feasible set determined offline, when constructing explicit MPC controller.
+If the MPC problem is precomputed also for non-reachable references, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to larger explicit solution of MPC, as the consequence of larger range of reference signal.
+			}
+
+			\textcolor{blue}{Next, regarding the calculation of parameter $\rho$, the setup of reference value is strict and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input/state constraints satisfaction, etc.
+			}
+
+			\textcolor{blue}{ [ TODO: Prosím ?a, pridaj 1-2 vety k tým dvom diskutovaným bodom aj do textu. ] }
+
 			\begin{quote}
@@
 			\end{quote}
-
 	}
@@
 	\answer{
-		We thank the Reviewer for a careful review. The equation was corrected as follows:
+		We thank the Reviewer for a careful review. The equation was corrected \textcolor{blue}{to remove a bug and now reads} as follows:
 		\begin{quote}
@@
 		To improve the readability of the manuscript, we added the mathematical description to the corresponding sentence.
-Moreover, based on the following comment, we added the description of asymmetric behavior in this paragraph as follows:
+Moreover, based on the following comment, we added the description of asymmetric \textcolor{blue}{system} behavior in this paragraph as follows:
 		\begin{quote}
 			Note, the relations in Eq.~(7) and Eq.~(8) operate with the absolute value of the reference.
-\change{It is not taken into account, whether the reference changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
-As many plants have nonlinear behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.}
+\change{It is not taken into account, whether the reference \textcolor{blue}{value} changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether \textcolor{blue}{holds inequality:} $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear \textcolor{blue}{system} behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller \textcolor{blue}{self-tuning procedure} to improve the control performance.}
 		\end{quote}
@@
 	\answer{
-		 The incorporation of this comment into the manuscript was merged with the previous comment, as it corresponds to the thoughts in the same paragraph.
+		 \textcolor{blue}{Thank for this comment.
+Please, see the previous answer as} the incorporation of this comment into the manuscript was merged with the previous comment, as it corresponds to the thoughts in the same paragraph.
 	}
@@
 	\answer{
-		The parameter $\gamma$ depends on the value of $\rho$, which is scalar. From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
+		\textcolor{blue}{As this paper investigates laboratory implementation considering a SISO system, then} the parameter $\gamma$ depends on the value of $\rho$, which is \textcolor{blue}{also a} scalar.
+From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
 	}
@@
 	\answer{
+		\textcolor{blue}{Thanks for pointing out insufficient discussion on the selection of the tuning penalty matrix $Q_\mathrm{y}$.
+We have carefully revisited the corresponding paragraph to describe the tuning procedure.}
+
 		\begin{quote}
@@
 Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
+		\end{quote}
+
+		\begin{quote}
+			\change{
+			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
+			First, the aim of the tuning procedure was to determine, which penalty matrix is the most suitable for real-time tuning.
+Based on the whole set of experimentally collected data, the penalty matrix $Q_\mathrm{y}$ was determined as the most relevant tuned penalty, as this penalty matrix had the most significant effect on the control trajectories.
+Tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance without steady-state control error and without significant oscillations around the reference value.
+Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
+			}
 		\end{quote}

### 2024-02-24 paper/JoPC/response_letter.tex
Paper: review: Reviewer 2: update

@@
 	}
+	\answer{
+		\textcolor{blue}{We thank for very insightful comment on the experiment setup. We find this comments is composed of three, closely related, crucial issues to be answered one by one.}
+
+		\textcolor{blue}{First, we agree with the reviewer that the hot stream temperature was considered to be constant.
+This assumption is supported by the implementation of the auxiliary PID controller dedicated to control the temperature in the boiler/retention tank of hot medium.
+Although the control profiles of the hot stream temperature ($T = 70^{\circ}$\,C) is not provided, the corresponding dynamics provided by the heat transfer were within the declared precision of the hot stream temperature sensor and hence negligible.}
+
+		\textcolor{blue}{Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature, etc.}
+
+		\textcolor{blue}{Finally, we would like to address the doubts related to the observation of the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the putlet temperature of heated medium.
+Although this performance may look as an error introduced during a single measurement, we realized a series of laboratory experiments to investigate this phenomenon with the analogous results.
+The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$), or close to the value of $U = 55\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$).
+Therefore, after the detailed analysis, we state that this phenomenon originates the physical construction of the heat exchanger in the consequence of the portion of heat releases from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.}
+	}
 

### 2024-02-25 paper/JoPC/response_letter.tex
Paper: Review: Update

@@
 We reformulated or added the corresponding statements to clarify the ideas.
+
+	\textcolor{blue}{ [ TODO: Prosím pozor na bibliografické referencie v texte odpovede, pretože niektoré sú statické - skopírované ?ísla - a potom to ?íslovanie nesedí so zoznamom referencií na konci tejto odpovede.
+] }
 
@@
 Therefore, after the detailed analysis, we state that this phenomenon originates the physical construction of the heat exchanger in the consequence of the portion of heat releases from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.}
+
+		\begin{quote}
+			\change{
+				\textcolor{blue}{ [ TODO: Zváži? možnos? prida? cca. 1 vetu ku každému bodu aj do textu ?lánku. ] }
+			}
+		\end{quote}
 	}

### 2024-02-26 paper/JoPC/response_letter.tex
comments on JO comments :)

@@
 
-		\textcolor{blue}{ [ TODO: Odporú?am prida? po?akovanie na úvod prvej odpovede každému recenzentovi---nastaví sa tým úvodná (pozitívna) ``nálada'' komunikácie. ] }
-
-		\textcolor{blue}{ We thank the Reviewer for pointing out unclear motivation for self-tunable control approach in section Introduciton.} 
+		We thank the Reviewer for pointing out unclear motivation for self-tunable control approach in section Introduciton. 
 		In order to clearly emphasize the need of a self-tunable technique, we revised the Introduction section in a following way:
@@
 
-		\textcolor{blue}{ [ TODO: Odporú?am po?akova? za konkrétnu vec, aby to nevyznelo len ako ``prázdne'' / všeobecné po?akovanie. ] }
-
-		We thank the reviewer for an important comment. We reformulated the sentence as follows:
+		We thank the reviewer for an important comment on application range of the proposed control method. We reformulated the corresponding sentence to make the implementation limits clear:
 		\begin{quote}
-			\change{If the MPC optimization problem can be pre-solved explicitly, the lower online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
-		\end{quote}
-
-		\textcolor{blue}{We thank the reviewer for an important comment on application range of the proposed control method.
-We reformulated the corresponding sentence to make the implementation limits clear}:
-		\begin{quote}
-			\change{If the MPC design problem can be addressed in a tractable form and pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
+			\change{If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
 		\end{quote}
@@
 	\answer{		
-		We thank the reviewer for the question and comment.
-If a moderately tuned optimal MPC also provided a reasonable or potentially better performance than the two boundary controllers, the self-tunable technique would be out of scope for such control application.
-Nevertheless, there are situations, when using only one controller with a constant setup leads to just ''satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance (e.g.
-high overshoots or settling time).
-When working on our case study results, different setups of penalty matrices were explored, also $Q_\mathrm{y} = 500$.
-In this scenario, the control performance was comparable with the tuned controller for the first two reference step changes (tracking the reference upwards).
-However, when the reference was tracked downwards, the undershoots similar to lower boundary controller, i.e., $Q_\mathrm{y} = 100$ were present.
-Therefore, it supports the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the control performance could be improved by including the benefits of two boundary controllers.
-
-		\textcolor{blue}{
 		We thank the reviewer for the comment on the performance of the proposed method.
-Obviously, if there exists a well-tuned (``universal'') controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, than implementation of the self-tuning procedure is out of scope for such control application.
-Nevertheless, there are numerous practical situations, when using only one controller with a constant setup leads to poor or just to ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
-When working on our laboratory case study, a set of different setups of penalty matrices were investigated, among them also the requested value of $Q_\mathrm{y} = 500$.
+Obviously, if there exists a well-tuned (``universal'') controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, there are numerous practical situations, when using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices was investigated, among them also the requested value of $Q_\mathrm{y} = 500$.
 In this control scenario, the control performance was comparable with the self-tuned controller for the first two step changes of the reference value (tracking the reference upwards).
-However, when the reference was tracked downwards, the significant undershoots were present---similar to the closed-loop performance of the lower boundary controller, i.e., $Q_\mathrm{y} = 100$.
+However, when the reference was tracked downwards, significant undershoots were present -- similar to the closed-loop performance of the lower boundary controller, i.e., $Q_\mathrm{y} = 100$.
 Therefore, these observations support the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the closed-loop control performance is improved by introducing the benefits of the self-tuning based on the two boundary MPC controllers.
-		} 
+		\begin{quote}
+			TODO
+		\end{quote}		
 	}
@@
 	\answer{		
-		We thank the reviewer for this important comment.
-We revisited the Conclusion section containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
-As the thoughts and ideas remind discussion more than conclusion, this part was transferred to the section Results and discussion.
+		We thank the Reviewer for this important comment on the reliable implementation in the industrial applications.
+We revisited the corresponding text in section Conclusion containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
+As the revised extended text includes ideas and comments reminding discussion more than conclusion, this part was transferred to the section Results and discussion, and now reads as follows:
 		\begin{quote}
@@
 			value of the manipulated variables is interpolated between them.
-\change{It is also possible to include the disturbance into the design process of the MPC controller.
-In such case, e.g., a robust MPC strategy (REF!) would be beneficial, which would lead to more conservative control actions in order to create space for disturbances.
-Nevertheless, if the problem is not large-scale and it is possible to obtain the explicit solution, it is still possible to interpolate between the control actions from the robust controllers.}
-		\end{quote}
-
-		\textcolor{blue}{We thank the reviewer for this important comment on the reliable implementation in the industrial applications.
-We revisited the corresponding text in section Conclusion containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
-As the revised extended text includes ideas and comments reminding discussion more than conclusion, this part was transferred to the section Results and discussion, and now reads as follows:}
-		\begin{quote}
-			Note, this strategy relies on a proper design of the two boundary controllers.
-			In case a non-negligible disturbance occurs, both boundary controllers
-			should be able to solve a disturbance rejection problem, as the final
-			value of the manipulated variables is interpolated between them.
-\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy \cite{PR11} should be considered.
+\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy should be considered, see e.g.~\cite{PR11}.
 Obviously, any robust MPC design method leads to conservative control actions as some portion of performance is scarified to compensate the impact of the disturbances.
-Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of robust explicit MPC offline, then exactly the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
+Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then exactly the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
 		\end{quote}	
@@
 	\answer{		
-
-		\textcolor{blue}{ [ TODO: Odporú?am po?akova? za konkrétnu vec, aby to nevyznelo len ako ``prázdne'' / všeobecné po?akovanie. ] }
-
-		We understand that this formulation might sound vague, so we reformulated the corresponding sentence as follows:
+		We agree that the used formulation sounds vague, therefore, we reformulated the corresponding sentence in Abstract as follows:
 		\begin{quote}
@@
 		\end{quote}			
-
-		\textcolor{blue}{We agree that the used formulation sounds vague, therefore, we reformulated the corresponding sentence in Abstract as follows:
-		\begin{quote}
-			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller whenever the operating conditions are changed/updated.}.
-		\end{quote}	
-		}
 	}
@@
 	\answer{
-		We revisited the Introduction section in order to \textcolor{blue}{clearly} define the asymmetric behavior \textcolor{blue}{of heat exchanger device, placed} at the place of its first occurrence.
+		We revisited the Introduction section in order to clearly define the asymmetric behavior at the place of its first occurrence.
 		\begin{quote}
-			From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior \change{(i.e.
-different behavior when the temperature is rising or decreasing)} of the heat exchangers is a challenging task [4].
-		\end{quote}	
-		\begin{quote}
-			\change{From the control viewpoint, the controller design of the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
+			\change{From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
 different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see [4].}
@@
 	\answer{
-		We revisited the Section 2.1 in order to \textcolor{blue}{explicitly} define the assumptions on the penalty matrices \textcolor{blue}{of the optimization problem}. The corresponding part reads as:
+		We revisited the Section 2.1 in order to define the assumptions on the penalty matrices of the optimization problem. The corresponding part reads as:
 		\begin{quote}
@@
 			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
-\change{\textcolor{blue}{Without loss of generality, } all the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
+\change{All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
 			The parameter $\theta \in \Theta$ in Eq.~(1f) represents the initial condition of the optimization problem for which it is parametrically pre-computed. 
@@
 	\answer{
-		To explain \textcolor{blue}{in detail} the assumptions on the penalty matrices and specify the tuned matrix, \textcolor{blue}{we revisited the text} in the corresponding paragraph of the Section 2.2 in the following way:
+		To explain the assumptions on the penalty matrices and specify the tuned matrix, we revisited the text in the corresponding paragraph of the Section 2.2 in the following way:
 		\begin{quote}
@@
 The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
-\change{The tuned matrix is either the state penalty or the control input penalty matrix.
-Based on the specific control application, and following the well-known LQR-based tuning rules, any penalty matrix can be determined/selected as the tuned parameter.
+\textcolor{blue}{The tuned matrix is either the state penalty or the control input penalty matrix.} \change{Based on the specific control application, and following the well-known LQR-based tuning rules, any penalty matrix can be selected as the tuned parameter.
 Therefore, this approach is applicable for any tuning parameter.

### 2024-02-27 paper/JoPC/response_letter.tex
comments on JO comments :)..part 2

@@
 		The aggressiveness of the MPC controller is associated with the setup of penalty matrices, namely $Q_\mathrm{y}$, $Q_\mathrm{I}$, $R$, as it determines the aggressiveness of the final control input.
-In general, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
+In general, followign the LQR design rules, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
 This process is similar to increasing the proportional gain in PID controller.
@@
 
-	\answer{
-		\textcolor{blue}{
-		The ``aggressiveness'' of the MPC controller is associated with the setup of penalty matrices, namely $Q_\mathrm{y}$, $Q_\mathrm{I}$, $R$, as it determines the aggressiveness of the final control input.
-In general, following the LQR design riles, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
-This tuning procedure is also similar to increasing the proportional gain of PID controller.
-On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-In order to make the notation of aggressive controller more clear, we added the following description:
-		}
-
-		\begin{quote}
-			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-The procedure of the self-tunable controller technique is presented.
-\change{The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the considered linearization point of the model linearization point.
-In the context of MPC design, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
-In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
-This tuning procedure is similar to increasing the proportional gain in PID controller.
-On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-The MPC tuning based on the distance from the steady-state operating point represented an efficient way how to compensate for the nonlinear behavior of the controlled system.}
-		\end{quote}
-
-		\begin{quote}
-			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-The procedure of the self-tunable controller technique is presented.
-\change{The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the considered linearization point of the model linearization point.
-In the context of MPC design, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
-In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
-This tuning procedure is similar to increasing the proportional gain in PID controller.
-On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-The MPC tuning based on the distance from the steady-state operating point represented an efficient way how to compensate for the nonlinear behavior of the controlled system.}
-		\end{quote} 
-	}
-
 	\comment{
@@
 	\answer{
-		We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the calculation process of $\rho$ in Eq.~(7) and Eq.~(9).
-Regarding the MPC optimization problem, the reference signal is a parameter which is usually constrained such that it covers the operating range of the corresponding control application.
-Therefore, during the control, the reference can be set only as a value from the feasible set.
-If the MPC problem is precomputed also for non-reachable references, e.g., because it is not clear a priori which reference values will be set during control, this would ''only'' lead to larger explicit solution of MPC because of larger range of reference signal.
-Regarding the calculation of parameter $\rho$, the setup of reference value is more strict, i.e., the value should be reachable and from the operating range to ensure that $0 \le \rho \le 1 $.
-		}
+		We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the calculation process of the tuning parameter $\rho$ in Eq.~(7) and Eq.~(9).
 
-		\answer{
-			\textcolor{blue}{
-			We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the procedure to determine the tuning parameter $\rho$ in Eq.~(7), (9).
-			}
-
-			\textcolor{blue}{
 		First, regarding the MPC optimization problem, the reference signal is a parameter which is usually constrained such that it covers the operating range of the corresponding control application.
@@
 If the MPC problem is precomputed also for non-reachable references, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to larger explicit solution of MPC, as the consequence of larger range of reference signal.
-			}
 
-			\textcolor{blue}{Next, regarding the calculation of parameter $\rho$, the setup of reference value is strict and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+		Next, regarding the calculation of parameter $\rho$, the setup of reference value is strict and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
 Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input/state constraints satisfaction, etc.
-			}
-
-			\textcolor{blue}{ [ TODO: Prosím ?a, pridaj 1-2 vety k tým dvom diskutovaným bodom aj do textu. ] }
 
@@
 	\answer{
-		We thank the Reviewer for a careful review. The equation was corrected \textcolor{blue}{to remove a bug and now reads} as follows:
+		We thank the Reviewer for a careful review. The equation was corrected as follows:
 		\begin{quote}
@@
 		To improve the readability of the manuscript, we added the mathematical description to the corresponding sentence.
-Moreover, based on the following comment, we added the description of asymmetric \textcolor{blue}{system} behavior in this paragraph as follows:
+Moreover, based on the following comment, we added the description of asymmetric system behavior in this paragraph as follows:
 		\begin{quote}
 			Note, the relations in Eq.~(7) and Eq.~(8) operate with the absolute value of the reference.
-\change{It is not taken into account, whether the reference \textcolor{blue}{value} changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether \textcolor{blue}{holds inequality:} $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
-As many plants have nonlinear \textcolor{blue}{system} behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller \textcolor{blue}{self-tuning procedure} to improve the control performance.}
+\change{It is not taken into account, whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether holds the inequality: $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.}
 		\end{quote}
@@
 	\answer{
-		 \textcolor{blue}{Thank for this comment.
-Please, see the previous answer as} the incorporation of this comment into the manuscript was merged with the previous comment, as it corresponds to the thoughts in the same paragraph.
+		 We thank the Reviewer for this comment.
+Please, see the previous answer as the incorporation of this comment into the manuscript was merged with the previous comment, because it corresponds to the thoughts in the same paragraph.
 	}
@@
 	\answer{
-		\textcolor{blue}{As this paper investigates laboratory implementation considering a SISO system, then} the parameter $\gamma$ depends on the value of $\rho$, which is \textcolor{blue}{also a} scalar.
+		\textcolor{blue}{As this paper investigates laboratory implementation considering a SISO system, then} the parameter $\gamma$ depends on the value of $\rho$, which is also a scalar.
 From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
@@
 	\answer{
-		We thank the reviewer for this attentive comment. We corrected the order of Figures.
+		We thank the Reviewer for this attentive comment. We corrected the order of Figures.
 	}
@@
 	\answer{
-		\textcolor{blue}{Thanks for pointing out insufficient discussion on the selection of the tuning penalty matrix $Q_\mathrm{y}$.
-We have carefully revisited the corresponding paragraph to describe the tuning procedure.}
+		We thank the Reviewer for pointing out insufficient discussion on the selection of the tuning penalty matrix $Q_\mathrm{y}$.
+We revisited the corresponding paragraph to describe the tuning procedure.
 
 		\begin{quote}
-			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
+			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control setup was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
 			First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
@@
 	\answer{
-		\textcolor{blue}{We thank for very insightful comment on the experiment setup. We find this comments is composed of three, closely related, crucial issues to be answered one by one.}
+		We thank the Reviewer for the very insightful comment on the experiment setup. We find this comment comprises three closely related points to be answered individually.
 
-		\textcolor{blue}{First, we agree with the reviewer that the hot stream temperature was considered to be constant.
-This assumption is supported by the implementation of the auxiliary PID controller dedicated to control the temperature in the boiler/retention tank of hot medium.
-Although the control profiles of the hot stream temperature ($T = 70^{\circ}$\,C) is not provided, the corresponding dynamics provided by the heat transfer were within the declared precision of the hot stream temperature sensor and hence negligible.}
+		\textcolor{blue}{First, we confirm that the hot stream temperature is considered constant.
+This assumption is supported by the implementation of the auxiliary PID controller dedicated to controlling the temperature in the boiler/retention tank of the hot medium.
+Although the control profiles of the hot stream temperature ($T = 70^{\circ}$\,C) are not provided, the corresponding dynamics provided by the heat transfer were within the declared precision of the hot stream temperature sensor and hence negligible.}
 
-		\textcolor{blue}{Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature, etc.}
+		Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature and the constant inlet temperature of the heating medium.
 
-		\textcolor{blue}{Finally, we would like to address the doubts related to the observation of the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the putlet temperature of heated medium.
-Although this performance may look as an error introduced during a single measurement, we realized a series of laboratory experiments to investigate this phenomenon with the analogous results.
+		\textcolor{blue}{ Finally, we would like to address the doubts related to observing the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the outlet temperature of the heated medium.
+Although this performance may look like an error introduced during a single measurement, we realized a series of laboratory experiments to investigate this phenomenon with analogous results.
 The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$), or close to the value of $U = 55\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$).
-Therefore, after the detailed analysis, we state that this phenomenon originates the physical construction of the heat exchanger in the consequence of the portion of heat releases from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.}
+Therefore, after the detailed analysis, we state that this phenomenon originates from the physical construction of the heat exchanger due to the portion of heat released from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.}
 
 		\begin{quote}
-			\change{
-				\textcolor{blue}{ [ TODO: Zváži? možnos? prida? cca. 1 vetu ku každému bodu aj do textu ?lánku. ] }
-			}
+			TODO: Zapracovat do clanku. 			
 		\end{quote}

### 2024-02-27 paper/JoPC/response_letter.tex
comments on JO comments :)..part 3

@@
 
-	\textcolor{blue}{ [ TODO: Prosím pozor na bibliografické referencie v texte odpovede, pretože niektoré sú statické - skopírované ?ísla - a potom to ?íslovanie nesedí so zoznamom referencií na konci tejto odpovede.
-] }
-
 	\section*{Answer to Reviewer 1}
@@
 			TODO: Update the introduction
-			%The paper [27] pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+			%The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
 		\end{quote}
@@
 			\change{From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
-different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see [4].}
+different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
 		\end{quote}

### 2024-02-27 paper/JoPC/response_letter.tex
som z toho MIMO

@@
 How can this approach be applied to multivariable interacting systems with multiple control inputs?
+	}
+
+	\answer{
+		The approach of self-tunable technique can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the value of every control input.
+It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
+However, this is straightforward to implement only for decoupled systems.
+If there are strong interactions between the system states, the self-tunable technique is difficult to design.
+(My mame decoupled system?).
+To give the reader a clear view on the apllicability of the proposed approach, we added the following explanation to the manuscript:
+		TODO
 	}

### 2024-02-27 data/control_performance.m

@@ -1,5 +1,5 @@
 % clc, close all, clear 
-load('ref_tracking25.mat')
+load('ref_tracking23.mat')
 %% plots
 figure(11)
 hold on; grid minor; box on

### 2024-02-28 paper/JoPC/response_letter.tex
minor updates

@@
 However, this is straightforward to implement only for decoupled systems.
-If there are strong interactions between the system states, the self-tunable technique is difficult to design.
-(My mame decoupled system?).
+If there are strong interactions between the system states, the self-tunable technique is challenging to design.
 To give the reader a clear view on the apllicability of the proposed approach, we added the following explanation to the manuscript:
@@
 These sets include the origin in their strict interiors.
-\textcolor{blue}{The penalty matrices are expected to ensure strictly convex optimization problem of MPC design.
-Therefore,} the penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
+The penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
 The matrix $R \change{\succ 0} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squared value of control inputs.
@@
 These control actions result from evaluating two boundary explicit MPCs.
-The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices -- the tuned one.
+The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
 \change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any tuning parameter.

### 2024-02-29 paper/JoPC/response_letter.tex
some other answers

@@
 		\begin{quote}
-			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller}.
+			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller parameters}.
 		\end{quote}			
@@
 		Similarly, for the two boundary controllers explain the assumptions on the penalty matrices.
-Clearly, if the "upper" boundary matrices are equivalent to the "lower" boundary matrices multiplied by a scalar, there will be no difference between the solutions obtained by solving either controller.
-Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
+\change{Clearly, if the "upper" boundary matrices are equivalent to the "lower" boundary matrices multiplied by a scalar, there will be no difference between the solutions obtained by solving either controller.} Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
 	}
@@
 The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
-\change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any tuning parameter.
+\change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any penalty matrix.
 The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
@@
 
-		\begin{quote}
-			The idea of approximated tunable explicit MPC comes from the work ~\cite{Klauco_tunable}, where the control action is calculated based on linear interpolation between two boundary control actions.
-These control actions result from evaluating two boundary explicit MPCs.
-The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
-\textcolor{blue}{The tuned matrix is either the state penalty or the control input penalty matrix.} \change{Based on the specific control application, and following the well-known LQR-based tuning rules, any penalty matrix can be selected as the tuned parameter.
-Therefore, this approach is applicable for any tuning parameter.
-The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
-}
-		\end{quote}	
 	}
@@
 		Please clarify the last sentence on page 7, extending into page 8, which describes the tuning process as systematic, but the description appears to be ad hoc and depend on the system.
+	}
+
+	\answer{
+		We thank the Reviewer for the comment on systematic tuning.
+By systematic tuning we mean choosing one penalty matrix and observig the control results based on gradual increasing or decreasing of the diagonal elements of the penalty matrices.
+Then, the same procedure is performed for the rest of the penalty matrices.
+Regarding the initial setup of the penalty matrices, it is often based on balancing the orders of magnitude of the input and state variables.
+The aim is to compensate the contributions of all the terms of the cost function.
+Nevertheless, this procedure is not the aim of this work and we do not want to go into detail of the general MPC tuning.
+Therefore, we omitted the part mentioning judging the control performance subject to the specific system and reformulated the sentence as follows:
+
+		\begin{quote}
+			To determine which penalty matrix in Eq.~(4) should be tuned, it is suggested to judge the control performance \change{by systematic tuning of all the penalty matrices.
+Systematic tuning involves selecting a specific penalty matrix and observing the control results by gradually increasing or decreasing the diagonal elements of the matrix.
+This process is then repeated for the remaining penalty matrices in a similar manner.}
+		\end{quote}
+
 	}
@@
 
+		As only the second part of the answer is crucial for the proposed tuning technique, we incorporated the comment on selected reference value into manuscript as follows:
+
 			\begin{quote}
-				TODO: Somehow update text in manusctipt?
+				Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:  
+				\begin{equation} \tag{7}
+					\label{eq:rho_self_tunable}
+					\rho = \frac{\vert y_{\mathrm{ref}(k)} \vert}{d_{\max}}.
+				\end{equation}
+
+				Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
+As a consequence, the parameter $\rho$ represents a way how to normalize the deviation from the steady-state value and is exploited to scale the control action or, implicitly, to tune the aggressiveness of the controller.
+
+				\change{Note, the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input/state constraints satisfaction, etc.}
 			\end{quote}
@@
 	\answer{
-		\textcolor{blue}{As this paper investigates laboratory implementation considering a SISO system, then} the parameter $\gamma$ depends on the value of $\rho$, which is also a scalar.
-From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
+		The parameter $\gamma$ depends on the value of $\rho$, which is also a scalar. From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
 	}

### 2024-03-01 paper/JoPC/response_letter.tex
some other answers 2

@@
 		We thank the reviewer for the comment on the performance of the proposed method.
-Obviously, if there exists a well-tuned (``universal'') controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
 Nevertheless, there are numerous practical situations, when using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated, among them also the requested value of $Q_\mathrm{y} = 500$.
-In this control scenario, the control performance was comparable with the self-tuned controller for the first two step changes of the reference value (tracking the reference upwards).
-However, when the reference was tracked downwards, significant undershoots were present -- similar to the closed-loop performance of the lower boundary controller, i.e., $Q_\mathrm{y} = 100$.
+In this control scenario, the control performance was comparable with the lower boundary controller, i.e., $Q_\mathrm{y} = 100$, for the first two step changes of the reference value (tracking the reference upwards).
+However, when the reference was tracked downwards, significant undershoots were present.
 Therefore, these observations support the fact that the general aim of the control, i.e., achieving the reference value, is satisfied, but the closed-loop control performance is improved by introducing the benefits of the self-tuning based on the two boundary MPC controllers.
+To emphasize this benefit, we added the following comment to the end of the section Results and discussion:
 		\begin{quote}			
-			TODO
+			In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower SSE), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$).
+
+			\change{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning based on the two boundary MPC controllers.}
 		\end{quote}		
@@
 
+	\answer{
+
+	}
+
 	\comment{
@@
 		We thank the Reviewer for pointing out insufficient discussion on the selection of the tuning penalty matrix $Q_\mathrm{y}$.
+By significant effect we meant the direct association of the tuned penalty matrix with the tuning factor $\rho$, which is calculated based on the reference value.
 We revisited the corresponding paragraph to describe the tuning procedure.
@@
 		\begin{quote}			
-			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control setup was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
-			First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
-\change{Based on the set of experimentally collected data, the penalty matrix $Q_\mathrm{y}$ was chosen as the tuned one.} Based on the set of experimentally collected data, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the reference value.
-Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
-		\end{quote}
-
-		\begin{quote}
-			\change{
-			The penalty matrices of the problem in Eq.~(1) were systematically tuned and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
-			First, the aim of the tuning procedure was to determine, which penalty matrix is the most suitable for real-time tuning.
-Based on the whole set of experimentally collected data, the penalty matrix $Q_\mathrm{y}$ was determined as the most relevant tuned penalty, as this penalty matrix had the most significant effect on the control trajectories.
-Tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance without steady-state control error and without significant oscillations around the reference value.
-Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
-			}
+			\change{The penalty matrices of the problem in Eq.~(1) were systematically tuned, and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
+			First, the tuning procedure aimed to determine which penalty matrix is the most suitable for real-time tuning.
+The most relevant was the penalty matrix $Q_\mathrm{y}$ as the tuning is directly associated with a reference value, which takes place in the calculation of the tuning factor $\rho$.
+Moreover, the tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance.} Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
 		\end{quote}

### 2024-03-01 paper/JoPC/response_letter.tex
another answer

@@
 	\answer{
+		We thank the reviewer for the comment on the tuning parameter. We would like to divide our answer in three parts.
+
+		We explained the symbol $\lvert.\rvert$ in the corresponding part as follows:
+
+		\begin{quote}
+			Another suggestion is to fit the maximal deviation $d_{\max}$ based on the constraints on system outputs: 
+			\begin{equation} \tag{6}
+				\label{eq:d_max}
+				d_{\max} = \max(\vert y_{\min} \vert, y_{\max}),
+			\end{equation}
+			where \change{the symbol $\lvert.\rvert$ in Eq.~\eqref{eq:d_max} and everywhere else in the paper denotes the element-wise absolute value}, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
+		\end{quote}
+
+		Regarding the conservativeness of the parameter $d_{\max}$, we confirm that it is requested for this parameter to be equal to the maximum magnitude of the reference values.
+It is necessary to ensure this condition in order to satisfy $0 \le \rho \le 1$.
+If the parameter $d_{\max}$ would not correspond to the maximum magnitude of the reference values, the tuning parameter $\rho > 1$ would lead to extrapolation of the control input, which could result in losing of all theoretical guarantees, i.e., constraints satisfaction etc.
+As the satisfaction of the condition $0 \le \rho \le 1$ was emphasized in the comment regarding the reachable reference values, we did not incorporate this part of answer into the manuscript to avoid repetitions in the text.
+
+		Last but not least, we address the question about the parameter $\rho$ closer to value 1 for large magnitudes of references. 			
+		In the manuscript, it is suggested to increase the value of diagonal elements of the penalty matrix $Q_\mathrm{y}$ with increasing reference step change, i.e.:		
+		\begin{eqnarray*}
+			Q_\mathrm{y}(k) = (1-\rho(k)) \, Q_\mathrm{y,L} + \rho(k) \, Q_\mathrm{y,U}.
+		\end{eqnarray*}
+
+		The aim is to obtain a controller with higher penalization of the control error, leading to more ``aggressive'' or ``active'' control inputs.
+		If opposite nature of controller is requested, it is possible to adapt the tuning such that 
+		\begin{eqnarray*}
+			Q_\mathrm{y}(k) = \rho(k) \, Q_\mathrm{y,L} + (1-\rho(k)) \, Q_\mathrm{y,U}
+		\end{eqnarray*}
+		holds.
+This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$.
+To give the reader a better insight into the context of relation between parameter $\rho$ and the penalty matrix, we added this answer into Section 3.1 in the following way:
+
+		\begin{quote}			
+			Note, only the absolute value of $\Delta_{\mathrm{ref}}$ and $\Delta_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
+
+ 			\change{In Eq.~(9), it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
+Note, in this work the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with upper boundary controller, see Eq.~(4).
+If opposite logic of controller tuning is requested, it is possible to adapt the tuning such that
+				\begin{eqnarray*}
+					\label{eq:tunable_R}
+					&~& R(k) = \rho(k) \, R_\mathrm{L} + (1-\rho(k)) \, R_\mathrm{U}, \\
+					\label{eq:tunable_Qx}
+					&~& Q_\mathrm{I}(k) = \rho(k) \, Q_\mathrm{I,L} + (1-\rho(k)) \, Q_\mathrm{I,U}, \\
+					\label{eq:tunable_Qy}
+					&~& Q_\mathrm{y}(k) = \rho(k) \, Q_\mathrm{y,L} + (1-\rho(k)) \, Q_\mathrm{y,U},
+				\end{eqnarray*}
+ 			holds. This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$. }
+		\end{quote}
 

### 2024-03-05 paper/JoPC/response_letter.tex
first question

@@
 
-	We would like to thank the reviewers for the constructive and thoughtful comments on our manuscript.
+	We would like to thank the Reviewers for the constructive and thoughtful comments on our manuscript.
 	We revised the document based on these comments and we provide point-to-point answers below.
@@
 	We would like to thank the Editor for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality.
-We revised the paper based on the reviewers' comments and incorporated the suggestions into our manuscript.
+We revised the paper based on the Reviewers' comments and incorporated the suggestions into our manuscript.
 We reformulated or added the corresponding statements to clarify the ideas.
@@
 		\begin{quote}
-			TODO: Update the introduction
-			%The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+			The applicability of model predictive control expanded with the parametric solution of the MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in real-time control.
+Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
+The lower computational complexity makes the explicit MPC more suitable for practical industrial implementation.
+Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+\change{The inability to tune the controller online can be a disadvantage due to varying operating conditions, when different setup of controller is beneficial.}
+
+			...
+
+			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
+\change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
+The use of different controller setups can be helpful in handling the nonlinear behavior of the plant.} The procedure of the self-tunable controller technique is presented.
+The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
 		\end{quote}
@@
 
-		We thank the reviewer for an important comment on application range of the proposed control method. We reformulated the corresponding sentence to make the implementation limits clear:
+		We thank the Reviewer for an important comment on application range of the proposed control method. We reformulated the corresponding sentence to make the implementation limits clear:
 		\begin{quote}
@@
 	\answer{		
-		We thank the reviewer for the comment on the performance of the proposed method.
+		We thank the Reviewer for the comment on the performance of the proposed method.
 Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
@@
 		\begin{quote}
-			\change{From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
+			The heat exchangers in their numerous variants are integrated into many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
+\change{Simultaneously, the utility generation for heating or cooling is energy-demanding.
+From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
 different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
@@
 	\answer{
-		We thank the reviewer for the comment on the tuning parameter. We would like to divide our answer in three parts.
+		We thank the Reviewer for the comment on the tuning parameter. We would like to divide our answer in three parts.
 

### 2024-03-05 paper/JoPC/response_letter.tex
some other answers updated, HE_scheme added

@@
 	\answer{
-		We removed the Figure 6 and 7 in order to improve the concise presentation of the control results.
+		We understand that the data from Figures 6 and 7 are depicted also in Figures 10 and 11 and see the motivation to remove the Figures 6 and 7.
+However, the Figures 6 and 7 play an important role in maintaining the flow and coherence of the paper.
+Removing it could make it more difficult for readers to follow the presented ideas leading to the design of the tuning strategy.
+In the Figures 10 and 11, the third (green) trajectory was added, which is overlapping with the original (blue and red) trajectories in some time intervals.
+The intention was to bring the well-readable figures corresponding to the boundary controllers first, and then to add the last trajectory.
+We hope that this intention leads to better readability of the paper.
 	}
@@
 		Similarly, for the two boundary controllers explain the assumptions on the penalty matrices.
-\change{Clearly, if the "upper" boundary matrices are equivalent to the "lower" boundary matrices multiplied by a scalar, there will be no difference between the solutions obtained by solving either controller.} Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
+Clearly, if the "upper" boundary matrices are equivalent to the "lower" boundary matrices multiplied by a scalar, there will be no difference between the solutions obtained by solving either controller.
+Perhaps, this is what meant by statement: "The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices - the tuned one", but this statement can be further clarified (which matrix is the tuned one referring to?).
 	}
@@
 
+	\answer{
+		In order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion:
+
+		TODO: Nezabudnut pridat symboly to nomenklatury!
+
+		\begin{figure}
+			\begin{center}
+				\includegraphics[width=0.8\textwidth]{images/HE_scheme}
+				\caption{Scheme of Armfield PCT23.
+Heat exchanger (I), peristaltic pump for cold feed (II), peristaltic pump for heating medium (III), tank for cold feed (IV), heater for heating medium (V), temperature sensors ($\mathrm{T}$ -- controlled temperature, $\mathrm{T}_\mathrm{C}$ -- cold feed temperature, $\mathrm{T}_\mathrm{H}$ -- heating medium temperature), and electric power for maintaining the temperature of the heating medium (W).
+}
+				\label{fig:HE_scheme}
+			\end{center}
+		\end{figure}
+	}
+
 	\comment{
@@
 
-		\textcolor{blue}{First, we confirm that the hot stream temperature is considered constant.
-This assumption is supported by the implementation of the auxiliary PID controller dedicated to controlling the temperature in the boiler/retention tank of the hot medium.
-Although the control profiles of the hot stream temperature ($T = 70^{\circ}$\,C) are not provided, the corresponding dynamics provided by the heat transfer were within the declared precision of the hot stream temperature sensor and hence negligible.}
+		First, we confirm that the hot stream temperature is considered constant.
+This assumption is supported by the implementation of the auxiliary P controller dedicated to controlling the temperature in the heating tank for the hot medium.
+Although the control profiles of the hot stream temperature ($T = 70^{\circ}$\,C) are not provided, the corresponding dynamics was negligible and the steady-state values of the heating medium temperature were constant.
 
@@
 
-		\textcolor{blue}{ Finally, we would like to address the doubts related to observing the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the outlet temperature of the heated medium.
+		Finally, we would like to address the doubts related to observing the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the outlet temperature of the heated medium.
 Although this performance may look like an error introduced during a single measurement, we realized a series of laboratory experiments to investigate this phenomenon with analogous results.
-The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$), or close to the value of $U = 55\,\%$ (e.g., for $Q_{\mathrm{y}} = XXX, XXX$).
-Therefore, after the detailed analysis, we state that this phenomenon originates from the physical construction of the heat exchanger due to the portion of heat released from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.}
+The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$, or close to the value of $U = 55\,\%$.
+This phenomenon was even observed with different setup of weighting matrix $R = 100$ during the initial tuning and searching for the ``right'' setup of all penalty matrices.
+The input variable also settled close to $U = 45\,\%$ (e.g., for $Q_{\mathrm{y}} = 100$), or close to the value of $U = 55\,\%$ (e.g., for $Q_{\mathrm{y}} = 1000$).
+Therefore, after the detailed analysis, we state that this phenomenon originates from the physical construction of the heat exchanger due to the portion of heat released from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.
 

### 2024-03-06 paper/JoPC/response_letter.tex
last comment (steady state) and MIMO systems

@@
 	\answer{
-		The approach of self-tunable technique can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the value of every control input.
+		The approach of self-tunable technique can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
 It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
@@
 If there are strong interactions between the system states, the self-tunable technique is challenging to design.
-To give the reader a clear view on the apllicability of the proposed approach, we added the following explanation to the manuscript:
-		TODO
+To give the reader a better view on the apllicability of the proposed approach, we added the following explanation to the Concusion of the manuscript:
+
+		\begin{quote}
+			To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+
+			\change{The approach of self-tunable technique was investigated on a SISO system, but can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
+It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
+However, this is straightforward to implement only for decoupled systems.
+If there are strong interactions between the system states, the self-tunable technique is challenging to design.
+In such case, it is necessary to include expert knowledge about the system states interactions, and the resulting value of the tuning paramter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.}
+		\end{quote}
+
 	}
@@
 	\answer{
-		We understand that the data from Figures 6 and 7 are depicted also in Figures 10 and 11 and see the motivation to remove the Figures 6 and 7.
+		In order to bring a concise presentation of the results, we removed the Figures 6 and 7.
+		%We understand that the data from Figures 6 and 7 are depicted also in Figures 10 and 11 and see the motivation to remove the Figures 6 and 7.
 However, the Figures 6 and 7 play an important role in maintaining the flow and coherence of the paper.
@@
 If so, this should be stated explicitly in the problem setup.
+	}
+
+	\answer{
+		We thank for the comment on the application range of the proposed method.
+Also Reviewer~1 suggested to address this issue.
+We kindly invite the Reviewer~2 to revise the answer to the third comment of Reviewer 1, as it addresses the same topic.
+
+		Q: Staci to predsa len uviest do zaveru ako potencialne myslienky a riesenia MIMO problemov, ked tento reviewer to chce v problem setupe?
 	}
@@
 	\answer{
-		In order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion:
-
-		TODO: Nezabudnut pridat symboly to nomenklatury!
+		To prevent confusion associated with the term ``feed'', we replaced the corresponding parts in manuscript with ``cold medium''.
+Moreover, in order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion:
 
@@
 	\answer{
-		We thank the Reviewer for the very insightful comment on the experiment setup. We find this comment comprises three closely related points to be answered individually.
+		We thank the Reviewer for the very insightful comment on the experiment setup. 
+		First, we would like to address the doubts related to the constant steady-state values of cold and heating medium temperatures.
+Regarding the temperature of the cold medium, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
+Nevertheless, the temperature of the cold medium was checked multiple times during experiment and was constant.
+The advantage is that there is no other factor affecting the temperature of the cold medium, except the room temperature, which was constant.
+We added the information about the inlet temperature of the cold medium into the manuscript:
 
-		First, we confirm that the hot stream temperature is considered constant.
+		\begin{quote}
+			The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
+The heat exchange is performed between the cold medium (water) and the hot medium (water).
+\change{The cold medium as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
+The flow rate of the cold medium is constant, while the aim of control is to track the reference value of the outlet cold medium temperature.
+The inlet cold medium temperature was constant during the whole control, i.e., $T_\mathrm{C} = 19^{\circ}$\,C.}
+		\end{quote}
+
+		Regarding the temperature of the heating medium, we provide the corresponding trajectories of the temperature in Figure~\ref{fig:Th}.
+Note that the legend corresponds to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.
+It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
+The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
+As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of heating medium led to slight declining of the heating medium temperature.
+After approximately 100 seconds, the heating medium warmed up to the reference value, i.e., $T_{\mathrm{H, ref}} = 70^{\circ}$\,C and remained constant within the accuracy of the temperature sensor.
+It can be seen, that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
+Therefore, the same conditions for all control scenarios were fulfilled.
+We explain the different values of manipulated variable with the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
+When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
+Therefore, even different flow rates of the heating medium lead to the same temperature at the outlet.
+
+		Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature and the constant inlet temperature of the heating medium.
+
+		Based on our answer to the Reviewer's comment, we added Figure~\ref{fig:Th} and Figure~\ref{fig:W} to the manuscript with the following explanation to give the reader an insight into the dynamics of the heating medium:
+
+		\begin{quote}
+			An interesting phenomenon can be observed during tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
+Although the steady-state values of temperature have the same value, the values of the manipulated variable are different.
+To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
+\change{Also, the inlet temperatures of the cold and heating medium were checked in order to exclude the effect of a disturbance.
+Regarding the temperature of the cold medium, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
+Nevertheless, the temperature of the cold medium was checked multiple times during experiment and was constant.}
+
+			\change{Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th} and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
+Note that the legends correspond to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.}
+
+			\change{It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
+The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
+As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of heating medium led to slight declining of the heating medium temperature.
+After approximately 100 seconds, the heating medium warmed up to the reference value, i.e., $T_{\mathrm{H, ref}} = 70^{\circ}$\,C and remained constant within the accuracy of the temperature sensor.
+It can be seen, that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
+Therefore, the same conditions for all control scenarios were fulfilled.}
+
+			\change{The reason of this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~(TODO), blue.
+After approximately 100\,s, the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller, see Figure~(TODO), red.
+This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
+When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
+Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
+		\end{quote}
+
+		%We find this comment comprises three closely related points to be answered individually.
+
+		%First, we confirm that the hot stream temperature is considered constant.
 This assumption is supported by the implementation of the auxiliary P controller dedicated to controlling the temperature in the heating tank for the hot medium.
@@
 
-		Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature and the constant inlet temperature of the heating medium.
+		%Next, we would like to make clear that the repeatability of the realized laboratory experiments was ensured by fixing all the relevant conditions, such as the cold medium dosed into the heat exchanger from the large retention tanks at the laboratory temperature and the constant inlet temperature of the heating medium.
 
-		Finally, we would like to address the doubts related to observing the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the outlet temperature of the heated medium.
+		%Finally, we would like to address the doubts related to observing the varying steady-state values of the control inputs corresponding to the same value of the controlled variable - the outlet temperature of the heated medium.
 Although this performance may look like an error introduced during a single measurement, we realized a series of laboratory experiments to investigate this phenomenon with analogous results.
-The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$, or close to the value of $U = 55\,\%$.
+
+		%The steady-state value of control input settled either in the close neighborhood of $U = 45\,\%$, or close to the value of $U = 55\,\%$.
 This phenomenon was even observed with different setup of weighting matrix $R = 100$ during the initial tuning and searching for the ``right'' setup of all penalty matrices.
-The input variable also settled close to $U = 45\,\%$ (e.g., for $Q_{\mathrm{y}} = 100$), or close to the value of $U = 55\,\%$ (e.g., for $Q_{\mathrm{y}} = 1000$).
+The input variable also settled close to $U = 52\,\%$ (e.g., for $Q_{\mathrm{y}} = 1000$), or close to the value of $U = 42-45\,\%$ (e.g., for $Q_{\mathrm{y}} = 100$).
 Therefore, after the detailed analysis, we state that this phenomenon originates from the physical construction of the heat exchanger due to the portion of heat released from the plates for the (relatively high) reference value around $T = 50^{\circ}$\,C.
 
-		\begin{quote}
-			TODO: Zapracovat do clanku. 			
-		\end{quote}
+		\begin{figure}
+			\begin{center}
+				\includegraphics[width=0.7\textwidth]{images/Th}
+				\caption{The trajectory of heating medium temperature control (P controller).}
+				\label{fig:Th}
+			\end{center}
+		\end{figure}
+
+		\begin{figure}
+			\begin{center}
+				\includegraphics[width=0.7\textwidth]{images/W}
+				\caption{The trajectory of electric power controlling the heating medium temperature (P controller).}
+				\label{fig:W}
+			\end{center}
+		\end{figure}
+
 	}

### 2024-03-06 data/control_performance.m

@@ -1,5 +1,5 @@
 % clc, close all, clear 
-load('ref_tracking23.mat')
+load('ref_tracking27.mat')
 %% plots
 figure(11)
 hold on; grid minor; box on

### 2024-03-06 data/ploty.m

@@ -16,23 +16,29 @@ xlim([0 3000])
 
 %% Paper
 close all, clear
-tuned = 0; %default 0 - for boundary controllers
-load('ref_tracking31.mat') %1 -> Q_y = 1000
+tuned = 1; %default 0 - for boundary controllers
+load('ref_tracking23.mat') %1 -> Q_y = 1000
 from = 801;
 to = 6000;
 time = out.ScopeData(1:to-from+1,1);
 ref = out.ScopeData(from:to,4);
 input1 = out.ScopeData(from:to,3);
 output1 = out.ScopeData(from:to,2);
+Th1 = out.ScopeData6(from:to,3); %heating medium temperature
+W1 = out.ScopeData2(from:to,3); %electric power - spiral
 
-load('ref_tracking32.mat') %2 -> Q_y = 100
+load('ref_tracking24.mat') %2 -> Q_y = 100
 input2 = out.ScopeData(from:to,3);
 output2 = out.ScopeData(from:to,2);
+Th2 = out.ScopeData6(from:to,3); %heating medium temperature
+W2 = out.ScopeData2(from:to,3); %electric power - spiral
 
 if tuned == 1
-    load('ref_tracking33.mat') %2 -> Q_y = tuned
+    load('ref_tracking27.mat') %2 -> Q_y = tuned
     input3 = out.ScopeData(from:to,3);
     output3 = out.ScopeData(from:to,2);
+    Th3 = out.ScopeData6(from:to,3); %heating medium temperature
+    W3 = out.ScopeData2(from:to,3); %electric power - spiral
 end
 
 set(0,'defaulttextinterpreter','latex')
@@ -70,6 +76,40 @@ xlabel('time [s]')
 set(gca, 'TickLabelInterpreter','latex','FontSize', fs)
 xlabel('$t$ [s]')
 ylabel('$U$ [$\%$]','FontSize', fs)
+if tuned == 1
+    legend('$Q_\mathrm{y} = 1000$', '$Q_\mathrm{y} = 100$', '$Q_\mathrm{y}$ tuned', 'Interpreter','latex', 'FontSize', fs) %all
+else
+    legend('$Q_\mathrm{y} = 1000$', '$Q_\mathrm{y} = 100$', 'Interpreter','latex', 'FontSize', fs) %only boundaries
+end
+grid minor
+
+figure(5), hold on
[…]

### 2024-03-07 paper/JoPC/response_letter.tex
JO's comments worked in

@@
 Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
-The lower computational complexity makes the explicit MPC more suitable for practical industrial implementation.
-Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
-\change{The inability to tune the controller online can be a disadvantage due to varying operating conditions, when different setup of controller is beneficial.}
+			\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.} Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+\change{The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions, when different setup of controller is beneficial.}
 
@@
 		\begin{quote}
-			\change{If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
+			The applicability of model predictive control expanded with the parametric solution of the MPC optimization problem, known as explicit MPC~\cite{Bemporad_automatica}.
+As the MPC optimization problem is pre-solved offline, it does not need to be solved in the online phase, i.e., in real-time control.
+Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
+			\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
 		\end{quote}
@@
 	\answer{
-		The approach of self-tunable technique can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
+		The approach of the self-tunable technique can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
 It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
@@
 
-			\change{The approach of self-tunable technique was investigated on a SISO system, but can be extended also to multivariable systems by utilizing only single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
+			\change{The approach of self-tunable technique was successfully implemented on a SISO system, but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
 It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
@@
 In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning based on the two boundary MPC controllers.}
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
 		\end{quote}		
@@
 			value of the manipulated variables is interpolated between them.
-\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy should be considered, see e.g.~\cite{PR11}.
+\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
 Obviously, any robust MPC design method leads to conservative control actions as some portion of performance is scarified to compensate the impact of the disturbances.
@@
 		\begin{quote}
-			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller parameters}.
+			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller subject to the changed operating conditions.}
 		\end{quote}			
@@
 \change{Simultaneously, the utility generation for heating or cooling is energy-demanding.
-From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e.
-different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
+From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e., different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
 		\end{quote}
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $Q_\mathrm{y} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
-The matrix $R \change{\succ 0} \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squared value of control inputs.
+The penalty matrix $\change{Q_\mathrm{y} \succeq 0}, Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
+The matrix $\change{R \succ 0}, R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squared value of control inputs.
 			%
-			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \change{\succeq 0} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
+			The value of integrator is also penalized in the cost function with the penalty matrix $\change{Q_\mathrm{I} \succeq 0}, Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
 \change{All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
@@
 \change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any penalty matrix.
-The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
+The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup, respectively.
 }
@@
 The aim is to compensate the contributions of all the terms of the cost function.
-Nevertheless, this procedure is not the aim of this work and we do not want to go into detail of the general MPC tuning.
+Nevertheless, this procedure is not the aim of this work, and we choose not to delve into the details of the general MPC tuning.
 Therefore, we omitted the part mentioning judging the control performance subject to the specific system and reformulated the sentence as follows:
@@
 Also Reviewer~1 suggested to address this issue.
-We kindly invite the Reviewer~2 to revise the answer to the third comment of Reviewer 1, as it addresses the same topic.
-
-		Q: Staci to predsa len uviest do zaveru ako potencialne myslienky a riesenia MIMO problemov, ked tento reviewer to chce v problem setupe?
+Therefore, we kindly invite the Reviewer~2 to revise the answer to the third comment of Reviewer 1, as it addresses the same topic.
+We prefer to place the revised text into the Conclusions, where we comment on extending the self-tuning method towards the multivariable systems.
 	}
@@
 In general, followign the LQR design rules, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
-This process is similar to increasing the proportional gain in PID controller.
-On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, see e.g.~\cite{Maciejowski_MPC}.
-In order to make the notation of aggressive controller more clear for a reader, we added this description to the Section.
+This process is analogous to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
+In order to make the notation of aggressive controller more clear for a reader, we added this description to the section Introduction.
 
@@
 In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
-This process is similar to increasing the proportional gain in PID controller.
-On the contrary, higher penalization of the input variable leads to more sluggish control, see e.g.~\cite{Maciejowski_MPC}.
+This process is analogous to increasing the proportional gain in PID controller.
+On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
 The MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
@@
 Therefore, during the real-time control, the reference value can be selected only as a value from the feasible set determined offline, when constructing explicit MPC controller.
-If the MPC problem is precomputed also for non-reachable references, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to larger explicit solution of MPC, as the consequence of larger range of reference signal.
+Obviously, if the MPC problem is precomputed for a large range of reference values, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to larger explicit solution of MPC, as the consequence of larger range of reference signal.
 
 		Next, regarding the calculation of parameter $\rho$, the setup of reference value is strict and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input/state constraints satisfaction, etc.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.
 
-		As only the second part of the answer is crucial for the proposed tuning technique, we incorporated the comment on selected reference value into manuscript as follows:
+		To make clear the proposed tuning technique, we incorporated the comment on selected reference value into the manuscript as follows:
 
@@
 				\change{Note, the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input/state constraints satisfaction, etc.}
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.}
 			\end{quote}
@@
 	\answer{
-		We thank the Reviewer for the comment on the tuning parameter. We would like to divide our answer in three parts.
+		We thank the Reviewer for the comment on the properties of the tuning parameter. We would like to divide our answer in three parts.
 
@@
 			\end{equation}
-			where \change{the symbol $\lvert.\rvert$ in Eq.~\eqref{eq:d_max} and everywhere else in the paper denotes the element-wise absolute value}, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
+			where \change{the symbol $\lvert.\rvert$, hereafter, denotes the element-wise absolute value}, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
 		\end{quote}
@@
 It is necessary to ensure this condition in order to satisfy $0 \le \rho \le 1$.
-If the parameter $d_{\max}$ would not correspond to the maximum magnitude of the reference values, the tuning parameter $\rho > 1$ would lead to extrapolation of the control input, which could result in losing of all theoretical guarantees, i.e., constraints satisfaction etc.
-As the satisfaction of the condition $0 \le \rho \le 1$ was emphasized in the comment regarding the reachable reference values, we did not incorporate this part of answer into the manuscript to avoid repetitions in the text.
+If the parameter $d_{\max}$ would not correspond to the maximum magnitude of the reference values, the tuning parameter $\rho > 1$ would lead to extrapolation of the control input, which could result in losing of all guarantees, i.e., constraints satisfaction, etc.
+As the satisfaction of the condition $0 \le \rho \le 1$ was emphasized in the previous comment regarding the reachable reference values, we did not incorporate this part of answer into the manuscript to avoid repetitions in the text.
 
-		Last but not least, we address the question about the parameter $\rho$ closer to value 1 for large magnitudes of references. 			
+		Finally, we address the question about the parameter $\rho$ closer to value 1 for large magnitudes of references. 			
 		In the manuscript, it is suggested to increase the value of diagonal elements of the penalty matrix $Q_\mathrm{y}$ with increasing reference step change, i.e.:		
@@
 				\end{eqnarray*}
- 			holds. This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$. }
+ 			hold. This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$. }
 		\end{quote}
@@
 		To prevent confusion associated with the term ``feed'', we replaced the corresponding parts in manuscript with ``cold medium''.
-Moreover, in order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion:
+Moreover, in order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion.
 
@@
 				\caption{Scheme of Armfield PCT23.
-Heat exchanger (I), peristaltic pump for cold feed (II), peristaltic pump for heating medium (III), tank for cold feed (IV), heater for heating medium (V), temperature sensors ($\mathrm{T}$ -- controlled temperature, $\mathrm{T}_\mathrm{C}$ -- cold feed temperature, $\mathrm{T}_\mathrm{H}$ -- heating medium temperature), and electric power for maintaining the temperature of the heating medium (W).
+Heat exchanger (I), peristaltic pump for cold medium (II), peristaltic pump for heating medium (III), tank for cold medium (IV), heater for heating medium (V), temperature sensors ($\mathrm{T}$ -- controlled temperature, $\mathrm{T}_\mathrm{C}$ -- cold outlet cold medium temperature, $\mathrm{T}_\mathrm{H}$ -- heating medium temperature), and electric power for maintaining the temperature of the heating medium (W).
 }
@@
 		First, we would like to address the doubts related to the constant steady-state values of cold and heating medium temperatures.
-Regarding the temperature of the cold medium, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
-Nevertheless, the temperature of the cold medium was checked multiple times during experiment and was constant.
+Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
+Nevertheless, the temperature of the cold medium was manually checked multiple times during experiment and was constant.
 The advantage is that there is no other factor affecting the temperature of the cold medium, except the room temperature, which was constant.
@@
 		Regarding the temperature of the heating medium, we provide the corresponding trajectories of the temperature in Figure~\ref{fig:Th}.
-Note that the legend corresponds to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.
+Note that the legend corresponds to the specific setup of MPC, but the temperature of the heating medium was controlled with an auxiliary P controller with the same proportional gain in every control scenario.
 It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
@@
 Therefore, the same conditions for all control scenarios were fulfilled.
-We explain the different values of manipulated variable with the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+We explain the different values of manipulated variable with the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the cold medium.
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
@@
 \change{Also, the inlet temperatures of the cold and heating medium were checked in order to exclude the effect of a disturbance.
-Regarding the temperature of the cold medium, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
+Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
 Nevertheless, the temperature of the cold medium was checked multiple times during experiment and was constant.}
@@
 After approximately 100\,s, the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller, see Figure~(TODO), red.
-This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the cold medium.
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.

### 2024-03-07 paper/JoPC/response_letter.tex
grammarly

@@
 
-		We thank the Reviewer for pointing out unclear motivation for self-tunable control approach in section Introduciton. 
-		In order to clearly emphasize the need of a self-tunable technique, we revised the Introduction section in a following way:
+		We thank the Reviewer for pointing out the unclear motivation for the self-tunable control approach in the section Introduction. 
+		In order to clearly emphasize the need for a self-tunable technique, we revised the Introduction section in the following way:
 		\begin{quote}
@@
 			\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
-If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.} Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
-\change{The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions, when different setup of controller is beneficial.}
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for practical industrial implementation.} Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+\change{The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions when the different setups of the controllers are beneficial.}
 
@@
 \change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
-The use of different controller setups can be helpful in handling the nonlinear behavior of the plant.} The procedure of the self-tunable controller technique is presented.
+The use of different controller setups can help handle the plant's nonlinear behavior.} The procedure of the self-tunable controller technique is presented.
 The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
@@
 
-		We thank the Reviewer for an important comment on application range of the proposed control method. We reformulated the corresponding sentence to make the implementation limits clear:
+		We thank the Reviewer for an important comment on the application range of the proposed control method. We reformulated the corresponding sentence to make the implementation limits clear:
 		\begin{quote}
@@
 			\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
-If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for a practical industrial implementation.}
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for practical industrial implementation.}
 		\end{quote}
@@
 It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
-However, this is straightforward to implement only for decoupled systems.
+However, this is straightforward to be implemented only for decoupled systems.
 If there are strong interactions between the system states, the self-tunable technique is challenging to design.
-To give the reader a better view on the apllicability of the proposed approach, we added the following explanation to the Concusion of the manuscript:
+To give the reader a better view of the applicability of the proposed approach, we added the following explanation to the Concusion of the manuscript:
 
 		\begin{quote}
-			To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
+			To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
 The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
 
-			\change{The approach of self-tunable technique was successfully implemented on a SISO system, but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ for the interpolation of the values of every control input.
+			\change{The approach of the self-tunable technique was successfully implemented on a SISO system but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ to interpolate the values of every control input.
 It is suggested in Eq.~(8) that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
@@
 If there are strong interactions between the system states, the self-tunable technique is challenging to design.
-In such case, it is necessary to include expert knowledge about the system states interactions, and the resulting value of the tuning paramter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.}
+In such a case, it is necessary to include expert knowledge about the system state interactions, and the resulting value of the tuning parameter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.}
 		\end{quote}
@@
 Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
-Nevertheless, there are numerous practical situations, when using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+Nevertheless, there are numerous practical situations when using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved but with worse control performance, e.g., leading to high overshoots or settling times.
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated, among them also the requested value of $Q_\mathrm{y} = 500$.
@@
 	\answer{
-		In order to bring a concise presentation of the results, we removed the Figures 6 and 7.
+		In order to bring a concise presentation of the results, we removed Figures 6 and 7.
 		%We understand that the data from Figures 6 and 7 are depicted also in Figures 10 and 11 and see the motivation to remove the Figures 6 and 7.
@@
 	\answer{		
-		We thank the Reviewer for this important comment on the reliable implementation in the industrial applications.
-We revisited the corresponding text in section Conclusion containing the comments on disturbances and incorporated also the answer on unmeasured disturbances.
-As the revised extended text includes ideas and comments reminding discussion more than conclusion, this part was transferred to the section Results and discussion, and now reads as follows:
+		We thank the Reviewer for this important comment on the reliability of the implementation in industrial applications.
+We revisited the corresponding text in the section Conclusion containing the comments on disturbances and also incorporated the answer on unmeasured disturbances.
+As the revised, extended text includes ideas and comments reminding discussion more than the conclusion, this part was transferred to the section Results and discussion, and now reads as follows:
 		\begin{quote}
-			Note, this strategy relies on a proper design of the two boundary controllers.
+			Note that this strategy relies on a proper design of the two boundary controllers.
 			In case a non-negligible disturbance occurs, both boundary controllers
-			should be able to solve a disturbance rejection problem, as the final
+			should be able to solve a disturbance rejection problem as the final
 			value of the manipulated variables is interpolated between them.
-\change{To address the impact of the disturbances directly in the construction of the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
-Obviously, any robust MPC design method leads to conservative control actions as some portion of performance is scarified to compensate the impact of the disturbances.
-Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then exactly the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
+\change{To address the impact of the disturbances directly in constructing the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
+Any robust MPC design method leads to conservative control actions as some portion of the performance is sacrificed to compensate for the impact of the disturbances.
+Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
 		\end{quote}	
@@
 	\answer{
-		We thank the Reviewer for this important comment. We utilized the Reviewer's suggested formulation in a following way:
+		We thank the Reviewer for this important comment. We utilized the Reviewer's suggested formulation in the following way:
 		\begin{quote}
@@
 	\answer{
-		We revisited the Introduction section in order to clearly define the asymmetric behavior at the place of its first occurrence.
+		We revisited the Introduction section to clearly define the asymmetric behavior at the place of its first occurrence.
 		\begin{quote}
@@
 	\answer{
-		We revisited the Section 2.1 in order to define the assumptions on the penalty matrices of the optimization problem. The corresponding part reads as:
+		We revisited Section 2.1 in order to define the assumptions on the penalty matrices of the optimization problem. The corresponding part reads as:
 		\begin{quote}
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $\change{Q_\mathrm{y} \succeq 0}, Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
-The matrix $\change{R \succ 0}, R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squared value of control inputs.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{y} \succeq 0}$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
+The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}, \change{R \succ 0}$ penalizes the squared value of control inputs.
 			%
-			The value of integrator is also penalized in the cost function with the penalty matrix $\change{Q_\mathrm{I} \succeq 0}, Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$.
+			The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{I} \succeq 0}$.
 \change{All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
@@
 	\answer{
-		To explain the assumptions on the penalty matrices and specify the tuned matrix, we revisited the text in the corresponding paragraph of the Section 2.2 in the following way:
+		To explain the assumptions on the penalty matrices and specify the tuned matrix, we revisited the text in the corresponding paragraph of Section 2.2 in the following way:
 		\begin{quote}
@@
 		We thank the Reviewer for the comment on systematic tuning.
-By systematic tuning we mean choosing one penalty matrix and observig the control results based on gradual increasing or decreasing of the diagonal elements of the penalty matrices.
+By systematic tuning, we mean choosing one penalty matrix and observing the control results based on the gradual increase or decrease of the diagonal elements of the penalty matrices.
 Then, the same procedure is performed for the rest of the penalty matrices.
 Regarding the initial setup of the penalty matrices, it is often based on balancing the orders of magnitude of the input and state variables.
-The aim is to compensate the contributions of all the terms of the cost function.
+The aim is to compensate the contributions of all the cost function terms.
 Nevertheless, this procedure is not the aim of this work, and we choose not to delve into the details of the general MPC tuning.
@@
 	\answer{
-		We thank for the comment on the application range of the proposed method.
-Also Reviewer~1 suggested to address this issue.
-Therefore, we kindly invite the Reviewer~2 to revise the answer to the third comment of Reviewer 1, as it addresses the same topic.
-We prefer to place the revised text into the Conclusions, where we comment on extending the self-tuning method towards the multivariable systems.
+		We appreciate the comment on the application range of the proposed method.
+Reviewer~1 also suggested addressing this issue.
+Therefore, we kindly invite Reviewer~2 to revise the answer to the third comment of Reviewer 1, as it addresses the same topic.
+We prefer to place the revised text into the Conclusions, where we comment on extending the self-tuning method to multivariable systems.
 	}
@@
 		The aggressiveness of the MPC controller is associated with the setup of penalty matrices, namely $Q_\mathrm{y}$, $Q_\mathrm{I}$, $R$, as it determines the aggressiveness of the final control input.
-In general, followign the LQR design rules, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{I}$) leads to more aggressive control actions.
-This process is analogous to increasing the proportional gain in PID controller.
+In general, following the LQR design rules, higher penalization of the controlled states or control error (higher values of the diagonal elements of matrices $Q_\mathrm{y}$ and $Q_\mathrm{}$) leads to more aggressive control actions.
+This process is analogous to increasing the proportional gain in the PID controller.
 On the contrary, higher penalization of the input variable through the penalty matrix $R$ leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-In order to make the notation of aggressive controller more clear for a reader, we added this description to the section Introduction.
+To make the notation of the aggressive controller clearer for a reader, we added this description to the Introduction section.
 
@@
 In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
-This process is analogous to increasing the proportional gain in PID controller.
+This process is analogous to increasing the proportional gain in the PID controller.
 On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
@@
 	\answer{
-		We would like to divide the answer in two parts as the reference value is present in MPC optimization problem in Eq.~(1) and also in the calculation process of the tuning parameter $\rho$ in Eq.~(7) and Eq.~(9).
+		We would like to divide the answer into two parts as the reference value is present in the MPC optimization problem in Eq.~(1) and also in the calculation process of the tuning parameter $\rho$ in Eq.~(7) and Eq.~(9).
 
-		First, regarding the MPC optimization problem, the reference signal is a parameter which is usually constrained such that it covers the operating range of the corresponding control application.
-Therefore, during the real-time control, the reference value can be selected only as a value from the feasible set determined offline, when constructing explicit MPC controller.
-Obviously, if the MPC problem is precomputed for a large range of reference values, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to larger explicit solution of MPC, as the consequence of larger range of reference signal.
+		First, regarding the MPC optimization problem, the reference signal is a parameter usually constrained such that it covers the operating range of the corresponding control application.
+Therefore, during the real-time control, the reference value can be selected only as a value from the feasible set determined offline when constructing an explicit MPC controller.
+Obviously, if the MPC problem is precomputed for a large range of reference values, e.g., because it is not clear a priori which reference values will be set during control, this would ``only'' lead to the larger explicit solution of MPC, as the consequence of a larger range of reference signal.
 
-		Next, regarding the calculation of parameter $\rho$, the setup of reference value is strict and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.
+		Next, regarding the calculation of parameter $\rho$, the setup of the reference value is strict, and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.
 
@@
 					\label{eq:rho_self_tunable}
-					\rho = \frac{\vert y_{\mathrm{ref}(k)} \vert}{d_{\max}}.
+					\rho (k) = \frac{\vert y_{\mathrm{ref}}(k) \vert}{d_{\max}}.
 				\end{equation}
@@
 
-				\change{Note, the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.}
+				\change{Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.}
 			\end{quote}
@@
 	\answer{
-		We thank the Reviewer for the comment on the properties of the tuning parameter. We would like to divide our answer in three parts.
+		We thank the Reviewer for the comment on the properties of the tuning parameter. We would like to divide our answer into three parts.
 
@@
 		\begin{quote}
-			Another suggestion is to fit the maximal deviation $d_{\max}$ based on the constraints on system outputs: 
+			Another suggestion is to set the maximal deviation $d_{\max}$ based on the constraints on system outputs: 
 			\begin{equation} \tag{6}
@@
 		Regarding the conservativeness of the parameter $d_{\max}$, we confirm that it is requested for this parameter to be equal to the maximum magnitude of the reference values.
-It is necessary to ensure this condition in order to satisfy $0 \le \rho \le 1$.
-If the parameter $d_{\max}$ would not correspond to the maximum magnitude of the reference values, the tuning parameter $\rho > 1$ would lead to extrapolation of the control input, which could result in losing of all guarantees, i.e., constraints satisfaction, etc.
-As the satisfaction of the condition $0 \le \rho \le 1$ was emphasized in the previous comment regarding the reachable reference values, we did not incorporate this part of answer into the manuscript to avoid repetitions in the text.
+It is necessary to ensure this condition to satisfy $0 \le \rho \le 1$.
+If the parameter $d_{\max}$ does not correspond to the maximum magnitude of the reference values, the tuning parameter $\rho > 1$ will lead to extrapolation of the control input, which could result in losing of all guarantees, i.e., constraints satisfaction, etc.
+As the satisfaction of the condition $0 \le \rho \le 1$ was emphasized in the previous comment regarding the reachable reference values, we did not incorporate this part of the answer into the manuscript to avoid repetitions in the text.
 
@@
 		The aim is to obtain a controller with higher penalization of the control error, leading to more ``aggressive'' or ``active'' control inputs.
-		If opposite nature of controller is requested, it is possible to adapt the tuning such that 
+		If the opposite nature of the controller is requested, it is possible to adapt the tuning such that 
 		\begin{eqnarray*}
@@
 		holds.
-This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$.
-To give the reader a better insight into the context of relation between parameter $\rho$ and the penalty matrix, we added this answer into Section 3.1 in the following way:
+This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.
+To give the reader a better insight into the context of the relation between parameter $\rho$ and the penalty matrix, we added this answer into Section 3.1 in the following way:
 
@@
  			\change{In Eq.~(9), it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
-Note, in this work the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with upper boundary controller, see Eq.~(4).
-If opposite logic of controller tuning is requested, it is possible to adapt the tuning such that
+Note, in this work, the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with the upper boundary controller, see Eq.~(4).
+If the opposite logic of controller tuning is requested, it is possible to adapt the tuning such that
 				\begin{eqnarray*}
@@
 				\end{eqnarray*}
- 			hold. This change leads to adding more weight on the lower boundary controller with the increasing value of tuning parameter $\rho$. }
+ 			hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.}
 		\end{quote}
@@
 		\begin{quote}
-			Note, the relations in Eq.~(7) and Eq.~(8) operate with the absolute value of the reference.
-\change{It is not taken into account, whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether holds the inequality: $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ or $\Delta_\mathrm{ref}(k) < 0$.
-As many plants have nonlinear behavior with asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.}
+			Note that the relations in Eq.~(7) and Eq.~(8) operate with the absolute value of the reference.
+\change{It is not taken into account whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether the inequality $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ holds or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear behavior with an asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.}
 		\end{quote}
@@
 	\answer{
-		The parameter $\gamma$ depends on the value of $\rho$, which is also a scalar. From this it follows, that the domain of $\gamma$ is $\mathbb{R}$.
+		The parameter $\gamma$ depends on the value of $\rho$, which is also a scalar. From this, it follows that the domain of $\gamma$ is $\mathbb{R}$.
 	}
@@
 	\answer{
-		We thank the Reviewer for this attentive comment. We corrected the order of Figures.
+		We thank the Reviewer for this attentive comment. We corrected the order of the Figures.
 	}
@@
 	\answer{
-		To prevent confusion associated with the term ``feed'', we replaced the corresponding parts in manuscript with ``cold medium''.
-Moreover, in order to improve the quality of the paper, we added the Figure~\ref{fig:HE_scheme} to the section Results and discussion.
+		To prevent confusion associated with the term ``feed'', we replaced the corresponding parts in the manuscript with ``cold medium''.
+Moreover, to improve the paper's quality, we added Figure~\ref{fig:HE_scheme} to the section Results and discussion.
+Note that the order of Figures in the manuscript is different.
 
@@
 		We thank the Reviewer for pointing out insufficient discussion on the selection of the tuning penalty matrix $Q_\mathrm{y}$.
-By significant effect we meant the direct association of the tuned penalty matrix with the tuning factor $\rho$, which is calculated based on the reference value.
+By significant effect, we meant the direct association of the tuned penalty matrix with the tuning factor $\rho$, which is calculated based on the reference value.
 We revisited the corresponding paragraph to describe the tuning procedure.
@@
 		We thank the Reviewer for the very insightful comment on the experiment setup. 
-		First, we would like to address the doubts related to the constant steady-state values of cold and heating medium temperatures.
+		First, we would like to address the doubts about the constant steady-state values of cold and heating medium temperatures.
 Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
-Nevertheless, the temperature of the cold medium was manually checked multiple times during experiment and was constant.
-The advantage is that there is no other factor affecting the temperature of the cold medium, except the room temperature, which was constant.
+Nevertheless, the temperature of the cold medium was manually checked multiple times during the experiment and was constant.
+The advantage is that no other factor affects the temperature of the cold medium except the room temperature, which was constant.
 We added the information about the inlet temperature of the cold medium into the manuscript:
@@
 		Regarding the temperature of the heating medium, we provide the corresponding trajectories of the temperature in Figure~\ref{fig:Th}.
+We kindly remind the Reviewer that the order of the Figures in the manuscript is different.
 Note that the legend corresponds to the specific setup of MPC, but the temperature of the heating medium was controlled with an auxiliary P controller with the same proportional gain in every control scenario.
@@
 The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
-As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of heating medium led to slight declining of the heating medium temperature.
+As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of the heating medium led to a slight decline in the heating medium temperature.
 After approximately 100 seconds, the heating medium warmed up to the reference value, i.e., $T_{\mathrm{H, ref}} = 70^{\circ}$\,C and remained constant within the accuracy of the temperature sensor.
-It can be seen, that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
-Therefore, the same conditions for all control scenarios were fulfilled.
-We explain the different values of manipulated variable with the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the cold medium.
+It can be seen that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
+Therefore, the same conditions were fulfilled for all control scenarios.
+We explain the different values of the manipulated variable with the heat accumulated inside the heat exchanger plates, and therefore, less heating medium was necessary to heat the cold medium.
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
-When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
+When working in a higher temperature range, the gain of the heat transfer process decreases, and the sensitivity to changes in the heating medium flow is lower.
 Therefore, even different flow rates of the heating medium lead to the same temperature at the outlet.
@@
 		\begin{quote}
-			An interesting phenomenon can be observed during tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
+			An interesting phenomenon can be observed while tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
 Although the steady-state values of temperature have the same value, the values of the manipulated variable are different.
 To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
-\change{Also, the inlet temperatures of the cold and heating medium were checked in order to exclude the effect of a disturbance.
+\change{Also, the inlet temperatures of the cold and heating medium were checked to exclude the effect of a disturbance.
 Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
-Nevertheless, the temperature of the cold medium was checked multiple times during experiment and was constant.}
+Nevertheless, the temperature of the cold medium was manually checked multiple times during the experiment and was constant.}
 
-			\change{Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th} and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
+			\change{Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th}, and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
 Note that the legends correspond to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.}
@@
 The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
-As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of heating medium led to slight declining of the heating medium temperature.
+As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of the heating medium led to a slight decline in the heating medium temperature.
 After approximately 100 seconds, the heating medium warmed up to the reference value, i.e., $T_{\mathrm{H, ref}} = 70^{\circ}$\,C and remained constant within the accuracy of the temperature sensor.
-It can be seen, that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
-Therefore, the same conditions for all control scenarios were fulfilled.}
+It can be seen that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
+Therefore, the same conditions were fulfilled for all control scenarios.}
 
-			\change{The reason of this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~(TODO), blue.
-After approximately 100\,s, the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller, see Figure~(TODO), red.
-This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the cold medium.
+			\change{The reason for this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~(10), blue.
+After approximately 100\,s, the value of the manipulated variable dropped and settled at a value lower than the value associated with the lower boundary controller, see Figure~(10), red.
+This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore, less heating medium was necessary to heat the cold medium.
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
-When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
-Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
+When working in a higher temperature range, the gain of the heat transfer process decreases, and the sensitivity to changes in the heating medium flow is lower.
+Therefore, even different flow rates of the heating medium lead to the same temperature at the outlet.
 		\end{quote}
@@
 				\includegraphics[width=0.7\textwidth]{images/Th}
-				\caption{The trajectory of heating medium temperature control (P controller).}
+				\caption{Auxiliary P controller: The trajectory of heating medium temperature control }
 				\label{fig:Th}
@@
 				\includegraphics[width=0.7\textwidth]{images/W}
-				\caption{The trajectory of electric power controlling the heating medium temperature (P controller).}
+				\caption{Auxiliary P controller: The trajectory of electric power controlling the heating medium temperature.}
 				\label{fig:W}

### 2024-03-07 paper/JoPC/main_1st_round.tex
grammarly

--- 2023-07-25 paper/JoPC/main.tex
@@
 Analogous to the reference trajectory preview concept of MPC design, this value can be determined based on the general knowledge of the expected future reference values.
-Another suggestion is to fit the maximal deviation $d_{\max}$ based on the constraints on system outputs:
+Another suggestion is to set the maximal deviation $d_{\max}$ based on the constraints on system outputs:
 	\begin{eqnarray}
@@
 
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/HE}
+		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: feed pump\,(1), heating medium pump\,(2), feed tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
+		\label{fig:HE}
+	\end{center}
+\end{figure}
+
 The system was identified by experimental identification.
@@
 The corresponding polytopic partitions can be seen in Figure~\ref{fig:partition_U} for the upper boundary controller and Figure~\ref{fig:partition_L} for the lower boundary controller.
-To store the parametric solution associated with the upper boundary explicit MPC, 17.49\,MB of memory space is required.
-Storing the lower boundary explicit MPC, one needs 4.33\,MB of memory space.
 
@@
 Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{images/HE}
-		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: feed pump\,(1), heating medium pump\,(2), feed tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
-		\label{fig:HE}
-	\end{center}
-\end{figure}
 

### 2024-03-07 paper/JoPC/response_letter.tex
almost final

@@
 		\begin{quote}
-			Note that this strategy relies on a proper design of the two boundary controllers.
+			\change{Note that this strategy relies on a proper design of the two boundary controllers.
 			In case a non-negligible disturbance occurs, both boundary controllers
@@
 			value of the manipulated variables is interpolated between them.
-\change{To address the impact of the disturbances directly in constructing the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
+To address the impact of the disturbances directly in constructing the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
 Any robust MPC design method leads to conservative control actions as some portion of the performance is sacrificed to compensate for the impact of the disturbances.
@@
 		\begin{quote}
-			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller subject to the changed operating conditions.}
+			This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller subject to the changed working conditions.}
 		\end{quote}			
@@
 			The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-The procedure of the self-tunable controller technique is presented.
-The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+\change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
+The use of different controller setups can help handle the plant's nonlinear behavior.
+The paper~\cite{self_tunable} presents a procedure of the self-tunable controller technique.} The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
 \change{In the context of MPC, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
@@
 On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-The MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
+In~\cite{self_tunable}, the MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
 		\end{quote} 
@@
 The heat exchange is performed between the cold medium (water) and the hot medium (water).
+The heat exchange is performed between the \change{cold medium} (water) and the hot medium (water).
 \change{The cold medium as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
 The flow rate of the cold medium is constant, while the aim of control is to track the reference value of the outlet cold medium temperature.
+Therefore, the controlled variable is the \change{cold medium} temperature $T$ at the outlet of the heat exchanger.
 The inlet cold medium temperature was constant during the whole control, i.e., $T_\mathrm{C} = 19^{\circ}$\,C.}
@@
 
-			\change{The reason for this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~(10), blue.
-After approximately 100\,s, the value of the manipulated variable dropped and settled at a value lower than the value associated with the lower boundary controller, see Figure~(10), red.
+			\change{The reason for this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~10, blue.
+After approximately 100\,s, the value of the manipulated variable dropped and settled at a value lower than the value associated with the lower boundary controller, see Figure~10, red.
 This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore, less heating medium was necessary to heat the cold medium.
@@
 				\includegraphics[width=0.7\textwidth]{images/Th}
-				\caption{Auxiliary P controller: The trajectory of heating medium temperature control }
+				\caption{Auxiliary P controller: The trajectory of heating medium temperature control.}
 				\label{fig:Th}

### 2024-03-07 paper/JoPC/main.tex
reviewer 2 - the second part
some other answers 2
last comment (steady state) and MIMO systems
almost final

@@
 \usepackage{amsmath}
+
+\newcommand{\change}[1]{\textcolor{red}{#1}}
 
@@
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
-This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to properly tune the controller.
-Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
+This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller subject to the changed working conditions.} Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
 The adjustment of the tuning parameter depends on the current reference value, which makes this strategy suitable for reference tracking problems.
@@
 	The heat exchangers in their numerous variants are integrated into many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
-Simultaneously, the heat exchangers are highly energy-demanding and resource-intensive plants.
-From the control viewpoint, the controller design taking into account the nonlinear and asymmetric behavior of the heat exchangers is a challenging task~\cite{RL20}.
+\change{Simultaneously, the utility generation for heating or cooling is energy-demanding.
+From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e., different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
 
@@
 Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
-The lower computational complexity makes the explicit MPC more suitable for practical industrial implementation.
-Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+	\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for practical industrial implementation.} Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+\change{The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions when the different setups of the controllers are beneficial.}
 
@@
 	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-The procedure of the self-tunable controller technique is presented.
-The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-Tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
+\change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
+The use of different controller setups can help handle the plant's nonlinear behavior.
+The paper~\cite{self_tunable} presents a procedure of the self-tunable controller technique.} The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+\change{In the context of MPC, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
+In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
+This process is analogous to increasing the proportional gain in the PID controller.
+On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
+In~\cite{self_tunable}, the MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
 
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$ penalizes the squared control error, i.e., the deviation between the output and output reference value $y_\mathrm{ref}$.
-The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}$ penalizes the squarred value of control inputs.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{y} \succeq 0}$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
+The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}, \change{R \succ 0}$ penalizes the squared value of control inputs.
 	%
-	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}$. 
-	%
+	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{I} \succeq 0}$.
+\change{All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
 	The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically pre-computed.
@@
 These control actions result from evaluating two boundary explicit MPCs.
-The boundary explicit controllers have the same structure and setup, except for one of the penalty matrices -- the tuned one.
-The boundary penalty matrices are diagonal square matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup respectively.
+The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
+\change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any penalty matrix.
+The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup, respectively.
+}
 
@@
 From the implementation point of view, it is preferred to tune just a single penalty matrix, i.e., to store only two controllers corresponding to the boundary values of the selected penalty matrix.
-To determine which penalty matrix in Eq.~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance subject to the specific system and systematically tune all of the penalty matrices.
+To determine which penalty matrix in Eq.~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance \change{by systematic tuning of all the penalty matrices.
+Systematic tuning involves selecting a specific penalty matrix and observing the control results by gradually increasing or decreasing the diagonal elements of the matrix.
+This process is then repeated for the remaining penalty matrices in a similar manner.}
 
@@
 	\end{eqnarray}	
-	where $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
+	where \change{the symbol $\lvert.\rvert$, hereafter, denotes the element-wise absolute value}, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
 Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
+	\change{ 
 	\begin{eqnarray}
 		\label{eq:rho_self_tunable}
-		\rho = \frac{\vert y_{\mathrm{ref}(k)} \vert}{d_{\max}}.
-	\end{eqnarray}
-
+		\rho (k) = \frac{\vert y_{\mathrm{ref}}(k) \vert}{d_{\max}}.
+	\end{eqnarray}
+	}
 	Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
 As a consequence, the parameter $\rho$ represents a way how to normalize the deviation from the steady-state value and is exploited to scale the control action or, implicitly, to tune the aggressiveness of the controller.
+
+	\change{Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.}
 
@@
 
-	Note, the relations in Eq.~\eqref{eq:rho_self_tunable} and Eq.~\eqref{eq:rho_max} operate with the absolute value of the reference.
-It is not taken into account, whether the reference change was positive or negative with respect to the system steady-state value placed in the origin, i.e., whether it changed upwards or downwards.
-As many plants have asymmetric behavior, the positivity or negativity of the reference change could be considered in the controller tuning to improve the control performance.
+	Note that the relations in Eq.~\eqref{eq:rho_self_tunable} and Eq.~\eqref{eq:rho_max} operate with the absolute value of the reference.
+\change{It is not taken into account whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether the inequality $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ holds or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear behavior with an asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.}
 
@@
 	Note, only the absolute value of $\Delta_{\mathrm{ref}}$ and $\Delta_{\max}$ are considered in this procedure to ensure $\rho \ge 0$.
+
+	In Eq.~\eqref{eq:rho_delta_ref}, it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
+Note, in this work, the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with the upper boundary controller, see Eq.~\eqref{eq:tunable_matrices}.
+If the opposite logic of controller tuning is requested, it is possible to adapt the tuning such that
+	\begin{eqnarray}
+		\label{eq:tunable_R_2}
+		&~& R(k) = \rho(k) \, R_\mathrm{L} + (1-\rho(k)) \, R_\mathrm{U}, \\
+		\label{eq:tunable_Qx_2}
+		&~& Q_\mathrm{I}(k) = \rho(k) \, Q_\mathrm{I,L} + (1-\rho(k)) \, Q_\mathrm{I,U}, \\
+		\label{eq:tunable_Qy_2}
+		&~& Q_\mathrm{y}(k) = \rho(k) \, Q_\mathrm{y,L} + (1-\rho(k)) \, Q_\mathrm{y,U},
+	\end{eqnarray}
+	hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.
 
@@
 The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
-The heat exchange is performed between the cold feed (water) and the hot medium (water).
-The cold feed as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
-The flow rate of the feed is constant, while the aim of control is to track the reference value of the feed temperature.
-Therefore, the controlled variable is the feed temperature $T$ at the outlet of the heat exchanger.
-The temperature of the heated feed in the outlet stream was measured by the type K thermocouple.
+The heat exchange is performed between the \change{cold medium} (water) and the hot medium (water).
+\change{The cold medium as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
+The flow rate of the cold medium is constant, while the aim of control is to track the reference value of the outlet cold medium temperature.
+Therefore, the controlled variable is the \change{cold medium} temperature $T$ at the outlet of the heat exchanger.
+The inlet cold medium temperature was constant during the whole control, i.e., $T_\mathrm{C} = 19^{\circ}$\,C.} The temperature of the heated \change{cold medium} in the outlet stream was measured by the type K thermocouple.
 The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium.
@@
 The corresponding illustrative scheme of the implemented closed-loop control setup is in Figure~\ref{fig:CL}, where the ``Self-tuning'' block substitutes the more detailed scheme of the tuning procedure in Figure~\ref{fig:tuning}.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/HE}
+		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: \change{cold medium} pump\,(1), heating medium pump\,(2), \change{cold medium} tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
+		\label{fig:HE}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.8\textwidth]{images/HE_scheme}
+		\caption{Scheme of Armfield PCT23.
+Heat exchanger (I), peristaltic pump for cold medium (II), peristaltic pump for heating medium (III), tank for cold medium (IV), heater for heating medium (V), temperature sensors ($\mathrm{T}$ -- controlled temperature, $\mathrm{T}_\mathrm{C}$ -- cold outlet cold medium temperature, $\mathrm{T}_\mathrm{H}$ -- heating medium temperature), and electric power for maintaining the temperature of the heating medium (W).
+}
+		\label{fig:HE_scheme}
+	\end{center}
+\end{figure}
 
@@
 where the variable $u$ represents the control inputs in the deviation form.
-The values of feed temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35\,$^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\,\%.
+The values of \change{the heated cold medium} temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35\,$^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\,\%.
 Therefore, the physical constraints on the manipulated variable are actually
@@
 
-The penalty matrices of the problem in Eq.~\eqref{eq:mpc_problem} were systematically tuned and the corresponding control was implemented on the laboratory heat exchanger for each of the considered explicit MPC setups.
-First, the aim of tuning was to determine, which penalty matrix is the most suitable for real-time tuning.
-Based on the set of experimentally collected data, the most significant effect on the control trajectories had tuning the penalty matrix $Q_\mathrm{y}$, while still preserving a satisfactory control performance, i.e., without steady-state control error and significant oscillations around the reference value.
-Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned as $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
+\change{The penalty matrices of the problem in Eq.~\eqref{eq:mpc_problem} were systematically tuned, and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
+First, the tuning procedure aimed to determine which penalty matrix is the most suitable for real-time tuning.
+The most relevant was the penalty matrix $Q_\mathrm{y}$ as the tuning is directly associated with a reference value, which takes place in the calculation of the tuning factor $\rho$.
+Moreover, the tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance.} Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
 The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{I}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
@@
 
-The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV_boundaries} for the controlled variable, and in Figure~\ref{fig:MV_boundaries} for the control inputs.
+The control profiles generated for both considered boundary control setups are compared in Figure~\ref{fig:CV} for the controlled variable, and in Figure~\ref{fig:MV} for the control inputs. 
 Note, the constructed explicit MPC controller computed control inputs to respect the constraints on the control inputs and they need not be truncated afterward.
 
-An interesting phenomenon can be observed during tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
+An interesting phenomenon can be observed while tracking the third reference value, i.e., $T_{\mathrm{ref}}$ = 50\,$^{\circ}\mathrm{C}$.
 Although the steady-state values of temperature have the same value, the values of the manipulated variable are different.
 To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
-The reason could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~\ref{fig:MV_boundaries}, blue.
-After approximately 100\,s, the value of manipulated variable dropped and settled at a value that was lower than the value associated with the lower boundary controller, see Figure~\ref{fig:MV_boundaries}, red.
-This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore less heating medium was necessary to heat the feed.
+\change{Also, the inlet temperatures of the cold and heating medium were checked to exclude the effect of a disturbance.
+Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
+Nevertheless, the temperature of the cold medium was manually checked multiple times during the experiment and was constant.}
+
+\change{Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th}, and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
+Note that the legends correspond to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.}
+
+\change{It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
+The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
+As the upper boundary MPC calculated ``aggressive'' control inputs, the increased flow rate of the heating medium led to a slight decline in the heating medium temperature.
+After approximately 100 seconds, the heating medium warmed up to the reference value, i.e., $T_{\mathrm{H, ref}} = 70^{\circ}$\,C and remained constant within the accuracy of the temperature sensor.
+It can be seen that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
+Therefore, the same conditions were fulfilled for all control scenarios.}
+
+\change{The reason for this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~\ref{fig:MV}, blue.
+After approximately 100\,s, the value of the manipulated variable dropped and settled at a value lower than the value associated with the lower boundary controller, see Figure~\ref{fig:MV}, red.
+This is a consequence of the heat accumulated inside the heat exchanger plates, and therefore, less heating medium was necessary to heat the cold medium.
 This phenomenon does not happen when tracking the reference value $T_{\mathrm{ref}}$ = 45\,$^{\circ}\mathrm{C}$, which originates in the nonlinear nature of the heat transfer process.
-When working in higher temperature range, the gain of the heat transfer process decreases and the sensitivity to changes in the heating medium flow is lower.
-Therefore even different flow rates of the heating medium lead to the same temperature at the outlet.
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{images/HE}
-		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: feed pump\,(1), heating medium pump\,(2), feed tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
-		\label{fig:HE}
-	\end{center}
-\end{figure}
+When working in a higher temperature range, the gain of the heat transfer process decreases, and the sensitivity to changes in the heating medium flow is lower.
+Therefore, even different flow rates of the heating medium lead to the same temperature at the outlet.
 
@@
 
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
-		\caption{Controlled variable trajectory for two boundary controllers. The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
-		\label{fig:CV_boundaries}
-	\end{center}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
-		\caption{Manipulated variable trajectory for two boundary controllers. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
-		\label{fig:MV_boundaries}
-	\end{center}
-\end{figure}
-
-The trajectories in Figure~\ref{fig:CV_boundaries} show the asymmetric nature of controlling the plant of plate heat exchanger mainly when observing the overshoots and undershoots.
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=0.8\textwidth]{images/CV_boundaries}
+%		\caption{Controlled variable trajectory for two boundary controllers.
+The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $T_{\mathrm{ref}}$.}
+%		\label{fig:CV_boundaries}
+%	\end{center}
+%\end{figure}
+
+%\begin{figure}
+%	\begin{center}
+%		\includegraphics[width=0.8\textwidth]{images/MV_boundaries}
+%		\caption{Manipulated variable trajectory for two boundary controllers. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
+%		\label{fig:MV_boundaries}
+%	\end{center}
+%\end{figure}
+
+The trajectories in Figure~\ref{fig:CV} show the asymmetric nature of controlling the plant of plate heat exchanger mainly when observing the overshoots and undershoots.
 When applying the control inputs associated with the lower boundary penalty matrix $Q_\mathrm{y, L}$ in Eq.~\eqref{eq:mpc_problem_cost}, significant undershoots are present when tracking the reference downwards, i.e., when the reference change is negative.
-On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards, see Figure~\ref{fig:CV_boundaries}, blue.
+On the contrary, when implementing the controller associated with $Q_\mathrm{y, U}$ in Eq.~\eqref{eq:mpc_problem_cost}, the undershoots are negligible, but significant overshoots can be seen when tracking the reference upwards, see Figure~\ref{fig:CV}, blue.
 
@@
 		\includegraphics[width=0.8\textwidth]{images/CV}
-		\caption{Controlled variable trajectory for two boundary controllers and the tuned one.
-The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value $^{\circ}\mathrm{C}$.}
+		\caption{Explicit MPC: Controlled variable trajectory for two boundary controllers and the tuned one.
+The solid lines represent the controlled temperature $T$ and the dashed line represents the reference value.}
 		\label{fig:CV}
@@
 		\includegraphics[width=0.8\textwidth]{images/MV}
-		\caption{Manipulated variable trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
+		\caption{Explicit MPC: Manipulated variable trajectory for two boundary controllers and the tuned one. The solid lines represent the voltage $U$ and the dashed lines represent the constraints.}
 		\label{fig:MV}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.7\textwidth]{images/Th}
+		\caption{Auxiliary P controller: The trajectory of heating medium temperature control.}
+		\label{fig:Th}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.7\textwidth]{images/W}
+		\caption{Auxiliary P controller: The trajectory of electric power controlling the heating medium temperature.}
+		\label{fig:W}
 	\end{center}
@@
 	In general, utilizing the proposed controller with a scalable aggressiveness according to the operating conditions leads to higher accuracy (lower SSE), lower value of the overshoots (reduced $\sigma_{\mathrm{max}}$), and faster achieving the reference value (decreased $t_{\epsilon}$).
-%, while the control performance does not suffer in the terms of energy consumption.
-
-	%	Together with the reduced overshoots and settling times, the achieved improvements in the control performance enable non-negligible energy savings when the precision and the operating time ensure the product with the required properties.
+
+	\change{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
+
+	\change{Note that this strategy relies on a proper design of the two boundary controllers.
+	In case a non-negligible disturbance occurs, both boundary controllers
+	should be able to solve a disturbance rejection problem as the final
+	value of the manipulated variables is interpolated between them.
+To address the impact of the disturbances directly in constructing the MPC controller design, a robust MPC strategy should be considered, e.g., see~\cite{PR11}.
+Any robust MPC design method leads to conservative control actions as some portion of the performance is sacrificed to compensate for the impact of the disturbances.
+Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
 
@@
 On the contrary, when the reference changed downwards, the control input was tuned to approach the control input from the boundary controller with the upper bound on the penalty matrix.
-To investigate the control results properly, the control performance was judged also quantitatively using a set of quality criteria.
+
+	To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
 The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
-%In addition, the energy consumption corresponding to each of the constructed controllers was also analyzed.
-The energy consumption of the self-tunable explicit MPC controller was in between the values of the two boundary non-tunable explicit MPC controllers.
-% the total energy consumption trades off the performance of the boundary controllers.
-% did not deteriorate in general.
-	%To conclude, with saving energy compared to one of the boundary controllers, the control performance was significantly improved.
-
-	Note, this strategy relies on a proper design of the two boundary controllers.
-In case a non-negligible disturbance occurs, both boundary controllers should be able to solve a disturbance rejection problem, as the final value of the manipulated variables is interpolated between them.
-The future work will focus on incorporating also the measurable disturbances into the self-tuning strategy.
+
+	\change{The approach of the self-tunable technique was successfully implemented on a SISO system but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ to interpolate the values of every control input.
+It is suggested in Eq.~\eqref{eq:rho_max} that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
+However, this is straightforward to implement only for decoupled systems.
+If there are strong interactions between the system states, the self-tunable technique is challenging to design.
+In such a case, it is necessary to include expert knowledge about the system state interactions, and the resulting value of the tuning parameter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.}
 	\section*{Acknowledgments}
@@
 			$T$ & temperature, $^{\circ}\mathrm{C}$ \\
+			\change{$T_{\mathrm{C}}$} & \change{cold medium temperature, $^{\circ}\mathrm{C}$} \\
+			\change{$T_{\mathrm{H}}$} & \change{heating medium temperature, $^{\circ}\mathrm{C}$} \\
+			\change{$T_{\mathrm{H, ref}}$} & \change{heating medium reference temperature, $^{\circ}\mathrm{C}$} \\
 			$T_{\mathrm{ref}}$ & reference temperature, $^{\circ}\mathrm{C}$ \\
@@
 			$\mathcal{U}$ & set of control inputs \\
+			\change{$W$} & \change{electric power, \%} \\			
 			$x$ & system states \\
@@
 			LTI  & linear time-invariant (system) \\
+			\change{LQR} & \change{linear-quadratic regulator} \\
 			MIMO & multiple-inputs and multiple-outputs (system) \\

### 2024-03-07 paper/JoPC/response_letter.tex
final 2nd round

@@
 \change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
-The use of different controller setups can help handle the plant's nonlinear behavior.} The procedure of the self-tunable controller technique is presented.
-The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+The use of different controller setups can help handle the plant's nonlinear behavior.
+The paper~\cite{self_tunable} presents a procedure of the self-tunable controller technique.} The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
 		\end{quote}
@@
 		Next, regarding the calculation of parameter $\rho$, the setup of the reference value is strict, and the reference value is reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.
 
@@
 				\change{Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.}
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.}
 			\end{quote}

### 2024-03-07 paper/JoPC/main_clean.tex
final 2nd round

--- 2024-03-07 paper/JoPC/main.tex
@@
 
-\newcommand{\change}[1]{\textcolor{red}{#1}}
+\newcommand{\change}[1]{\textcolor{black}{#1}}
 
@@
 	\change{Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input, state constraints satisfaction, etc.}
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.}
 
@@
 
-	In Eq.~\eqref{eq:rho_delta_ref}, it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
+	\change{In Eq.~\eqref{eq:rho_delta_ref}, it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
 Note, in this work, the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with the upper boundary controller, see Eq.~\eqref{eq:tunable_matrices}.
@@
 	\end{eqnarray}
-	hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.
+	hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.}
 
@@
 	The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
-The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
+\change{The schematic of the plant is depicted in Figure~\ref{fig:HE_scheme}.} The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
 The heat exchange is performed between the \change{cold medium} (water) and the hot medium (water).
@@
 			\change{$T_{\mathrm{H, ref}}$} & \change{heating medium reference temperature, $^{\circ}\mathrm{C}$} \\			
+		\end{tabular}
+		%	\end{center}
+
+	%% Page - break
+
+	%	\begin{center}
+		\begin{tabular}{ l l }
 			$T_{\mathrm{ref}}$ & reference temperature, $^{\circ}\mathrm{C}$ \\
@@
 			$u$ & control inputs \\
-		\end{tabular}
-		%	\end{center}
-
-	%% Page - break
-
-	%	\begin{center}
-		\begin{tabular}{ l l }
 			$u_{\mathrm{L}}$ & control inputs associated with the lower boundary controller\\

### 2024-04-16 paper/JoPC/response_letter_2nd_round.tex
review 2nd round

\documentclass[a4paper,10pt]{article}

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{a4wide}
\usepackage{multicol}
\usepackage[ansinew]{inputenc}
\usepackage{color}
\usepackage{url}
%\usepackage{floatflt}
\usepackage{multirow}
\usepackage{rotating, graphicx}

\newcommand{\opt}{^{\star}} % \opt
\newcommand{\tr}{\intercal} % transpose

% RESPONSE LETTER SYNTAX:
% =====================================================
\newcommand{\change}[1]{\textcolor{red}{#1}}

\newcommand{\comment}[1]{
	\begin{itemize}
		\item \textbf{Comment:}\\ \sf{#1}
	\end{itemize}
}

\newcommand{\answer}[1]{
	\begin{itemize}
		\item[] \textbf{Answer:}\\ #1
	\end{itemize}
}

\newcommand{\pointout}[1]{\textcolor{blue}{#1}}
\definecolor{YJ}{rgb}{0.0,0.5,0.0}

% =====================================================

\newcommand{\diam}[1]{\mathrm{diam}\left(#1\right)}

% \newcommand {\mm}[1]{\textcolor{blue}{#1}}

%opening
\title{Response to the review comments}
\author{}
\date{}

\sloppy
\begin{document}

	\maketitle

	We would like to thank the Reviewers for the constructive and thoughtful comments on our manuscript.
	We revised the document based on these comments and we provide point-to-point answers below.
	All changes relative to our initial submission are highlighted in \change{red}. TODO!

	\section*{Answer to Editor}
	We would like to thank the Editor for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality. We revised the paper based on the Reviewers' comments and incorporated the suggestions into our manuscript. We reformulated or added the corresponding statements to clarify the ideas.  TODO!

	\section*{Answer to Reviewer 1}
	\comment{ The authors have not addressed some of my comments in the previous submission thoroughly. I have the following follow-up comments:\\

	 The control performance with Qy = 500 is not quantified, and whether the performance benefits of the proposed method reported in Table 2 still remain is not clarified. Since Qy =500 would give a moderately tuned controller, it can provide a better overall performance than the two boundary controllers chosen with "extreme" tuning.
	}

	\answer{		
		We thank the Reviewer for pointing out...

	\begin{table}[h!]
		\begin{center}
			\caption{Control performance criteria.}
			\label{tab:control_performance}
			\begin{tabular}{c|c|c|c|c} 
				Reference step change & $Q_\mathrm{y}$ & SSE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
				\hline
				\multirow{4}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 714 & 33.5 & 16.5 \\
				& 100 & 867 & 16.7 & 12.5 \\ 
				& 500 & \textbf{583} & 17.6 & \textbf{7.5} \\
				& self-tuned & \textbf{678} & \textbf{15.2} & \textbf{9.5}  \\ 
				\hline
				\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1\,000 & 365 & 47.2 & \textbf{5} \\
				& 100 & 606 & 23.3 & 26.5  \\ 
				& 500 & \textbf{168} & \textbf{18.2} & \textbf{6.5} \\
				& self-tuned & \textbf{248} & \textbf{19.1} & 9.5  \\ 
				\hline
				\multirow{4}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 245 & \textbf{18.9} & \textbf{6.5}  \\
				& 100 & 398 & 79.6 & 31  \\ 
				& 500 & 211 & \textbf{22.3} & 8 \\
				& self-tuned & \textbf{186} & 24.6 & \textbf{6.5}  \\ 
				\hline
				\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1\,000 & 1\,024 & 18.4 & 22.5  \\
				& 100 & 1\,402 & 41.9 & 90  \\ 
				& 500 & 1064 & 25.6 & 67 \\
				& self-tuned & \textbf{967} & \textbf{16.5} & \textbf{18.5}   
			\end{tabular}
		\end{center}
	\end{table}

%		\begin{quote}
%			quote			
%		\end{quote}
	}

	\comment{
		For the metrics in Table 2, can the authors also report average values of the three metrics (relative improvements) obtained across the four set point changes considered? The average values would give an idea of the overall control performance. It seems that the overall performance for the settling time would be worse, and only little improvement in the overshoot metric?
	}

	\answer{
		\begin{table}[h!]
			\begin{center}
				\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
				\label{tab:improvement}
				\begin{tabular}{c|c|c|c|c} 
					Reference step change & Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
					\hline
					\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 121 &  9 & 74 \\
					& 100 & 28 &  10 & 32 \\  
					\hline
					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
					& 100 & 144 &  22 & 179 \\ 
					\hline
					\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
					& 100 & 114 & 224 & 377 \\
					\hline
					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
					& 100 & 45 &  154 & 386 \\
					\hline
					\multirow{2}{*}{Average for all steps} &  1000 & 23 & 64 & 12 \\
					& 100 & 83 &  102 & 243  
				\end{tabular}
			\end{center}
		\end{table}
	}

	\comment{
		All the three performance metric are related to the controlled temperature variable. Why did the authors not consider any metric related to the control input?	
	}

	\comment{
		In addition, the authors only summarize the best case performance improvements in the conclusions. This can be a bit misleading to readers since the proposed method also performs worse (significantly) in some parts of the simulations. So summarizing average values would be more appropriate to give a better picture of the overall performance.
	}

	\comment{
		Based on the responses to my previous comments, it appears that the applicability of the proposed self-tunable explicit MPC method is limited to "small-scale multivariable systems, with decoupled dynamics"? If so, please mention this clearly in the abstract.
	}

	\section*{Answer to Reviewer 2}
	\comment{My comments from the previous round have been fully address. I suggest publication.}

	\answer{		
		We thank the Reviewer again for the review.		
	}

	\bibliographystyle{plain}
	\bibliography{references}

\end{document}

### 2024-04-16 data/control_performance.m

@@ -1,5 +1,5 @@
 % clc, close all, clear 
-load('ref_tracking27.mat')
+load('ref_tracking25.mat')
 %% plots
 figure(11)
 hold on; grid minor; box on

### 2024-04-16 data/energy_evaluation.m

@@ -1,20 +1,30 @@
-clc, clear all
+clc, clear all, close all
 from = 801;
 to = 6000;
+figure(1), hold on
 
 load('ref_tracking23.mat') %1000
 P_per = out.ScopeData2(from:to+1,3);
 P = P_per/100*2; %kJ/s
 E_1000 = sum(P*Ts) %kJ
+plot(P_per)
 
 load('ref_tracking24.mat') %100
 P_per = out.ScopeData2(from:to+1,3);
 P = P_per/100*2; %kJ/s
 E_100 = sum(P*Ts) %kJ
+plot(P_per)
 
 load('ref_tracking27.mat') %tuned
 P_per = out.ScopeData2(from:to+1,3);
 P = P_per/100*2; %kJ/s
 E = sum(P*Ts) %kJ
+plot(P_per)
+
+% load('ref_tracking25.mat') %500
+% P_per = out.ScopeData2(from:to+1,3);
+% P = P_per/100*2; %kJ/s
+% E_500 = sum(P*Ts) %kJ
+% plot(P_per)
 
 

### 2024-04-17 paper/JoPC/response_letter_2nd_round.tex
review 2nd round - 1st question

@@
 
-	We would like to thank the Reviewers for the constructive and thoughtful comments on our manuscript.
-	We revised the document based on these comments and we provide point-to-point answers below.
-	All changes relative to our initial submission are highlighted in \change{red}. TODO!
+	We thank the Reviewers for all comments and suggestions.
+	The document was revised according to these comments and we provide point-to-point answers below.
+	All changes relative to our initial submission are highlighted in \change{red}.
 
 	\section*{Answer to Editor}
-	We would like to thank the Editor for summarizing substantial and high-quality review comments, which helped us to improve our manuscript's quality.
-We revised the paper based on the Reviewers' comments and incorporated the suggestions into our manuscript.
-We reformulated or added the corresponding statements to clarify the ideas.
-TODO!
+	The authors would like to thank the Editor for collecting the review comments. We revised the paper based on the Reviewers' comments, and incorporated the suggestions
+	into our manuscript.
 
@@
 	\answer{		
-		We thank the Reviewer for pointing out...
+		We revisited Table~\ref{tab:control_performance} to evaluate the control performance criteria.
+		The values highlighted in \textbf{bold} represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
+It can be seen, that the values are the best in 5 out of 12 performance criteria.
+On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions.
+
+		When excluding the boundary controllers and comparing only the self-tunable controller with the setup $Q_\mathrm{y} = 500$, the moderate controller outperforms the self-tunable MPC in half of the performance criteria.
+It happens mostly in tracking the reference value upwards.
+Nevertheless, when the reference changes downwards, the self-tuned controller becomes beneficial.
+Therefore, it supports choosing the tunable control technique.
+
+		\textcolor{blue}{Pozn.: Zvazme teraz dva scenare - bud toto o 500vke zapracujem nejako do clanku, alebo to odbavime nasledovne:}
+
+		To ensure a good readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+We prefer to emphasize the consideration of the self-tuning method based on the revised comment from the first round of review:
+
+		\begin{quote}
+			Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
+		\end{quote}
 
@@
 				& 500 & \textbf{583} & 17.6 & \textbf{7.5} \\
-				& self-tuned & \textbf{678} & \textbf{15.2} & \textbf{9.5}  \\ 
+				& self-tuned & 678 & 15.2 & 9.5  \\ 
 				\hline
-				\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1\,000 & 365 & 47.2 & \textbf{5} \\
+				\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1\,000 & 365 & 47.2 & 5 \\
 				& 100 & 606 & 23.3 & 26.5  \\ 
-				& 500 & \textbf{168} & \textbf{18.2} & \textbf{6.5} \\
-				& self-tuned & \textbf{248} & \textbf{19.1} & 9.5  \\ 
+				& 500 & \textbf{168} & \textbf{18.2} & 6.5 \\
+				& self-tuned & 248 & 19.1 & 9.5  \\ 
 				\hline
-				\multirow{4}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 245 & \textbf{18.9} & \textbf{6.5}  \\
+				\multirow{4}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 245 & 18.9 & 6.5  \\
 				& 100 & 398 & 79.6 & 31  \\ 
-				& 500 & 211 & \textbf{22.3} & 8 \\
-				& self-tuned & \textbf{186} & 24.6 & \textbf{6.5}  \\ 
+				& 500 & \textbf{211} & 22.3 & 8 \\
+				& self-tuned & 186 & 24.6 & 6.5  \\ 
 				\hline
@@
 				& 500 & 1064 & 25.6 & 67 \\
-				& self-tuned & \textbf{967} & \textbf{16.5} & \textbf{18.5}   
+				& self-tuned & 967 & 16.5 & 18.5  
 			\end{tabular}
@@
 
-%		\begin{quote}
-%			quote			
-%		\end{quote}
 	}
@@
 	\answer{
+		We would like to thank the Reviewer for the comment on the relative improvements.
+If the values in Table~2 were averaged, it is true that the average settling time would be worse, and the average relative improvement of the overshoot would be very low.
+However, considering the average of these values would be very strict because of the way how the relative improvements were calculated.
+
+		The values in Table~2 are computed subject to the second best setup for each reference step change individually.
+The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
+It means, that the base subject to which is every value calculated, changes.
+Therefore, averaging the values of the relative improvements would not be fair, as it would not reflect improvement subject to one controller with a constant setup.
+
+		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that it provides the relative improvements subject to each boundary controller individually, see Table~\ref{tab:improvement}.
+
 		\begin{table}[h!]
@@
 				\begin{tabular}{c|c|c|c|c} 
-					Reference step change & Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+					& Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 					\hline
-					\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 121 &  9 & 74 \\
-					& 100 & 28 &  10 & 32 \\  
+					\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
+					& 100 & 22 &  9 & 24 \\  
 					\hline
-					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
-					& 100 & 144 &  22 & 179 \\ 
+					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
+					& 100 & 59 &  18 & 64 \\ 
 					\hline
-					\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
-					& 100 & 114 & 224 & 377 \\
+					\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
+					& 100 & 53 & 69 & 79 \\
 					\hline
-					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
-					& 100 & 45 &  154 & 386 \\
+					\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
+					& 100 & 31 &  61 & 79 \\
 					\hline
-					\multirow{2}{*}{Average for all steps} &  1000 & 23 & 64 & 12 \\
-					& 100 & 83 &  102 & 243  
+					\multirow{2}{*}{Average across all steps} &  1000 & 17 & 24 & -7 \\
+					& 100 & 41 &  39 & 62  
 				\end{tabular}
@@
 	\answer{		
-		We thank the Reviewer again for the review.		
+		We thank the Reviewer for reviewing our revised manuscript.		
 	}

### 2024-04-17 paper/JoPC/response_letter_2nd_round.tex
review 2nd round - 2nd question
review 2nd round - 3rd question

@@
 		\end{table}
+
+			\begin{table}[h!]
+		\begin{center}
+			\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
+			\label{tab:improvement2}
+			\begin{tabular}{c|c|c|c|c} 
+				& Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+				\hline
+				\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
+				& 100 & 22 &  9 & 24 \\ 
+				& 500 & -16 & 13 & -27 \\
+				\hline
+				\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
+				& 100 & 59 &  18 & 64 \\ 
+				& 500 & -48 & -5 & -46 \\
+				\hline
+				\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
+				& 100 & 53 & 69 & 79 \\
+				& 500 & 12 & -10 & 19 \\
+				\hline
+				\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
+				& 100 & 31 &  61 & 79 \\
+				& 500 & 9 & 36 & 72 \\
+				\hline
+				\multirow{3}{*}{Average across all steps} &  1000 & 17 & 24 & -7 \\
+				& 100 & 41 &  39 & 62 \\ 
+				& 500 & -11 & 8 &  5
+			\end{tabular}
+		\end{center}
+	\end{table}
+
 	}
@@
 
+	\answer{
+		We thank the Reviewer for commenting on the control performance criteria related to the control input.
+Although we considered such an evaluation, we chose not to include the criteria for the following reasons.
+This kind of criteria usually reflects some costs or energy demands associated with the control.
+
+		The first kind of criterium related to the control input could be intuitively some (potentially weighted) ISU (integral-of-squared input) or, in a discrete-time manner, SSU (sum-of-squared input).
+These criteria correspond to the summing of the control input, i.e., voltage, to set the operating speed of the pump.
+The operating speed of the pump itself does not play any significant role in the costs of the control.
+Therefore, it could be converted to the amount of liquid transported to the heat exchanger during the whole control experiment.
+Nevertheless, the heating medium is dosed to the heat exchanger plant as a recycle, i.e., the same amount of heating medium is re-used during operation, which would represent fictitious performance criteria not related to the actual plant setup.
+
+		Another criterion related to the control input we considered was the energy consumed to pre-heat the heating medium in the heater.
+However, this is not directly associated with the MPC's control inputs.
+The consumed energy corresponds to the control involving the proportional controller, which sets the electric power.
+Therefore, we decided not to include such a criterion as well.
+	}
+
 	\comment{
@@
 So summarizing average values would be more appropriate to give a better picture of the overall performance.
+	}
+
+	\answer{
+		We thank the Reviewer for pointing out the misleading communication of the control results...
 	}

### 2024-04-17 paper/JoPC/response_letter_2nd_round.tex
review 2nd round - 5th question

@@
 	\answer{
-		We thank the Reviewer for pointing out the misleading communication of the control results...
+		We thank the Reviewer for pointing out the communication of the control performance improvements...
 	}
@@
 If so, please mention this clearly in the abstract.
+	}
+
+	\answer{
+		We incorporated the Reviewer's suggestion into the Abstract as follows:
+
+		\begin{quote}
+			The tunable approximated explicit model predictive control (MPC) comes
+			with the benefits of real-time tunability without the necessity of solving the optimization problem online.
+This paper provides a novel self-tunable control policy that does not require any intervention from the control engineer during operation in order to retune the controller subject to the changed working conditions.
+Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
+The adjustment of the tuning parameter depends on the current reference value, which makes this strategy suitable for reference tracking problems.
+Furthermore, a novel technique for scaling the tuning parameter is proposed.
+This extension exploits different ranges of the tuning parameter assigned to specified operating conditions.
+\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems or MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+The asymmetric behavior of the plant was compensated by tuning the controller’s aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
+The designed self-tunable controller improved control performance by decreasing sum-of-squared control error, maximal overshoots/undershoots, and settling time compared to the conventional control strategy based on a single (non-tunable) controller.
+		\end{quote}
+
+	TODO: Potom  vymazat vysvetlivky skratiek MIMO a SISO dalej v texte.
 	}
@@
 
-	\bibliographystyle{plain}
-	\bibliography{references}
+	%\bibliographystyle{plain}
+	%\bibliography{references}
 

### 2024-04-18 paper/JoPC/response_letter_2nd_round.tex
review 2nd round - 1st and 2nd question update

@@
 Therefore, it supports choosing the tunable control technique.
-
-		\textcolor{blue}{Pozn.: Zvazme teraz dva scenare - bud toto o 500vke zapracujem nejako do clanku, alebo to odbavime nasledovne:}
-
-		To ensure a good readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-We prefer to emphasize the consideration of the self-tuning method based on the revised comment from the first round of review:
-
-		\begin{quote}
-			Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
-Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
-When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
-		\end{quote}
+To support our statement, the average control performance for all controllers was also elaborated.
+As the average control performance was the topic of the Reviewer's second comment, it can be found in the answer to the following comment.
 
@@
 				\begin{tabular}{c|c|c|c|c} 
-				Reference step change & $Q_\mathrm{y}$ & SSE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
+					Reference change & $Q_\mathrm{y}$ & SSE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
 					\hline
@@
 
+		To ensure a good readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+We prefer to emphasize the consideration of the self-tuning method based on the revised comment from the first round of review:
+
+		\begin{quote}
+			Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
+When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
+		\end{quote}
+
 	}
@@
 If the values in Table~2 were averaged, it is true that the average settling time would be worse, and the average relative improvement of the overshoot would be very low.
-However, considering the average of these values would be very strict because of the way how the relative improvements were calculated.
+However, considering the average of these values would be ``unfair'' because of the way how the relative improvements were calculated.
 
@@
 
-		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that it provides the relative improvements subject to each boundary controller individually, see Table~\ref{tab:improvement}.
+		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that it provides the relative improvements subject to each boundary controller individually, see Table~\ref{tab:improvement500}.
+Note, for the purposes of this response letter, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
+
+		Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not map the overall improvement.
+For example, let us compare the 79\% improvement in the settling time of the MPC setup $Q_\mathrm{y} = 100$ during the third and fourth reference tracking.
+In the third reference step change, the relative improvement of 79\% corresponds to the settling time difference $31-6.5$\,s.
+In the fourth reference step change, the relative improvement of 79\% corresponds to the settling time difference $90-18.5$\,s.
+Although the values in Table~\ref{tab:improvement500} provide a better overview of how better or worse the self-tunable controller performed in the specific operating conditions, averaging the values across the reference changes would give a somewhat distorted idea.
+Therefore, some kind of ``normalization'' would lead to a better vision of the average control performance.
+Our idea is to first average the values of the control performance criteria for every controller setup across the reference changes, and then calculate the relative improvements from the averaged values, see Table~\ref{tab:average_improvement500}.
+The symbol $\bar{(.)}$ represents an average value of the corresponding criterion.
+
+		As we explained our idea of the average control performance, we would like to return to the topic of the first comment—whether the moderate controller performs better in the overall metric.
+Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.
+The Table~\ref{tab:average_improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was (not very significantly) worse, the rest of the criteria improved in average (the maximal overshoor improved by 11\% and the settling time improved by 102\%).
+Therefore, considering the tunable technique is beneficial.
+
+		\begin{table}[h!]
+			\begin{center}
+				\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
+				\label{tab:improvement500}
+				\begin{tabular}{c|c|c|c|c} 
+					Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+					\hline
+					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
+					& 100 & 22 &  9 & 24 \\ 
+					& 500 & $-16$ & 13 & $-27$ \\
+					\hline
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
+					& 100 & 59 &  18 & 64 \\ 
+					& 500 & $-48$ & $-5$ & $-46$ \\
+					\hline
+					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
+					& 100 & 53 & 69 & 79 \\
+					& 500 & 12 & $-10$ & 19 \\
+					\hline
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
+					& 100 & 31 &  61 & 79 \\
+					& 500 & 9 & 36 & 72 
+				\end{tabular}
+			\end{center}
+		\end{table}
+
+		\begin{table}[h!]
+			\begin{center}
+				\caption{Average control performance criteria.}
+				\label{tab:average_improvement500}
+				\begin{tabular}{c|c|c|c|c|c|c} 
+					$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
+					\hline
+					1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
+					100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
+					500 & 506.5 & $-3$ & 20.9 & 11 & 22.5 & 102 \\
+					self-tuned & 519.8 & - & 18.9 & - & 11 & - 			
+				\end{tabular}
+			\end{center}
+		\end{table}
+
+		As we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$, we prefer to include the original comparison subject to the boundary controllers as follows:
+
+		\begin{quote}
 
@@
 					\begin{tabular}{c|c|c|c|c} 
-					& Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+						Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 						\hline
@@
 						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
-					& 100 & 31 &  61 & 79 \\
-					\hline
-					\multirow{2}{*}{Average across all steps} &  1000 & 17 & 24 & -7 \\
-					& 100 & 41 &  39 & 62  
+						& 100 & 31 &  61 & 79 
 					\end{tabular}
@@
 		\begin{center}
-			\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
-			\label{tab:improvement2}
-			\begin{tabular}{c|c|c|c|c} 
-				& Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+			\caption{Average control performance criteria.}
+			\label{tab:average_improvement}
+			\begin{tabular}{c|c|c|c|c|c|c} 
+				$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
 				\hline
-				\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
-				& 100 & 22 &  9 & 24 \\ 
-				& 500 & -16 & 13 & -27 \\
-				\hline
-				\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
-				& 100 & 59 &  18 & 64 \\ 
-				& 500 & -48 & -5 & -46 \\
-				\hline
-				\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
-				& 100 & 53 & 69 & 79 \\
-				& 500 & 12 & -10 & 19 \\
-				\hline
-				\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
-				& 100 & 31 &  61 & 79 \\
-				& 500 & 9 & 36 & 72 \\
-				\hline
-				\multirow{3}{*}{Average across all steps} &  1000 & 17 & 24 & -7 \\
-				& 100 & 41 &  39 & 62 \\ 
-				& 500 & -11 & 8 &  5
+				1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
+				100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
+				self-tuned & 519.8 & - & 18.9 & - & 11 & - 		
 			\end{tabular}
@@
 	\end{table}
+
+		\end{quote}
+
+%	\begin{table}[h!]
+%		\begin{center}
+%			\caption{Average relative improvement of the control performance using the self-tunable explicit MPC controller.}
+%			\label{tab:improvement4}
+%			\begin{tabular}{c|c|c|c} 
+%				Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+%				\hline
+%				1000 & 13 &  57 & 15 \\
+%				100 & 57 &  114 & 264 \\ 
+%				500 & $-3$ & 11 & 102 			
+%			\end{tabular}
+%		\end{center}
+%	\end{table}
 
@@
 
-		The first kind of criterium related to the control input could be intuitively some (potentially weighted) ISU (integral-of-squared input) or, in a discrete-time manner, SSU (sum-of-squared input).
+		The first kind of criterium related to the control input could be intuitively some (potentially weighted) ISI (integral-of-squared input) or, in a discrete-time manner, SSI (sum-of-squared input).
 These criteria correspond to the summing of the control input, i.e., voltage, to set the operating speed of the pump.
@@
 Therefore, it could be converted to the amount of liquid transported to the heat exchanger during the whole control experiment.
-Nevertheless, the heating medium is dosed to the heat exchanger plant as a recycle, i.e., the same amount of heating medium is re-used during operation, which would represent fictitious performance criteria not related to the actual plant setup.
+Nevertheless, the heating medium is dosed to the heat exchanger plant as a recycle, i.e., the same amount of heating medium is re-used during operation, which would represent fictitious performance criteria not related to the actual plant setup, see Figure 3 in the manuscript.
 
@@
 The consumed energy corresponds to the control involving the proportional controller, which sets the electric power.
-Therefore, we decided not to include such a criterion as well.
+Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.	To conclude, we decided not to include such a criterion as well.
+
 	}

### 2024-04-19 paper/JoPC/response_letter_2nd_round.tex
review 2nd round - small reformulation

@@
 
-		Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not map the overall improvement.
-For example, let us compare the 79\% improvement in the settling time of the MPC setup $Q_\mathrm{y} = 100$ during the third and fourth reference tracking.
-In the third reference step change, the relative improvement of 79\% corresponds to the settling time difference $31-6.5$\,s.
-In the fourth reference step change, the relative improvement of 79\% corresponds to the settling time difference $90-18.5$\,s.
-Although the values in Table~\ref{tab:improvement500} provide a better overview of how better or worse the self-tunable controller performed in the specific operating conditions, averaging the values across the reference changes would give a somewhat distorted idea.
+		Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not properly map the overall improvement.
+For example, let us compare the 79\% improvement in the settling time subject to the MPC setup $Q_\mathrm{y} = 100$ during the third and fourth reference tracking.
+In the third reference step change, the relative improvement of 79\% corresponds to the settling time difference $31 - 6.5 = 24.5$\,s.
+In the fourth reference step change, the relative improvement of 79\% corresponds to the settling time difference $90 - 18.5 = 71.5$\,s.
+Although the values in Table~\ref{tab:improvement500} provide an extended overview of how better or worse the self-tunable controller performed in the specific operating conditions, averaging the values across the reference changes would give a somewhat distorted idea.
 Therefore, some kind of ``normalization'' would lead to a better vision of the average control performance.
@@
 
-		As we explained our idea of the average control performance, we would like to return to the topic of the first comment—whether the moderate controller performs better in the overall metric.
+		Based on this explanation of our idea of the average control performance, at this place we would like to return to the topic of the first comment—whether the moderate controller performs better in the overall metric.
 Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.

### 2024-04-19 paper/JoPC/response_letter_2nd_round.tex
minor

@@
 	\answer{
-		We thank the Reviewer for pointing out the communication of the control performance improvements...
+		We thank the Reviewer for pointing out the communication of the control performance improvements.
+Based on the answers to the comments related to relative improvements, we updated the Conclusion section:
+
+		\begin{quote}
+			To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+		\end{quote}
 	}

### 2024-04-19 paper/JoPC/response_letter_2nd_round.tex
new way of relative improvement evaluation

@@
 \newcommand{\change}[1]{\textcolor{red}{#1}}
+\newcommand{\textblue}[1]{\textcolor{blue}{#1}}
 
@@
 		The values highlighted in \textbf{bold} represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
-It can be seen, that the values are the best in 5 out of 12 performance criteria.
-On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions.
+It can be seen, that the values are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
+On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
 
@@
 					& 100 & 867 & 16.7 & 12.5 \\ 
-					& 500 & \textbf{583} & 17.6 & \textbf{7.5} \\
-					& self-tuned & 678 & 15.2 & 9.5  \\ 
+					& 500 & \textblue{\textbf{583}} & 17.6 & \textblue{\textbf{7.5}} \\
+					& self-tuned & \change{\textbf{678}} & \change{\textbf{15.2}} & \change{\textbf{9.5}}  \\ 
 					\hline
@@
 					& 100 & 606 & 23.3 & 26.5  \\ 
-					& 500 & \textbf{168} & \textbf{18.2} & 6.5 \\
-					& self-tuned & 248 & 19.1 & 9.5  \\ 
+					& 500 & \textblue{\textbf{168}} & \textblue{\textbf{18.2}} & 6.5 \\
+					& self-tuned & \change{\textbf{248}} & \change{\textbf{19.1}} & 9.5  \\ 
 					\hline
@@
 					& 100 & 398 & 79.6 & 31  \\ 
-					& 500 & \textbf{211} & 22.3 & 8 \\
-					& self-tuned & 186 & 24.6 & 6.5  \\ 
+					& 500 & \textblue{\textbf{211}} & 22.3 & 8 \\
+					& self-tuned & \change{\textbf{186}} & 24.6 & \change{\textbf{6.5}}  \\ 
 					\hline
@@
 					& 500 & 1064 & 25.6 & 67 \\
-					& self-tuned & 967 & 16.5 & 18.5  
+					& self-tuned & \change{\textbf{967}} & \change{\textbf{16.5}} & \change{\textbf{18.5}} 
 				\end{tabular}
@@
 
-		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that it provides the relative improvements subject to each boundary controller individually, see Table~\ref{tab:improvement500}.
+		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that every optimal MPC is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
+In such way, the base subject to which the relative improvements are calculated, remains the same.
 Note, for the purposes of this response letter, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
 
-		Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not properly map the overall improvement.
+		%Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not properly map the overall improvement.
 For example, let us compare the 79\% improvement in the settling time subject to the MPC setup $Q_\mathrm{y} = 100$ during the third and fourth reference tracking.
@@
 Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.
-The Table~\ref{tab:average_improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was (not very significantly) worse, the rest of the criteria improved in average (the maximal overshoor improved by 11\% and the settling time improved by 102\%).
+The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\% worse, the rest of the criteria improved in average (the maximal overshoor improved by 14\% and the settling time improved by 58\%).
 Therefore, considering the tunable technique is beneficial.
@@
 				\begin{tabular}{c|c|c|c|c} 
-					Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+					& Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 					\hline
-					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
-					& 100 & 22 &  9 & 24 \\ 
-					& 500 & $-16$ & 13 & $-27$ \\
+					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  121 & 74 \\
+					& 100 & 28 &  10 & 32 \\ 
+					& 500 & $-14$ & 16 & $-21$ \\
 					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
-					& 100 & 59 &  18 & 64 \\ 
-					& 500 & $-48$ & $-5$ & $-46$ \\
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
+					& 100 & 144 &  22 & 179 \\ 
+					& 500 & $-32$ & $-5$ & $-32$ \\
 					\hline
-					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
-					& 100 & 53 & 69 & 79 \\
-					& 500 & 12 & $-10$ & 19 \\
+					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
+					& 100 & 114 & 224 & 377 \\
+					& 500 & 13 & $-9$ & 23 \\
 					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
-					& 100 & 31 &  61 & 79 \\
-					& 500 & 9 & 36 & 72 
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
+					& 100 & 45 &  154 & 386 \\
+					& 500 & 10 & 55 & 262 \\
+					\hline					
+					\multirow{3}{*}{Average} &  1000 & 23 & 64 & 12 \\
+					& 100 & 83 &  102 & 244 \\
+					& 500 & $-6$ & 14 & 58 
 				\end{tabular}
@@
 
-		\begin{table}[h!]
-			\begin{center}
-				\caption{Average control performance criteria.}
-				\label{tab:average_improvement500}
-				\begin{tabular}{c|c|c|c|c|c|c} 
-					$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
-					\hline
-					1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
-					100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
-					500 & 506.5 & $-3$ & 20.9 & 11 & 22.5 & 102 \\
-					self-tuned & 519.8 & - & 18.9 & - & 11 & - 			
-				\end{tabular}
-			\end{center}
-		\end{table}
+%		\begin{table}[h!]
+%			\begin{center}
+%				\caption{Average control performance criteria.}
+%				\label{tab:average_improvement500}
+%				\begin{tabular}{c|c|c|c|c|c|c} 
+%					$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
+%					\hline
+%					1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
+%					100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
+%					500 & 506.5 & $-3$ & 20.9 & 11 & 22.5 & 102 \\
+%					self-tuned & 519.8 & - & 18.9 & - & 11 & - 			
+%				\end{tabular}
+%			\end{center}
+%		\end{table}
 
@@
 		\begin{quote}
+
+		As can be seen in Table~\ref{tab:control_performance}, the real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value. 	
+		\change{The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller is summarized in Table~\ref{tab:improvement} for each reference step change separately.
+The values were computed as the difference between two criteria values corresponding to the optimal and self-tunable MPC, referred to the self-tunable MPC.
+The negative numbers represent deterioration of the specific performance criterion in the corresponding reference tracking.}
 
@@
 					\hline
-						\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
-						& 100 & 22 &  9 & 24 \\  
+					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  121 & 74 \\
+					& 100 & 28 &  10 & 32 \\ 
 					\hline
-						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
-						& 100 & 59 &  18 & 64 \\ 
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
+					& 100 & 144 &  22 & 179 \\
 					\hline
-						\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
-						& 100 & 53 & 69 & 79 \\
+					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
+					& 100 & 114 & 224 & 377 \\
 					\hline
-						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
-						& 100 & 31 &  61 & 79 
+					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
+					& 100 & 45 &  154 & 386 \\
+					\hline
+					\multirow{3}{*}{Average} &  1000 & 23 & 64 & 12 \\
+					& 100 & 83 &  102 & 244
 				\end{tabular}
@@
 
-		\begin{table}[h!]
-		\begin{center}
-			\caption{Average control performance criteria.}
-			\label{tab:average_improvement}
-			\begin{tabular}{c|c|c|c|c|c|c} 
-				$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
-				\hline
-				1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
-				100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
-				self-tuned & 519.8 & - & 18.9 & - & 11 & - 		
-			\end{tabular}
-		\end{center}
-	\end{table}
+	Compared to the considered non-self-tunable controllers, the control trajectories and the evaluated quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behavior.
+Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
+	\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
 
-		\end{quote}
-
+% Relative improvement - subject to the specific investigated controller (old method)			
 %			\begin{table}[h!]
 %				\begin{center}
-%			\caption{Average relative improvement of the control performance using the self-tunable explicit MPC controller.}
-%			\label{tab:improvement4}
-%			\begin{tabular}{c|c|c|c} 
-%				Comparison subject to the $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+%					\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
+%					\label{tab:improvement}
+%					\begin{tabular}{c|c|c|c|c} 
+%						Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 %						\hline
-%				1000 & 13 &  57 & 15 \\
-%				100 & 57 &  114 & 264 \\ 
-%				500 & $-3$ & 11 & 102 			
+%						\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
+%						& 100 & 22 &  9 & 24 \\  
+%						\hline
+%						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
+%						& 100 & 59 &  18 & 64 \\ 
+%						\hline
+%						\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
+%						& 100 & 53 & 69 & 79 \\
+%						\hline
+%						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
+%						& 100 & 31 &  61 & 79 
 %					\end{tabular}
@@
 %			\end{table}
+
+% Average - subject to the specific investigated controller	(old method)
+%		\begin{table}[h!]
+%		\begin{center}
+%			\caption{Average control performance criteria.}
+%			\label{tab:average_improvement}
+%			\begin{tabular}{c|c|c|c|c|c|c} 
+%				$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
+%				\hline
+%				1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
+%				100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
+%				self-tuned & 519.8 & - & 18.9 & - & 11 & - 		
+%			\end{tabular}
+%		\end{center}
+%	\end{table}
+
+		\end{quote}
 
@@
 The consumed energy corresponds to the control involving the proportional controller, which sets the electric power.
-Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.	To conclude, we decided not to include such a criterion as well.
+Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.
+To conclude, we decided not to include such a criterion as well.
 
@@
 			To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
-The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller.
+\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
 		\end{quote}

### 2024-04-20 paper/JoPC/response_letter_2nd_round.tex
Paper: Review: Response Letter 2: reviewed

@@
 
-	We thank the Reviewers for all comments and suggestions.
-	The document was revised according to these comments and we provide point-to-point answers below.
-	All changes relative to our initial submission are highlighted in \change{red}.
+	We thank the Reviewers for revisiting our manuscript and for all comments and suggestions.
+	The document was modified according to these comments and we provide point-to-point answers below.
+	All changes relative to our previous submission are highlighted in \change{red}.
 
 	\section*{Answer to Editor}
-	The authors would like to thank the Editor for collecting the review comments. We revised the paper based on the Reviewers' comments, and incorporated the suggestions
+	The authors would like to thank the Editor for collecting the 2nd round of review comments. We revised the paper based on the Reviewer's comments, and incorporated the suggestions
 	into our manuscript.
@@
 	\answer{
-		We revisited Table~\ref{tab:control_performance} to evaluate the control performance criteria.
-		The values highlighted in \textbf{bold} represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
-It can be seen, that the values are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
-On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
+		\textcolor{blue}{ We apologize for providing answers that were considered not sufficient. We have carefully revisited our recent manuscript to appropriately address all the Reviewer's comments. }
 
-		When excluding the boundary controllers and comparing only the self-tunable controller with the setup $Q_\mathrm{y} = 500$, the moderate controller outperforms the self-tunable MPC in half of the performance criteria.
+		\textcolor{blue}{First,} we revisited Table~\ref{tab:control_performance} to evaluate the \textcolor{blue}{required} control performance criteria \textcolor{blue}{for the trade-off MPC controller setup $Q_\mathrm{y} = 500$}.
+		The values highlighted in \textbf{bold} represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, \textcolor{blue}{but} excluding the \textcolor{blue}{comparison subject to the} self-tunable MPC \textcolor{blue}{controller}.
+
+		\textcolor{blue}{We recall that Table~\ref{tab:control_performance} summarizes 3 control performance criteria evaluated for 4 operating conditions represented by reference step change.
+Hence, Table~\ref{tab:control_performance} investigates 12 control cases in total.}
+		It can be seen, that the values \textcolor{blue}{ensured for the setup $Q_\mathrm{y} = 500$} are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
+On the contrary, the self-tuned controller \textcolor{blue}{ensured (acquired)} 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
+
+		When excluding the boundary controllers and comparing only the self-tunable controller with the setup $Q_\mathrm{y} = 500$, \textcolor{blue}{this trade-off (the moderate)} controller outperforms the self-tunable MPC in half of the performance criteria.
 It happens mostly in tracking the reference value upwards.
-Nevertheless, when the reference changes downwards, the self-tuned controller becomes beneficial.
-Therefore, it supports choosing the tunable control technique.
-To support our statement, the average control performance for all controllers was also elaborated.
-As the average control performance was the topic of the Reviewer's second comment, it can be found in the answer to the following comment.
+Nevertheless, when the reference changes downwards, the self-tuned controller becomes \textcolor{blue}{significantly} beneficial.
+Therefore, it supports \textcolor{blue}{implementing (choosing)} the tunable control technique.
+To support our statement \textcolor{blue}{by providing the required data}, the average control performance for all controllers was also elaborated.
+As the average control performance was the \textcolor{blue}{main} topic of the Reviewer's \textcolor{blue}{(second) comment No.2, these data are analyzed in detail (it can be found) in the answer to the following comment}.
 
@@
 
-		To ensure a good readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-We prefer to emphasize the consideration of the self-tuning method based on the revised comment from the first round of review:
+		To ensure a \textcolor{blue}{consistent flow and not to disturb the (good)} readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+We prefer to emphasize the consideration of the self-tuning method based on the \textcolor{blue}{carefully} revised comment from the first round of review:
 
@@
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
+In \textcolor{blue}{each (every)} control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is \textcolor{blue}{significantly} improved by introducing the benefits of the \textcolor{blue}{easy-to-implement} self-tuning method based on the two \textcolor{blue}{well-tuned} boundary MPC controllers.
 		\end{quote}
@@
 	\answer{
-		We would like to thank the Reviewer for the comment on the relative improvements.
-If the values in Table~2 were averaged, it is true that the average settling time would be worse, and the average relative improvement of the overshoot would be very low.
-However, considering the average of these values would be ``unfair'' because of the way how the relative improvements were calculated.
+		We would like to thank the Reviewer for the comment on the \textcolor{blue}{missing evaluation of the} relative improvements.
+If the values in \textcolor{blue}{original} Table~2 were averaged, it is true that \textcolor{blue}{such} the average settling time would \textcolor{blue}{lead to the misleading impression of the significantly decreased performance as (be worse and)} the average relative improvement of the overshoot would be very low.
+However, considering the average of these values would be unfair because of the way how the relative improvements were \textcolor{blue}{originally} calculated.
+		\textcolor{blue}{To prevent such a missleading of our reader, we have completely re-evaluated the relative improvements data in Table~2.}
 
-		The values in Table~2 are computed subject to the second best setup for each reference step change individually.
-The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
+		\textcolor{blue}{First, we point out that originally} the values in Table~2 \textcolor{blue}{were (are)} computed subject to the \textcolor{blue}{reference boundary controller with the best performance, i.e., subject to the} second best \textcolor{blue}{performance (setup)} for each reference step change individually.
+\textcolor{blue}{Obviously,} the negative numbers \textcolor{blue}{of the relative improvement} represent deterioration compared to the best controller setup in the corresponding reference tracking.
 It means, that the base subject to which is every value calculated, changes.
-Therefore, averaging the values of the relative improvements would not be fair, as it would not reflect improvement subject to one controller with a constant setup.
+Therefore, averaging the values of the relative improvements would not be fair, as \textcolor{blue}{the relative improvements do not share the same base to calculate the values in percent.
+As the consequence of considering an inconsistent base, average values (it)} would not reflect improvement subject to one controller with a constant setup.
 
-		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that every optimal MPC is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
+		To avoid \textcolor{blue}{such} the unfair evaluation of the relative improvement, we extended Table~\ref{tab:improvement500} such that every \textcolor{blue}{value of relative improvement (optimal MPC)} is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
 In such way, the base subject to which the relative improvements are calculated, remains the same.
-Note, for the purposes of this response letter, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
+Note, \textcolor{blue}{that following the Reviewer's comment No.1 (for the purposes of this response letter)}, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
 
@@
 
-		Based on this explanation of our idea of the average control performance, at this place we would like to return to the topic of the first comment—whether the moderate controller performs better in the overall metric.
+		\textcolor{blue}{Therefore,} based on \textcolor{blue}{the (this)} explanation of our idea of the \textcolor{blue}{evaluation of} average control performance, at this place we would like to return to the \textcolor{blue}{Reviewer's comment No.1 (topic of the first comment)---to analyze} whether the moderate controller performs better in the overall metric.
 Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.
-The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\% worse, the rest of the criteria improved in average (the maximal overshoor improved by 14\% and the settling time improved by 58\%).
-Therefore, considering the tunable technique is beneficial.
+The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\,\% worse, the rest of the criteria improved in average (the maximal overshoor improved by 14\,\% and the settling time improved by 58\,\%).
+\textcolor{blue}{We recall, the trade-off MPC controller does not provide satisfactory performance for the decreasing reference step change.} Therefore, considering the \textcolor{blue}{proposed} tunable technique is beneficial.
 
@@
 
-		As we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$, we prefer to include the original comparison subject to the boundary controllers as follows:
+		\textcolor{blue}{As the fine-tuning of the trade-off MPC controlled is out of the primal scope of our paper, we prefer preserving the consistent flow of the manuscript.
+Therefore, (As)} we incline not to branch the \textcolor{blue}{story line (case study also)} in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+\textcolor{blue}{Hence, our preference is to keep (, we prefer to include)} the original comparison subject to the boundary controllers as follows:
 
@@
 	\answer{
-		We thank the Reviewer for commenting on the control performance criteria related to the control input.
-Although we considered such an evaluation, we chose not to include the criteria for the following reasons.
+		We thank the Reviewer for commenting on the control performance criteria \textcolor{blue}{evaluated subject to (related to)} the control input.
 This kind of criteria usually reflects some costs or energy demands associated with the control.
+Although we considered such a \textcolor{blue}{numerical} evaluation, \textcolor{blue}{finally we decided (we chose)} not to include the criteria \textcolor{blue}{and we consider providing the control input profiles in Figure~10 satisfactory} for the following reasons.
 
-		The first kind of criterium related to the control input could be intuitively some (potentially weighted) ISI (integral-of-squared input) or, in a discrete-time manner, SSI (sum-of-squared input).
-These criteria correspond to the summing of the control input, i.e., voltage, to set the operating speed of the pump.
-The operating speed of the pump itself does not play any significant role in the costs of the control.
-Therefore, it could be converted to the amount of liquid transported to the heat exchanger during the whole control experiment.
-Nevertheless, the heating medium is dosed to the heat exchanger plant as a recycle, i.e., the same amount of heating medium is re-used during operation, which would represent fictitious performance criteria not related to the actual plant setup, see Figure 3 in the manuscript.
+		The first \textcolor{blue}{admissible} kind of criterion related to the control input could be intuitively some, potentially weighted, integral-of-squared input (ISI) or, in a discrete-time manner, sum-of-squared input (SSI).
+These criteria correspond to the summing of the control input, i.e., \textcolor{blue}{the corresponding value of the} voltage, \textcolor{blue}{necessary} to set the operating speed of the pump.
+\textcolor{blue}{But} the operating speed of the pump itself does not play any significant role in the costs of the control \textcolor{blue}{and, hence, is negligible}.
+		\textcolor{blue}{Obviously the control inputs could be interpreted by (Therefore, it could be converted to)} the amount of \textcolor{blue}{hot medium (liquid)} transported to the heat exchanger during the whole control experiment.
+Nevertheless, the heating medium is dosed to the heat exchanger plant \textcolor{blue}{in (as)} a recycle \textcolor{blue}{setup}, i.e., the same amount of heating medium is re-used during operation, see the corresponding setup scheme in Figure 3 of the manuscript.
+\textcolor{blue}{\textcolor{blue}{As such an evaluation (which)}} would represent fictitious performance criteria not related to the actual plant setup, \textcolor{blue}{we prefer not to confuse the reader by such a criterion}.
 
 		Another criterion related to the control input we considered was the energy consumed to pre-heat the heating medium in the heater.
-However, this is not directly associated with the MPC's control inputs.
-The consumed energy corresponds to the control involving the proportional controller, which sets the electric power.
+\textcolor{blue}{Although the energy consumption may sound as a relevant criterion, (However)}, this is not directly associated with the MPC's control inputs.
+The \textcolor{blue}{reason is that the} consumed energy corresponds to the control involving the \textcolor{blue}{auxiliary} proportional controller, which sets the electric power.
 Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.
-To conclude, we decided not to include such a criterion as well.
+To conclude, we \textcolor{blue}{prefer (decided)} not to include a criterion \textcolor{blue}{unrelated to the MPC controller} as well \textcolor{blue}{and keep the evaluation of the control inputs in the visual form of the profiles in Figure~10 in the manuscript}.
 
@@
 	\answer{
-		We thank the Reviewer for pointing out the communication of the control performance improvements.
-Based on the answers to the comments related to relative improvements, we updated the Conclusion section:
+		We thank the Reviewer for pointing out the \textcolor{blue}{confusing} communication of the control performance improvements.
+Based on the \textcolor{blue}{results (answers to the comments)} related to relative improvements \textcolor{blue}{reported in our answer to the Reviewer's comment No.2}, we updated the \textcolor{blue}{section Conclusion that now reads as follows (section)}:
 
@@
 The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller.
-\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
+\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\,\% and 83\,\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\,\% and 102\,\%, and the settling time $t_{\epsilon}$ reduced by 12\,\% and 244\,\%.}
 		\end{quote}
@@
 	\answer{
-		We incorporated the Reviewer's suggestion into the Abstract as follows:
+		We incorporated the Reviewer's suggestion \textcolor{blue}{to update (into)} the Abstract as follows:
 
@@
 This extension exploits different ranges of the tuning parameter assigned to specified operating conditions.
-\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems or MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems \textcolor{blue}{and straighforward to implement for (or)} MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller’s aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
@@
 
-	TODO: Potom  vymazat vysvetlivky skratiek MIMO a SISO dalej v texte.
+	TODO: Potom  vymazat vysvetlivky skratiek MIMO a SISO dalej v texte. \\
+	Podla mna netreba, lebo Abstrakt je samostatny a skratky byvaju vysvetlene znovu aj v samotnom texte.
 	}

### 2024-04-21 paper/JoPC/response_letter_2nd_round.tex
reponse letter 2 - revision

--- 2024-04-19 paper/JoPC/response_letter_2nd_round.tex
@@
 	\answer{
-		We revisited Table~\ref{tab:control_performance} to evaluate the control performance criteria.
-		The values highlighted in \textbf{bold} represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
-It can be seen, that the values are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
-On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
+		We apologize for providing answers that were considered not sufficient. We have carefully revisited our recent manuscript to appropriately address all the Reviewer's comments.
+
+		First, we revisited Table~\ref{tab:control_performance} to evaluate the required control performance criteria for the moderate MPC setup $Q_\mathrm{y} = 500$.
+		The values highlighted in blue represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
+
+		We recall that Table~\ref{tab:control_performance} summarizes 3 control performance criteria evaluated for 4 operating conditions represented by reference step change.
+Hence, Table~\ref{tab:control_performance} investigates 12 control cases in total.
+		It can be seen, that the values \textcolor{blue}{ensured for the setup $Q_\mathrm{y} = 500$} are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
+On the contrary, the self-tuned controller \textcolor{blue}{ensured (acquired)} 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
 
@@
 It happens mostly in tracking the reference value upwards.
-Nevertheless, when the reference changes downwards, the self-tuned controller becomes beneficial.
-Therefore, it supports choosing the tunable control technique.
+Nevertheless, when the reference changes downwards, the self-tuned controller becomes significantly beneficial.
+Therefore, it supports implementing the tunable control technique.
 To support our statement, the average control performance for all controllers was also elaborated.
-As the average control performance was the topic of the Reviewer's second comment, it can be found in the answer to the following comment.
+As the average control performance was the main topic of the Reviewer's \textcolor{blue}{(second) comment No.2}, these data are analyzed in detail in the answer to the following comment.
 
@@
 
-		To ensure a good readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-We prefer to emphasize the consideration of the self-tuning method based on the revised comment from the first round of review:
+		To ensure a consistent flow and not to disturb the readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+We prefer to emphasize the consideration of the self-tuning method based on the carefully revised comment from the first round of review:
 
@@
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
+In each control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is significantly improved by introducing the benefits of the self-tuning method based on the two well-tuned boundary MPC controllers.
 		\end{quote}
@@
 		We would like to thank the Reviewer for the comment on the relative improvements.
-If the values in Table~2 were averaged, it is true that the average settling time would be worse, and the average relative improvement of the overshoot would be very low.
-However, considering the average of these values would be ``unfair'' because of the way how the relative improvements were calculated.
+If the values in the original Table~2 were averaged, it is true that it would lead to the misleading impression of the decreased performance in terms of the settling time and the average relative improvement of the overshoot would be very low.
+However, considering the average of these values would be unfair because of the way how the relative improvements were originally calculated.
+		%To prevent such a missleading of our reader, we completely re-evaluated the relative improvements data in Table~2.
 
-		The values in Table~2 are computed subject to the second best setup for each reference step change individually.
-The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
+		First, we point out that the values in Table~2 were originally computed subject to the boundary controller with the best performance for each reference step change individually.
+Obviously, the negative numbers of the relative improvement represent deterioration compared to the best controller setup in the corresponding reference tracking.
 It means, that the base subject to which is every value calculated, changes.
@@
 
-		To avoid the ``unfair'' evaluation of the relative improvement, we extended Table~2 such that every optimal MPC is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
+		To avoid the unfair evaluation of the relative improvement, we extended Table~\ref{tab:improvement500} such that every performance criterion of the optimal MPC is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
 In such way, the base subject to which the relative improvements are calculated, remains the same.
-Note, for the purposes of this response letter, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
+Note, that following up on the Reviewer's comment No.1, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
 
@@
 
-		Based on this explanation of our idea of the average control performance, at this place we would like to return to the topic of the first comment—whether the moderate controller performs better in the overall metric.
+		Therefore, based on the explanation of our idea of the average control performance evaluation, at this place we would like to return to the Reviewer's comment No.1--to analyze whether the moderate controller performs better in the overall metric.
 Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.
-The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\% worse, the rest of the criteria improved in average (the maximal overshoor improved by 14\% and the settling time improved by 58\%).
-Therefore, considering the tunable technique is beneficial.
+The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\,\% worse, the rest of the criteria improved in average (the maximal overshoot improved by 14\,\% and the settling time improved by 58\,\%).
+\textcolor{blue}{We recall, the moderate MPC controller does not provide SATISFACTORY performance for the decreasing reference step change.} Therefore, considering the proposed tunable technique is beneficial.
 
@@
 
-		As we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$, we prefer to include the original comparison subject to the boundary controllers as follows:
+		As the fine-tuning of the trade-off MPC controlled is out of the primal scope of our paper, we prefer preserving the consistent flow of the manuscript.
+Therefore, we incline not to branch the story line in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
+Hence, our preference is to keep the original comparison subject to the boundary controllers as follows:
 
@@
 	\answer{
-		We thank the Reviewer for commenting on the control performance criteria related to the control input.
-Although we considered such an evaluation, we chose not to include the criteria for the following reasons.
+		We thank the Reviewer for commenting on the control performance criteria evaluated subject to the control input.
 This kind of criteria usually reflects some costs or energy demands associated with the control.
+Although we considered such a numerical evaluation, finally we decided not to include the criteria for the following reasons.
 
-		The first kind of criterium related to the control input could be intuitively some (potentially weighted) ISI (integral-of-squared input) or, in a discrete-time manner, SSI (sum-of-squared input).
-These criteria correspond to the summing of the control input, i.e., voltage, to set the operating speed of the pump.
-The operating speed of the pump itself does not play any significant role in the costs of the control.
-Therefore, it could be converted to the amount of liquid transported to the heat exchanger during the whole control experiment.
-Nevertheless, the heating medium is dosed to the heat exchanger plant as a recycle, i.e., the same amount of heating medium is re-used during operation, which would represent fictitious performance criteria not related to the actual plant setup, see Figure 3 in the manuscript.
+		The first admissible kind of criterion related to the control input could be intuitively some, potentially weighted, integral-of-squared input (ISI) or, in a discrete-time manner, sum-of-squared input (SSI).
+These criteria correspond to the summing of the control input, i.e., voltage to set the operating speed of the pump.
+However, the operating speed of the pump itself does not play any significant role in the costs of the control and, hence, is negligible.
+		Therefore, the control inputs could be converted to the amount of the heating medium transported to the heat exchanger during the whole control experiment.
+Nevertheless, the heating medium is dosed to the heat exchanger plant in a recycle setup, i.e., the same amount of heating medium is re-used during operation, see the corresponding setup scheme in Figure 3 of the manuscript.
+As such an evaluation would represent fictitious performance criteria not related to the actual plant setup, we prefer not to confuse the reader by such a criterion.
 
 		Another criterion related to the control input we considered was the energy consumed to pre-heat the heating medium in the heater.
-However, this is not directly associated with the MPC's control inputs.
-The consumed energy corresponds to the control involving the proportional controller, which sets the electric power.
+Although the energy consumption may sound as a relevant criterion, this is not directly associated with the MPC's control inputs.
+The reason is that the consumed energy corresponds to the control involving the auxiliary proportional controller, which sets the electric power.
 Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.
-To conclude, we decided not to include such a criterion as well.
-
+To conclude, we prefer not to include this criterion that is unrelated to the MPC controller and keep the evaluation of the control inputs in the visual form of the profiles in Figure~10 in the manuscript.
 	}
@@
 	\answer{
-		We thank the Reviewer for pointing out the communication of the control performance improvements.
-Based on the answers to the comments related to relative improvements, we updated the Conclusion section:
+		We thank the Reviewer for pointing out the confusing communication of the control performance improvements.
+Based on the results related to relative improvements reported in our answer to the Reviewer's comment No.2, we updated the section Conclusion which now reads as follows:
 
@@
 This extension exploits different ranges of the tuning parameter assigned to specified operating conditions.
-\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems or MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems \textcolor{blue}{and is straighforward to implement for} MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller’s aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
@@
 
-	TODO: Potom  vymazat vysvetlivky skratiek MIMO a SISO dalej v texte.
 	}

### 2024-04-21 paper/JoPC/main_3rd_round_marked.tex
reponse letter 2 - bugfix, main_3rdround.tex created

--- 2024-03-07 paper/JoPC/main_clean.tex
@@
 This extension provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+\textcolor{red}{The self-tunable technique is suitable for SISO (single-input and single-output) systems and is straighforward to implement for MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
@@
 As can be seen in Table~\ref{tab:control_performance}, the real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value. 	
-The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller computed subject to the second best setup is summarized in Table~\ref{tab:improvement} for each reference step change separately.
-The negative numbers represent deterioration compared to the best controller setup in the corresponding reference tracking.
+\textcolor{red}{The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller is summarized in Table~\ref{tab:improvement} for each reference step change separately.
+The values were computed as the difference between two criteria values corresponding to the optimal and self-tunable MPC, referred to the self-tunable MPC.
+The negative numbers represent deterioration of the specific performance criterion in the corresponding reference tracking.}
 
@@
 		\label{tab:improvement}
-		\begin{tabular}{c|c|c|c} 
-			Reference step change & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+		\begin{tabular}{c|c|c|c|c} 
+			& Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 			\hline
-			35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C &  5 &  9 & 24 \\ 
-			% \hline
-			45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C & 32 & 18 &$-90$  \\ 
-			% \hline
-			50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C & 24 &$-30$& 0 \\ 
-			% \hline
-			45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C &  6 & 11 & 18   
+			\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  121 & 74 \\
+			& 100 & 28 &  10 & 32 \\ 
+			\hline
+			\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
+			& 100 & 144 &  22 & 179 \\
+			\hline
+			\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
+			& 100 & 114 & 224 & 377 \\
+			\hline
+			\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
+			& 100 & 45 &  154 & 386 \\
+			\hline
+			\multirow{3}{*}{Average} &  1000 & 23 & 64 & 12 \\
+			& 100 & 83 &  102 & 244
 		\end{tabular}
@@
 Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
-The squared-error-based criterion (SSE) improved in every control scenario within a range $[5-32]$\,\%, the maximal overshoots/undershoots $\sigma_{\mathrm{max}}$ reduced up to 18\,\%, and the settling time $t_{\epsilon}$ decreased up to 24\,\%.
+\textcolor{red}{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
 
@@
 
-	\change{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+	\textcolor{red}{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
 Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
+In each control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is significantly improved by introducing the benefits of the self-tuning method based on the two well-tuned boundary MPC controllers.}
 
@@
 	To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
-The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller, by minimizing the sum-of-squared control error up to 32\,\%, reducing maximal overshoots/undershoots up to 18\,\%, and decreasing settling time up to 24\,\%.
+The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller.
+\textcolor{red}{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\,\% and 83\,\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\,\% and 102\,\%, and the settling time $t_{\epsilon}$ reduced by 12\,\% and 244\,\%.}
 

### 2024-04-22 paper/JoPC/response_letter_2nd_round.tex
reponse letter 2 - bugfix, main_3rdround.tex created
response letter 2 - almost final?

@@
 Hence, Table~\ref{tab:control_performance} investigates 12 control cases in total.
-		It can be seen, that the values \textcolor{blue}{ensured for the setup $Q_\mathrm{y} = 500$} are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
-On the contrary, the self-tuned controller \textcolor{blue}{ensured (acquired)} 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
+		It can be seen, that the values related to the the setup $Q_\mathrm{y} = 500$ are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
+On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
 
@@
 To support our statement, the average control performance for all controllers was also elaborated.
-As the average control performance was the main topic of the Reviewer's \textcolor{blue}{(second) comment No.2}, these data are analyzed in detail in the answer to the following comment.
+As the average control performance was the main topic of the Reviewer's comment No.2, these data are analyzed in detail in the answer to the following comment.
 
@@
 The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\,\% worse, the rest of the criteria improved in average (the maximal overshoot improved by 14\,\% and the settling time improved by 58\,\%).
-\textcolor{blue}{We recall, the moderate MPC controller does not provide SATISFACTORY performance for the decreasing reference step change.} Therefore, considering the proposed tunable technique is beneficial.
+Moreover, we recall that the moderate MPC controller is not advantageous for the decreasing reference step changes.
+Therefore, considering the proposed tunable technique is beneficial.
 
@@
 				\begin{tabular}{c|c|c|c|c} 
-					Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
+					& Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
 					\hline
@@
 This extension exploits different ranges of the tuning parameter assigned to specified operating conditions.
-\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems \textcolor{blue}{and is straighforward to implement for} MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller’s aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.

### 2024-04-22 paper/JoPC/main_3rd_round_marked.tex
response letter 2 - almost final?

@@
 This extension provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-\textcolor{red}{The self-tunable technique is suitable for SISO (single-input and single-output) systems and is straighforward to implement for MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+\textcolor{red}{The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.

### 2024-04-22 paper/JoPC/response_letter_2nd_round.tex
Paper: Review: Minor TODO
response letter 2 - almost final part 2

@@
 	\answer{
-		We apologize for providing answers that were considered not sufficient. We have carefully revisited our recent manuscript to appropriately address all the Reviewer's comments.
+		We apologize for providing answers that were considered as not sufficient. We carefully revisited our recent manuscript to appropriately address all the Reviewer's comments.
 
@@
 		To ensure a consistent flow and not to disturb the readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-We prefer to emphasize the consideration of the self-tuning method based on the carefully revised comment from the first round of review:
+We prefer to emphasize the consideration of the self-tuning method in the form of the revised comment from the first round of the review.
+The corresponding part in the manuscript reads as follows:
 
 		\begin{quote}
-			Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+			\change{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
 Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In each control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is significantly improved by introducing the benefits of the self-tuning method based on the two well-tuned boundary MPC controllers.
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
 		\end{quote}
@@
 Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.
-To conclude, we prefer not to include this criterion that is unrelated to the MPC controller and keep the evaluation of the control inputs in the visual form of the profiles in Figure~10 in the manuscript.
+To conclude, we prefer not to include this criterion that is unrelated to the MPC controller and keep the analysis of the control inputs in the visual form of the profiles in Figure~10 in the manuscript.
 	}

### 2024-04-22 paper/JoPC/main_3rd_round_marked.tex
response letter 2 - almost final part 2

@@
 When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In each control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is significantly improved by introducing the benefits of the self-tuning method based on the two well-tuned boundary MPC controllers.}
+In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
 

### 2024-04-22 paper/JoPC/main_3rd_round.tex
response letter 2 - almost final part 3

--- 2024-04-22 paper/JoPC/main_3rd_round_marked.tex
@@
 This extension provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-\textcolor{red}{The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller's aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
@@
 As can be seen in Table~\ref{tab:control_performance}, the real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value. 	
-\textcolor{red}{The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller is summarized in Table~\ref{tab:improvement} for each reference step change separately.
+The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller is summarized in Table~\ref{tab:improvement} for each reference step change separately.
 The values were computed as the difference between two criteria values corresponding to the optimal and self-tunable MPC, referred to the self-tunable MPC.
-The negative numbers represent deterioration of the specific performance criterion in the corresponding reference tracking.}
+The negative numbers represent deterioration of the specific performance criterion in the corresponding reference tracking.
 
@@
 Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
-\textcolor{red}{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
+In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.
 
@@
 
-	\textcolor{red}{Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
+	Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
 Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
@@
 In every control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.}
+Therefore, the closed-loop control performance is improved by introducing the benefits of the self-tuning method based on the two boundary MPC controllers.
 
@@
 The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller.
-\textcolor{red}{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\,\% and 83\,\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\,\% and 102\,\%, and the settling time $t_{\epsilon}$ reduced by 12\,\% and 244\,\%.}
+In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\,\% and 83\,\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\,\% and 102\,\%, and the settling time $t_{\epsilon}$ reduced by 12\,\% and 244\,\%.
 

### 2024-04-23 paper/JoPC/response_letter_2nd_round.tex
response letter 2 - final

@@
 	\answer{
-		We thank the Reviewer for pointing out the confusing communication of the control performance improvements.
+		%We thank the Reviewer for pointing out the confusing communication of the control performance improvements. 
 		Based on the results related to relative improvements reported in our answer to the Reviewer's comment No.2, we updated the section Conclusion which now reads as follows:
@@
 	\answer{
+		We thank the Reviewer for pointing out the applicability of the proposed method. 
+		If the controlled system is multivariable, not exclusively small-scale, and has a decoupled dynamics, it is generally suitable for the implementation of the self-tuning method.		
 		We incorporated the Reviewer's suggestion into the Abstract as follows:

### 2024-06-03 paper/JoPC/response_letter_3rd_round.tex
response last round

--- 2024-04-22 paper/JoPC/response_letter_2nd_round.tex
@@
 	\maketitle
-
-	We thank the Reviewers for revisiting our manuscript and for all comments and suggestions.
-	The document was modified according to these comments and we provide point-to-point answers below.
-	All changes relative to our previous submission are highlighted in \change{red}.
-
 	\section*{Answer to Editor}
-	The authors would like to thank the Editor for collecting the 2nd round of review comments. We revised the paper based on the Reviewer's comments, and incorporated the suggestions
-	into our manuscript.
+	The authors would like to thank the Editor for collecting the 3rd round of review comments.
+We revised the paper based on the Reviewer's comments, and incorporated the suggestions into our manuscript.
 
 	\section*{Answer to Reviewer 1}
-	\comment{ The authors have not addressed some of my comments in the previous submission thoroughly. I have the following follow-up comments:\\
 
-	 The control performance with Qy = 500 is not quantified, and whether the performance benefits of the proposed method reported in Table 2 still remain is not clarified.
-Since Qy =500 would give a moderately tuned controller, it can provide a better overall performance than the two boundary controllers chosen with "extreme" tuning.
+	\comment{
+		The authors have addressed the remaining comments in a good manner.
+However, the comment about the method applying to MIMO systems with decoupled dynamics is vague.
+What does the author mean?
+For instance a system with N inputs and N outputs in which input u$_i$ affects only output y$_i$?
+If so, this is not a MIMO system, just N independent SISO systems.
+		Moreover, there is no practical evidence of applicability to MIMO system, so the comment placed in the abstract is also misleading.
+		It is recommended to delete the sentence from the abstract.
 	}
@@
 	\answer{
-		We apologize for providing answers that were considered not sufficient. We have carefully revisited our recent manuscript to appropriately address all the Reviewer's comments.
-
-		First, we revisited Table~\ref{tab:control_performance} to evaluate the required control performance criteria for the moderate MPC setup $Q_\mathrm{y} = 500$.
-		The values highlighted in blue represent the scenarios when the controller with the investigated setup $Q_\mathrm{y} = 500$ performed as the best one, excluding the self-tunable MPC.
-
-		We recall that Table~\ref{tab:control_performance} summarizes 3 control performance criteria evaluated for 4 operating conditions represented by reference step change.
-Hence, Table~\ref{tab:control_performance} investigates 12 control cases in total.
-		It can be seen, that the values related to the the setup $Q_\mathrm{y} = 500$ are the best in 5 out of 12 performance criteria, see Table~\ref{tab:control_performance}, blue.
-On the contrary, the self-tuned controller acquired 10 best values out of 12 performance criteria thanks to the tuning based on the varying operating conditions, see Table~\ref{tab:control_performance}, red.
-
-		When excluding the boundary controllers and comparing only the self-tunable controller with the setup $Q_\mathrm{y} = 500$, the moderate controller outperforms the self-tunable MPC in half of the performance criteria.
-It happens mostly in tracking the reference value upwards.
-Nevertheless, when the reference changes downwards, the self-tuned controller becomes significantly beneficial.
-Therefore, it supports implementing the tunable control technique.
-To support our statement, the average control performance for all controllers was also elaborated.
-As the average control performance was the main topic of the Reviewer's comment No.2, these data are analyzed in detail in the answer to the following comment.
-
-		\begin{table}[h!]
-			\begin{center}
-				\caption{Control performance criteria.}
-				\label{tab:control_performance}
-				\begin{tabular}{c|c|c|c|c} 
-					Reference change & $Q_\mathrm{y}$ & SSE [$^{\circ}\mathrm{C}^2$\,s] & $\sigma_{\mathrm{max}}$\,[\%] & $t_{\epsilon}$\,[s]  \\
-					\hline
-					\multirow{4}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 714 & 33.5 & 16.5 \\
-					& 100 & 867 & 16.7 & 12.5 \\ 
-					& 500 & \textblue{\textbf{583}} & 17.6 & \textblue{\textbf{7.5}} \\
-					& self-tuned & \change{\textbf{678}} & \change{\textbf{15.2}} & \change{\textbf{9.5}}  \\ 
-					\hline
-					\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1\,000 & 365 & 47.2 & 5 \\
-					& 100 & 606 & 23.3 & 26.5  \\ 
-					& 500 & \textblue{\textbf{168}} & \textblue{\textbf{18.2}} & 6.5 \\
-					& self-tuned & \change{\textbf{248}} & \change{\textbf{19.1}} & 9.5  \\ 
-					\hline
-					\multirow{4}{*}{ 50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1\,000 & 245 & 18.9 & 6.5  \\
-					& 100 & 398 & 79.6 & 31  \\ 
-					& 500 & \textblue{\textbf{211}} & 22.3 & 8 \\
-					& self-tuned & \change{\textbf{186}} & 24.6 & \change{\textbf{6.5}}  \\ 
-					\hline
-					\multirow{4}{*}{ 45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } & 1\,000 & 1\,024 & 18.4 & 22.5  \\
-					& 100 & 1\,402 & 41.9 & 90  \\ 
-					& 500 & 1064 & 25.6 & 67 \\
-					& self-tuned & \change{\textbf{967}} & \change{\textbf{16.5}} & \change{\textbf{18.5}} 
-				\end{tabular}
-			\end{center}
-		\end{table}
-
-		To ensure a consistent flow and not to disturb the readability of the paper, we incline not to branch the case study also in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-We prefer to emphasize the consideration of the self-tuning method based on the carefully revised comment from the first round of review:
-
-		\begin{quote}
-			Obviously, if there exists a well-tuned ``universal'' controller that satisfies the requirements on the control performance in the whole range of the considered operating conditions, then the implementation of the self-tuning procedure is out of scope for such control application.
-Nevertheless, in numerous practical situations, using only one controller with a constant setup leads to poor or just ``satisfactory'' control results, i.e., the reference value is achieved, but with worse control performance, e.g., leading to high overshoots or settling times.
-When working on our laboratory case study, a set of different setups of penalty matrices was investigated.
-In each control scenario, the setup was beneficial only in some working conditions (tracking the reference upwards or downwards).
-Therefore, the closed-loop control performance is significantly improved by introducing the benefits of the self-tuning method based on the two well-tuned boundary MPC controllers.
-		\end{quote}
-
-	}
-
-	\comment{
-		For the metrics in Table 2, can the authors also report average values of the three metrics (relative improvements) obtained across the four set point changes considered?
-The average values would give an idea of the overall control performance.
-It seems that the overall performance for the settling time would be worse, and only little improvement in the overshoot metric?
-	}
-
-	\answer{
-		We would like to thank the Reviewer for the comment on the relative improvements.
-If the values in the original Table~2 were averaged, it is true that it would lead to the misleading impression of the decreased performance in terms of the settling time and the average relative improvement of the overshoot would be very low.
-However, considering the average of these values would be unfair because of the way how the relative improvements were originally calculated.
-		%To prevent such a missleading of our reader, we completely re-evaluated the relative improvements data in Table~2.
-
-		First, we point out that the values in Table~2 were originally computed subject to the boundary controller with the best performance for each reference step change individually.
-Obviously, the negative numbers of the relative improvement represent deterioration compared to the best controller setup in the corresponding reference tracking.
-It means, that the base subject to which is every value calculated, changes.
-Therefore, averaging the values of the relative improvements would not be fair, as it would not reflect improvement subject to one controller with a constant setup.
-
-		To avoid the unfair evaluation of the relative improvement, we extended Table~\ref{tab:improvement500} such that every performance criterion of the optimal MPC is compared subject to the self-tunable MPC, see Table~\ref{tab:improvement500}.
-In such way, the base subject to which the relative improvements are calculated, remains the same.
-Note, that following up on the Reviewer's comment No.1, we also added the evaluation of the controller with the moderate setup, i.e., $Q_\mathrm{y} = 500$ to support the statements from the answer to the previous comment.
-
-		%Regarding the average values of the relative improvements, simple average of the values for every controller across all reference changes would not properly map the overall improvement.
-For example, let us compare the 79\% improvement in the settling time subject to the MPC setup $Q_\mathrm{y} = 100$ during the third and fourth reference tracking.
-In the third reference step change, the relative improvement of 79\% corresponds to the settling time difference $31 - 6.5 = 24.5$\,s.
-In the fourth reference step change, the relative improvement of 79\% corresponds to the settling time difference $90 - 18.5 = 71.5$\,s.
-Although the values in Table~\ref{tab:improvement500} provide an extended overview of how better or worse the self-tunable controller performed in the specific operating conditions, averaging the values across the reference changes would give a somewhat distorted idea.
-Therefore, some kind of ``normalization'' would lead to a better vision of the average control performance.
-Our idea is to first average the values of the control performance criteria for every controller setup across the reference changes, and then calculate the relative improvements from the averaged values, see Table~\ref{tab:average_improvement500}.
-The symbol $\bar{(.)}$ represents an average value of the corresponding criterion.
-
-		Therefore, based on the explanation of our idea of the average control performance evaluation, at this place we would like to return to the Reviewer's comment No.1--to analyze whether the moderate controller performs better in the overall metric.
-Let us compare the average relative control improvement of the moderate MPC and the self-tunable approximated MPC.
-The Table~\ref{tab:improvement500} shows that although in average the SSE criterion corresponding to the self-tunable MPC  was 6\,\% worse, the rest of the criteria improved in average (the maximal overshoot improved by 14\,\% and the settling time improved by 58\,\%).
-Moreover, we recall that the moderate MPC controller is not advantageous for the decreasing reference step changes.
-Therefore, considering the proposed tunable technique is beneficial.
-
-		\begin{table}[h!]
-			\begin{center}
-				\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
-				\label{tab:improvement500}
-				\begin{tabular}{c|c|c|c|c} 
-					& Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
-					\hline
-					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  121 & 74 \\
-					& 100 & 28 &  10 & 32 \\ 
-					& 500 & $-14$ & 16 & $-21$ \\
-					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
-					& 100 & 144 &  22 & 179 \\ 
-					& 500 & $-32$ & $-5$ & $-32$ \\
-					\hline
-					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
-					& 100 & 114 & 224 & 377 \\
-					& 500 & 13 & $-9$ & 23 \\
-					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
-					& 100 & 45 &  154 & 386 \\
-					& 500 & 10 & 55 & 262 \\
-					\hline					
-					\multirow{3}{*}{Average} &  1000 & 23 & 64 & 12 \\
-					& 100 & 83 &  102 & 244 \\
-					& 500 & $-6$ & 14 & 58 
-				\end{tabular}
-			\end{center}
-		\end{table}
-
-%		\begin{table}[h!]
-%			\begin{center}
-%				\caption{Average control performance criteria.}
-%				\label{tab:average_improvement500}
-%				\begin{tabular}{c|c|c|c|c|c|c} 
-%					$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
-%					\hline
-%					1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
-%					100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
-%					500 & 506.5 & $-3$ & 20.9 & 11 & 22.5 & 102 \\
-%					self-tuned & 519.8 & - & 18.9 & - & 11 & - 			
-%				\end{tabular}
-%			\end{center}
-%		\end{table}
-
-		As the fine-tuning of the trade-off MPC controlled is out of the primal scope of our paper, we prefer preserving the consistent flow of the manuscript.
-Therefore, we incline not to branch the story line in the direction of the moderate setup, i.e., $Q_\mathrm{y} = 500$.
-Hence, our preference is to keep the original comparison subject to the boundary controllers as follows:
-
-		\begin{quote}
-
-		As can be seen in Table~\ref{tab:control_performance}, the real-time self-tuning of the explicit MPC controller helped to improve two to three criteria when tracking each reference value. 	
-		\change{The relative improvement in the percentage, denoted by $\delta$, of using the self-tunable controller is summarized in Table~\ref{tab:improvement} for each reference step change separately.
-The values were computed as the difference between two criteria values corresponding to the optimal and self-tunable MPC, referred to the self-tunable MPC.
-The negative numbers represent deterioration of the specific performance criterion in the corresponding reference tracking.}
-
-		\begin{table}[h!]
-			\begin{center}
-				\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
-				\label{tab:improvement}
-				\begin{tabular}{c|c|c|c|c} 
-					& Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
-					\hline
-					\multirow{3}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  121 & 74 \\
-					& 100 & 28 &  10 & 32 \\ 
-					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 47 & 147 &$-47$  \\ 
-					& 100 & 144 &  22 & 179 \\
-					\hline
-					\multirow{3}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 32 &$-23$& 0 \\ 
-					& 100 & 114 & 224 & 377 \\
-					\hline
-					\multirow{3}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 12 & 22 \\
-					& 100 & 45 &  154 & 386 \\
-					\hline
-					\multirow{3}{*}{Average} &  1000 & 23 & 64 & 12 \\
-					& 100 & 83 &  102 & 244
-				\end{tabular}
-			\end{center}
-		\end{table}
-
-	Compared to the considered non-self-tunable controllers, the control trajectories and the evaluated quality criteria confirmed the improved control performance for the reference tracking control problem of the heat exchanger with the non-linear and asymmetric behavior.
-Implementing a self-tunable explicit MPC controller leads to improved control performance in the most analyzed quality criteria, see Table~\ref{tab:improvement}.
-	\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\% and 83\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\% and 102\%, and the settling time $t_{\epsilon}$ reduced by 12\% and 244\%.}
-
-% Relative improvement - subject to the specific investigated controller (old method)			
-%			\begin{table}[h!]
-%				\begin{center}
-%					\caption{Relative improvement of the control performance using the self-tunable explicit MPC controller.}
-%					\label{tab:improvement}
-%					\begin{tabular}{c|c|c|c|c} 
-%						Reference change & Comparison with $Q_\mathrm{y}$ setup & $\delta$ SSE\,[\%] & $\delta \sigma_{\mathrm{max}}$\,[\%] & $\delta t_{\epsilon}$\,[\%]  \\
-%						\hline
-%						\multirow{2}{*}{ 35\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 5 &  55 & 42 \\
-%						& 100 & 22 &  9 & 24 \\  
-%						\hline
-%						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 50\,$^{\circ}$C } & 1000 & 32 & 59 &$-90$  \\ 
-%						& 100 & 59 &  18 & 64 \\ 
-%						\hline
-%						\multirow{2}{*}{50\,$^{\circ}$C $\rightarrow$ 45\,$^{\circ}$C } & 1000 & 24 &$-30$& 0 \\ 
-%						& 100 & 53 & 69 & 79 \\
-%						\hline
-%						\multirow{2}{*}{45\,$^{\circ}$C $\rightarrow$ 35\,$^{\circ}$C } &  1000 & 6 & 11 & 18 \\
-%						& 100 & 31 &  61 & 79 
-%					\end{tabular}
-%				\end{center}
-%			\end{table}
-
-% Average - subject to the specific investigated controller	(old method)
-%		\begin{table}[h!]
-%		\begin{center}
-%			\caption{Average control performance criteria.}
-%			\label{tab:average_improvement}
-%			\begin{tabular}{c|c|c|c|c|c|c} 
-%				$Q_\mathrm{y}$ & $\overline{\mathrm{SSE}}$ [$^{\circ}\mathrm{C}^2$\,s] & $\delta \overline{\mathrm{SSE}}$\,[\%] & $\bar{\sigma}_{\mathrm{max}}$\,[\%] & $\delta \bar{\sigma}_{\mathrm{max}}$\,[\%] & $\bar{t}_{\epsilon}$\,[s] & $\delta \bar{t}_{\epsilon}$\,[\%] \\
-%				\hline
-%				1000 & 587 & 13 &  29.5 & 57 & 15 & 15 \\
-%				100 & 818 & 57 & 40.4 & 114 & 40 & 264 \\ 
-%				self-tuned & 519.8 & - & 18.9 & - & 11 & - 		
-%			\end{tabular}
-%		\end{center}
-%	\end{table}
-
-		\end{quote}
-
-	}
-
-	\comment{
-		All the three performance metric are related to the controlled temperature variable. Why did the authors not consider any metric related to the control input?	
-	}
-
-	\answer{
-		We thank the Reviewer for commenting on the control performance criteria evaluated subject to the control input.
-This kind of criteria usually reflects some costs or energy demands associated with the control.
-Although we considered such a numerical evaluation, finally we decided not to include the criteria for the following reasons.
-
-		The first admissible kind of criterion related to the control input could be intuitively some, potentially weighted, integral-of-squared input (ISI) or, in a discrete-time manner, sum-of-squared input (SSI).
-These criteria correspond to the summing of the control input, i.e., voltage to set the operating speed of the pump.
-However, the operating speed of the pump itself does not play any significant role in the costs of the control and, hence, is negligible.
-		Therefore, the control inputs could be converted to the amount of the heating medium transported to the heat exchanger during the whole control experiment.
-Nevertheless, the heating medium is dosed to the heat exchanger plant in a recycle setup, i.e., the same amount of heating medium is re-used during operation, see the corresponding setup scheme in Figure 3 of the manuscript.
-As such an evaluation would represent fictitious performance criteria not related to the actual plant setup, we prefer not to confuse the reader by such a criterion.
-
-		Another criterion related to the control input we considered was the energy consumed to pre-heat the heating medium in the heater.
-Although the energy consumption may sound as a relevant criterion, this is not directly associated with the MPC's control inputs.
-The reason is that the consumed energy corresponds to the control involving the auxiliary proportional controller, which sets the electric power.
-Therefore, any energy minimization should be primarily addressed by fine tuning of this auxiliary controller.
-To conclude, we prefer not to include this criterion that is unrelated to the MPC controller and keep the evaluation of the control inputs in the visual form of the profiles in Figure~10 in the manuscript.
-	}
-
-	\comment{
-		In addition, the authors only summarize the best case performance improvements in the conclusions.
-This can be a bit misleading to readers since the proposed method also performs worse (significantly) in some parts of the simulations.
-So summarizing average values would be more appropriate to give a better picture of the overall performance.
-	}
-
-	\answer{
-		We thank the Reviewer for pointing out the confusing communication of the control performance improvements.
-Based on the results related to relative improvements reported in our answer to the Reviewer's comment No.2, we updated the section Conclusion which now reads as follows:
-
-		\begin{quote}
-			To properly investigate the control results, the control performance was also judged quantitatively using a set of quality criteria.
-The self-tunable control approach outperformed the conventional control strategy handling just a single controller, i.e., non-tunable controller.
-\change{In average, the control performance criteria improved compared to the upper and lower boundary MPC respectively as follows: the squared-error-based criterion (SSE) reduced by 23\,\% and 83\,\%, the maximal overshoot/undershoot $\sigma_{\mathrm{max}}$ reduced by 64\,\% and 102\,\%, and the settling time $t_{\epsilon}$ reduced by 12\,\% and 244\,\%.}
-		\end{quote}
-	}
-
-	\comment{
-		Based on the responses to my previous comments, it appears that the applicability of the proposed self-tunable explicit MPC method is limited to "small-scale multivariable systems, with decoupled dynamics"?
-If so, please mention this clearly in the abstract.
-	}
-
-	\answer{
-		We incorporated the Reviewer's suggestion into the Abstract as follows:
+		We thank the Reviewer for the comment on the applicability of the proposed method. 		
+		We removed the sentence from the Abstract based on the Reviewer's suggestion. Now the Abstract reads as follows:
 
@@
 This extension exploits different ranges of the tuning parameter assigned to specified operating conditions.
-\change{The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.} The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
+The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
 The asymmetric behavior of the plant was compensated by tuning the controller’s aggressiveness, as the negative or positive sign of reference change was considered in the tuning procedure.
@@
 
-	}
+	\newpage
 
-	\section*{Answer to Reviewer 2}
-	\comment{My comments from the previous round have been fully address. I suggest publication.}
+	Additionally, to avoid misunderstandings, we updated also the corresponding part from Section 2.3 mentioning MIMO systems, which now reads as follows:
 
-	\answer{		
-		We thank the Reviewer for reviewing our revised manuscript.		
+	\begin{quote}
+		Consider a single-input and single-output (SISO) system or a system with completely decoupled pairs of the control inputs and the system outputs. 		
+	\end{quote}
 	}

### 2024-06-03 paper/JoPC/main_final.tex
response last round

--- 2024-04-22 paper/JoPC/main_3rd_round.tex
@@
 \usepackage{amsmath}
-
-\newcommand{\change}[1]{\textcolor{black}{#1}}
 
@@
 		\begin{abstract}						
-			%%max 250 words!			
 			The tunable approximated explicit model predictive control (MPC) comes with the benefits of real-time tunability without the necessity of solving the optimization problem online.
-This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to \change{retune the controller subject to the changed working conditions.} Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
+This paper provides a novel self-tunable control policy that does not require any interventions of the control engineer during operation in order to retune the controller subject to the changed working conditions.
+Based on the current operating conditions, the autonomous tuning parameter scales the control input using linear interpolation between the boundary optimal control actions.
 The adjustment of the tuning parameter depends on the current reference value, which makes this strategy suitable for reference tracking problems.
@@
 This extension provides to exploit different ranges of the tuning parameter assigned to specified operating conditions.
-The self-tunable technique is suitable for SISO (single-input and single-output) systems and MIMO (multiple-input and multiple-output) systems with decoupled dynamics.
 The self-tunable explicit MPC was implemented on a laboratory heat exchanger with nonlinear and asymmetric behavior.
@@
 	The heat exchangers in their numerous variants are integrated into many industrial plants as the heat transfer represents the crucial phenomena for all thermal energy applications~\cite{KV18}.
-\change{Simultaneously, the utility generation for heating or cooling is energy-demanding.
-From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e., different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.}
+Simultaneously, the utility generation for heating or cooling is energy-demanding.
+From the control viewpoint, the controller design for the heat exchangers is a challenging task due to the necessity to take into account the nonlinear and asymmetric behavior of the device, i.e., different plant behavior when the temperature is increasing, in contrast to the behavior when the temperature is decreasing, see~\cite{RL20}.
 
@@
 Instead, a piece-wise affine (PWA) control law is evaluated to apply the optimal control action in each control step.
-	\change{The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
-If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for practical industrial implementation.} Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
-\change{The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions when the different setups of the controllers are beneficial.}
+	The complexity of construction of the explicit MPC controller grows exponentially with the number of considered constraints.
+If the MPC design problem can be pre-solved explicitly offline, the consequent reduced online computational complexity makes the explicit MPC more suitable for practical industrial implementation.
+Nevertheless, the explicit MPC is not tunable in default as the conventional approach in~\cite{Bemporad_automatica} considers the penalty matrices with fixed structure and values.
+The inability to tune the explicit controller online can be a disadvantage due to varying operating conditions when the different setups of the controllers are beneficial.
 
@@
 	The paper~\cite{self_tunable} pushes the idea of tunable explicit MPC further and deals with the issues of practical industrial-oriented implementation.
-\change{In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
+In numerous practical applications, the reference value of the controlled variable is changed and acquires values from a wide range of operating conditions.
 The use of different controller setups can help handle the plant's nonlinear behavior.
-The paper~\cite{self_tunable} presents a procedure of the self-tunable controller technique.} The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
-\change{In the context of MPC, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
+The paper~\cite{self_tunable} presents a procedure of the self-tunable controller technique.
+The controller's aggressivity is tuned based on the difference between the reference value and the steady state corresponding to the model linearization point.
+In the context of MPC, the aggressiveness is associated with the setup of the penalty matrices, as it determines the aggressiveness of the final control input.
 In general, higher penalization of the controlled states or control error in the cost function leads to more aggressive control actions.
@@
 On the contrary, higher penalization of the input variable leads to more sluggish control, e.g., see~\cite{Maciejowski_MPC}.
-In~\cite{self_tunable}, the MPC tuning} based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
+In~\cite{self_tunable}, the MPC tuning based on the distance from the steady-state operating point represented a way how to compensate for the system's nonlinear behavior.
 
@@
 These sets include the origin in their strict interiors.
-The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{y} \succeq 0}$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
-The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}, \change{R \succ 0}$ penalizes the squared value of control inputs.
+The penalty matrix $Q_\mathrm{y} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, Q_\mathrm{y} \succeq 0$ penalizes the squared control error, i.e., the deviation between the controlled output and output reference value $y_\mathrm{ref}$.
+The matrix $R \in \mathbb{R}^{n_{\mathrm{u}} \times n_{\mathrm{u}}}, R \succ 0$ penalizes the squared value of control inputs.
 	%
-	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, \change{Q_\mathrm{I} \succeq 0}$.
-\change{All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.}
+	The value of integrator is also penalized in the cost function with the penalty matrix $Q_\mathrm{I} \in \mathbb{R}^{n_{\mathrm{y}} \times n_{\mathrm{y}}}, Q_\mathrm{I} \succeq 0$.
+All the penalty matrices are considered to be diagonal due to the applicability of the self-tunable explicit MPC approach.
 	The parameter $\theta \in \Theta$ in Eq.~\eqref{eq:mpc_problem_initial_coindition} represents the initial condition of the optimization problem for which it is parametrically pre-computed.
@@
 These control actions result from evaluating two boundary explicit MPCs.
-The boundary explicit controllers \change{are constructed by solving the optimization problem having} the same structure and setup, except for one of the penalty matrices -- the tuned one.
-\change{Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any penalty matrix.
+The boundary explicit controllers are constructed by solving the optimization problem having the same structure and setup, except for one of the penalty matrices -- the tuned one.
+Based on the specific control application, any penalty matrix can be chosen as the tuned parameter, i.e., this approach is applicable for any penalty matrix.
 The boundary penalty matrices follow the assumptions on the penalty matrices from Section 2.1 and are diagonal matrices such that $\lambda_{i,\mathrm{L}} \le \lambda_{i,\mathrm{U}}$, $\forall i = 1,\dots,s$, where $\lambda$ denotes the vector of eigenvalues of the penalty matrix, $s$ is the rank of the tuned penalty matrix, and $L$, $U$ denote the lower and upper boundary setup, respectively.
-}
 
@@
 From the implementation point of view, it is preferred to tune just a single penalty matrix, i.e., to store only two controllers corresponding to the boundary values of the selected penalty matrix.
-To determine which penalty matrix in Eq.~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance \change{by systematic tuning of all the penalty matrices.
+To determine which penalty matrix in Eq.~\eqref{eq:tunable_matrices} should be tuned, it is suggested to judge the control performance by systematic tuning of all the penalty matrices.
 Systematic tuning involves selecting a specific penalty matrix and observing the control results by gradually increasing or decreasing the diagonal elements of the matrix.
-This process is then repeated for the remaining penalty matrices in a similar manner.}
+This process is then repeated for the remaining penalty matrices in a similar manner.
 
@@
 
-	Consider a single-input and single-output (SISO) system or a multiple-inputs and multiple-outputs (MIMO) system with completely decoupled pairs of the control inputs and the system outputs. 
+	Consider a single-input and single-output (SISO) system or a system with completely decoupled pairs of the control inputs and the system outputs. 
 	Then, the procedure of tuning the controller is based on evaluating the different operating points between the current value of the reference and the system steady-state value.
@@
 	\end{eqnarray}	
-	where \change{the symbol $\lvert.\rvert$, hereafter, denotes the element-wise absolute value}, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
+	where the symbol $\lvert.\rvert$, hereafter, denotes the element-wise absolute value, $y_{\min}$ and $y_{\max}$ are respectively lower and upper bound on the output variable in the deviation form, i.e., zero (origin) corresponds to the system steady-state value.
 Using the information about the maximal possible deviation $d_{\max}$, the tuning parameter $\rho$ can be calculated as the ratio between the current reference value and the maximal deviation:
-	\change{ 
 	\begin{eqnarray}
@@
 	\end{eqnarray}
-	}
 	Based on Eq.~\eqref{eq:rho_self_tunable}, the property $0 \le \rho \le 1$ holds, as $\vert y_{\mathrm{ref}} \vert \le d_{\max}$.
@@
 
-	\change{Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
-Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.}
+	Note that the reference value must be reachable from the operating range to ensure that $0 \le \rho \le 1 $ holds.
+Otherwise, the interpolated control action would be the ``extrapolation'' leading to the loss of guarantees on the input or state constraints satisfaction, etc.
 
@@
 	Note that the relations in Eq.~\eqref{eq:rho_self_tunable} and Eq.~\eqref{eq:rho_max} operate with the absolute value of the reference.
-\change{It is not taken into account whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether the inequality $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ holds or $\Delta_\mathrm{ref}(k) < 0$.
-As many plants have nonlinear behavior with an asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.}
+It is not taken into account whether the reference value changed upwards or downwards with respect to the system steady-state value placed in the origin, i.e., whether the inequality $\Delta_\mathrm{ref}(k) = y_\mathrm{ref}(k)-y_\mathrm{ref}(k-1) > 0$ holds or $\Delta_\mathrm{ref}(k) < 0$.
+As many plants have nonlinear behavior with an asymmetric nature (different behavior when the process variable is rising or decreasing), the positivity or negativity of the reference change could be considered in the controller self-tuning procedure to improve the control performance.
 
@@
 
-	\change{In Eq.~\eqref{eq:rho_delta_ref}, it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
+	In Eq.~\eqref{eq:rho_delta_ref}, it is suggested to increase the value of tuning parameter $\rho$ with increasing value of reference step change.
 Note, in this work, the larger value of the tuning parameter leads to adding more weight on the penalty matrices associated with the upper boundary controller, see Eq.~\eqref{eq:tunable_matrices}.
@@
 	\end{eqnarray}
-	hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.}
+	hold. This change leads to adding more weight to the lower boundary controller with the increasing value of the tuning parameter $\rho$.
 
@@
 	The plant on which the control was implemented and analyzed is a laboratory-scaled counter-current liquid-to-liquid plate heat exchanger Armfield Process Plant Trainer PCT23~\cite{pct23}, see Figure~\ref{fig:HE}.
-\change{The schematic of the plant is depicted in Figure~\ref{fig:HE_scheme}.} The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
-The heat exchange is performed between the \change{cold medium} (water) and the hot medium (water).
-\change{The cold medium as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
+The schematic of the plant is depicted in Figure~\ref{fig:HE_scheme}.
+The heat exchanger is 90\,mm wide, 103\,mm long, and 160\,mm high.
+The heat exchange is performed between the cold medium (water) and the hot medium (water).
+The cold medium as well as the heating medium are transported to the heat exchanger by two peristaltic pumps with flexible tubing from silicon rubber.
 The flow rate of the cold medium is constant, while the aim of control is to track the reference value of the outlet cold medium temperature.
-Therefore, the controlled variable is the \change{cold medium} temperature $T$ at the outlet of the heat exchanger.
-The inlet cold medium temperature was constant during the whole control, i.e., $T_\mathrm{C} = 19^{\circ}$\,C.} The temperature of the heated \change{cold medium} in the outlet stream was measured by the type K thermocouple.
+Therefore, the controlled variable is the cold medium temperature $T$ at the outlet of the heat exchanger.
+The inlet cold medium temperature was constant during the whole control, i.e., $T_\mathrm{C} = 19^{\circ}$\,C.
+The temperature of the heated cold medium in the outlet stream was measured by the type K thermocouple.
 The associated manipulated variable is the voltage $U$ corresponding to the power of the pump feeding the heat exchanger by the hot medium.
@@
 		\includegraphics[width=0.8\textwidth]{images/HE}
-		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: \change{cold medium} pump\,(1), heating medium pump\,(2), \change{cold medium} tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
+		\caption[Heat exchanger Armfield Process Plant Trainer PCT23]{Laboratory heat exchanger Armfield Process Plant Trainer PCT23: cold medium pump\,(1), heating medium pump\,(2), cold medium tanks\,(3), heater for heating medium\,(4), heat exchanger\,(5).}
 		\label{fig:HE}
@@
 where the variable $u$ represents the control inputs in the deviation form.
-The values of \change{the heated cold medium} temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35\,$^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\,\%.
+The values of the heated cold medium temperature and voltage of the heating medium pump corresponding to zero steady states are respectively $T^\mathrm{s}$~=~35\,$^{\circ}\mathrm{C}$ and $U^\mathrm{s}$~=~35\,\%.
 Therefore, the physical constraints on the manipulated variable are actually
@@
 
-\change{The penalty matrices of the problem in Eq.~\eqref{eq:mpc_problem} were systematically tuned, and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
+The penalty matrices of the problem in Eq.~\eqref{eq:mpc_problem} were systematically tuned, and the corresponding control setup was implemented on the laboratory heat exchanger for each setup of the considered explicit MPC controllers.
 First, the tuning procedure aimed to determine which penalty matrix is the most suitable for real-time tuning.
 The most relevant was the penalty matrix $Q_\mathrm{y}$ as the tuning is directly associated with a reference value, which takes place in the calculation of the tuning factor $\rho$.
-Moreover, the tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance.} Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
+Moreover, the tuning of $Q_\mathrm{y}$ preserved a satisfactory control performance.
+Next, the boundary values of the tunable matrix $Q_\mathrm{y}$ were tuned until the following limit values were determined based on the measured closed-loop control data: $Q_\mathrm{y, L}$ = 100 and $Q_\mathrm{y, U}$ = 1\,000.
 The built-in integrator was penalized with the fixed penalty matrix $Q_\mathrm{I}$ = 1 and the control input with the fixed penalty matrix $R$ = 10.
@@
 To check the correctness of the results, the measurements were performed multiple times and led to the same behavior.
-\change{Also, the inlet temperatures of the cold and heating medium were checked to exclude the effect of a disturbance.
+Also, the inlet temperatures of the cold and heating medium were checked to exclude the effect of a disturbance.
 Regarding the temperature of the cold medium, due to the limited hardware interface, it was not possible to measure the data continuously, store them, and plot the trajectory in a Figure.
-Nevertheless, the temperature of the cold medium was manually checked multiple times during the experiment and was constant.}
-
-\change{Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th}, and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
-Note that the legends correspond to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.}
-
-\change{It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
+Nevertheless, the temperature of the cold medium was manually checked multiple times during the experiment and was constant.
+
+Regarding the temperature of the heating medium, the corresponding trajectories of the temperature can be seen in Figure~\ref{fig:Th}, and the electric power, i.e., the corresponding manipulated variable, can be seen in Figure~\ref{fig:W}.
+Note that the legends correspond to the specific setup of MPC, but the temperature of the heating medium was controlled with a simple P controller with the same proportional gain in every control scenario.
+
+It can be seen that the temperature of the heating medium remains relatively constant during the whole control, except for the undershoots in the scenario with upper boundary MPC, i.e., blue trajectory.
 The undershoots can be easily associated with the trajectory of the voltage on the pump dosing the heating medium (and ultimately the heating medium flow rate).
@@
 It can be seen that although the temperature of the heating medium is constant and identical for all control scenarios (MPC setups), the value of the voltage on the pump dosing the heating medium is not the same when tracking the temperature $T_{\mathrm{ref}} = 50^{\circ}$\,C.
-Therefore, the same conditions were fulfilled for all control scenarios.}
-
-\change{The reason for this behavior} could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~\ref{fig:MV}, blue.
+Therefore, the same conditions were fulfilled for all control scenarios.
+
+The reason for this behavior could be explained by the peak of the manipulated variable associated with the upper boundary controller at time 800\,s, see Figure~\ref{fig:MV}, blue.
 After approximately 100\,s, the value of the manipulated variable dropped and settled at a value lower than the value associated with the lower boundary controller, see Figure~\ref{fig:MV}, red.
@@
 
-	\change{Note that this strategy relies on a proper design of the two boundary controllers.
+	Note that this strategy relies on a proper design of the two boundary controllers.
 	In case a non-negligible disturbance occurs, both boundary controllers
@@
 Any robust MPC design method leads to conservative control actions as some portion of the performance is sacrificed to compensate for the impact of the disturbances.
-Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.}
+Nevertheless, if it is possible to obtain the explicit (multi-parametric) solution of the robust explicit MPC offline, then the same self-tuning procedure is applicable to interpolate between the control actions from the robust controllers.
 
@@
 
-	\change{The approach of the self-tunable technique was successfully implemented on a SISO system but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ to interpolate the values of every control input.
+	The approach of the self-tunable technique was successfully implemented on a SISO system but can also be extended to multivariable systems by utilizing only a single value of the tuning parameter $\rho$ to interpolate the values of every control input.
 It is suggested in Eq.~\eqref{eq:rho_max} that the tuning parameter $\rho$ can be calculated as the maximal value of all the tuning parameters computed for every output reference.
@@
 If there are strong interactions between the system states, the self-tunable technique is challenging to design.
-In such a case, it is necessary to include expert knowledge about the system state interactions, and the resulting value of the tuning parameter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.}
+In such a case, it is necessary to include expert knowledge about the system state interactions, and the resulting value of the tuning parameter $\rho$ could be computed, e.g., as a weighted average of the individual tuning parameters.
 	\section*{Acknowledgments}
@@
 			$T$ & temperature, $^{\circ}\mathrm{C}$ \\
-			\change{$T_{\mathrm{C}}$} & \change{cold medium temperature, $^{\circ}\mathrm{C}$} \\
-			\change{$T_{\mathrm{H}}$} & \change{heating medium temperature, $^{\circ}\mathrm{C}$} \\
-			\change{$T_{\mathrm{H, ref}}$} & \change{heating medium reference temperature, $^{\circ}\mathrm{C}$} \\			
+			$T_{\mathrm{C}}$ & cold medium temperature, $^{\circ}\mathrm{C}$ \\
+			$T_{\mathrm{H}}$ & heating medium temperature, $^{\circ}\mathrm{C}$ \\
+			$T_{\mathrm{H, ref}}$ & heating medium reference temperature, $^{\circ}\mathrm{C}$ \\			
 		\end{tabular}
@@
 			$\mathcal{U}$ & set of control inputs \\
-			\change{$W$} & \change{electric power, \%} \\			
+			$W$ & electric power, \% \\			
 			$x$ & system states \\
@@
 			LTI  & linear time-invariant (system) \\
-			\change{LQR} & \change{linear-quadratic regulator} \\
-			MIMO & multiple-inputs and multiple-outputs (system) \\
+			LQR & linear-quadratic regulator \\
 			MPC  & model predictive control \\
